### 2019-03-31 paper/main.tex
paper added

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%2345678901234567890123456789012345678901234567890123456789012345678901234567890
%        1         2         3         4         5         6         7         8

\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out
                                                          % if you need a4paper
%\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4
                                                          % paper

\IEEEoverridecommandlockouts                              % This command is only
                                                          % needed if you want to
                                                          % use the \thanks command
\overrideIEEEmargins
% See the \addtolength command later in the file to balance the column lengths
% on the last page of the document

\usepackage{romannum}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\graphicspath{ {./images/} }
\usepackage{subfig}
\usepackage{listings}
\usepackage{textcomp}
\usepackage{gensymb}
\usepackage{mathtools}
\usepackage[skipbelow=\topskip,skipabove=\topskip]{mdframed}
\usepackage{multirow}
\setlength{\parskip}{0em}
\usepackage{array}
\usepackage[font=small]{caption}
\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}

% The following packages can be found on http:\\www.ctan.org
%\usepackage{graphics} % for pdf, bitmapped graphics files
%\usepackage{epsfig} % for postscript graphics files
%\usepackage{mathptmx} % assumes new font selection scheme installed
%\usepackage{times} % assumes new font selection scheme installed
%\usepackage{amsmath} % assumes amsmath package installed
%\usepackage{amssymb}  % assumes amsmath package installed

\makeatletter
\let\NAT@parse\undefined
\makeatother
\usepackage{hyperref}
% \hypersetup{citecolor=green}

\title{\LARGE \bf
Title
}

\author{Agrim Gupta, Pranav Sankhe \\ Kumar Appaiah$^{*}$ \\
Indian Institute of Technology, Bombay, India \\
$\{ \text{pranav\_sankhe}\}$@iitb.ac.in \\
akumar@ee.iitb.ac.in \hspace{1cm}
% <-this % stops a space
\thanks{$^{*}$Prof. Kumar Appaiah is a Faculty in Department of Electrical Engineering, IIT Bombay}% <-this % stops a space
}

\begin{document}
\captionsetup[figure]{labelfont={bf}, labelformat={simple}, labelsep=colon, name={Figure}}
\maketitle
\thispagestyle{empty}
\pagestyle{empty}

\begin{abstract}
 %We identify potential applications for this system which range from asset tracking, security, and human-computer interface, to robot navigation and the management of services as diverse as medical care and postal delivery.

\textit{Index Terms} - Indoor Localization; WiFi; Received Signal Strength Indicator (RSSI); Long Short-Term Memory Network (LSTM).

% We identify potential applications for this system which range from asset tracking, security, and human-computer interface, to robot navigation and the management of services as diverse as medical care and postal delivery.
\end{abstract}

\section{INTRODUCTION}

\section{LITERATURE REVIEW}

\section{APPROACH}

\subsection{System Design}

\subsection{Machine Learning Architecture}

\subsection{Results}
\section{Conclusion and Future Work}

\section{Acknowledgements}

% \begin{table}[h]
% \caption{Testing Results}
% \label{table_example}
% \begin{center}
% \begin{tabular}{|c||c|}
% \hline
% Dataset 1 & Two\\
% \hline
% Dataset 2 & Two\\
% \hline
% Dataset 3 & Four\\
% \hline
% Dataset 4 & Four\\
% \end{tabular}
% \end{center}
% \end{table}

\addtolength{\textheight}{-10cm}   % This command serves to balance the column lengths
                                  % on the last page of the document manually. It shortens
                                  % the textheight of the last page by a suitable amount.
                                  % This command does not take effect until the next page
                                  % so it should come on the page before the last. Make
                                  % sure that you do not shorten the textheight too much.

% \section*{APPENDIX}
% \subsection{User Datagram Protocol}
% User Datagram Protocol is an alternative communication protocol to Transmission Control Protocol(TCP).  Both layers are on top of Internet Protocol layer. TCP sends individual packets and is reliable whereas UDP sends messages called datagrams. TCP is more dominant protocol in today’s internet world because of its ability to break datasets into packets, check for and resend lost packets, and reassemble packets in the correct sequence. But these lead to additional data overhead and latency whereas in UDP packets can take different paths between sender and receiver resulting in some packets getting lost or received out of order. Following are some applications and features of this Protocol: 
% \begin{enumerate}
% \item Advantageous in applications that can tolerate losing of data
% \item Allows data to be dropped or received out of order making it suitable for real-time applications such as gaming, video conferences etc.
% \end{enumerate}

\newpage
\begin{thebibliography}{99}

\bibitem{c1} S. Sadowski and P. Spachos, "RSSI-Based Indoor Localization With the Internet of Things," in IEEE Access, vol. 6, pp. 30149-30161, 2018.

\end{thebibliography}

\end{document}

### 2019-04-03 chan_gen.py
Comparison with Time Pred Qt

@@ -37,7 +37,7 @@ Nr=2
 # Simulation Parameters
 number_simulations=1000
 num_chan_realisations=1
-fdts=3.5*1e-4   
+fdts=1e-5
 start_time=time.time()
 save=True
 vec_list=np.zeros((num_chan_realisations,number_simulations,num_subcarriers,Nr*(2*Nt-Nr+1)))
@@ -71,8 +71,8 @@ for chan_index in range(num_chan_realisations):
 pdb.set_trace()
 # Save Channel Generation variables for BER and sumrate evaluation by eavl.py
 if(save==True):
-    np.save("./Data/ped_1_1000_4_2.npy",vec_list)
-    np.save("./Data/qt_ped_1_1000_4_2.npy",qt_vec_list)
+    np.save("./Data/ped_1_1000_4_2_norm5.npy",vec_list)
+    np.save("./Data/qt_ped_1_1000_4_2_norm5.npy",qt_vec_list)
 
 
 

### 2019-04-03 main.py

@@ -3,7 +3,7 @@ import networkx
 from mimo_tdl_chan import *
 
 class reservoir:
-	def __init__(self,Nt=4,Nr=2,train_vals=5,num_nodes=300,p1=0.2):
+	def __init__(self,Nt=4,Nr=2,train_vals=5,num_nodes=60,p1=0.2):
 		self.Nt = Nt
 		self.Nr = Nr
 		self.vec_dim = Nr*(2*Nt-Nr+1)
@@ -15,7 +15,7 @@ class reservoir:
 		self.input_coupler = np.random.randn(num_nodes, self.input_dim)
 		self.output_coupler = np.random.randn(self.output_dim, num_nodes)
 		self.p1 = p1
-		self.A = np.array(networkx.to_numpy_matrix(networkx.erdos_renyi_graph(num_nodes, p1)))
+		self.A = np.array(networkx.to_numpy_matrix(networkx.erdos_renyi_graph(num_nodes, p1,seed=12)))
 		self.reservoir_history = np.zeros((train_vals,num_nodes))
 		self.output_history = np.zeros((train_vals,self.output_dim))
 		self.history_pointer=0
@@ -24,9 +24,18 @@ class reservoir:
 		val = np.add(np.matmul(self.A, self.reservoir_state), np.matmul(self.input_coupler, inp_vec))
 		return np.matmul(self.output_coupler, np.tanh(val))
 
-	def update_output_coupler(self):
-		self.output_coupler=np.sum(np.array([np.outer(self.output_history[j],self.reservoir_history[j])/la.norm(self.reservoir_history[j])**2\
-			for j in range(self.train_vals)]),axis=0)
+
+	def update_input_coupler(self,inp_vec,out_vec,lr=0.001):
+		diff_vec=self.get_output(inp_vec)-out_vec
+		for i in range(self.num_nodes):
+			self.input_coupler[i]=self.input_coupler[i]-2*lr*np.inner(self.output_coupler[:,i],diff_vec)*(1-self.reservoir_state[i]**2)*inp_vec
+
+	def update_output_coupler(self,beta=0,factor=2):
[…]

### 2019-04-03 mimo_tdl_chan.py

@@ -6,6 +6,7 @@ import itpp
 import numpy as np
 import scipy.linalg as la
 import pdb
+np.random.seed(1)
 
 def sH_lift(A,B,ret_vec=False):
     p=A.shape[1]
@@ -78,6 +79,7 @@ def stiefCD(A,B):
 
 
 def qtisn(pU,rU,g,num_iter,sH_list,norm_fn,sk=0.0):
+    np.random.seed(1)
     diff_frob_norm = lambda A,B:np.linalg.norm(A-B, 'fro')
     trials=0
     sp=0.0
@@ -93,6 +95,7 @@ def qtisn(pU,rU,g,num_iter,sH_list,norm_fn,sk=0.0):
         if(norm_fn=="diff_frob_norm"):
             chordal_dists=np.array([diff_frob_norm(Q[i],rU) for i in range(len(Q))])
         else:
+            # print("Yes")
             chordal_dists=np.array([stiefCD(Q[i],rU) for i in range(len(Q))])
 
         trials=trials+1
@@ -306,6 +309,42 @@ def convex_interpolation(self, S_current, S_next, num_indices_to_be_filled, last
     if(last_fill_flag):
         S_interpolate.append(S_next)
     return np.array(S_interpolate)
+
+def onlyT_pred(center,pred_list):
+    np.random.seed(1)
+    num_iter=20
+    i=0
+    Np=pred_list.shape[0]
+    while (i<num_iter):
+        tangent_list=np.array([lift(center,manifold_pt) for manifold_pt in pred_list])
+        new_tangent=np.sum(tangent_list,axis=0)/Np
+        center=retract(center,new_tangent)
+        i+=1
+    tangent_list=np.array([lift(center,manifold_pt) for manifold_pt in pred_list])
+    sum_itp=np.sum(np.array([(i+1)*tangent_list[i] for i in range(Np)]),axis=0)
+    sum_tp=np.sum(tangent_list,axis=0)
+    T_1=((-sum_itp+((1+Np)/2)*sum_tp)*12)/((Np-1)*(Np**2+Np))
+    T_0=(sum_tp-((Np-1)*Np/2)*T_1)/Np
+    pU=retract(center,T_0+Np*T_1)
+    return pU
+
+
+def lift(A,B):
+    p=A.shape[0]
+    n=A.shape[1]
+    A_mat=np.matrix(A)
[…]

### 2019-04-09 chan_gen.py
Adding BER/logsum rate code

@@ -37,7 +37,7 @@ Nr=2
 # Simulation Parameters
 number_simulations=1000
 num_chan_realisations=1
-fdts=1e-5
+fdts=1e-4
 start_time=time.time()
 save=True
 vec_list=np.zeros((num_chan_realisations,number_simulations,num_subcarriers,Nr*(2*Nt-Nr+1)))
@@ -71,8 +71,8 @@ for chan_index in range(num_chan_realisations):
 pdb.set_trace()
 # Save Channel Generation variables for BER and sumrate evaluation by eavl.py
 if(save==True):
-    np.save("./Data/ped_1_1000_4_2_norm5.npy",vec_list)
-    np.save("./Data/qt_ped_1_1000_4_2_norm5.npy",qt_vec_list)
+    np.save("./Data/ped_1_1000_4_2_norm4.npy",vec_list)
+    np.save("./Data/qt_ped_1_1000_4_2_norm4.npy",qt_vec_list)
 
 
 

### 2019-04-09 eval.py

@@ -1,0 +1,135 @@
+import numpy as np 
+from mimo_tdl_chan import *
+from sumrate_BER import leakage_analysis, calculate_BER_performance_QPSK,calculate_BER_performance_QAM256,waterfilling
+import sys
+import signal
+#SIGINT handler
+def sigint_handler(signal, frame):
+    #Do something while breaking
+    pdb.set_trace()
+    sys.exit(0)
+
+signal.signal(signal.SIGINT, sigint_handler)
+# np.random.seed(0)
+np.random.seed(1)
+U_data=np.load("./BER_calc1/ped_10_100_4_2.npy")
+qt_U_data=np.load("./BER_calc1/qt_ped_10_100_4_2.npy")
+H_data=np.load("./BER_calc1/ped_10_100_4_2_H.npy")
+sigma_data=np.load("./BER_calc1/ped_10_100_4_2_sigma.npy")
+num_chans=10
+num_evols=100
+Nt=4
+Nr=2
+
+norm_fn='stiefCD'
+# norm_fn='diff_frob_norm'
+feedback_subc=8
+num_subcarriers=64
+feedback_indices=np.arange(feedback_subc)*(num_subcarriers-1)/(feedback_subc-1)
+subcarrier_ind=0
+# Eb_N0_dB=np.arange(-6,20,3)
+Eb_N0_dB=np.arange(-3,22,2)
+#Store BER here
+resBER_QPSK=np.zeros(Eb_N0_dB.shape[0])
+otBER_QPSK=np.zeros(Eb_N0_dB.shape[0])
+unqtBER_QPSK=np.zeros(Eb_N0_dB.shape[0])
+indqtBER_QPSK=np.zeros(Eb_N0_dB.shape[0])
+count=0
+sil_BER=0
+# qtiz_U=np.load('./Intmd_Res/qtiz_U0.npy')
+# cmp_qtiz_U=np.load('./Intmd_Res/cmp_qtiz_U0.npy')
+# cmp_qtiz_err=np.load('./Intmd_Res/cmp_qtiz_err0.npy')
+# qtiz_err=np.load('./Intmd_Res/qtiz_err0.npy')
+# fin_qt_U=np.load('./Intmd_Res/fin_qt_U0.npy')
+qtiz_U=np.load('./BER_calc1/qtiz_U.npy')
+cmp_qtiz_U=np.load('./BER_calc1/cmp_qtiz_U.npy')
[…]

### 2019-04-09 main.py

@@ -1,6 +1,14 @@
 import numpy as np 
 import networkx 
 from mimo_tdl_chan import *
+import sys
+import signal
+#SIGINT handler
+def sigint_handler(signal, frame):
+    #Do something while breaking
+    pdb.set_trace()
+    sys.exit(0)
+#---------------------------------------------------------------------------
 
 class reservoir:
 	def __init__(self,Nt=4,Nr=2,train_vals=5,num_nodes=60,p1=0.2):
@@ -44,12 +52,13 @@ class reservoir:
 		self.output_history[self.history_pointer]=out_vec
 		self.history_pointer=(self.history_pointer+1)%self.train_vals
 
+signal.signal(signal.SIGINT, sigint_handler)
 # np.random.seed(0)
 np.random.seed(1)
-data=np.load("./Data/ped_1_1000_4_2.npy")
-ind_qt_data=np.load("./Data/qt_ped_1_1000_4_2.npy")
-num_chans=1
-num_evols=1000
+data=np.load("./BER_Data/ped_10_100_4_2_norm5.npy")
+ind_qt_data=np.load("./BER_Data/qt_ped_10_100_4_2_norm5.npy")
+num_chans=10
+num_evols=100
 Nt=4
 Nr=2
 past_vals=10
@@ -60,44 +69,55 @@ sHt_list=[vec_to_tangent(vec,Nt,Nr) for vec in vec_list]
 norm_fn='stiefCD'
 # norm_fn='diff_frob_norm'
 feedback_subc=8
-reservoir_objs=[reservoir(Nt,Nr,train_vals) for i in range(feedback_subc)]
-fin_qt_U=np.zeros((feedback_subc,num_evols,Nr*(2*Nt-Nr+1)))
-qtiz_U=np.zeros((feedback_subc,num_evols,Nt,Nr),dtype='complex')
-qtiz_err=np.zeros((feedback_subc,num_evols-1))
-cmp_qtiz_U=np.zeros((feedback_subc,num_evols,Nt,Nr),dtype='complex')
-cmp_qtiz_err=np.zeros((feedback_subc,num_evols-1))
-time_vals=5
-subcarrier_ind=0
+fin_qt_U=np.zeros((num_chans,num_evols,feedback_subc,Nr*(2*Nt-Nr+1)))
[…]

### 2019-04-09 mimo_tdl_chan.py

@@ -191,6 +191,34 @@ def rand_SH(n):
     return A
 
 
+def quasiGeodinterp(qtized_Us, num_subcarriers, feedback_indices):
+    recon_U=np.zeros((num_subcarriers,qtized_Us.shape[1],qtized_Us.shape[2]),dtype='complex')
+    recon_U[feedback_indices]=qtized_Us
+    separation=int((num_subcarriers-1)/(qtized_Us.shape[0]-1))
+    for i in range(qtized_Us.shape[0]-1):    
+        U_current=qtized_Us[i]
+        U_next=qtized_Us[i+1]
+        M=np.matrix(U_next)
+        S=sH_lift(U_current,M)
+        t=np.arange(1,separation)/separation
+        interpolation_fn= lambda  t:sH_retract(U_current,t*S)
+        U_interpolate=list(map(interpolation_fn, t))
+        recon_U[feedback_indices[i]+1:feedback_indices[i+1]]=U_interpolate
+    return recon_U
+
+def sigmaInterp_qtize(sigma_data,num_subcarriers,feedback_indices,sigma_cb):
+    interpS=np.zeros((num_subcarriers,sigma_data.shape[1]))
+    diff_freq=feedback_indices[1]-feedback_indices[0]
+    for i in range(feedback_indices.shape[0]-1):
+        curr_S = sigma_data[i]
+        next_S = sigma_data[i+1]
+        qcurr_S=sigma_cb[np.argmin([la.norm(curr_S-codeword) for codeword in sigma_cb])]
+        qnext_S=sigma_cb[np.argmin([la.norm(next_S-codeword) for codeword in sigma_cb])]
+        interpS[feedback_indices[i]:feedback_indices[i+1]]=[(1-(t/diff_freq))*qcurr_S+(t/diff_freq)*qnext_S\
+            for t in range(0,diff_freq)]
+    interpS[feedback_indices[feedback_indices.shape[0]-1]]=qnext_S
+    return interpS
+
 def find_precoder_list(H_list,ret_full=False):
     V_list = []
     U_list = []
@@ -275,16 +303,6 @@ def Geodesic_interpolation(self, U_current, U_next, num_indices_to_be_filled, Nr
         U_interpolate.append(U_next[:,np.arange(Nr)])
     return np.array(U_interpolate)
 
-def quasiGeodesic_interpolation(self, U_current, U_next, num_indices_to_be_filled, last_fill_flag=False):
[…]

### 2019-04-09 sumrate_BER.py

@@ -1,0 +1,264 @@
+#The python script [sumrate\_BER.py](./sumrate_BER.py) 
+#contains the codes used to obtain the BER and achievable rate
+
+from __future__ import division
+import numpy as np
+import scipy.linalg as la
+import pdb
+
+diff_frobenius_norm = lambda A,B:np.linalg.norm(A-B, 'fro')
+
+def waterfilling(alpha,P=1):
+	n=alpha.size
+	ind=np.argsort(alpha)
+	lambda1=0
+	for m in range(n):
+		t=0
+		for j in range(m,n):
+			t=t+(1/alpha[ind[j]])
+		t=(t+P)/(n-m)
+		lambda1=1/t
+		if(lambda1<alpha[ind[m]]):
+			break
+	result=[((1/lambda1)-(1/alpha[j])) if (lambda1<alpha[j]) else 0 for j in range(n)]
+	return result
+
+def leakage_analysis(H_list,U_list,interpolated_U,num_subcarriers,wf_sigma_list,wf_interp_S,Nt,Nr,ret_abs=False):
+    fig_merit=np.zeros(num_subcarriers)
+    subopt_cap=np.zeros(num_subcarriers)
+    for i in range(num_subcarriers):
+        H=np.matrix(H_list[i])
+        U=np.matrix(U_list[i][:,np.arange(Nr)])
+        U_tilde=np.matrix(interpolated_U[i])
+        opt_vec=wf_sigma_list[Nr*i:Nr*(i+1)]
+        interpopt_vec=wf_interp_S[Nr*i:Nr*(i+1)]
+        #Get Maximal Capacity
+        Q=U*np.diag(opt_vec)*U.H
+        det_mat=np.identity(Nr)+H.H*Q*H
+        max_cap=np.real(np.log(la.det(det_mat)))
+        #Get Suboptimal Capacity
+        Q_tilde=U_tilde*np.diag(interpopt_vec)*U_tilde.H
+        det_mat=np.identity(Nr)+H.H*Q_tilde*H
+        subopt_cap[i]=np.real(np.log(la.det(det_mat)))
+        #print("SubOptCap also is: "+str(subopt_cap))
+        fig_merit[i]=(subopt_cap[i]/max_cap)*100
+    #print(norm_err)
+    if(ret_abs):
+        return subopt_cap
+    else:
+        return fig_merit
+
[…]

### 2019-04-11 paper/main.tex
Adding absract

@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%2345678901234567890123456789012345678901234567890123456789012345678901234567890
-%        1         2         3         4         5         6         7         8
+%% This is a skeleton file demonstrating the use of IEEEtran.cls (requires IEEEtran.cls version 1.8a or later) with an IEEE conference paper.
+%%
+%% Modified by Khan Reaz( kahn.reaz@ieee.org)
+%% Support sites:
+%% http://www.ieee.org/
 
-\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out
-                                                          % if you need a4paper
-%\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4
-                                                          % paper
+%%***********************************************************
+%% Legal Notice:
+%% This code is offered as-is without any warranty either expressed or implied; without even the implied warranty of MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE! 
+%% User assumes all risk and can modify as s/he wants.
 
-\IEEEoverridecommandlockouts                              % This command is only
-                                                          % needed if you want to
-                                                          % use the \thanks command
-\overrideIEEEmargins
-% See the \addtolength command later in the file to balance the column lengths
-% on the last page of the document
+%%***********************************************************
 
-\usepackage{romannum}
+\def\b0{{\bf 0}}
+\def\ba{{\bf a}}
+\def\bb{{\bf b}}
+\def\bc{{\bf c}}
+\def\bd{{\bf d}}
+\def\be{{\bf e}}
+\def\bg{{\bf g}}
+\def\bh{{\bf h}}
+\def\bi{{\bf i}}
+\def\bj{{\bf j}}
+\def\bk{{\bf k}}
+\def\bl{{\bf l}}
+\def\bm{{\bf m}}
+\def\bn{{\bf n}}
+\def\bo{{\bf o}}
+\def\bp{{\bf p}}
+\def\bq{{\bf q}}
+\def\br{{\bf r}}
+\def\bs{{\bf s}}
+\def\bt{{\bf t}}
+\def\bu{{\bf u}}
+\def\bv{{\bf v}}
+\def\bw{{\bf w}}
+\def\bx{{\bf x}}
+\def\by{{\bf y}}
+\def\bz{{\bf z}}
+
+\def\bSigma{{\bf \Sigma}}
+\def\bA{{\bf A}}
+\def\bB{{\bf B}}
+\def\bC{{\bf C}}
+\def\bD{{\bf D}}
+\def\bE{{\bf E}}
+\def\bF{{\bf F}}
+\def\bG{{\bf G}}
+\def\bH{{\bf H}}
+\def\bI{{\bf I}}
+\def\bJ{{\bf J}}
+\def\bK{{\bf K}}
+\def\bL{{\bf L}}
+\def\bM{{\bf M}}
+\def\bN{{\bf N}}
+\def\bO{{\bf O}}
+\def\bP{{\bf P}}
+\def\bQ{{\bf Q}}
+\def\bR{{\bf R}}
+\def\bS{{\bf S}}
+\def\bT{{\bf T}}
+\def\bU{{\bf U}}
+\def\bV{{\bf V}}
+\def\bW{{\bf W}}
+\def\bX{{\bf X}}
+\def\bY{{\bf Y}}
+\def\bZ{{\bf Z}}
+
+%package list
+\documentclass[conference]{IEEEtran}
+\IEEEoverridecommandlockouts
+\let\labelindent\relax
+\usepackage{enumitem}
+\usepackage{fleqn}
+\usepackage{cite}
+\usepackage{graphicx}
+\usepackage[varg]{newtxmath}
+\graphicspath{ {images/} }
+\usepackage{pdfpages}	
+\usepackage{wrapfig}
+\usepackage{fancyhdr}
+\usepackage{lastpage}
+\usepackage{lettrine}
 \usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{graphicx}
-\graphicspath{ {./images/} }
-\usepackage{subfig}
-\usepackage{listings}
-\usepackage{textcomp}
-\usepackage{gensymb}
-\usepackage{mathtools}
-\usepackage[skipbelow=\topskip,skipabove=\topskip]{mdframed}
-\usepackage{multirow}
-\setlength{\parskip}{0em}
-\usepackage{array}
-\usepackage[font=small]{caption}
-\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
+\usepackage[colorinlistoftodos]{todonotes}
+\usepackage{float}
+\usepackage[font={footnotesize}]{caption}
+\usepackage[numbers,sort,square,compress]{natbib}
+\usepackage[para]{footmisc}
+% \usepackage{parskip}
+% \setlength{\parskip}{0.02\baselineskip}
 
-% The following packages can be found on http:\\www.ctan.org
-%\usepackage{graphics} % for pdf, bitmapped graphics files
-%\usepackage{epsfig} % for postscript graphics files
-%\usepackage{mathptmx} % assumes new font selection scheme installed
-%\usepackage{times} % assumes new font selection scheme installed
-%\usepackage{amsmath} % assumes amsmath package installed
-%\usepackage{amssymb}  % assumes amsmath package installed
+% \fancypagestyle{plain}{
+%   \fancyhf{} % sets both header and footer to nothing
+% \renewcommand{\headrulewidth}{0pt}
+%   \fancyhead[C]{2018 International Conference on Indoor Positioning and Indoor Navigation (IPIN), 24-27 September 2018, Nantes, France}% Right header
 
-\makeatletter
-\let\NAT@parse\undefined
-\makeatother
-\usepackage{hyperref}
-% \hypersetup{citecolor=green}
+% }
+\pagestyle{plain}% Set page style to plain.
 
-\title{\LARGE \bf
-Title
+% \pagestyle{fancyplain}
+% \fancyhf{}
+% \renewcommand{\headrulewidth}{0pt}
+% \fancyhead[C]{2018 International Conference on Indoor Positioning and Indoor Navigation (IPIN), 24-27 September 2018, Nantes, France}
+\DeclareMathOperator*{\argmin}{argmin}
+\begin{document}
+%Here goes the title
+
+\title{Predictive Quantization for MIMO-OFDM SVD Precoders using Reservoir Computing Framework}
+
+%Authors List
+
+ \author{\authorblockN{Agrim Gupta\authorrefmark{1}, Pranav Sankhe\authorrefmark{1}, Kumar Appaiah\authorrefmark{1}, Manoj Gopalkrishnan\authorrefmark{1}}
+ \
+ \authorblockA{\authorrefmark{1}Department of Electrical Engineering, Indian Institute of Technology Bombay\\
+ \{agrim,pranavs,akumar,manojg\}@ee.iitb.ac.in}
+% \thanks{Parts of this work was supported by the Bharti Centre for Communication in
+% IIT Bombay, and the Visvesvaraya
+% PhD Scheme of Ministry of Electronics \& Information Technology,
+% Government of India (implemented by the Digital India Corporation).
+% }}
 }
+\maketitle
 
-\author{Agrim Gupta, Pranav Sankhe \\ Kumar Appaiah$^{*}$ \\
-Indian Institute of Technology, Bombay, India \\
-$\{ \text{pranav\_sankhe}\}$@iitb.ac.in \\
-akumar@ee.iitb.ac.in \hspace{1cm}
-% <-this % stops a space
-\thanks{$^{*}$Prof. Kumar Appaiah is a Faculty in Department of Electrical Engineering, IIT Bombay}% <-this % stops a space
-}
+\thispagestyle{plain}
+%Main body starts
 
-\begin{document}
-\captionsetup[figure]{labelfont={bf}, labelformat={simple}, labelsep=colon, name={Figure}}
-\maketitle
-\thispagestyle{empty}
-\pagestyle{empty}
+  % \noindent We consider problem of quantization and interpolation of
+  % time and frequency varying precoding matrices in wireless MIMO
+  % systems. Knowledge of precoder matrices at the transmitter can We first establish a result comparing the performance of
+  % quantization and interpolation attempted directly over the Stiefel
+  % manifold rather than over the Unitary manifold, as has been the
+  % primary approach thus far. We propose a predictive quantization
+  % algorithm to improve upon the quantization metric by exploiting both
+  % time and frequency correlations in a constructed frequency hopping
+  % scenario. Building upon these, we finally propose a joint
+  % time-frequency interpolating algorithm to estimate the precoders
+  % which were not fed back. We demonstrate significant improvements in
+  % both BER curve and log-sum rate capacity over the existing
+  % approaches.
+\begin{abstract}
 
-\begin{abstract}
- %We identify potential applications for this system which range from asset tracking, security, and human-computer interface, to robot navigation and the management of services as diverse as medical care and postal delivery.
+  % Precoding transmissions in wireless MIMO systems is essential to
+  % enable optimal utilization of the spatial degrees of
+  % freedom. However, communicating the precoding matrices from the
+  % receiver is challenging, owing to large feedback requirements. Past
+  % work has shown that predictive quantization in time, as well as
+  % interpolation over frequency can be used to reconstruct the
+  % precoders over a wide band, although these techniques have not been
+  % used jointly. We propose both a predictive quantization as well as a
+  % joint time-frequency interpolation strategy for precoding matrices
+  % over the Stiefel manifold. The key insight that we use is that
+  % local tangent spaces in the manifold permit effective combination of
+  % both temporal and frequency domain information for more accurate
+  % precoder reconstruction. Simulations reveal that we obtain a
+  % significant improvement in achievable rate as well as BER reduction
+  % when compared to existing strategies.
 
-\textit{Index Terms} - Indoor Localization; WiFi; Received Signal Strength Indicator (RSSI); Long Short-Term Memory Network (LSTM).
+Precoding matrices obtained via SVD\footnote{Singular Value Decomposition} of the MIMO channel matrix can be utilized at the transmitter for optimum power allocation and lower BER\footnote{Bit Error Rate} transmissions.
+However, a key step enabling this improved performance is the feedback of these precoders to the transmitter from the receiver.
+Considering the limited bit budget for such CSI\footnote{Channel State Information} feedback, the precoders need to be quantized with single digit bits.
+For a $N_T \times N_R$\footnote{$N_T(R)$: Number of Transmit (Receive) Antennas} MIMO system, this amounts to quantizing a $N_T \times N_R$ complex valued matrix.
+This odious task is helped by the presence of an underlying manifold structure, and temporal/frequency correlations in the precoders. 
+In this work, we introduce a reservoir computing framework for the task of prediction of new precoders upon observation of past such precoders, by utilizing temporal correlations. 
+This is a departure from existing methods which exploit the non linear geometry endowed by the manifold structure to perform the same.
+Alternately, the non-linear relation is captured in our work via the dynamical reservoir state via the training process of the reservoir. 
+Simulations reveal reduced quantization error, which results in lower BER as well as improved achievable rate, as compared to previous work.
 
-% We identify potential applications for this system which range from asset tracking, security, and human-computer interface, to robot navigation and the management of services as diverse as medical care and postal delivery.
 \end{abstract}
 
-\section{INTRODUCTION}
+\section{Introduction}
+\label{intro}
 
-\section{LITERATURE REVIEW}
+%
 
-\section{APPROACH}
+\section{System Model}
+\label{section2}
 
-\subsection{System Design}
+\section{Reservoir model for Predictive Quantization}
+\label{section3}
 
-\subsection{Machine Learning Architecture}
+\section{Simulation Results}
+\label{section4}
 
-\subsection{Results}
-\section{Conclusion and Future Work}
+\section{Conclusions}
+\label {section5}
 
-\section{Acknowledgements}
+% \section{Acknowledgment}
+% % \label {section6}
+% % \input{sections/6_section.tex}
+% Parts of this work was supported by the Bharti Centre for Communication in
+% IIT Bombay, and the Visvesvaraya
+% PhD Scheme of Ministry of Electronics \& Information Technology,
+% Government of India, being implemented by Digital India Corporation.
 
-% \begin{table}[h]
-% \caption{Testing Results}
-% \label{table_example}
-% \begin{center}
-% \begin{tabular}{|c||c|}
-% \hline
-% Dataset 1 & Two\\
-% \hline
-% Dataset 2 & Two\\
-% \hline
-% Dataset 3 & Four\\
-% \hline
-% Dataset 4 & Four\\
-% \end{tabular}
-% \end{center}
-% \end{table}
+\renewcommand{\bibfont}{\footnotesize}
+\bibliography{IEEEabrv,main}
+\bibliographystyle{IEEEtran}
+\end{document}
 
-\addtolength{\textheight}{-10cm}   % This command serves to balance the column lengths
-                                  % on the last page of the document manually. It shortens
-                                  % the textheight of the last page by a suitable amount.
-                                  % This command does not take effect until the next page
-                                  % so it should come on the page before the last. Make
-                                  % sure that you do not shorten the textheight too much.
-
-% \section*{APPENDIX}
-% \subsection{User Datagram Protocol}
-% User Datagram Protocol is an alternative communication protocol to Transmission Control Protocol(TCP).
-Both layers are on top of Internet Protocol layer.
-TCP sends individual packets and is reliable whereas UDP sends messages called datagrams.
-TCP is more dominant protocol in today’s internet world because of its ability to break datasets into packets, check for and resend lost packets, and reassemble packets in the correct sequence.
-But these lead to additional data overhead and latency whereas in UDP packets can take different paths between sender and receiver resulting in some packets getting lost or received out of order.
-Following are some applications and features of this Protocol:
-% \begin{enumerate}
-% \item Advantageous in applications that can tolerate losing of data
-% \item Allows data to be dropped or received out of order making it suitable for real-time applications such as gaming, video conferences etc.
-% \end{enumerate}
-
-\newpage
-\begin{thebibliography}{99}
-
-\bibitem{c1} S. Sadowski and P. Spachos, "RSSI-Based Indoor Localization With the Internet of Things," in IEEE Access, vol. 6, pp. 30149-30161, 2018.
-
-\end{thebibliography}
-
-\end{document}
+% Remove the first para of FSM. State what r1,r2,d,\theta are in the FSM model states themselves. As a concluding statement of STAT-2 state that using the 
+% inherit geometery of the problem, we get AoA

### 2019-04-11 eval.py

@@ -12,10 +12,11 @@ def sigint_handler(signal, frame):
 signal.signal(signal.SIGINT, sigint_handler)
 # np.random.seed(0)
 np.random.seed(1)
-U_data=np.load("./BER_calc1/ped_10_100_4_2.npy")
-qt_U_data=np.load("./BER_calc1/qt_ped_10_100_4_2.npy")
-H_data=np.load("./BER_calc1/ped_10_100_4_2_H.npy")
-sigma_data=np.load("./BER_calc1/ped_10_100_4_2_sigma.npy")
+norm=1
+U_data=np.load("./BER_Data/ped_10_100_4_2.npy")
+qt_U_data=np.load("./BER_Data/qt_ped_10_100_4_2.npy")
+H_data=np.load("./BER_Data/ped_10_100_4_2_H.npy")
+sigma_data=np.load("./BER_Data/ped_10_100_4_2_sigma.npy")
 num_chans=10
 num_evols=100
 Nt=4
@@ -36,21 +37,22 @@ unqtBER_QPSK=np.zeros(Eb_N0_dB.shape[0])
 indqtBER_QPSK=np.zeros(Eb_N0_dB.shape[0])
 count=0
 sil_BER=0
+sil_cap=1
 # qtiz_U=np.load('./Intmd_Res/qtiz_U0.npy')
 # cmp_qtiz_U=np.load('./Intmd_Res/cmp_qtiz_U0.npy')
 # cmp_qtiz_err=np.load('./Intmd_Res/cmp_qtiz_err0.npy')
 # qtiz_err=np.load('./Intmd_Res/qtiz_err0.npy')
 # fin_qt_U=np.load('./Intmd_Res/fin_qt_U0.npy')
-qtiz_U=np.load('./BER_calc1/qtiz_U.npy')
-cmp_qtiz_U=np.load('./BER_calc1/cmp_qtiz_U.npy')
-cmp_qtiz_err=np.load('./BER_calc1/cmp_qtiz_err.npy')
-qtiz_err=np.load('./BER_calc1/qtiz_err.npy')
-fin_qt_U=np.load('./BER_calc1/fin_qt_U.npy')
-# sigma_cb=np.load('./Codebooks/Independent_qt/sigma_cb_2bits_10000.npy')
+qtiz_U=np.load('./BER_Data/qtiz_U.npy')
+cmp_qtiz_U=np.load('./BER_Data/cmp_qtiz_U.npy')
[…]

### 2019-04-13 paper/main.tex
Adding system model

@@
 
- \author{\authorblockN{Agrim Gupta\authorrefmark{1}, Pranav Sankhe\authorrefmark{1}, Kumar Appaiah\authorrefmark{1}, Manoj Gopalkrishnan\authorrefmark{1}}
+ \author{\authorblockN{Agrim Gupta, Pranav Sankhe, Kumar Appaiah, Manoj Gopalkrishnan}
  \
- \authorblockA{\authorrefmark{1}Department of Electrical Engineering, Indian Institute of Technology Bombay\\
+ \authorblockA{Department of Electrical Engineering, Indian Institute of Technology Bombay\\
  \{agrim,pranavs,akumar,manojg\}@ee.iitb.ac.in}
@@
 However, a key step enabling this improved performance is the feedback of these precoders to the transmitter from the receiver.
-Considering the limited bit budget for such CSI\footnote{Channel State Information} feedback, the precoders need to be quantized with single digit bits.
+Considering the limited bit budget for such CSI\footnote{Channel State Information} feedback, the precoders need to be quantized with single digit number of bits.
 For a $N_T \times N_R$\footnote{$N_T(R)$: Number of Transmit (Receive) Antennas} MIMO system, this amounts to quantizing a $N_T \times N_R$ complex valued matrix.
@@
 \label{intro}
+% Broad summary of your work, come to your problem definition. 
+In MIMO wireless systems, precoding matrices are used for matrix transformation of $N_S$-dimensional ($N_S \leq \text{min}(N_T,N_R))$ information vector onto the $N_T$-dimensional transmit vector, corresponding to the signal emanating out of the $N_T$ antennas of the transmitter.
+The optimum precoding matrix, to achieve channel capacity via optimum power allocation is obtained via the SVD of the MIMO channel matrix. \cite{love2008overview}
+The MIMO channel matrix is estimated at the receiver, and the transmitter has no a-priori knowledge of the same.
+Hence, to avail the said benefits of SVD precoders, the receiver needs to quantize and feedback the precoders it obtains from SVD of the MIMO channel matrix.
+To respect the bit budget imposed by limited feedback CSI schemes, the quantization needs to be performed only with a few single number of bits.
+Given the high dimensionality of the precoders (which form a $N_T \times N_R$ complex valued matrix, viz.
+$2\times N_T\times N_R$ real numbers), effective quantization with just a few bits pose a significant challenge.
+
+% Elaborate on each point (what people have done before) lecunnas
+This challenge has been overcome in past work via two inherent properties of the precoders. 
+Firstly, the precoders are not actually $2\times N_T\times N_R$ dimensional entities, and these actually have an underlying manifold structure which allows one to work with lower dimensions if one performs operations over the manifold directly.
+Secondly, these precoders are correlated nicely along both time and frequency. 
+Capturing temporal correlations allow for predictive quantization algorithms, which allow improvement of the quantization error with time.
+Exploiting frequency correlations allow for various interpolation algorithms, which in turn reduce the feedback overhead in a single OFDM frame, by feeding back only for certain subcarriers, and interpolating over the others.
+Although the underlying manifold structure allows one to work with effective lower dimensions, most of the naive linear algorithms to predict and interpolate don't work well here, owing to the inherent non-linear structure of the manifold.
+Hence, combining these two properties, viz.
+the underlying manifold structure and temporal-frequency correlations, require generalization of such linear algorithms to the manifold under consideration, by exploiting the differential geometry of the manifold.
+Relevant past work in this direction has been \cite{Gupt1905:Predictive,6891198,6545375,5671092,Li2016,khaled2005quantized,krishnamachari2013geometry}.
+
+% What is the way ahead
+The manifold based approaches have provided significant performance benefits, given that they work with effective lower dimensions.
+However, these approaches are difficult to implement and require some familiarity with manifold geometry for a complete grasp.
+In this paper, we propose a reservoir computing based predictive quantizer to exploit the temporal correlations effectively.
+The proposed scheme offers a cleaner solution to the predictive quantization problem, which brings about both ease of implementability, and improved performance as well, when compared to \cite{6891198}, which proposed a manifold based method of predictive quantization.
+
+% How to we do this 
+Reservoir computing is a computational framework designed for sequential data processing. 
+It's design takes inspiration from several frameworks of recurrent neural networks \cite{jaeger2004harnessing} including Liquid State Machines \cite{jalalvand2015real}. 
+A reservoir computing system maps the inputs to spatio-temporal patterns in higher dimensional dynamical reservoir state. 
+The pattern analysis over these spatio-temporal patterns is performed by an output coupler which maps the higher dimensional reservoir state back to the output dimension, generally having lower dimensionality than reservoir state.
+% A important characteristic of reservoir computing is that while training, the input weights and the weights within the reservoir are not kept fixed and the weights of the output coupler are updated.
+The major advantage of reservoir computing system is that it’s extremely easy to train in comparison to its counterparts like Deep Neural Networks. 
+The input features can be efficiently read out by a simple learning algorithm because the reservoir non-linearly transforms sequential inputs into the higher dimensional reservoir state. 
+Reservoir computing has been successfully used to solve problems like spoken digit recognition \cite{verstraeten2005isolated}, handwritten digit image recognition \cite{jalalvand2015real} and climate prediction \cite{pathak2017using}.
+% Owing to the versatility of reservoir computing, it can deal with any sequential data in principle and hence further expansion of its application fields is widely expected.
+
+Reservoir computing has also been applied to solve problems in the domain of wireless communications \cite{jaeger2004harnessing,mosleh2017brain,shafin2018realizing}. 
+\cite{jaeger2004harnessing} used reservoir computing framework to harness channel non-linearities in order for smarter channel equalization.
+\cite{mosleh2017brain,shafin2018realizing} utilized the same for OFDM symbol detection while tapping in channel, as well as power amplifier non-linearities.
+In our work, we utilize the reservoir computing framework to discover the underlying non-linear relations between previously observed precoding matrices, in order to predict the next precoder in series.
+Upon vectorizing the precoding matrices, this becomes analogous to time series prediction algorithms, which the reservoir computing framework has been known to work really well for \cite{mosleh2017brain}.
 
@@
 \label{section2}
+\noindent We consider a point-to-point MIMO-OFDM wireless system that
+has $N_T$ transmit antennas and $N_R$ receive antennas. 
+The available bandwidth is divided into $N$ subcarriers, so that individually for each subcarrier, the channel can be considered flat fading. 
+The transmitter communicates an $N_s \times 1$ information data vector, where
+$N_s \leq \text{min}(N_T,N_R)$, and the $N_T \times N_s$ precoding
+matrix maps the $N_s \times 1$ information data vector onto the $N_T \times 1$ transmit vector emanating out of the transmitter.
 
+In this discussion, we assume that $N_T > N_R$ and $N_s = N_R$. Keeping notations consistent with \cite{6891198,Gupt1905:Predictive}, the $N_R \times 1$ data stream received is denoted by:
+\begin{equation}
+\by_{i,t}=\bH^{H}_{i,t}\tilde{\bU}_{i,t}\bx_{i,t}+ \bw_{i,t}
+\end{equation}
+Here $\tilde{\bU}_{i,t} \in \mathbb{C}^{N_T \times N_R}$ denotes the precoding matrix which is a function of quantized CSI fed back by the receiver, $\by_{i,t} \in \mathbb{C}^{N_R \times 1}$ is the received data stream, $\bx_{i,t} \in \mathbb{C}^{N_R \times 1}$ denotes the transmitted signal, all at the $i$-th subcarrier of the $t$-th OFDM frame, $\bH_{i,t} \in \mathbb{C}^{N_T \times N_R}$ denotes the MIMO channel matrix and $\bw_{i,t}$ denotes the i.i.d.
+complex Gaussian noise with $\bw_{i,t} \sim \mathcal{N}_{\mathbb{C}}(0,N_0\bI_{N_R})$, $N_0$ being the noise variance.
+
+% Tell that if infinite bit budget available, transmitter can directly use matrices obtained from SVD as precoders.
+However, since this is not the case we have to quantize (N dimensional) manifold, incurring substantial quantization error.
+Independent quantization techniques (references).
+Predictive quantization techniques can be used on the top of independently initialized values to improve the error.
+This is done in a way intuitively similar to Delta PCM, in which quantization error is reduced substanitally by using a linear predictor and quantizing the difference between the predicted and observed value.
+Since these preocders lie on Stiefel manifold, linear schemes will not work, due to non linearity of the manifold.
+However,past work has generalized the ideas to the manifold by exploiting the differential geometry of the manifold.
+Once a prediction is obtained, one has to quantize only the difference between the prediction and the observed value, which allows for improved quantization error.
+As the prediction becomes closer to the original value, the quantization error also decreases.
+The quantization algorithm is illustrated in Section 3.3
+
+Provided an infinite bit budget for quantization, the transmitter can directly use the matrices obtained from SVD of $\bH^{H}_{i,t}$ as precoder $\tilde{\bU}_{i,t}$.
+In particular, if $\text{SVD}(\bH_{i,t}) = \bU_{i,t},\Sigma_{i,t}, \bV_{i,t}$, then $\tilde{\bU}_{i,t} = \bU_{i,t}$.
+Notice that matrices $\bU_{i,t}$ reside on the Stiefel manifold $\text{St}(N_T,N_R)$, since the columns of $\bU_{i,t}$ form a set of $N_R$ orthogonal vectors in $N_T$ dimensions \cite{Gupt1905:Predictive,6891198}.
+Given practical limitations, only limited feedback is available from the receiver, and the objective is to find a `reasonable' estimate of $\bU_{i,t}$, given by $\tilde{\bU}_{i,t}$ using the available feedback bits.
+
+Algorithms similar to Lloyd codebook algorithm have been studied for quantizing $\text{St}(N_T,N_R)$ \cite{6678348}.
+However, this method treats precoders close-by in time/frequency to each other as independent, since it doesn't exploit any temporal/spectral correlations for quantization. 
+Predictive quantization algorithms \cite{Gupt1905:Predictive,6891198} can be utilized to reduce the quantization error with time by tapping in available correlations.
+
+We now discuss the basic mathematical model central to predictive quantization algorithms for precoding matrices.
+Consider that we predict based on past $p$ observed precoding matrices, and hence $\tilde{\bU}_{i,t-p},\tilde{\bU}_{i,t-p+1},\ldots,\tilde{\bU}_{i,t-2},\tilde{\bU}_{i,t-1}$ have been fed back and available at the transmitter.
+Using a prediction algorithm and exploiting time correlations among precoders at $t-p,t-p+1,\ldots,t-2,t-1$ time instances, the transmitter can predict $\tilde{\bU}_{i,t}$ to be some $\bP_{i,t}=f_P(\tilde{\bU}_{i,t-p},\tilde{\bU}_{i,t-p+1},\ldots,\tilde{\bU}_{i,t-2},\tilde{\bU}_{i,t-1})$, where $f_P: \text{St}(N_T,N_R)^p \to \text{St}(N_T,N_R)$ is a prediction function.
+Now since the transmitter already knows a coarse estimate of $\tilde{\bU}_{i,t}$ given by $\bP_{i,t}$, the receiver just quantizes the local space of $\text{St}(N_T,N_R)$ nearby $\bP_{i,t}$ to enable a refined estimate of $\tilde{\bU}_{i,t}$ at the transmitter.
+That is, the transmitter utilizes a quantization function $q_P:\text{St}(N_T,N_R) \times \mathbb{N} \to \text{St}(N_T,N_R)$, to obtain $\tilde{\bU}_{i,t} \gets q_P(\bP_{i,t},\text{fb}_{i,t})$, where $\text{fb}_{i,t} \in \{1,2\ldots2^{\mathcal{B}}\}$ is the feedback from the receiver for precoder at $i$-th subcarrier and $t$-th time instant, considering bit budget of $\mathcal{B}$ bits.
+In \cite{Gupt1905:Predictive,6891198,6545375}, $\text{fb}_{i,t}$ denotes the codeword index for the codebook obtained for quantizing the local tangent space at $\bP_{i,t}$.
+
+Since using predictive quantization scheme, quantization is on a smaller subspace as compared to the entire manifold in case of independent quantization, the quantization error is substantially lower as well.
+However, that being said, independent quantization algorithms are important for initialization the predictive quantization strategies.
+Observe that, predictive quantization algorithms for SVD precoders are typically the higher dimensional analogs of the well known approaches to reduce quantization error using Linear Prediction Codes and Delta PCM.
+In both LPC and Delta PCM, quantization error is reduced substantially by using a linear predictor and quantizing the scalar difference between the predicted and observed value. 
+Analogous to this, for $\text{St}(N_T,N_R)$ quantization error is reduced by quantizing a smaller subspace around predicted value, compared to the entire manifold.
+
+In our work, we propose a reservoir computing based prediction framework, which predicts the new precoders by tapping the temporal correlations captured from past observed precoders ($f_P$). 
+We reuse the $q_P$ algorithm from \cite{Gupt1905:Predictive,6891198}, however, by incorporating the $q_P$ in the prediction framework, as discussed in subsequent sections, the $f_P$ function also exploits correlations in $q_P$ (codebook locality correlations), along with temporal correlations.
+Previous work \cite{Gupt1905:Predictive,6891198} have $f_P$ and $q_P$ independent of each other.
+The detailed discussion on reservoir computing based model for $f_P$ and $q_P$ is presented in Section \ref{section3}. 
+The proposed reservoir computing scheme is evaluated against the temporal predictive quantization scheme in \cite{6891198}, and the simulation results are discussed in Section \ref{section4}.
+Finally, Section \ref{section5} concludes and presents future lines of work.
+
+%Explain prediction and quantization steps here itself ! (succintly)
 \section{Reservoir model for Predictive Quantization}
 \label{section3}
-
+\subsection{Vectorizing matrices in Stiefel Manifold}
+%Focus on the fact that you don't actually pay a penalty
+%The thing to quantize remains on the Stiefel Manifold
+\subsection{Prediction and Quantization}
+%Reservoir Pic
 \section{Simulation Results}
 \label{section4}
-
-\section{Conclusions}
-\label {section5}
+%Qtisn error with 1000 chan evols
+%Qtisn error with 100 chan evols
+%BER
+%Achievable rate
+\section{Conclusions and Future Work}
+\label{section5}
 

### 2019-04-13 paper/main.tex
Adding section 3 half

@@
 \subsection{Vectorizing matrices in Stiefel Manifold}
+The reservoir computing framework has inputs/outputs as vectors, and hence it is necessary to convert the precoder matrices to vectors. 
+A precoding matrix $\mathcal{\bM} \in \text{St}(N_T,N_R)$ is a $N_T\times N_R$ matrix with the property $\mathcal{\bM}^H\mathcal{\bM}=\mathbb{I}_{N_R}$. 
+For brevity sake, let us say that such a matrix $\mathcal{\bM}$ is a \'semi-unitary\' matrix.
+A naive method of vectorizing a $N_T\times N_R$ semi-unitary matrix would be to take all it's $N_TN_R$ complex numbers individually and stack them onto a $2N_TN_R$ dimensional vector.
+However, we can do this a little more efficiently, considering the $\mathcal{\bM}^H\mathcal{\bM}=\mathbb{I}_{N_R}$ property, which implies that each vector representing the columns of $\mathcal{\bM}$ is orthogonal to other columns.
+For the first column, we take the $N_T$ complex numbers and stack them onto a $2N_T$ vector. 
+For the second column, we take only the first $N_T-1$ complex numbers, since the last number can be determined by utilizing orthogonality with the first vector. 
+For the third column, we take only the first $N_T-2$ complex numbers, and so on. 
+Hence, we can vectorize the $N_T\times N_R$ $\mathcal{\bM}$ into a $2(N_T)+2(N_T-1)+\ldots+2(N_T-N_R+1)= 2N_TN_R-(N_R^2-N_R)$ dimensional vector. 
+For any semi-unitary matrix $\mathcal{\bM}$, denote by $\mathcal{\bm}$ the vectorized representation.
+
+Observe here that we do pay a dimensional penalty upon vectorizing the semi-unitary $\mathcal{\bM}$. 
+$\mathcal{\bM} \in \text{St}(N_T,N_R)$, which is a $2N_TN_R-N_R^2$ dimensional manifold. 
+We vectorize $\mathcal{\bM}$ to a $2N_TN_R-N_R^2+N_R$ dimensional vector, an overhead of $N_R$ dimensions, since we didn't exploit the fact that each column vector is a norm 1 vector as well.
+It looks as if we could just take $N_T-1$ complex numbers when vectorizing the first column, instead of $N_T$, but this would lead to a non-unique representation, since there could then be infinite possibilities of the missing one complex number, such that the vector has a norm 1.
 %Focus on the fact that you don't actually pay a penalty
@@
 \subsection{Prediction and Quantization}
-%Reservoir Pic
+The vector representation of semi-unitary matrices allow us to proceed with the discussion on reservoir computing framework for predictive quantization of SVD precoders.
+Consider the reservoir computing framework as in Fig.
+%Ref Fig.
+Reservoir Pic
+
+The input to the reservoir $i$ corresponding to subcarrier $i$, is $\tilde{\bu}_{i,t-1}$, which is the vectorized representation of $\tilde{\bU}_{i,t-1}$. 
+Let $D_{\text{in}}=2N_TN_R-N_R^2+N_R$ be the dimension of the input vector to the dimension.
+Using a randomly initialized $D_{\text{in}}\times D_{\text{resv}}$ input coupler matrix $\bW^{\text{in}}_i$, the $D_{\text{in}}$ dimensional input is mapped to a $D_{\text{resv}}$ dimensional vector, where $D_{\text{resv}}$ is the dimension of the reservoir state vector $\br_{i,t}$.
+The reservoir state vector $\br_{i,t}$ is initialized with $D_{\text{resv}}$ zeros, and is updated via the following equation,
+\begin{equation}
+\br_{i,t}=\text{tanh}(\bA_i\br_{i,t-1}+\bW^{\text{in}}_i\tilde{\bu}_{i,t-1})
+\label{res_upd}
+\end{equation}
+where $\bA_i$ is the adjacency matrix which captures the reservoir dynamics and correlates reservoir state across time, and tanh is applied element wise. 
+Typical choices for $\bA_i$ have been erdos-renyi graphs with an upper bounded maximum eigen value \cite{mosleh2017brain,pathak2017using}.
+
+The output of the reservoir is $\bp_{i,t}$, a vectorized representation of $\bP_{i,t}$. 
+Hence, the output of the reservoir is also a $D_{\text{in}}$ dimensional vector ($D_{\text{out}}=D_{\text{in}}$). 
+The output $\bp_{i,t}$ is obtained via matrix transformation of the reservoir state $\br_{i,t}$ via the $D_{\text{resv}}\times D_{\text{out}}$ output coupler matrix $\bW^{\text{out}}_i$, viz.
+\begin{equation}
+\bp_{i,t}=\bW^{\text{out}}_i\br_{i,t}
+\label{pred_op}
+\end{equation}
+
+This completes the forward prediction algorithm to obtain $\bP_{i,t}$ using just one past observed $\bU_{i,t-1}$. That is,
+\begin{equation}
+\bP_{i,t}=f_P(\tilde{\bU}_{i,t-1})=\bW^{\text{out}}_i\text{tanh}(\bA_i\br_{i,t-1}+\bW^{\text{in}}_i\tilde{\bu}_{i,t-1})\footnote{For Brevity sake, $\bp_{i,t}$ and $\bP_{i,t}$ are treated to be one and the same}
+\label{fwd_pred}
+\end{equation}
+
+However, a complete discussion of the prediction algorithm also involves a backward pass, involving the updation of output couplers $\bW^{\text{out}}_i$, which would follow next.
+
+Before proceeding ahead, it is critical to detail out the quantization function $q_P(\bP_{i,t},\text{fb}_{i,t})$. 
+The quantization method is similar to the one used in \cite{6891198,Gupt1905:Predictive,6545375}. 
+Central to the quantization algorithm is the fact that tangent spaces local to a point in manifold, are actually linear vector spaces.
+Given two points $\bX$ and $\bY$ in $\text{St}(N_T,NR)$, a lifting operation $\bT^Y_X=\texttt{lift}(\bX,\bY)$, $\texttt{lift}:\text{St}(N_T,NR)^2 \to \mathcal{T}_X \text{St}(N_T,NR)$ gives a tangent from X to Y, $\bT^Y_X \in \mathcal{T}_X \text{St}(N_T,NR)$, where $\mathcal{T}_X \text{St}(N_T,NR)$ is the local tangent space at $\bX$.
+A corresponding retraction operation $Y=\texttt{retract}(X,\bT^Y_X)$gives back the manifold point obtained by traversing in the tangent direction.
+In this work, the chosen lifting-retraction operations are the Cayley Exponentials, elaborated in \cite{DBLP:journals/corr/abs-1708-00045} and used in \cite{Gupt1905:Predictive}.
+The Cayley exponential lifting operation maps two points in $\text{St}(N_T,N_R)$, to a $N_T\times N_T$ skew hermitian matrix representing the tangent from first point to the other.
+
+The quantization algorithm exploits the linear vector space property of the tangent space and quantizes the local tangent space at the predicted precoder $\bP_{i,t}$.
+The codebook for the local tangent space basically corresponds to a collection of codewords representing the different directions (tangents) in the local tangent space.
+This codebook is also referred to as the base codebook for the quantization function.
+The feedback from the receiver indicates the optimum direction in the base codebook, which the transmitter can choose to get closest to the actual value $\bU_{i,t}$.
+With the optimum direction chosen, the next step is to determine how much to move in that particular direction, viz. the length of the chosen tangent direction.
+For this, we adopt the strategy in \cite{6891198}, which
+controls the magnitude of tangent steps, by having two codebooks
+$T^{\mathcal{C}}_p,T^{\mathcal{C}}_m$ of different spreads, but same
+$2^{\mathcal{B}-1}$ base vectors from the base codebook. 
+The base vectors correspond to $2^{\mathcal{B}-1}$ quantized directions, and by spread of codewords, we mean the length of base vectors considered, with $T^{\mathcal{C}}_p$ having tangents of higher length than $T^{\mathcal{C}}_m$.
+The two codebooks are concatenated to form a $2^\mathcal{B}$ length codebook $T^\mathcal{C}$. 
+The receiver finds the optimal index $c_n$ in $T^\mathcal{C}$ by comparing the chordal distance metric ($d_s$) of Stiefel Manifold \cite{Gupt1905:Predictive,6891198}, of each codeword to the actual precoder $\bU_{i,t}$ obtained from the SVD of the channel matrix, using \eqref{eqn:cn1}.
+The receiver then feeds back $c_n$ to the transmitter using $\mathcal{B}$ bits.
+The transmitter uses the fed back $c_n$ and \eqref{eqn:cn2} to calculate $\tilde{\bU}_{i,t}$,
+\begin{equation}
+\label{eqn:cn1}
+c_n \gets \text{argmin}_{i \in 2^\mathcal{B}}\left (d_s\left (\bU_{k,l},\text{retract}(\bP_{k,l},T^\mathcal{C}[i])\right ) \right)
+\end{equation}
+\begin{equation}
+\tilde{\bU}_{k,l}=\text{retract}(\bP_{k,l},T^\mathcal{C}[c_n])
+\label{eqn:cn2}
+\end{equation}
+
+% \textcolor{blue}
+{We now describe the algorithm used to control the spread of the codebooks, as discussed in \cite{6891198}. The base codebook ($\mathcal{T}^B$) consists of
+  $2^{\mathcal{B}-1}$ matrices belonging to the local tangent space at
+  $\bP_{k,l}$, which represent the $2^{\mathcal{B}-1}$ quantized directions. The two codebooks,
+  $T^{\mathcal{C}}_p,T^{\mathcal{C}}_m$, have the same set of base
+  vectors, but different spreads $g^{s_p}$ and $g^{s_m}$, where $g$ is
+  the growth factor and $s_p,s_m$ control the spread of the two
+  codebooks. Depending on whether $c_n \geq 2^{\mathcal{B}-1}$,
+  i.e. whether the optimum codeword is in $T^{\mathcal{C}}_p$ or
+  $T^{\mathcal{C}}_m$, the scale parameter $s[k]$, which in turn
+  controls values of $s_p, s_m$ is updated in the following manner,
+$$s_p=g^{\text{min}(s[k-1]+1,0)}, s_m = g^{s[k-1]-1}$$
+$$
+s[k]=
+\begin{cases}
+\text{min}(s[k-1]+1,0), \text{ for }c_n \in T^{\mathcal{C}}_p\\
+s[k-1]-1, \text{otherwise}\\
+\end{cases}
+$$
+with $s[0]=0$. Intuitively, the algorithm reduces/increases the spread
+of the codebook till the operation of reduction/increase is no longer
+beneficial, i.e. the optimum codeword lies in the higher/lower spread
+codebook instead. The scheme we use for obtaining the quantized
+directions, however, differs slightly from the one presented in
+\cite{6891198}. As discussed in Section \ref{section3}, the Cayley
+type lifting map takes inputs from the Stiefel manifold and maps them
+to $N_T \times N_T$ skew Hermitian matrices. This allows for vector
+quantization of the tangent space, since a skew Hermitian matrix can
+be easily converted to a vector, by taking the upper triangular
+entries and stacking them in a vector. Vector quantization for the
+base codebook, $\mathcal{T}^B$ allows for isotropic $2^{\mathcal{B}-1}$ quantized
+directions for the tangent space local to $\bP_{k,l}$. \cite{6891198}
+proposed a randomly initialized $\mathcal{T}^B$ which does not guarantee
+isotropic $2^{\mathcal{B}-1}$ quantized directions, which can
+potentially hurt the performance of the system in the cases when
+random initialization gives directions which are close to each
+other. More details on codebook construction are provided in Section
+\ref{section5}. This concludes the proposed predictive quantization
+algorithm.}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% More information needed about the adjacency
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Simulation Results}
@@
 %BER
-%Achievable rate
+%Achievable rat
 \section{Conclusions and Future Work}

### 2019-04-14 paper/main.tex
Adding Section 3 draft

--- 2019-04-13 paper/main.tex
@@
 \usepackage[para]{footmisc}
+\usepackage{xcolor}
+
+\newcommand{\highlight}[1]{%
+  \colorbox{red!50}{$\displaystyle#1$}}
+
 % \usepackage{parskip}
@@
 \subsection{Vectorizing matrices in Stiefel Manifold}
+The reservoir computing framework has inputs/outputs as vectors, and hence it is necessary to convert the precoder matrices to vectors. 
+A precoding matrix $\mathcal{\bM} \in \text{St}(N_T,N_R)$ is a $N_T\times N_R$ matrix with the property $\mathcal{\bM}^H\mathcal{\bM}=\mathbb{I}_{N_R}$. 
+For brevity sake, let us say that such a matrix $\mathcal{\bM}$ is a \'semi-unitary\' matrix.
+A naive method of vectorizing a $N_T\times N_R$ semi-unitary matrix would be to take all it's $N_TN_R$ complex numbers individually and stack them onto a $2N_TN_R$ dimensional vector.
+However, we can do this a little more efficiently, considering the $\mathcal{\bM}^H\mathcal{\bM}=\mathbb{I}_{N_R}$ property, which implies that each vector representing the columns of $\mathcal{\bM}$ is orthogonal to other columns.
+For the first column, we take the $N_T$ complex numbers and stack them onto a $2N_T$ vector. 
+For the second column, we take only the first $N_T-1$ complex numbers, since the last number can be determined by utilizing orthogonality with the first vector. 
+For the third column, we take only the first $N_T-2$ complex numbers, and so on. 
+Hence, we can vectorize the $N_T\times N_R$ $\mathcal{\bM}$ into a $2(N_T)+2(N_T-1)+\ldots+2(N_T-N_R+1)= 2N_TN_R-(N_R^2-N_R)$ dimensional vector. 
+For any semi-unitary matrix $\mathcal{\bM}$, denote by $\mathcal{\bm}$ the vectorized representation.
+
+Observe here that we do pay a dimensional penalty upon vectorizing the semi-unitary $\mathcal{\bM}$. 
+$\mathcal{\bM} \in \text{St}(N_T,N_R)$, which is a $2N_TN_R-N_R^2$ dimensional manifold. 
+We vectorize $\mathcal{\bM}$ to a $2N_TN_R-N_R^2+N_R$ dimensional vector, an overhead of $N_R$ dimensions, since we didn't exploit the fact that each column vector is a norm 1 vector as well.
+It looks as if we could just take $N_T-1$ complex numbers when vectorizing the first column, instead of $N_T$, but this would lead to a non-unique representation, since there could then be infinite possibilities of the missing one complex number, such that the vector has a norm 1.
 %Focus on the fact that you don't actually pay a penalty
 %The thing to quantize remains on the Stiefel Manifold
-\subsection{Prediction and Quantization}
-%Reservoir Pic
+\subsection{Forward Prediction $f_P$ function}
+The vector representation of semi-unitary matrices allow us to proceed with the discussion on reservoir computing framework for predictive quantization of SVD precoders.
+Consider the reservoir computing framework as in Fig.
+%Ref Fig.
+Reservoir Pic
+
+The input to the reservoir $i$ corresponding to subcarrier $i$, is $\tilde{\bu}_{i,t-1}$, which is the vectorized representation of $\tilde{\bU}_{i,t-1}$. 
+Let $D_{\text{in}}=2N_TN_R-N_R^2+N_R$ be the dimension of the input vector to the dimension.
+Using a randomly initialized $D_{\text{in}}\times D_{\text{resv}}$ input coupler matrix $\bW^{\text{in}}_i$, the $D_{\text{in}}$ dimensional input is mapped to a $D_{\text{resv}}$ dimensional vector, where $D_{\text{resv}}$ is the dimension of the reservoir state vector $\br_{i,t}$.
+The reservoir state vector $\br_{i,t}$ is initialized with $D_{\text{resv}}$ zeros, and is updated via the following equation,
+\begin{equation}
+\br_{i,t}=\text{tanh}(\bA_i\br_{i,t-1}+\bW^{\text{in}}_i\tilde{\bu}_{i,t-1})
+\label{res_upd}
+\end{equation}
+where $\bA_i$ is the adjacency matrix which captures the reservoir dynamics and correlates reservoir state across time, and tanh is applied element wise. 
+Typical choices for $\bA_i$ have been erdos-renyi graphs with an upper bounded maximum eigen value \cite{mosleh2017brain,pathak2017using}.
+
+The output of the reservoir is $\bp_{i,t}$, a vectorized representation of $\bP_{i,t}$. 
+Hence, the output of the reservoir is also a $D_{\text{in}}$ dimensional vector ($D_{\text{out}}=D_{\text{in}}$). 
+The output $\bp_{i,t}$ is obtained via matrix transformation of the reservoir state $\br_{i,t}$ via the $D_{\text{resv}}\times D_{\text{out}}$ output coupler matrix $\bW^{\text{out}}_{i,t-1}$\footnote{Why it is $t-1$ and not $t$ would surface up in Section \ref{train}}, viz.
+\begin{equation}
+\bp_{i,t}=\bW^{\text{out}}_{i,t-1}\br_{i,t}
+\label{pred_op}
+\end{equation}
+
+This completes the forward prediction algorithm to obtain $\bP_{i,t}$ using just one past observed $\bU_{i,t-1}$. That is,
+\begin{equation}
+\bP_{i,t}=f_P(\tilde{\bU}_{i,t-1})=\bW^{\text{out}}_{i,t-1}\text{tanh}(\bA_i\br_{i,t-1}+\bW^{\text{in}}_i\tilde{\bu}_{i,t-1})\footnote{For Brevity sake, $\bp_{i,t}$ and $\bP_{i,t}$ are treated to be one and the same}
+\label{fwd_pred}
+\end{equation}
+However, a complete discussion of the prediction algorithm also involves a backward pass, involving the updation of output couplers $\bW^{\text{out}}_{i,t}$, which would follow subsequently. 
+\subsection{Quantization function $q_P$}
+Before proceeding ahead, it is critical to detail out the quantization function $q_P(\bP_{i,t},\text{fb}_{i,t})$, which is similar to the one used in \cite{6891198,Gupt1905:Predictive,6545375}. 
+Central to the quantization algorithm is the fact that tangent spaces local to a point in manifold, are actually linear vector spaces.
+Given two points $\bX$ and $\bY$ in $\text{St}(N_T,N_R)$, a lifting operation $\bT^Y_X=\texttt{lift}(\bX,\bY)$, $\texttt{lift}:\text{St}(N_T,N_R)\times \text{St}(N_T,N_R) \to \mathcal{T}_X \text{St}(N_T,N_R)$ gives a tangent from X to Y, $\bT^Y_X \in \mathcal{T}_X \text{St}(N_T,N_R)$, where $\mathcal{T}_X \text{St}(N_T,N_R)$ is the local tangent space at $\bX$.
+A corresponding retraction operation $Y=\texttt{retract}(X,\bT^Y_X)$, $\texttt{retract}: \text{St}(N_T,N_R)\times \mathcal{T}_X \text{St}(N_T,N_R) \to \text{St}(N_T,N_R)$ gives back the manifold point obtained by traversing in the tangent direction given by the second argument.
+In this work, the chosen lifting-retraction operations are the Cayley Exponentials, elaborated in \cite{DBLP:journals/corr/abs-1708-00045} and used in \cite{Gupt1905:Predictive}.
+The Cayley exponential lifting operation maps two points in $\text{St}(N_T,N_R)$, to a $N_T\times N_T$ skew hermitian matrix representing the tangent from first point to the other.
+
+The quantization algorithm exploits the linear vector space property of the tangent space and quantizes the local tangent space at the predicted precoder $\bP_{i,t}$, viz $\mathcal{T}_{\bP_{i,t}} \text{St}(N_T,N_R)$.
+The codebook for $\mathcal{T}_{\bP_{i,t}} \text{St}(N_T,N_R)$ basically corresponds to a collection of codewords representing the different directions (tangents) in $\mathcal{T}_{\bP_{i,t}} \text{St}(N_T,N_R)$.
+This codebook is also referred to as the base codebook ($\text{base}^{\mathcal{C}}$) for the quantization function.
+The feedback from the receiver indicates the optimum tangent in the $\text{base}^{\mathcal{C}}$, which the transmitter can choose to get closest (in terms of chordal distance metric, $d_s(\bX,\bY)$ for $\bX,\bY \in \text{St}(N_T,N_R)$ detailed in \cite{Gupt1905:Predictive,6891198}) to the actual value $\bU_{i,t}$.
+With the optimum direction chosen, the next step is to determine how much to move in that particular direction, viz. the length of the chosen tangent direction.
+For this, we adopt the strategy in \cite{6891198}, which
+controls the magnitude of tangent steps, by having two codebooks
+$T^{\mathcal{C}}_p,T^{\mathcal{C}}_m$ of different spreads $s_p,s_m$, but same $2^{\mathcal{B}-1}$ base vectors from $\text{base}^{\mathcal{C}}$, i.e.
+$T^{\mathcal{C}}_{\{p/m\}}=s_{\{p/m\}}\text{base}^{\mathcal{C}}$ (All codewords $\in \text{base}^{\mathcal{C}}$ multiplied by $s_{\{p/m\}}$ individually).
+The two codebooks are concatenated to form a $2^\mathcal{B}$ length codebook $T^\mathcal{C}$. 
+The receiver finds the optimal index $\text{fb}_{i,t} \in \{1,2,\ldots,2^{\mathcal{B}}\}$ in $T^\mathcal{C}$ by comparing the chordal distance metric ($d_s$), of each codeword to the actual precoder $\bU_{i,t}$ obtained from the SVD of the channel matrix, using \eqref{eqn:cn1}.
+The receiver then feeds back $\text{fb}_{i,t}$ to the transmitter using $\mathcal{B}$ bits.
+The transmitter uses the fed back $\text{fb}_{i,t}$ and \eqref{eqn:cn2} to calculate $\tilde{\bU}_{i,t}$,
+\begin{equation}
+\label{eqn:cn1}
+\text{fb}_{i,t} \gets \text{argmin}_{i \in \{1,2,\ldots,2^{\mathcal{B}}\}}\left (d_s\left (\bU_{i,t},\text{retract}(\bP_{i,t},T^\mathcal{C}[i])\right ) \right)
+\end{equation}
+\begin{equation}
+\tilde{\bU}_{i,t}=q_P(\bP_{i,t},\text{fb}_{i,t})=\text{retract}(\bP_{i,t},T^\mathcal{C}[\text{fb}_{i,t}])
+\label{eqn:cn2}
+\end{equation}
+
+$\text{fb}_{i,t}$ is also used to update the spread of the codebooks $T^{\mathcal{C}}_p,T^{\mathcal{C}}_m$. 
+Depending on whether $\text{fb}_{i,t} \geq 2^{\mathcal{B}-1}$,
+i.e. whether the optimum codeword is in $T^{\mathcal{C}}_p$ or
+$T^{\mathcal{C}}_m$, the scale parameter $s[k]$, which in turn
+controls values of $s_p, s_m$, is updated in the following manner,
+$$s_p=g^{\text{min}(s[k-1]+1,0)}, s_m = g^{s[k-1]-1}$$
+$$
+s[k]=
+\begin{cases}
+\text{min}(s[k-1]+1,0), \text{ for } \text{fb}_{i,t} \in T^{\mathcal{C}}_p\\
+s[k-1]-1, \text{otherwise}\\
+\end{cases}
+$$
+with $s[0]=0$. 
+Intuitively, the algorithm reduces/increases the spread of the codebook till the operation of reduction/increase is no longer beneficial, i.e.
+the optimum codeword lies in the higher/lower spread codebook instead.
+The scheme used by us to obtain $\text{base}^{\mathcal{C}}$ is similar to the one presented in \cite{Gupt1905:Predictive}, which performs a $k$-means ($k=2^{\mathcal{B}-1}$) clustering on a collection of tangents to obtain an isotropic collection of $2^{\mathcal{B}-1}$ tangent codewords.
+This completes the discussion on the quantization function $q_P$ to obtain $\tilde{\bU}_{i,t}=q_P(\bP_{i,t},\text{fb}_{i,t})$ from $\bP_{i,t},\text{fb}_{i,t}$.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% More information needed about the adjacency
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Reservoir Training Procedure, the backward pass}
+\label{train}
+Armed with the descriptions of $f_P, q_P$ we are now ready to describe the training process for the reservoir.
+Recall that to obtain $\tilde{\bU}_{i,t}$ from  $\tilde{\bU}_{i,t-1}$, we have,
+\begin{equation}
+\tilde{\bU}_{i,t}=q_P(\bP_{i,t},\text{fb}_{i,t})=q_P(f_P(\tilde{\bU}_{i,t-1}),\text{fb}_{i,t})
+\label{fpqp}
+\end{equation}
+The key idea here is that as the predicted matrix $\bP_{i,t}$, which is basically the coarse estimate for $\bU_{i,t}$, gets closer to the refined estimate $\tilde{\bU}_{i,t}$, the receiver has to quantize even smaller subspaces and can thus provide an even refined estimate via it's feedback $\text{fb}_{i,t}$.
+Hence, for the time instant $t\geq1$, we train the reservoir output coupler such that the following objective function is optimized,
+\begin{equation}
+\mathcal{O}_t=\sum_{s=1}^{t}\frac{1}{\lambda^{t-s}}||\bp_{i,t}-\tilde{\bu}_{i,t}||^2=\sum_{s=1}^{t}\frac{1}{\lambda^{t-s}}||W_{i,t}^{\text{out}}\br_{i,t}-\tilde{\bu}_{i,t}||^2
+\end{equation}
+here $\lambda>1$ is the history parameter.
+We wish to perform the following optimization in order to find the optimum $\bW_{i,t}^{\text{out}}$ from whatever we have observed about $\tilde{\bu}_{i,t}$ uptill now,
+\begin{equation}
+W_{i,t}^{\text{out}}\gets\text{argmin}_{W_{i,t}^{\text{out}}}(\mathcal{O}_t=\sum_{s=1}^{t}\frac{1}{\lambda^{t-s}}||W_{i,t}^{\text{out}}\br_{i,t}-\tilde{\bu}_{i,t}||^2)
+\end{equation}
+Computing the gradients $\frac{\partial \mathcal{O}_t}{\partial W_{i,t}^{\text{out}}}$ and setting it to null gives,
+\begin{equation}
+W_{i,t}^{\text{out}}=\frac{\sum_{s=1}^{t}\frac{1}{\lambda^{t-s}}\texttt{outer}(\tilde{\bu}_{i,s},\br_{i,s})}{\sum_{s=1}^{t}\frac{1}{\lambda^{t-s}}||\br_{i,s}||^2}
+\end{equation}
+where $\texttt{outer}(\bx,\by)$ is the outer product between $N_x$ dimensional vector $\bx$ and $N_y$ dimensional vector $\by$ to give a $N_x\times N_y$ matrix.
+Let $\sum_{s=1}^{t}\frac{1}{\lambda^{t-s}}\texttt{outer}(\tilde{\bu}_{i,s},\br_{i,s})$ be $\text{num}_{i,t}$ and $\sum_{s=1}^{t}\frac{1}{\lambda^{t-s}}||\br_{i,s}||^2$ be $\text{den}_{i,t}$, with $W_{i,t}^{\text{out}}=\frac{\text{num}_{i,t}}{\text{den}_{i,t}}$.
+Observe that,
+\begin{equation}
+W_{i,t}^{\text{out}}=\frac{\frac{\text{num}_{i,t-1}}{\lambda}+\texttt{outer}(\tilde{\bu}_{i,t},\br_{i,t})}{\frac{\text{den}_{i,t-1}}{\lambda}+||\br_{i,t}||^2}
+\label{wout_upd}
+\end{equation}
+\eqref{wout_upd} makes training of the reservoir easy to implement, and of low complexity as well. 
+We just need to store the matrix $\text{num}_{i,t-1}$, a number $\text{den}_{i,t-1}$, and using the current reservoir state $\br_{i,t}$ and obtained $\tilde{\bu}_{i,t}$ from \eqref{fpqp}, one can calculate $W_{i,t}^{\text{out}}$ for forward calculation of $\tilde{\bu}_{i,t+1}$.
+This completes our technical discussion for the complete reservoir computing based framework for predictive quantization illustrated in Fig. %Ref Fig.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+To conclude this section, now summarize and touch upon the novel points of the reservoir computing based framework proposed for predictive quantization of SVD precoding. 
+The first key advantage of the proposed framework, over the past work in this line \cite{Gupt1905:Predictive,6891198,6545375} is that the prediction function and quantization function are not independent of each other.
+To support the above statement, observe \eqref{res_upd},\eqref{fpqp} to obtain $\bW^{\text{out}}_{i,t}$ from $\tilde{\bu}_{i,t}$, and \eqref{fwd_pred} to obtain $\bP_{i,t+1}$ combinedly,
+\begin{equation*}
+\highlight{W_{i,t}^{\text{out}}}=\frac{\frac{\text{num}_{i,t-1}}{\lambda}+\texttt{outer}(\highlight{q_P}(f_P(\tilde{\bu}_{i,t-1}),\text{fb}_{i,t}),\br_{i,t})}{\frac{\text{den}_{i,t-1}}{\lambda}+||\br_{i,t}||^2}
+\end{equation*}
+\begin{equation*}
+\highlight{\bP_{i,t+1}}=f_P(\tilde{\bU}_{i,t})=\highlight{\bW^{\text{out}}_{i,t}}\text{tanh}(\bA_i\br_{i,t}+\bW^{\text{in}}_i\highlight{\tilde{\bu}_{i,t}})
+\end{equation*}
+The dependence between $f_P$ and $q_P$ in our framework is in the sense that the backward pass of the framework ensures that prediction function `'learns' the correlations brought about by $q_P$, in addition to temporal correlations.
+%Better framing possible
+This is done by optimizing $W_{i,t}^{\text{out}}$ such that the prediction output to be as close to the output from $q_P$ (Objective function $\mathcal{O}_t$).
+The updated $W_{i,t}^{\text{out}}$ is then used in forward pass to predict $\bP_{i,t+1}$, which is hopefully closer to $\tilde{\bU}_{i,t+1}$ than $\bP_{i,t}$ was to $\tilde{\bU}_{i,t}$ due to optimization of $\mathcal{O}_t$.
+
+The second key advantage of the proposed scheme comes from the ease of training the reservoir, entailed by \eqref{res_upd}. 
+By storing just one matrix $\text{num}_{i,t}$ and a number $\text{den}_{i,t}$, we can capture the history of the reservoir, with past values weighted by $\lambda$. 
+This is a departure from previous schemes \cite{Gupt1905:Predictive,6891198,6545375} which store the past $n$ (which has to be pre-decided) precoders in a $n$ sized cyclic buffer kind-of arrangement.
+Reservoir computing, thus proposes an easier to implement data centric scheme, which is a rarity for typical data centric ML based schemes. 
 \section{Simulation Results}

### 2019-04-14 eval.py

@@ -43,11 +43,11 @@ sil_cap=1
 # cmp_qtiz_err=np.load('./Intmd_Res/cmp_qtiz_err0.npy')
 # qtiz_err=np.load('./Intmd_Res/qtiz_err0.npy')
 # fin_qt_U=np.load('./Intmd_Res/fin_qt_U0.npy')
-qtiz_U=np.load('./BER_Data/qtiz_U.npy')
-cmp_qtiz_U=np.load('./BER_Data/cmp_qtiz_U.npy')
-cmp_qtiz_err=np.load('./BER_Data/cmp_qtiz_err.npy')
-qtiz_err=np.load('./BER_Data/qtiz_err0.npy')
-fin_qt_U=np.load('./BER_Data/fin_qt_U.npy')
+qtiz_U=np.load('./BER_Data2/qtiz_U_norm.npy')
+cmp_qtiz_U=np.load('./BER_Data2/cmp_qtiz_U_norm.npy')
+cmp_qtiz_err=np.load('./BER_Data2/cmp_qtiz_err_norm.npy')
+qtiz_err=np.load('./BER_Data2/qtiz_err_norm.npy')
+fin_qt_U=np.load('./BER_Data2/fin_qt_U_norm.npy')
 sigma_cb=np.load('./Codebooks/Independent_qt/sigma_cb_2bits_10000.npy')
 num_Cappar=7
 avg_rescap=np.zeros(num_Cappar)
@@ -62,9 +62,8 @@ for chan_inst in range(num_chans):
 		print("Channel Evolution: "+str(i)+" Qtisn Error: "+str(np.mean(qtiz_err[chan_inst][i-1]))+" Cmp Qtisn Error: "+str(np.mean(cmp_qtiz_err[chan_inst][i-1])))
 		reservoir_reconstructed_Us=quasiGeodinterp(qtiz_U[chan_inst][i],num_subcarriers,feedback_indices)
 		time_reconstructed_Us=quasiGeodinterp(cmp_qtiz_U[chan_inst][i],num_subcarriers,feedback_indices)
-		
-		# unqt_reconstructed_Us=quasiGeodinterp(np.array([vec_to_semiunitary(U_data[chan_inst][i][j],Nt,Nr) for j in feedback_indices]),num_subcarriers,feedback_indices)
-		indqt_reconstructed_Us=quasiGeodinterp(np.array([vec_to_semiunitary(qt_U_data[chan_inst][i][j],Nt,Nr) for j in feedback_indices]),num_subcarriers,feedback_indices)
[…]

### 2019-04-14 main.py

@@ -11,7 +11,7 @@ def sigint_handler(signal, frame):
 #---------------------------------------------------------------------------
 
 class reservoir:
-	def __init__(self,Nt=4,Nr=2,train_vals=5,num_nodes=60,p1=0.2):
+	def __init__(self,Nt=4,Nr=2,train_vals=5,num_nodes=60,p1=0.2,train_fac=2):
 		self.Nt = Nt
 		self.Nr = Nr
 		self.vec_dim = Nr*(2*Nt-Nr+1)
@@ -24,9 +24,9 @@ class reservoir:
 		self.output_coupler = np.random.randn(self.output_dim, num_nodes)
 		self.p1 = p1
 		self.A = np.array(networkx.to_numpy_matrix(networkx.erdos_renyi_graph(num_nodes, p1,seed=12)))
-		self.reservoir_history = np.zeros((train_vals,num_nodes))
-		self.output_history = np.zeros((train_vals,self.output_dim))
-		self.history_pointer=0
+		self.train_fac=train_fac
+		self.reservoir_history = 0
+		self.output_history = np.zeros((self.output_dim,num_nodes))
 
 	def get_output(self,inp_vec):
 		val = np.add(np.matmul(self.A, self.reservoir_state), np.matmul(self.input_coupler, inp_vec))
@@ -38,27 +38,24 @@ class reservoir:
 		for i in range(self.num_nodes):
 			self.input_coupler[i]=self.input_coupler[i]-2*lr*np.inner(self.output_coupler[:,i],diff_vec)*(1-self.reservoir_state[i]**2)*inp_vec
 
-	def update_output_coupler(self,beta=0,factor=2):
+	def update_output_coupler(self,beta=0):
 		# self.output_coupler=np.sum(np.array([np.outer(self.output_history[j],self.reservoir_history[j])/(la.norm(self.reservoir_history[j])**2+beta)\
 		# 	for j in range(self.train_vals)]),axis=0)
-		latest_index=(self.history_pointer-1)%self.train_vals
-		self.output_coupler = self.output_coupler/factor + np.outer(self.output_history[latest_index],self.reservoir_history[latest_index])\
-		/(la.norm(self.reservoir_history[latest_index])**2+beta)
[…]

### 2019-04-15 paper/main.tex
Adding system model pdf

@@
 \end{equation}
-
+\begin{figure*}[ht]
+\centering
+\includegraphics[width=0.8\textwidth]{images/system.pdf}
+\label{res_overview}
+\caption{An overview of the reservoir computing framework proposed for predictive quantization of $\bu_{i,t}$}
+\end{figure*}
 $\text{fb}_{i,t}$ is also used to update the spread of the codebooks $T^{\mathcal{C}}_p,T^{\mathcal{C}}_m$. 
@@
 The second key advantage of the proposed scheme comes from the ease of training the reservoir, entailed by \eqref{res_upd}. 
-By storing just one matrix $\text{num}_{i,t}$ and a number $\text{den}_{i,t}$, we can capture the history of the reservoir, with past values weighted by $\lambda$. 
+By storing just one matrix $\text{num}_{i,t}$ and a number $\text{den}_{i,t}$, we can capture the enitre history of the precoding matrices, with past values weighted by $\lambda$. 
 This is a departure from previous schemes \cite{Gupt1905:Predictive,6891198,6545375} which store the past $n$ (which has to be pre-decided) precoders in a $n$ sized cyclic buffer kind-of arrangement.
 Reservoir computing, thus proposes an easier to implement data centric scheme, which is a rarity for typical data centric ML based schemes.
+
 \section{Simulation Results}
 \label{section4}
+\subsection{Simulation setting considered}
+\label{setting}
+\noindent We compare the results of the proposed reservoir computing framework with the predictive quantization scheme presented in \cite{6891198}, which also captures the temporal correlations to enable reduced quantization error.
+\subsection{Quantization Error, BER and Achievable Rate Results}
+\label{res}
 %Qtisn error with 1000 chan evols

### 2019-04-15 main.py

@@ -52,10 +52,11 @@ class reservoir:
 signal.signal(signal.SIGINT, sigint_handler)
 # np.random.seed(0)
 np.random.seed(1)
-data=np.load("./BER_Data/ped_10_100_4_2.npy")
-ind_qt_data=np.load("./BER_Data/qt_ped_10_100_4_2.npy")
+norm=4
+data=np.load("./BER_Data/ped_10_100_4_2_norm"+str(norm)+".npy")
+ind_qt_data=np.load("./BER_Data/qt_ped_10_100_4_2_norm"+str(norm)+".npy")
 num_chans=10
-num_evols=1000
+num_evols=100
 Nt=4
 Nr=2
 past_vals=10
@@ -72,7 +73,7 @@ qtiz_err=np.zeros((num_chans,num_evols-1,feedback_subc))
 cmp_qtiz_U=np.zeros((num_chans,num_evols,feedback_subc,Nt,Nr),dtype='complex')
 cmp_qtiz_err=np.zeros((num_chans,num_evols-1,feedback_subc))
 time_vals=4
-for chan_inst in range(2,3):
+for chan_inst in range(num_chans):
 	print("--------------------------------------------------")
 	print("Starting Channel Instance: "+str(chan_inst))
 	print("--------------------------------------------------")

### 2019-04-15 paper/main.tex
Alter abstract

@@
 
-Precoding matrices obtained via SVD\footnote{Singular Value Decomposition} of the MIMO channel matrix can be utilized at the transmitter for optimum power allocation and lower BER\footnote{Bit Error Rate} transmissions.
-However, a key step enabling this improved performance is the feedback of these precoders to the transmitter from the receiver.
-Considering the limited bit budget for such CSI\footnote{Channel State Information} feedback, the precoders need to be quantized with single digit number of bits.
-For a $N_T \times N_R$\footnote{$N_T(R)$: Number of Transmit (Receive) Antennas} MIMO system, this amounts to quantizing a $N_T \times N_R$ complex valued matrix.
-This odious task is helped by the presence of an underlying manifold structure, and temporal/frequency correlations in the precoders. 
-In this work, we introduce a reservoir computing framework for the task of prediction of new precoders upon observation of past such precoders, by utilizing temporal correlations. 
-This is a departure from existing methods which exploit the non linear geometry endowed by the manifold structure to perform the same.
-Alternately, the non-linear relation is captured in our work via the dynamical reservoir state via the training process of the reservoir. 
-Simulations reveal reduced quantization error, which results in lower BER as well as improved achievable rate, as compared to previous work.
+Precoding matrices obtained from the SVD of the wireless MIMO channel matrix can be utilized at the transmitter for optimum power allocation and lower BER\footnote{Bit Error Rate} transmissions. 
+However, a key step that enables this improved performance is feedback of these precoders to the transmitter from the receiver.
+Since bit budget for such channel state information (CSI) feedback is limited, precoders need to be quantized effectively using with very few bits.
+For a $N_T \times N_R$ MIMO system, this amounts to quantizing a $N_T \times N_R$ complex valued matrix.
+This can be simplified by using the underlying manifold structure, and temporal/frequency correlations in the precoders. 
+In this work, we introduce a reservoir computing based framework for prediction of the new precoders by observing pastprecoders and utilizing temporal correlations. 
+Past methods have primarily exploited the nonlinear geometry endowed by the manifold structure to for precoder interpolation and prediction.
+Here, this non-linear relationship is captured using the dynamical reservoir state as part of the training process of the reservoir. 
+Simulations reveal that this approach produces reduced quantization error, thereby resulting in lower BER as well as improved achievable rates when compared to earlier work.
 

### 2019-04-15 paper/main.tex
Minor edits in introduction

@@
 % Broad summary of your work, come to your problem definition. 
-In MIMO wireless systems, precoding matrices are used for matrix transformation of $N_S$-dimensional ($N_S \leq \text{min}(N_T,N_R))$ information vector onto the $N_T$-dimensional transmit vector, corresponding to the signal emanating out of the $N_T$ antennas of the transmitter.
-The optimum precoding matrix, to achieve channel capacity via optimum power allocation is obtained via the SVD of the MIMO channel matrix. \cite{love2008overview}
+In MIMO wireless systems, precoding matrices are used for transformation of an $N_S$-dimensional ($N_S \leq \text{min}(N_T,N_R))$ information vector onto an $N_T$-dimensional transmit vector that corresponds to the signal emanating out of the $N_T$ antennas of the transmitter.
+The precoding matrix used to achieve the channel capacity using optimal power allocation is obtained using the SVD of the MIMO channel matrix \cite{love2008overview}.
 The MIMO channel matrix is estimated at the receiver, and the transmitter has no a-priori knowledge of the same.
-Hence, to avail the said benefits of SVD precoders, the receiver needs to quantize and feedback the precoders it obtains from SVD of the MIMO channel matrix.
-To respect the bit budget imposed by limited feedback CSI schemes, the quantization needs to be performed only with a few single number of bits.
+Therefore, to obtain the said benefits of SVD precoders, the receiver needs to quantize and feed back the precoders it estimates from the SVD of the MIMO channel matrix.
+To honour the bit budget imposed by limited feedback CSI schemes, the quantization needs to be performed using very few bits.
 Given the high dimensionality of the precoders (which form a $N_T \times N_R$ complex valued matrix, viz.
-$2\times N_T\times N_R$ real numbers), effective quantization with just a few bits pose a significant challenge.
+$2\times N_T\times N_R$ real numbers), effective quantization with just a few bits poses a significant challenge.
 

### 2019-04-15 paper/main.tex
More changes

@@
 % Elaborate on each point (what people have done before) lecunnas
-This challenge has been overcome in past work via two inherent properties of the precoders. 
-Firstly, the precoders are not actually $2\times N_T\times N_R$ dimensional entities, and these actually have an underlying manifold structure which allows one to work with lower dimensions if one performs operations over the manifold directly.
-Secondly, these precoders are correlated nicely along both time and frequency. 
-Capturing temporal correlations allow for predictive quantization algorithms, which allow improvement of the quantization error with time.
-Exploiting frequency correlations allow for various interpolation algorithms, which in turn reduce the feedback overhead in a single OFDM frame, by feeding back only for certain subcarriers, and interpolating over the others.
-Although the underlying manifold structure allows one to work with effective lower dimensions, most of the naive linear algorithms to predict and interpolate don't work well here, owing to the inherent non-linear structure of the manifold.
-Hence, combining these two properties, viz.
-the underlying manifold structure and temporal-frequency correlations, require generalization of such linear algorithms to the manifold under consideration, by exploiting the differential geometry of the manifold.
+Past work has used two inherent properties of the precoders to enable effective low-rate precoder feedback. 
+First, the precoders are not actually $2\times N_T\times N_R$ dimensional entities, and these have an underlying manifold structure that allows one to work with lower dimensions if one performs operations over the manifold directly.
+Second, these precoders are correlated in both time and frequency. 
+Capturing temporal correlations allows the use off predictive quantization algorithms that improvement of the quantization error with time by effectively utilizing all information.
+Exploiting frequency correlations permits the use of interpolation algorithms, which in turn reduce the feedback overhead in a single OFDM frame, by feeding back CSI information only for certain subcarriers, and interpolating over the others.
+Despite the existence of the underlying manifold structure that possesses effective lower dimensions, most of the na{\"i}ve algorithms that predict and interpolate are limited in their effectiveness, owing to the inherent non-linear structure of the manifold.
+Thus, combining these two properties, viz.
+the underlying manifold structure and temporal-frequency correlations, requires a generalization of such linear algorithms to the manifold under consideration, by exploiting the differential geometry of the manifold.
 Relevant past work in this direction has been \cite{Gupt1905:Predictive,6891198,6545375,5671092,Li2016,khaled2005quantized,krishnamachari2013geometry}.
@@
 % What is the way ahead
-The manifold based approaches have provided significant performance benefits, given that they work with effective lower dimensions.
+Manifold based approaches have provided significant performance benefits, given that they work with effective lower dimensions.
 However, these approaches are difficult to implement and require some familiarity with manifold geometry for a complete grasp.
@@
 Reservoir computing is a computational framework designed for sequential data processing. 
-It's design takes inspiration from several frameworks of recurrent neural networks \cite{jaeger2004harnessing} including Liquid State Machines \cite{jalalvand2015real}. 
-A reservoir computing system maps the inputs to spatio-temporal patterns in higher dimensional dynamical reservoir state. 
-The pattern analysis over these spatio-temporal patterns is performed by an output coupler which maps the higher dimensional reservoir state back to the output dimension, generally having lower dimensionality than reservoir state.
+Its design is inspired from several frameworks of recurrent neural networks \cite{jaeger2004harnessing}, including Liquid State Machines \cite{jalalvand2015real}. 
+A reservoir computing system maps the inputs to spatio-temporal patterns in a higher dimensional dynamical reservoir state. 
+The pattern analysis over these spatio-temporal patterns is performed by an output coupler that maps the higher dimensional reservoir state back to the output dimension that generally possesses lower dimensionality than the reservoir state.
 % A important characteristic of reservoir computing is that while training, the input weights and the weights within the reservoir are not kept fixed and the weights of the output coupler are updated.
-The major advantage of reservoir computing system is that it’s extremely easy to train in comparison to its counterparts like Deep Neural Networks. 
-The input features can be efficiently read out by a simple learning algorithm because the reservoir non-linearly transforms sequential inputs into the higher dimensional reservoir state. 
+The key advantage of a reservoir computing based system is that it is extremely easy to train in comparison to its counterparts like Deep Neural Networks. CITATION NEEDED
+The input features can be efficiently learnt using a simple learning algorithm, since the reservoir non-linearly transforms sequential inputs into a higher dimensional reservoir state. 
 Reservoir computing has been successfully used to solve problems like spoken digit recognition \cite{verstraeten2005isolated}, handwritten digit image recognition \cite{jalalvand2015real} and climate prediction \cite{pathak2017using}.
@@
 \cite{jaeger2004harnessing} used reservoir computing framework to harness channel non-linearities in order for smarter channel equalization.
-\cite{mosleh2017brain,shafin2018realizing} utilized the same for OFDM symbol detection while tapping in channel, as well as power amplifier non-linearities.
-In our work, we utilize the reservoir computing framework to discover the underlying non-linear relations between previously observed precoding matrices, in order to predict the next precoder in series.
-Upon vectorizing the precoding matrices, this becomes analogous to time series prediction algorithms, which the reservoir computing framework has been known to work really well for \cite{mosleh2017brain}.
+\cite{mosleh2017brain,shafin2018realizing} utilized this technique for OFDM symbol detection while accounting for channel and power amplifier non-linearities.
+In our work, we utilize the reservoir computing framework to discover the underlying nonlinear relations between previously observed precoding matrices, in order to predict the next precoder in series.
+Upon vectorizing the precoding matrices, this becomes analogous to time series prediction algorithms, for which the reservoir computing framework has been known to work effectively \cite{mosleh2017brain}.
 

### 2019-04-15 paper/main.tex
Remove whitespace
More changes

@@
 
+The rest of this paper is organized as follows TODO
 %
@@
 has $N_T$ transmit antennas and $N_R$ receive antennas.
-The available bandwidth is divided into $N$ subcarriers, so that individually for each subcarrier, the channel can be considered flat fading. 
-The transmitter communicates an $N_s \times 1$ information data vector, where
-$N_s \leq \text{min}(N_T,N_R)$, and the $N_T \times N_s$ precoding
-matrix maps the $N_s \times 1$ information data vector onto the $N_T \times 1$ transmit vector emanating out of the transmitter.
+The available bandwidth is divided into $N$ subcarriers, so that, individually for each subcarrier, the channel can be assumed to be flat fading.
+The transmitter communicates an $N_s \times 1$ information data vector, where $N_s \leq \text{min}(N_T,N_R)$, and the $N_T \times N_s$ precoding matrix maps the $N_s \times 1$ information data vector onto the $N_T \times 1$ transmit vector emanating out of the transmitter.
 
-In this discussion, we assume that $N_T > N_R$ and $N_s = N_R$. Keeping notations consistent with \cite{6891198,Gupt1905:Predictive}, the $N_R \times 1$ data stream received is denoted by:
+In this discussion, we assume that $N_T > N_R$ and $N_s = N_R$.
+Consistent with notation in \cite{6891198,Gupt1905:Predictive}, the $N_R \times 1$ data stream received on the $i$-th subcarrier is denoted by:
 \begin{equation}
@@
 \end{equation}
-Here $\tilde{\bU}_{i,t} \in \mathbb{C}^{N_T \times N_R}$ denotes the precoding matrix which is a function of quantized CSI fed back by the receiver, $\by_{i,t} \in \mathbb{C}^{N_R \times 1}$ is the received data stream, $\bx_{i,t} \in \mathbb{C}^{N_R \times 1}$ denotes the transmitted signal, all at the $i$-th subcarrier of the $t$-th OFDM frame, $\bH_{i,t} \in \mathbb{C}^{N_T \times N_R}$ denotes the MIMO channel matrix and $\bw_{i,t}$ denotes the i.i.d.
+$\tilde{\bU}_{i,t} \in \mathbb{C}^{N_T \times N_R}$ represents the precoding matrix, which is a function of quantized CSI fed back by the receiver, $\by_{i,t} \in \mathbb{C}^{N_R \times 1}$ is the received data stream, $\bx_{i,t} \in \mathbb{C}^{N_R \times 1}$ denotes the transmitted signal, $\bH_{i,t} \in \mathbb{C}^{N_T \times N_R}$ denotes the MIMO channel matrix and $\bw_{i,t}$ denotes the i.i.d.
 complex Gaussian noise with $\bw_{i,t} \sim \mathcal{N}_{\mathbb{C}}(0,N_0\bI_{N_R})$, $N_0$ being the noise variance.
@@
 
-Provided an infinite bit budget for quantization, the transmitter can directly use the matrices obtained from SVD of $\bH^{H}_{i,t}$ as precoder $\tilde{\bU}_{i,t}$.
+If an infinite bit budget is available for quantization, the transmitter can directly use the matrices obtained from SVD of $\bH^{H}_{i,t}$ as the precoder $\tilde{\bU}_{i,t}$.
 In particular, if $\text{SVD}(\bH_{i,t}) = \bU_{i,t},\Sigma_{i,t}, \bV_{i,t}$, then $\tilde{\bU}_{i,t} = \bU_{i,t}$.
@@
 
-Algorithms similar to Lloyd codebook algorithm have been studied for quantizing $\text{St}(N_T,N_R)$ \cite{6678348}.
-However, this method treats precoders close-by in time/frequency to each other as independent, since it doesn't exploit any temporal/spectral correlations for quantization. 
-Predictive quantization algorithms \cite{Gupt1905:Predictive,6891198} can be utilized to reduce the quantization error with time by tapping in available correlations.
+Algorithms similar to the Lloyd codebook algorithm have been studied for quantizing $\text{St}(N_T,N_R)$ \cite{6678348}.
+However, this method treats precoders that are close to each other in time or frequency as independent, since it does not exploit any temporal/spectral correlations for quantization.
+Predictive quantization algorithms \cite{Gupt1905:Predictive,6891198} can be utilized to reduce the quantization error with time by utilizing the available correlations.
 
-We now discuss the basic mathematical model central to predictive quantization algorithms for precoding matrices.
-Consider that we predict based on past $p$ observed precoding matrices, and hence $\tilde{\bU}_{i,t-p},\tilde{\bU}_{i,t-p+1},\ldots,\tilde{\bU}_{i,t-2},\tilde{\bU}_{i,t-1}$ have been fed back and available at the transmitter.
-Using a prediction algorithm and exploiting time correlations among precoders at $t-p,t-p+1,\ldots,t-2,t-1$ time instances, the transmitter can predict $\tilde{\bU}_{i,t}$ to be some $\bP_{i,t}=f_P(\tilde{\bU}_{i,t-p},\tilde{\bU}_{i,t-p+1},\ldots,\tilde{\bU}_{i,t-2},\tilde{\bU}_{i,t-1})$, where $f_P: \text{St}(N_T,N_R)^p \to \text{St}(N_T,N_R)$ is a prediction function.
-Now since the transmitter already knows a coarse estimate of $\tilde{\bU}_{i,t}$ given by $\bP_{i,t}$, the receiver just quantizes the local space of $\text{St}(N_T,N_R)$ nearby $\bP_{i,t}$ to enable a refined estimate of $\tilde{\bU}_{i,t}$ at the transmitter.
+We now discuss the basic mathematical model that is central to predictive quantization algorithms for precoding matrices.
+Suppose that we predict the current precoding matrix based on the past $p$ observed precoding matrices, and hence $\tilde{\bU}_{i,t-p},\tilde{\bU}_{i,t-p+1},\ldots,\tilde{\bU}_{i,t-2},\tilde{\bU}_{i,t-1}$ have been fed back and available at the transmitter.
+By using a prediction algorithm  and by exploiting time correlations among precoders at $t-p,t-p+1,\ldots,t-2,t-1$ time instances, the transmitter can predict $\tilde{\bU}_{i,t}$ to be some $\bP_{i,t}=f_P(\tilde{\bU}_{i,t-p},\tilde{\bU}_{i,t-p+1},\ldots,\tilde{\bU}_{i,t-2},\tilde{\bU}_{i,t-1})$, where $f_P: \text{St}(N_T,N_R)^p \to \text{St}(N_T,N_R)$ is a prediction function.
+Now, since the transmitter already possesses a coarse estimate of $\tilde{\bU}_{i,t}$ given by $\bP_{i,t}$, the receiver just quantizes the local space of $\text{St}(N_T,N_R)$ nearby $\bP_{i,t}$ to facilitate the construction of a refined estimate of $\tilde{\bU}_{i,t}$ at the transmitter.
 That is, the transmitter utilizes a quantization function $q_P:\text{St}(N_T,N_R) \times \mathbb{N} \to \text{St}(N_T,N_R)$, to obtain $\tilde{\bU}_{i,t} \gets q_P(\bP_{i,t},\text{fb}_{i,t})$, where $\text{fb}_{i,t} \in \{1,2\ldots2^{\mathcal{B}}\}$ is the feedback from the receiver for precoder at $i$-th subcarrier and $t$-th time instant, considering bit budget of $\mathcal{B}$ bits.
@@
 
-Since using predictive quantization scheme, quantization is on a smaller subspace as compared to the entire manifold in case of independent quantization, the quantization error is substantially lower as well.
-However, that being said, independent quantization algorithms are important for initialization the predictive quantization strategies.
-Observe that, predictive quantization algorithms for SVD precoders are typically the higher dimensional analogs of the well known approaches to reduce quantization error using Linear Prediction Codes and Delta PCM.
-In both LPC and Delta PCM, quantization error is reduced substantially by using a linear predictor and quantizing the scalar difference between the predicted and observed value. 
-Analogous to this, for $\text{St}(N_T,N_R)$ quantization error is reduced by quantizing a smaller subspace around predicted value, compared to the entire manifold.
+When using predictive quantization scheme, the quantization is performed on a smaller subspace when compared to the entire manifold in case of independent quantization.
+Therefore, the quantization error is substantially lower as well.
+However, quantization algorithms that are independent of these specific predictive structures are important for the initialization of these predictive quantization strategies.
+Observe that predictive quantization algorithms for SVD precoders are typically the higher dimensional analogs of the well known approaches to reduce quantization error using linear prediction codes (LPCs) and Delta PCM.
+In both LPCs and Delta PCM, quantization error can be reduced substantially using a linear predictor and quantizing the scalar difference between the predicted and observed value (innovation).
+Analogous to this, for $\text{St}(N_T,N_R)$ quantization error is reduced by quantizing a subspace around the predicted value that is much smaller than the entire manifold.
 

### 2019-04-15 paper/main.tex
Revise system model

@@
 
-The rest of this paper is organized as follows TODO
-%
-
 \section{System Model}
@@
 
-In our work, we propose a reservoir computing based prediction framework, which predicts the new precoders by tapping the temporal correlations captured from past observed precoders ($f_P$).
-We reuse the $q_P$ algorithm from \cite{Gupt1905:Predictive,6891198}, however, by incorporating the $q_P$ in the prediction framework, as discussed in subsequent sections, the $f_P$ function also exploits correlations in $q_P$ (codebook locality correlations), along with temporal correlations.
-Previous work \cite{Gupt1905:Predictive,6891198} have $f_P$ and $q_P$ independent of each other.
-The detailed discussion on reservoir computing based model for $f_P$ and $q_P$ is presented in Section \ref{section3}.
+In our work, we propose a reservoir computing based prediction framework that predicts the new precoders by utilizing  temporal correlations that are captured from past observed precoders ($f_P$).
+We reuse the $q_P$ algorithm from \cite{Gupt1905:Predictive,6891198}.
+However, by incorporating the $q_P$ in the prediction framework, as discussed in subsequent sections, the $f_P$ function also exploits correlations in $q_P$ (codebook locality correlations), along with temporal correlations.
+Previous work \cite{Gupt1905:Predictive,6891198} has considered $f_P$ and $q_P$ to be independent of each other.
+A detailed discussion on the reservoir computing based model for $f_P$ and $q_P$ is presented in Section \ref{section3}.
 The proposed reservoir computing scheme is evaluated against the temporal predictive quantization scheme in \cite{6891198}, and the simulation results are discussed in Section \ref{section4}.

### 2019-04-15 paper/main.tex
Revise vectorizing

@@
 \subsection{Vectorizing matrices in Stiefel Manifold}
-The reservoir computing framework has inputs/outputs as vectors, and hence it is necessary to convert the precoder matrices to vectors.
+The reservoir computing framework has inputs and outputs as vectors, and thus, it is necessary to convert the precoder matrices to vectors.
 A precoding matrix $\mathcal{\bM} \in \text{St}(N_T,N_R)$ is a $N_T\times N_R$ matrix with the property $\mathcal{\bM}^H\mathcal{\bM}=\mathbb{I}_{N_R}$.
-For brevity sake, let us say that such a matrix $\mathcal{\bM}$ is a \'semi-unitary\' matrix.
-A naive method of vectorizing a $N_T\times N_R$ semi-unitary matrix would be to take all it's $N_TN_R$ complex numbers individually and stack them onto a $2N_TN_R$ dimensional vector.
-However, we can do this a little more efficiently, considering the $\mathcal{\bM}^H\mathcal{\bM}=\mathbb{I}_{N_R}$ property, which implies that each vector representing the columns of $\mathcal{\bM}$ is orthogonal to other columns.
-For the first column, we take the $N_T$ complex numbers and stack them onto a $2N_T$ vector.
+For brevity, let us assume that such a matrix $\mathcal{\bM}$ is a \'semi-unitary\' matrix.
+A na{\"i}ve method to vectorize a $N_T\times N_R$ semi-unitary matrix would be to take all it's $N_TN_R$ complex numbers individually and stack them onto a $2N_TN_R$ dimensional real vector.
+However, a more efficiennt approach would be to use the $\mathcal{\bM}^H\mathcal{\bM}=\mathbb{I}_{N_R}$ property, which implies that each vector representing the columns of $\mathcal{\bM}$ is orthogonal to other columns.
+For the first column, we take its $N_T$ complex numbers and stack them onto a $2N_T$ vector.
 For the second column, we take only the first $N_T-1$ complex numbers, since the last number can be determined by utilizing orthogonality with the first vector.
 For the third column, we take only the first $N_T-2$ complex numbers, and so on.
-Hence, we can vectorize the $N_T\times N_R$ $\mathcal{\bM}$ into a $2(N_T)+2(N_T-1)+\ldots+2(N_T-N_R+1)= 2N_TN_R-(N_R^2-N_R)$ dimensional vector.
+Therefore, we can vectorize the $N_T\times N_R$ $\mathcal{\bM}$ into a $2(N_T)+2(N_T-1)+\ldots+2(N_T-N_R+1)= 2N_TN_R-(N_R^2-N_R)$ dimensional vector.
 For any semi-unitary matrix $\mathcal{\bM}$, denote by $\mathcal{\bm}$ the vectorized representation.

### 2019-04-15 paper/main.tex
Add more changes

@@
 A na{\"i}ve method to vectorize a $N_T\times N_R$ semi-unitary matrix would be to take all it's $N_TN_R$ complex numbers individually and stack them onto a $2N_TN_R$ dimensional real vector.
-However, a more efficiennt approach would be to use the $\mathcal{\bM}^H\mathcal{\bM}=\mathbb{I}_{N_R}$ property, which implies that each vector representing the columns of $\mathcal{\bM}$ is orthogonal to other columns.
+However, a more efficient approach would be to use the $\mathcal{\bM}^H\mathcal{\bM}=\mathbb{I}_{N_R}$ property, which implies that each vector representing the columns of $\mathcal{\bM}$ is orthogonal to other columns.
 For the first column, we take its $N_T$ complex numbers and stack them onto a $2N_T$ vector.
@@
 
-Observe here that we do pay a dimensional penalty upon vectorizing the semi-unitary $\mathcal{\bM}$.
+Observe here that there is a dimensional penalty; upon vectorizing the semi-unitary $\mathcal{\bM}$,
 $\mathcal{\bM} \in \text{St}(N_T,N_R)$, which is a $2N_TN_R-N_R^2$ dimensional manifold.
-We vectorize $\mathcal{\bM}$ to a $2N_TN_R-N_R^2+N_R$ dimensional vector, an overhead of $N_R$ dimensions, since we didn't exploit the fact that each column vector is a norm 1 vector as well.
-It looks as if we could just take $N_T-1$ complex numbers when vectorizing the first column, instead of $N_T$, but this would lead to a non-unique representation, since there could then be infinite possibilities of the missing one complex number, such that the vector has a norm 1.
+We vectorize $\mathcal{\bM}$ to a $2N_TN_R-N_R^2+N_R$ dimensional vector, corresponding to an overhead of $N_R$ dimensions, since we have not exploited the fact that each column vector is a unit norm vector as well.
+One could attempt to use only $N_T-1$ complex numbers when vectorizing the first column, rather than all $N_T$.
+However, this would lead to a non-unique representation, since there could then be infinitely many values for the missing complex number, all of which yield a unit norm vector.
 %Focus on the fact that you don't actually pay a penalty
@@
 \subsection{Forward Prediction $f_P$ function}
-The vector representation of semi-unitary matrices allow us to proceed with the discussion on reservoir computing framework for predictive quantization of SVD precoders.
-Consider the reservoir computing framework as in Fig.
-%Ref Fig.
-Reservoir Pic
+The vector representation of semi-unitary matrices allows us to proceed with the discussion on reservoir computing framework for predictive quantization of SVD precoders.
+Consider the reservoir computing framework shown in Fig. TODO %Ref Fig. Reservoir Pic
 
-The input to the reservoir $i$ corresponding to subcarrier $i$, is $\tilde{\bu}_{i,t-1}$, which is the vectorized representation of $\tilde{\bU}_{i,t-1}$.
+The input to the reservoir $i$ corresponding to subcarrier $i$ is $\tilde{\bu}_{i,t-1}$, which is the vectorized representation of $\tilde{\bU}_{i,t-1}$.
 Let $D_{\text{in}}=2N_TN_R-N_R^2+N_R$ be the dimension of the input vector to the dimension.
@@
 \end{equation}
-where $\bA_i$ is the adjacency matrix which captures the reservoir dynamics and correlates reservoir state across time, and tanh is applied element wise.
-Typical choices for $\bA_i$ have been erdos-renyi graphs with an upper bounded maximum eigen value \cite{mosleh2017brain,pathak2017using}.
+where $\bA_i$ is the adjacency matrix that captures the reservoir dynamics and correlates reservoir state across time, and $\text{tanh}$ is applied element wise.
+Typical choices for $\bA_i$ have been Erdos-Renyi graphs with an upper bounded maximum eigen value \cite{mosleh2017brain,pathak2017using}.
 
 The output of the reservoir is $\bp_{i,t}$, a vectorized representation of $\bP_{i,t}$.
-Hence, the output of the reservoir is also a $D_{\text{in}}$ dimensional vector ($D_{\text{out}}=D_{\text{in}}$).
+Therefore, the output of the reservoir is also a $D_{\text{in}}$ dimensional vector ($D_{\text{out}}=D_{\text{in}}$).
 The output $\bp_{i,t}$ is obtained via matrix transformation of the reservoir state $\br_{i,t}$ via the $D_{\text{resv}}\times D_{\text{out}}$ output coupler matrix $\bW^{\text{out}}_{i,t-1}$\footnote{Why it is $t-1$ and not $t$ would surface up in Section \ref{train}}, viz.
@@
 \begin{equation}
-\bP_{i,t}=f_P(\tilde{\bU}_{i,t-1})=\bW^{\text{out}}_{i,t-1}\text{tanh}(\bA_i\br_{i,t-1}+\bW^{\text{in}}_i\tilde{\bu}_{i,t-1})\footnote{For Brevity sake, $\bp_{i,t}$ and $\bP_{i,t}$ are treated to be one and the same}
+\bP_{i,t}=f_P(\tilde{\bU}_{i,t-1})=\bW^{\text{out}}_{i,t-1}\text{tanh}(\bA_i\br_{i,t-1}+\bW^{\text{in}}_i\tilde{\bu}_{i,t-1})\footnote{For brevity, $\bp_{i,t}$ and $\bP_{i,t}$ are treated to be one and the same}
 \label{fwd_pred}
@@
 \subsection{Quantization function $q_P$}
-Before proceeding ahead, it is critical to detail out the quantization function $q_P(\bP_{i,t},\text{fb}_{i,t})$, which is similar to the one used in \cite{6891198,Gupt1905:Predictive,6545375}.
-Central to the quantization algorithm is the fact that tangent spaces local to a point in manifold, are actually linear vector spaces.
-Given two points $\bX$ and $\bY$ in $\text{St}(N_T,N_R)$, a lifting operation $\bT^Y_X=\texttt{lift}(\bX,\bY)$, $\texttt{lift}:\text{St}(N_T,N_R)\times \text{St}(N_T,N_R) \to \mathcal{T}_X \text{St}(N_T,N_R)$ gives a tangent from X to Y, $\bT^Y_X \in \mathcal{T}_X \text{St}(N_T,N_R)$, where $\mathcal{T}_X \text{St}(N_T,N_R)$ is the local tangent space at $\bX$.
+Before proceeding, it is critical to describe the quantization function $q_P(\bP_{i,t},\text{fb}_{i,t})$, which is similar to the one used in \cite{6891198,Gupt1905:Predictive,6545375}.
+Central to the quantization algorithm is the fact that tangent spaces local to a point in manifold are linear vector spaces.
+Given two points $\bX$ and $\bY$ in $\text{St}(N_T,N_R)$, a lifting operation $\bT^Y_X=\texttt{lift}(\bX,\bY)$, $\texttt{lift}:\text{St}(N_T,N_R)\times \text{St}(N_T,N_R) \to \mathcal{T}_X \text{St}(N_T,N_R)$ yields a tangent from $X$ to $Y$, denoted as $\bT^Y_X \in \mathcal{T}_X \text{St}(N_T,N_R)$, where $\mathcal{T}_X \text{St}(N_T,N_R)$ is the local tangent space at $\bX$.
 A corresponding retraction operation $Y=\texttt{retract}(X,\bT^Y_X)$, $\texttt{retract}: \text{St}(N_T,N_R)\times \mathcal{T}_X \text{St}(N_T,N_R) \to \text{St}(N_T,N_R)$ gives back the manifold point obtained by traversing in the tangent direction given by the second argument.
-In this work, the chosen lifting-retraction operations are the Cayley Exponentials, elaborated in \cite{DBLP:journals/corr/abs-1708-00045} and used in \cite{Gupt1905:Predictive}.
-The Cayley exponential lifting operation maps two points in $\text{St}(N_T,N_R)$, to a $N_T\times N_T$ skew hermitian matrix representing the tangent from first point to the other.
+In this work, the chosen lifting-retraction operations are the Cayley Exponentials, elaborated in \cite{DBLP:journals/corr/abs-1708-00045}. % and used in \cite{Gupt1905:Predictive}.
+The Cayley exponential lifting operation maps two points in $\text{St}(N_T,N_R)$, to a $N_T\times N_T$ skew Hermitian matrix that represents the tangent from first point to the other.
 
 The quantization algorithm exploits the linear vector space property of the tangent space and quantizes the local tangent space at the predicted precoder $\bP_{i,t}$, viz $\mathcal{T}_{\bP_{i,t}} \text{St}(N_T,N_R)$.
-The codebook for $\mathcal{T}_{\bP_{i,t}} \text{St}(N_T,N_R)$ basically corresponds to a collection of codewords representing the different directions (tangents) in $\mathcal{T}_{\bP_{i,t}} \text{St}(N_T,N_R)$.
+The codebook for $\mathcal{T}_{\bP_{i,t}} \text{St}(N_T,N_R)$ corresponds to a collection of codewords that represent the different directions (tangents) in $\mathcal{T}_{\bP_{i,t}} \text{St}(N_T,N_R)$.
 This codebook is also referred to as the base codebook ($\text{base}^{\mathcal{C}}$) for the quantization function.

### 2019-04-17 paper/main.tex
Adding section4 half

--- 2019-04-15 paper/main.tex
@@
 
-Precoding matrices obtained from the SVD of the wireless MIMO channel matrix can be utilized at the transmitter for optimum power allocation and lower BER\footnote{Bit Error Rate} transmissions.
-However, a key step that enables this improved performance is feedback of these precoders to the transmitter from the receiver.
-Since bit budget for such channel state information (CSI) feedback is limited, precoders need to be quantized effectively using with very few bits.
-For a $N_T \times N_R$ MIMO system, this amounts to quantizing a $N_T \times N_R$ complex valued matrix.
-This can be simplified by using the underlying manifold structure, and temporal/frequency correlations in the precoders.
-In this work, we introduce a reservoir computing based framework for prediction of the new precoders by observing pastprecoders and utilizing temporal correlations.
-Past methods have primarily exploited the nonlinear geometry endowed by the manifold structure to for precoder interpolation and prediction.
-Here, this non-linear relationship is captured using the dynamical reservoir state as part of the training process of the reservoir.
-Simulations reveal that this approach produces reduced quantization error, thereby resulting in lower BER as well as improved achievable rates when compared to earlier work.
+Precoding matrices obtained via SVD\footnote{Singular Value Decomposition} of the MIMO channel matrix can be utilized at the transmitter for optimum power allocation and lower BER\footnote{Bit Error Rate} transmissions.
+However, a key step enabling this improved performance is the feedback of these precoders to the transmitter from the receiver.
+Considering the limited bit budget for such CSI\footnote{Channel State Information} feedback, the precoders need to be quantized with single digit number of bits.
+For a $N_T \times N_R$\footnote{$N_T(R)$: Number of Transmit (Receive) Antennas} MIMO system, this amounts to quantizing a $N_T \times N_R$ complex valued matrix.
+This odious task is helped by the presence of an underlying manifold structure, and temporal/frequency correlations in the precoders. 
+In this work, we introduce a reservoir computing framework for the task of prediction of new precoders upon observation of past such precoders, by utilizing temporal correlations. 
+This is a departure from existing methods which exploit the non linear geometry endowed by the manifold structure to perform the same.
+Alternately, the non-linear relation is captured in our work via the dynamical reservoir state via the training process of the reservoir. 
+Simulations reveal reduced quantization error, which results in lower BER as well as improved achievable rate, as compared to previous work.
 
@@
 % Broad summary of your work, come to your problem definition. 
-In MIMO wireless systems, precoding matrices are used for transformation of an $N_S$-dimensional ($N_S \leq \text{min}(N_T,N_R))$ information vector onto an $N_T$-dimensional transmit vector that corresponds to the signal emanating out of the $N_T$ antennas of the transmitter.
-The precoding matrix used to achieve the channel capacity using optimal power allocation is obtained using the SVD of the MIMO channel matrix \cite{love2008overview}.
+In MIMO wireless systems, precoding matrices are used for matrix transformation of $N_S$-dimensional ($N_S \leq \text{min}(N_T,N_R))$ information vector onto the $N_T$-dimensional transmit vector, corresponding to the signal emanating out of the $N_T$ antennas of the transmitter.
+The optimum precoding matrix, to achieve channel capacity via optimum power allocation is obtained via the SVD of the MIMO channel matrix. \cite{love2008overview}
 The MIMO channel matrix is estimated at the receiver, and the transmitter has no a-priori knowledge of the same.
-Therefore, to obtain the said benefits of SVD precoders, the receiver needs to quantize and feed back the precoders it estimates from the SVD of the MIMO channel matrix.
-To honour the bit budget imposed by limited feedback CSI schemes, the quantization needs to be performed using very few bits.
+Hence, to avail the said benefits of SVD precoders, the receiver needs to quantize and feedback the precoders it obtains from SVD of the MIMO channel matrix.
+To respect the bit budget imposed by limited feedback CSI schemes, the quantization needs to be performed only with a few single number of bits.
 Given the high dimensionality of the precoders (which form a $N_T \times N_R$ complex valued matrix, viz.
-$2\times N_T\times N_R$ real numbers), effective quantization with just a few bits poses a significant challenge.
+$2\times N_T\times N_R$ real numbers), effective quantization with just a few bits pose a significant challenge.
 
 % Elaborate on each point (what people have done before) lecunnas
-Past work has used two inherent properties of the precoders to enable effective low-rate precoder feedback.
-First, the precoders are not actually $2\times N_T\times N_R$ dimensional entities, and these have an underlying manifold structure that allows one to work with lower dimensions if one performs operations over the manifold directly.
-Second, these precoders are correlated in both time and frequency.
-Capturing temporal correlations allows the use off predictive quantization algorithms that improvement of the quantization error with time by effectively utilizing all information.
-Exploiting frequency correlations permits the use of interpolation algorithms, which in turn reduce the feedback overhead in a single OFDM frame, by feeding back CSI information only for certain subcarriers, and interpolating over the others.
-Despite the existence of the underlying manifold structure that possesses effective lower dimensions, most of the na{\"i}ve algorithms that predict and interpolate are limited in their effectiveness, owing to the inherent non-linear structure of the manifold.
-Thus, combining these two properties, viz.
-the underlying manifold structure and temporal-frequency correlations, requires a generalization of such linear algorithms to the manifold under consideration, by exploiting the differential geometry of the manifold.
+This challenge has been overcome in past work via two inherent properties of the precoders. 
+Firstly, the precoders are not actually $2\times N_T\times N_R$ dimensional entities, and these actually have an underlying manifold structure which allows one to work with lower dimensions if one performs operations over the manifold directly.
+Secondly, these precoders are correlated nicely along both time and frequency. 
+Capturing temporal correlations allow for predictive quantization algorithms, which allow improvement of the quantization error with time.
+Exploiting frequency correlations allow for various interpolation algorithms, which in turn reduce the feedback overhead in a single OFDM frame, by feeding back only for certain subcarriers, and interpolating over the others.
+Although the underlying manifold structure allows one to work with effective lower dimensions, most of the naive linear algorithms to predict and interpolate don't work well here, owing to the inherent non-linear structure of the manifold.
+Hence, combining these two properties, viz.
+the underlying manifold structure and temporal-frequency correlations, require generalization of such linear algorithms to the manifold under consideration, by exploiting the differential geometry of the manifold.
 Relevant past work in this direction has been \cite{Gupt1905:Predictive,6891198,6545375,5671092,Li2016,khaled2005quantized,krishnamachari2013geometry}.
@@
 % What is the way ahead
-Manifold based approaches have provided significant performance benefits, given that they work with effective lower dimensions.
+The manifold based approaches have provided significant performance benefits, given that they work with effective lower dimensions.
 However, these approaches are difficult to implement and require some familiarity with manifold geometry for a complete grasp.
@@
 Reservoir computing is a computational framework designed for sequential data processing. 
-Its design is inspired from several frameworks of recurrent neural networks \cite{jaeger2004harnessing}, including Liquid State Machines \cite{jalalvand2015real}.
-A reservoir computing system maps the inputs to spatio-temporal patterns in a higher dimensional dynamical reservoir state.
-The pattern analysis over these spatio-temporal patterns is performed by an output coupler that maps the higher dimensional reservoir state back to the output dimension that generally possesses lower dimensionality than the reservoir state.
+It's design takes inspiration from several frameworks of recurrent neural networks \cite{jaeger2004harnessing} including Liquid State Machines \cite{jalalvand2015real}. 
+A reservoir computing system maps the inputs to spatio-temporal patterns in higher dimensional dynamical reservoir state. 
+The pattern analysis over these spatio-temporal patterns is performed by an output coupler which maps the higher dimensional reservoir state back to the output dimension, generally having lower dimensionality than reservoir state.
 % A important characteristic of reservoir computing is that while training, the input weights and the weights within the reservoir are not kept fixed and the weights of the output coupler are updated.
-The key advantage of a reservoir computing based system is that it is extremely easy to train in comparison to its counterparts like Deep Neural Networks. CITATION NEEDED
-The input features can be efficiently learnt using a simple learning algorithm, since the reservoir non-linearly transforms sequential inputs into a higher dimensional reservoir state.
+The major advantage of reservoir computing system is that it’s extremely easy to train in comparison to its counterparts like Deep Neural Networks. 
+The input features can be efficiently read out by a simple learning algorithm because the reservoir non-linearly transforms sequential inputs into the higher dimensional reservoir state. 
 Reservoir computing has been successfully used to solve problems like spoken digit recognition \cite{verstraeten2005isolated}, handwritten digit image recognition \cite{jalalvand2015real} and climate prediction \cite{pathak2017using}.
@@
 \cite{jaeger2004harnessing} used reservoir computing framework to harness channel non-linearities in order for smarter channel equalization.
-\cite{mosleh2017brain,shafin2018realizing} utilized this technique for OFDM symbol detection while accounting for channel and power amplifier non-linearities.
-In our work, we utilize the reservoir computing framework to discover the underlying nonlinear relations between previously observed precoding matrices, in order to predict the next precoder in series.
-Upon vectorizing the precoding matrices, this becomes analogous to time series prediction algorithms, for which the reservoir computing framework has been known to work effectively \cite{mosleh2017brain}.
+\cite{mosleh2017brain,shafin2018realizing} utilized the same for OFDM symbol detection while tapping in channel, as well as power amplifier non-linearities.
+In our work, we utilize the reservoir computing framework to discover the underlying non-linear relations between previously observed precoding matrices, in order to predict the next precoder in series.
+Upon vectorizing the precoding matrices, this becomes analogous to time series prediction algorithms, which the reservoir computing framework has been known to work really well for \cite{mosleh2017brain}.
+
+%
 
@@
 has $N_T$ transmit antennas and $N_R$ receive antennas. 
-The available bandwidth is divided into $N$ subcarriers, so that, individually for each subcarrier, the channel can be assumed to be flat fading.
-The transmitter communicates an $N_s \times 1$ information data vector, where $N_s \leq \text{min}(N_T,N_R)$, and the $N_T \times N_s$ precoding matrix maps the $N_s \times 1$ information data vector onto the $N_T \times 1$ transmit vector emanating out of the transmitter.
+The available bandwidth is divided into $N$ subcarriers, so that individually for each subcarrier, the channel can be considered flat fading. 
+The transmitter communicates an $N_s \times 1$ information data vector, where
+$N_s \leq \text{min}(N_T,N_R)$, and the $N_T \times N_s$ precoding
+matrix maps the $N_s \times 1$ information data vector onto the $N_T \times 1$ transmit vector emanating out of the transmitter.
 
-In this discussion, we assume that $N_T > N_R$ and $N_s = N_R$.
-Consistent with notation in \cite{6891198,Gupt1905:Predictive}, the $N_R \times 1$ data stream received on the $i$-th subcarrier is denoted by:
+In this discussion, we assume that $N_T > N_R$ and $N_s = N_R$. Keeping notations consistent with \cite{6891198,Gupt1905:Predictive}, the $N_R \times 1$ data stream received is denoted by:
 \begin{equation}
@@
 \end{equation}
-$\tilde{\bU}_{i,t} \in \mathbb{C}^{N_T \times N_R}$ represents the precoding matrix, which is a function of quantized CSI fed back by the receiver, $\by_{i,t} \in \mathbb{C}^{N_R \times 1}$ is the received data stream, $\bx_{i,t} \in \mathbb{C}^{N_R \times 1}$ denotes the transmitted signal, $\bH_{i,t} \in \mathbb{C}^{N_T \times N_R}$ denotes the MIMO channel matrix and $\bw_{i,t}$ denotes the i.i.d.
+Here $\tilde{\bU}_{i,t} \in \mathbb{C}^{N_T \times N_R}$ denotes the precoding matrix which is a function of quantized CSI fed back by the receiver, $\by_{i,t} \in \mathbb{C}^{N_R \times 1}$ is the received data stream, $\bx_{i,t} \in \mathbb{C}^{N_R \times 1}$ denotes the transmitted signal, all at the $i$-th subcarrier of the $t$-th OFDM frame, $\bH_{i,t} \in \mathbb{C}^{N_T \times N_R}$ denotes the MIMO channel matrix and $\bw_{i,t}$ denotes the i.i.d.
 complex Gaussian noise with $\bw_{i,t} \sim \mathcal{N}_{\mathbb{C}}(0,N_0\bI_{N_R})$, $N_0$ being the noise variance.
@@
 
-If an infinite bit budget is available for quantization, the transmitter can directly use the matrices obtained from SVD of $\bH^{H}_{i,t}$ as the precoder $\tilde{\bU}_{i,t}$.
+Provided an infinite bit budget for quantization, the transmitter can directly use the matrices obtained from SVD of $\bH^{H}_{i,t}$ as precoder $\tilde{\bU}_{i,t}$.
 In particular, if $\text{SVD}(\bH_{i,t}) = \bU_{i,t},\Sigma_{i,t}, \bV_{i,t}$, then $\tilde{\bU}_{i,t} = \bU_{i,t}$.
@@
 
-Algorithms similar to the Lloyd codebook algorithm have been studied for quantizing $\text{St}(N_T,N_R)$ \cite{6678348}.
-However, this method treats precoders that are close to each other in time or frequency as independent, since it does not exploit any temporal/spectral correlations for quantization.
-Predictive quantization algorithms \cite{Gupt1905:Predictive,6891198} can be utilized to reduce the quantization error with time by utilizing the available correlations.
+Algorithms similar to Lloyd codebook algorithm have been studied for quantizing $\text{St}(N_T,N_R)$ \cite{6678348}.
+However, this method treats precoders close-by in time/frequency to each other as independent, since it doesn't exploit any temporal/spectral correlations for quantization. 
+Predictive quantization algorithms \cite{Gupt1905:Predictive,6891198} can be utilized to reduce the quantization error with time by tapping in available correlations.
 
-We now discuss the basic mathematical model that is central to predictive quantization algorithms for precoding matrices.
-Suppose that we predict the current precoding matrix based on the past $p$ observed precoding matrices, and hence $\tilde{\bU}_{i,t-p},\tilde{\bU}_{i,t-p+1},\ldots,\tilde{\bU}_{i,t-2},\tilde{\bU}_{i,t-1}$ have been fed back and available at the transmitter.
-By using a prediction algorithm  and by exploiting time correlations among precoders at $t-p,t-p+1,\ldots,t-2,t-1$ time instances, the transmitter can predict $\tilde{\bU}_{i,t}$ to be some $\bP_{i,t}=f_P(\tilde{\bU}_{i,t-p},\tilde{\bU}_{i,t-p+1},\ldots,\tilde{\bU}_{i,t-2},\tilde{\bU}_{i,t-1})$, where $f_P: \text{St}(N_T,N_R)^p \to \text{St}(N_T,N_R)$ is a prediction function.
-Now, since the transmitter already possesses a coarse estimate of $\tilde{\bU}_{i,t}$ given by $\bP_{i,t}$, the receiver just quantizes the local space of $\text{St}(N_T,N_R)$ nearby $\bP_{i,t}$ to facilitate the construction of a refined estimate of $\tilde{\bU}_{i,t}$ at the transmitter.
+We now discuss the basic mathematical model central to predictive quantization algorithms for precoding matrices.
+Consider that we predict based on past $p$ observed precoding matrices, and hence $\tilde{\bU}_{i,t-p},\tilde{\bU}_{i,t-p+1},\ldots,\tilde{\bU}_{i,t-2},\tilde{\bU}_{i,t-1}$ have been fed back and available at the transmitter.
+Using a prediction algorithm and exploiting time correlations among precoders at $t-p,t-p+1,\ldots,t-2,t-1$ time instances, the transmitter can predict $\tilde{\bU}_{i,t}$ to be some $\bP_{i,t}=f_P(\tilde{\bU}_{i,t-p},\tilde{\bU}_{i,t-p+1},\ldots,\tilde{\bU}_{i,t-2},\tilde{\bU}_{i,t-1})$, where $f_P: \text{St}(N_T,N_R)^p \to \text{St}(N_T,N_R)$ is a prediction function.
+Now since the transmitter already knows a coarse estimate of $\tilde{\bU}_{i,t}$ given by $\bP_{i,t}$, the receiver just quantizes the local space of $\text{St}(N_T,N_R)$ nearby $\bP_{i,t}$ to enable a refined estimate of $\tilde{\bU}_{i,t}$ at the transmitter.
 That is, the transmitter utilizes a quantization function $q_P:\text{St}(N_T,N_R) \times \mathbb{N} \to \text{St}(N_T,N_R)$, to obtain $\tilde{\bU}_{i,t} \gets q_P(\bP_{i,t},\text{fb}_{i,t})$, where $\text{fb}_{i,t} \in \{1,2\ldots2^{\mathcal{B}}\}$ is the feedback from the receiver for precoder at $i$-th subcarrier and $t$-th time instant, considering bit budget of $\mathcal{B}$ bits.
@@
 
-When using predictive quantization scheme, the quantization is performed on a smaller subspace when compared to the entire manifold in case of independent quantization.
-Therefore, the quantization error is substantially lower as well.
-However, quantization algorithms that are independent of these specific predictive structures are important for the initialization of these predictive quantization strategies.
-Observe that predictive quantization algorithms for SVD precoders are typically the higher dimensional analogs of the well known approaches to reduce quantization error using linear prediction codes (LPCs) and Delta PCM.
-In both LPCs and Delta PCM, quantization error can be reduced substantially using a linear predictor and quantizing the scalar difference between the predicted and observed value (innovation).
-Analogous to this, for $\text{St}(N_T,N_R)$ quantization error is reduced by quantizing a subspace around the predicted value that is much smaller than the entire manifold.
+Since using predictive quantization scheme, quantization is on a smaller subspace as compared to the entire manifold in case of independent quantization, the quantization error is substantially lower as well.
+However, that being said, independent quantization algorithms are important for initialization the predictive quantization strategies.
+Observe that, predictive quantization algorithms for SVD precoders are typically the higher dimensional analogs of the well known approaches to reduce quantization error using Linear Prediction Codes and Delta PCM.
+In both LPC and Delta PCM, quantization error is reduced substantially by using a linear predictor and quantizing the scalar difference between the predicted and observed value. 
+Analogous to this, for $\text{St}(N_T,N_R)$ quantization error is reduced by quantizing a smaller subspace around predicted value, compared to the entire manifold.
 
-In our work, we propose a reservoir computing based prediction framework that predicts the new precoders by utilizing  temporal correlations that are captured from past observed precoders ($f_P$).
-We reuse the $q_P$ algorithm from \cite{Gupt1905:Predictive,6891198}.
-However, by incorporating the $q_P$ in the prediction framework, as discussed in subsequent sections, the $f_P$ function also exploits correlations in $q_P$ (codebook locality correlations), along with temporal correlations.
-Previous work \cite{Gupt1905:Predictive,6891198} has considered $f_P$ and $q_P$ to be independent of each other.
-A detailed discussion on the reservoir computing based model for $f_P$ and $q_P$ is presented in Section \ref{section3}.
+In our work, we propose a reservoir computing based prediction framework, which predicts the new precoders by tapping the temporal correlations captured from past observed precoders ($f_P$). 
+We reuse the $q_P$ algorithm from \cite{Gupt1905:Predictive,6891198}, however, by incorporating the $q_P$ in the prediction framework, as discussed in subsequent sections, the $f_P$ function also exploits correlations in $q_P$ (codebook locality correlations), along with temporal correlations.
+Previous work \cite{Gupt1905:Predictive,6891198} have $f_P$ and $q_P$ independent of each other.
+The detailed discussion on reservoir computing based model for $f_P$ and $q_P$ is presented in Section \ref{section3}. 
 The proposed reservoir computing scheme is evaluated against the temporal predictive quantization scheme in \cite{6891198}, and the simulation results are discussed in Section \ref{section4}.
@@
 \label{setting}
-\noindent We compare the results of the proposed reservoir computing framework with the predictive quantization scheme presented in \cite{6891198}, which also captures the temporal correlations to enable reduced quantization error.
+\noindent We compare the results of the proposed reservoir computing framework with the predictive quantization scheme presented in \cite{6891198}, which captures the temporal correlations to enable reduced quantization error.
+We simulate both our predictive quantization algorithms and the one presented in \cite{6891198} for the IEEE Pedestrian-A channel, with $N_T=4$, $N_R=2$.
+We simulated our algorithms by using the IT++ library through the Python wrapper py-itpp \cite{ViditPy}, with the channels being generated using Jake’s model for realistic simulations.
+Although in both our work and \cite{6891198}, only temporal correlations are exploited, we compare the BER, quantization error and logsum rate results for the MIMO-OFDM setting with number of subcarriers $N=64$, and evenly spaced $8$ feedback subcarriers, indexed from 0, viz.
+$\{0,9,\ldots,63\}$ ($\{9k, k \in \{0,1,\ldots,7\}\}$).
+The precoding matrices at non fedback subcarriers ($i\neq\{9k\}$) are estimated via the Cayley Interpolation method presented in \cite{Gupt1905:Predictive}.
+Feedback is available for $i=\{9k\}$ subcarriers (i.e.
+transmitter obtains $\text{fb}_{\{9k\},t}$) for predictive quantization.
+The setting is visually illustrated in Fig.
+BER, quantization error results have been simulated for $f_DT_s=3.5\times10^{-4}$, whereas for achievable rate we compare results for $f_DT_s=10^{-4},10^{-2},10^{-1}$.
+\newpage
 \subsection{Quantization Error, BER and Achievable Rate Results}
+Considering mitigation against randomly appearing drastic events in wireless channels, like sudden interferences, and dynamic environment, only 100 channel evolutions are considered for the simulations.
 \label{res}

### 2019-04-17 main.py

@@ -112,8 +112,13 @@ for chan_inst in range(num_chans):
 
 pdb.set_trace()
 
-# np.save('./BER_Data2/cmp_qtiz_U_1_1000.npy',cmp_qtiz_U)
-# np.save('./BER_Data2/cmp_qtiz_err_1_1000.npy',cmp_qtiz_err)
-# np.save('./BER_Data2/fin_qt_U_1_1000.npy',fin_qt_U)
-# np.save('./BER_Data2/qtiz_err_1_1000.npy',qtiz_err)
-# np.save('./BER_Data2/qtiz_U_1_1000.npy',qtiz_U)
+# np.save('./BER_Data2/cmp_qtiz_U_10_100_norm'+str(norm)+'.npy',cmp_qtiz_U)
+# np.save('./BER_Data2/cmp_qtiz_err_10_100_norm'+str(norm)+'.npy',cmp_qtiz_err)
+# np.save('./BER_Data2/fin_qt_U_10_100_norm'+str(norm)+'.npy',fin_qt_U)
+# np.save('./BER_Data2/qtiz_err_10_100_norm'+str(norm)+'.npy',qtiz_err)
+# np.save('./BER_Data2/qtiz_U_10_100_norm'+str(norm)+'.npy',qtiz_U)
+
+# import matplotlib.pyplot as plt
+# plt.plot(np.mean(np.mean(qtiz_err,axis=0),axis=1))
+# plt.plot(np.mean(np.mean(cmp_qtiz_err,axis=0),axis=1))
+# plt.show()

### 2019-04-18 paper/main.tex
Adding results

@@
 \end{equation}
-
+\begin{figure*}[ht]
+\centering
+\includegraphics[width=0.8\textwidth]{images/system.pdf}
+\label{res_overview}
+\caption{An overview of the reservoir computing framework proposed for predictive quantization of $\bu_{i,t}$}
+\end{figure*}
 This completes the forward prediction algorithm to obtain $\bP_{i,t}$ using just one past observed $\bU_{i,t-1}$. That is,
@@
 \end{equation}
-\begin{figure*}[ht]
-\centering
-\includegraphics[width=0.8\textwidth]{images/system.pdf}
-\label{res_overview}
-\caption{An overview of the reservoir computing framework proposed for predictive quantization of $\bu_{i,t}$}
-\end{figure*}
+
 $\text{fb}_{i,t}$ is also used to update the spread of the codebooks $T^{\mathcal{C}}_p,T^{\mathcal{C}}_m$.
@@
 BER, quantization error results have been simulated for $f_DT_s=3.5\times10^{-4}$, whereas for achievable rate we compare results for $f_DT_s=10^{-4},10^{-2},10^{-1}$.
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.5\textwidth]{images/table.pdf}
+\label{table}
+\caption{The transmitter obtains feedback for $\{0,9,\ldots,63\}$ ($\{9k, k \in \{0,1,\ldots,7\}\}$ subcarriers, and uses the $\tilde{\bU}_{i,t}$ of the previous time instance with $f_P,q_P$ (\eqref{fpqp}) to obtain $\tilde{\bU}_{i,t}$, illustrated in the figure via cyan arrows.
+For each time instant, the transmitter uses the Cayley Exponential Lifting map to interpolate $\tilde{\bU}_{i,t}$ at $i\neq\{9k\}$ subcarriers}
+\end{figure}
 \newpage
 \subsection{Quantization Error, BER and Achievable Rate Results}
+\label{res}
 Considering mitigation against randomly appearing drastic events in wireless channels, like sudden interferences, and dynamic environment, only 100 channel evolutions are considered for the simulations.
-\label{res}
+Averaging is done over 10 independent channel realizations, to ensure that the simulation results hold in general for the chosen IEEE Pedestrian A channel profile.
+Hence, the quantization error, BER and achievable rate results are simulated for 1000 channel instances, with 100 channel evolutions of 10 independent channel realizations.
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.5\textwidth]{images/qtizErr.pdf}
+\caption{Quantization Error in terms of chordal distance to the actual precoder $\bU_{\{9k\},t}$ observed at the receiver, from the quantized estimate $\tilde{\bU}_{\{9k\},t}$ at the transmitter, averaged over 8 feedback subcarriers ($\{9k, k \in \{0,1,\ldots,7\}\}$) and 10 independent channel realizations ($f_DT_s=3.5\times10^{-4}$)}
+\label{qtiz_err}
+\end{figure}
+
+From Fig.
+\ref{qtiz_err} it is evident that the reservoir computing based predictive quantizer is able to reduce the quantization error below what was obtained from the existing temporal based predictive quantizer in \cite{6891198}.
+In addition, the quantization error is much more smoother, which can be explained from the fact that the reservoir computing approach optimizes, $\mathcal{O}_t$ which captures the long term dynamics of the channel and hence, is able to correct for jittery variations.
+
+We simulate the (uncoded QPSK) BER performance for precoders obtained after interpolation ($\tilde{\bU}_{i\neq\{9k\},t}$) and quantization ($\tilde{\bU}_{\{9k\},t}$), for all the 63 subcarriers.
+Observe from Fig.
+\ref{BER} that reservoir computing framework is able to achieve substantial imporvements in $\text{E}_\text{b}\text{N}_0$ levels at $\text{BER}\leq 10^{-3}$.
+Particularly, observe, for $\text{BER}=10^{-4}$ we observe around 5dB improvement.
+Also, notice the substanial improvement which both the predictive quantization schemes offer from the independent quantization scheme with Lloyd codebook for precoders \cite{6678348}, using the same number of bits.
+
+For simulating the achievable rate for the point-to-point MIMO system considered, we quantize the sigma values ($\Sigma_{i,t}$ obtained from SVD of $\bH_{i,t}$) using a 2 bit vector quantizer ($k$-means), and feed them back to the transmitter for fed back subcarriers ($\{9k, k \in \{0,1,\ldots,7\}\}$).
+For the non-fed back subcarriers, they are interpolated via nai\"ve linear interpolation method as in \cite{Gupt1905:Predictive}.
+Observe from Fig.
+\ref{achievrate} that the reservoir computing framework offers signicant improvement in achievable rate for $f_DT_s=10^{-4}$.
+Since the temporal variations for $f_DT_s=10^{-2}, 10^{-1}$ are higher, the resrvoir computing framework has to learn a faster-varying function, and hence the degradation in performance.
+However, it still matches the performance of the predictive quantizer in \cite{6891198} for $f_DT_s=10^{-2}$ and performs slightly better for $f_DT_s=10^{-1}$.
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.5\textwidth]{images/BER_res.pdf}
+\caption{BER results after obtaining non fed back $\tilde{\bU}_{i\neq\{9k\},t}$ from $\tilde{\bU}_{\{9k\},t}$ via Cayley interpolation \cite{Gupt1905:Predictive}, averaged over 10 independent channel realizations, 100 channel evolutions each ($f_DT_s=3.5\times10^{-4}$)}
+\label{BER}
+\end{figure}
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.5\textwidth]{images/achievRate.pdf}
+\caption{Achievable Rate results for the two predictive quantization methods considered.
+The results are presented as a perecentage of the ideal acheivable rate obtained when the transmitter has the accurate (unquantized) and non-interpolated estimates of $\bU_{i,t}$ for each subcarrier and each time instant.
+The results have been averaged over 10 independent channel realizations, 100 channel evolutions each, for each $f_DT_s$}
+\label{achievrate}
+\end{figure}
 %Qtisn error with 1000 chan evols
@@
 \label{section5}
+In this paper, we presented a reservoir computing framework to exploit temporal correlations for predictive quantization of SVD based precoders.
+The simulations reveal reduced quantization error, improved BER performance, and higher achievable rate from the proposed framework.
+This motivates further study into the framework as well, and future lines of work here would be a generalization of the framework to capture frequency correlations as well for predictive quantization, and a detailed analysis of impact on performance caused by choice of certain reservoir parameters like $\bA,\text{tanh}(\cdot)$, number of dimensions of the resrvoir state.
 

### 2019-04-18 paper/main.tex
Minor fixes

@@
 \begin{equation}
-\mathcal{O}_t=\sum_{s=1}^{t}\frac{1}{\lambda^{t-s}}||\bp_{i,t}-\tilde{\bu}_{i,t}||^2=\sum_{s=1}^{t}\frac{1}{\lambda^{t-s}}||W_{i,t}^{\text{out}}\br_{i,t}-\tilde{\bu}_{i,t}||^2
+\mathcal{O}_t=\sum_{s=1}^{t}\frac{1}{\lambda^{t-s}}||\bp_{i,t}-\tilde{\bu}_{i,t}||^2=\sum_{s=1}^{t}\frac{1}{\lambda^{t-s}}||\bW_{i,t}^{\text{out}}\br_{i,t}-\tilde{\bu}_{i,t}||^2
 \end{equation}
@@
 \begin{equation}
-W_{i,t}^{\text{out}}\gets\text{argmin}_{W_{i,t}^{\text{out}}}(\mathcal{O}_t=\sum_{s=1}^{t}\frac{1}{\lambda^{t-s}}||W_{i,t}^{\text{out}}\br_{i,t}-\tilde{\bu}_{i,t}||^2)
+\bW_{i,t}^{\text{out}}\gets\text{argmin}_{\bW_{i,t}^{\text{out}}}(\mathcal{O}_t=\sum_{s=1}^{t}\frac{1}{\lambda^{t-s}}||\bW_{i,t}^{\text{out}}\br_{i,t}-\tilde{\bu}_{i,t}||^2)
 \end{equation}
-Computing the gradients $\frac{\partial \mathcal{O}_t}{\partial W_{i,t}^{\text{out}}}$ and setting it to null gives,
+Computing the gradients $\frac{\partial \mathcal{O}_t}{\partial \bW_{i,t}^{\text{out}}}$ and setting it to null gives,
 \begin{equation}
-W_{i,t}^{\text{out}}=\frac{\sum_{s=1}^{t}\frac{1}{\lambda^{t-s}}\texttt{outer}(\tilde{\bu}_{i,s},\br_{i,s})}{\sum_{s=1}^{t}\frac{1}{\lambda^{t-s}}||\br_{i,s}||^2}
+\bW_{i,t}^{\text{out}}=\frac{\sum_{s=1}^{t}\frac{1}{\lambda^{t-s}}\texttt{outer}(\tilde{\bu}_{i,s},\br_{i,s})}{\sum_{s=1}^{t}\frac{1}{\lambda^{t-s}}||\br_{i,s}||^2}
 \end{equation}
 where $\texttt{outer}(\bx,\by)$ is the outer product between $N_x$ dimensional vector $\bx$ and $N_y$ dimensional vector $\by$ to give a $N_x\times N_y$ matrix.
-Let $\sum_{s=1}^{t}\frac{1}{\lambda^{t-s}}\texttt{outer}(\tilde{\bu}_{i,s},\br_{i,s})$ be $\text{num}_{i,t}$ and $\sum_{s=1}^{t}\frac{1}{\lambda^{t-s}}||\br_{i,s}||^2$ be $\text{den}_{i,t}$, with $W_{i,t}^{\text{out}}=\frac{\text{num}_{i,t}}{\text{den}_{i,t}}$.
+Let $\sum_{s=1}^{t}\frac{1}{\lambda^{t-s}}\texttt{outer}(\tilde{\bu}_{i,s},\br_{i,s})$ be $\text{num}_{i,t}$ and $\sum_{s=1}^{t}\frac{1}{\lambda^{t-s}}||\br_{i,s}||^2$ be $\text{den}_{i,t}$, with $\bW_{i,t}^{\text{out}}=\frac{\text{num}_{i,t}}{\text{den}_{i,t}}$.
 Observe that,
 \begin{equation}
-W_{i,t}^{\text{out}}=\frac{\frac{\text{num}_{i,t-1}}{\lambda}+\texttt{outer}(\tilde{\bu}_{i,t},\br_{i,t})}{\frac{\text{den}_{i,t-1}}{\lambda}+||\br_{i,t}||^2}
+\bW_{i,t}^{\text{out}}=\frac{\frac{\text{num}_{i,t-1}}{\lambda}+\texttt{outer}(\tilde{\bu}_{i,t},\br_{i,t})}{\frac{\text{den}_{i,t-1}}{\lambda}+||\br_{i,t}||^2}
 \label{wout_upd}
@@
 \eqref{wout_upd} makes training of the reservoir easy to implement, and of low complexity as well.
-We just need to store the matrix $\text{num}_{i,t-1}$, a number $\text{den}_{i,t-1}$, and using the current reservoir state $\br_{i,t}$ and obtained $\tilde{\bu}_{i,t}$ from \eqref{fpqp}, one can calculate $W_{i,t}^{\text{out}}$ for forward calculation of $\tilde{\bu}_{i,t+1}$.
+We just need to store the matrix $\text{num}_{i,t-1}$, a number $\text{den}_{i,t-1}$, and using the current reservoir state $\br_{i,t}$ and obtained $\tilde{\bu}_{i,t}$ from \eqref{fpqp}, one can calculate $\bW_{i,t}^{\text{out}}$ for forward calculation of $\tilde{\bu}_{i,t+1}$.
 This completes our technical discussion for the complete reservoir computing based framework for predictive quantization illustrated in Fig. %Ref Fig.
@@
 \begin{equation*}
-\highlight{W_{i,t}^{\text{out}}}=\frac{\frac{\text{num}_{i,t-1}}{\lambda}+\texttt{outer}(\highlight{q_P}(f_P(\tilde{\bu}_{i,t-1}),\text{fb}_{i,t}),\br_{i,t})}{\frac{\text{den}_{i,t-1}}{\lambda}+||\br_{i,t}||^2}
+\highlight{\bW_{i,t}^{\text{out}}}=\frac{\frac{\text{num}_{i,t-1}}{\lambda}+\texttt{outer}(\highlight{q_P}(f_P(\tilde{\bu}_{i,t-1}),\text{fb}_{i,t}),\br_{i,t})}{\frac{\text{den}_{i,t-1}}{\lambda}+||\br_{i,t}||^2}
 \end{equation*}
@@
 %Better framing possible
-This is done by optimizing $W_{i,t}^{\text{out}}$ such that the prediction output to be as close to the output from $q_P$ (Objective function $\mathcal{O}_t$).
-The updated $W_{i,t}^{\text{out}}$ is then used in forward pass to predict $\bP_{i,t+1}$, which is hopefully closer to $\tilde{\bU}_{i,t+1}$ than $\bP_{i,t}$ was to $\tilde{\bU}_{i,t}$ due to optimization of $\mathcal{O}_t$.
+This is done by optimizing $\bW_{i,t}^{\text{out}}$ such that the prediction output to be as close to the output from $q_P$ (Objective function $\mathcal{O}_t$).
+The updated $\bW_{i,t}^{\text{out}}$ is then used in forward pass to predict $\bP_{i,t+1}$, which is hopefully closer to $\tilde{\bU}_{i,t+1}$ than $\bP_{i,t}$ was to $\tilde{\bU}_{i,t}$ due to optimization of $\mathcal{O}_t$.
 

### 2019-04-18 paper/main.tex
6 page draft

@@
 \usepackage{xcolor}
-
+\setlength{\belowcaptionskip}{-10pt}
 \newcommand{\highlight}[1]{%
@@
 
-Precoding matrices obtained from the SVD of the wireless MIMO channel matrix can be utilized at the transmitter for optimum power allocation and lower BER\footnote{Bit Error Rate} transmissions.
+Precoding matrices obtained from the SVD of the wireless MIMO channel matrix can be utilized at the transmitter for optimum power allocation and lower BER transmissions.
 However, a key step that enables this improved performance is feedback of these precoders to the transmitter from the receiver.
@@
 \subsection{Vectorizing matrices in Stiefel Manifold}
+\label{vectorize}
 The reservoir computing framework has inputs and outputs as vectors, and thus, it is necessary to convert the precoder matrices to vectors.
@@
 \subsection{Forward Prediction $f_P$ function}
-The vector representation of semi-unitary matrices allows us to proceed with the discussion on reservoir computing framework for predictive quantization of SVD precoders.
-Consider the reservoir computing framework shown in Fig. TODO %Ref Fig. Reservoir Pic
+\noindent The vector representation of semi-unitary matrices allows us to proceed with the discussion on reservoir computing framework for predictive quantization of SVD precoders.
+Consider the reservoir computing framework shown in Fig. \ref{res_overview} %Ref Fig. Reservoir Pic
 
@@
 \includegraphics[width=0.8\textwidth]{images/system.pdf}
+\caption{An overview of the reservoir computing framework proposed for predictive quantization of $\bu_{i,t}$}
 \label{res_overview}
-\caption{An overview of the reservoir computing framework proposed for predictive quantization of $\bu_{i,t}$}
 \end{figure*}
@@
 \bW_{i,t}^{\text{out}}=\frac{\sum_{s=1}^{t}\frac{1}{\lambda^{t-s}}\texttt{outer}(\tilde{\bu}_{i,s},\br_{i,s})}{\sum_{s=1}^{t}\frac{1}{\lambda^{t-s}}||\br_{i,s}||^2}
+\label{backpass}
 \end{equation}
@@
 
-To conclude this section, now summarize and touch upon the novel points of the reservoir computing based framework proposed for predictive quantization of SVD precoding.
+To conclude this section, we will now summarize and touch upon the novel points of the reservoir computing based framework proposed for predictive quantization of SVD precoding.
 The first key advantage of the proposed framework, over the past work in this line \cite{Gupt1905:Predictive,6891198,6545375} is that the prediction function and quantization function are not independent of each other.
@@
 \label{setting}
-\noindent We compare the results of the proposed reservoir computing framework with the predictive quantization scheme presented in \cite{6891198}, which captures the temporal correlations to enable reduced quantization error.
-We simulate both our predictive quantization algorithms and the one presented in \cite{6891198} for the IEEE Pedestrian-A channel, with $N_T=4$, $N_R=2$.
+\noindent We simulate both our predictive quantization algorithms and the one presented in \cite{6891198} for the IEEE Pedestrian-A channel, with $N_T=4$, $N_R=2$.
 We simulated our algorithms by using the IT++ library through the Python wrapper py-itpp \cite{ViditPy}, with the channels being generated using Jake’s model for realistic simulations.
@@
 The setting is visually illustrated in Fig.
-BER, quantization error results have been simulated for $f_DT_s=3.5\times10^{-4}$, whereas for achievable rate we compare results for $f_DT_s=10^{-4},10^{-2},10^{-1}$.
-\begin{figure}[h]
+\ref{table}.
+A 6 bit codebook generated via Lloyd codebook algorithm for the Stiefel Manifold in \cite{6678348} is used to feedback $\tilde{\bU}_{\{9k\},0}$ and differential quantization (i.e.
+$\bP_{i,t}=\tilde{\bU}_{i,t-1}$) is used for 10 time instances to provide provide the initial training data for the reservoir and for overcoming initial transient response of the reservoir discussed in \cite{mosleh2017brain}.
+A 6 bit base codebook is used for the quantization function $q_P$, generated via vector quantization via $k$-means over a tangent list, comprising of actual tangents from the predicted precoder to the actual precoder obtained from SVD of channel matrix, to guarantee isotropic codewords \cite{Gupt1905:Predictive}.
+
+For prediction of each of the $8$ fed-back subcarriers, we consider $8$ separate reservoirs, each of them evolved separately, with $i\in\{9k, k \in \{0,1,\ldots,7\}\}$ in both the forward pass prediction and quantization ($f_P,q_P$) \eqref{fpqp} and backward pass to update $\bW_{i,t}^{\text{out}}$ \eqref{backpass}.
+Unlike \cite{Gupt1905:Predictive}, we don't exploit frequency correlations for predictive quantization, and the $8$ reservoirs for prediction of $8$ fed-back subcarriers are kept independent of each other.
+All these 8 resrvoirs are initialized with $\bA_{i\in\{9k\}}$ being an Erdos-Renyi\" graph, with probability of edge connections being $0.2$, $\lambda=2$, $\bW^{\text{out/in}}_{i\in\{9k\},0}$ being randomly assigned, $D_{\text{in}}=D_{\text{out}}=14$ (vectorized representation of $4\times2$ semi-unitary matrix, Section \ref{vectorize}) and $D_{\text{resv}}=60$.
+
+\begin{figure}
 \centering
 \includegraphics[width=0.5\textwidth]{images/table.pdf}
+\caption{The transmitter obtains feedback for $\{0,9,\ldots,63\}$ ($\{9k, k \in \{0,1,\ldots,7\}\}$ subcarriers, and uses $\tilde{\bU}_{i,t-1}$, alongwith $f_P,q_P$ \eqref{fpqp} to obtain $\tilde{\bU}_{i,t}$, illustrated in the figure via cyan arrows.
+For each time instant, the transmitter uses the Cayley mehtod to interpolate $\tilde{\bU}_{i,t}$ at $i\neq\{9k\}$ subcarriers}
 \label{table}
-\caption{The transmitter obtains feedback for $\{0,9,\ldots,63\}$ ($\{9k, k \in \{0,1,\ldots,7\}\}$ subcarriers, and uses the $\tilde{\bU}_{i,t}$ of the previous time instance with $f_P,q_P$ (\eqref{fpqp}) to obtain $\tilde{\bU}_{i,t}$, illustrated in the figure via cyan arrows.
-For each time instant, the transmitter uses the Cayley Exponential Lifting map to interpolate $\tilde{\bU}_{i,t}$ at $i\neq\{9k\}$ subcarriers}
 \end{figure}
-\newpage
+
 \subsection{Quantization Error, BER and Achievable Rate Results}
-\label{res}
+\label{res}{}
 Considering mitigation against randomly appearing drastic events in wireless channels, like sudden interferences, and dynamic environment, only 100 channel evolutions are considered for the simulations.
@@
 Hence, the quantization error, BER and achievable rate results are simulated for 1000 channel instances, with 100 channel evolutions of 10 independent channel realizations.
+
 \begin{figure}[h]
@@
 The simulations reveal reduced quantization error, improved BER performance, and higher achievable rate from the proposed framework.
-This motivates further study into the framework as well, and future lines of work here would be a generalization of the framework to capture frequency correlations as well for predictive quantization, and a detailed analysis of impact on performance caused by choice of certain reservoir parameters like $\bA,\text{tanh}(\cdot)$, number of dimensions of the resrvoir state.
+This motivates further study into the framework as well, and future lines of work here would be a generalization of the framework to capture frequency correlations as well for predictive quantization, and a detailed analysis of impact on performance caused by choice of certain reservoir parameters like $\bA,\text{tanh}(\cdot)$, number of dimensions of the reservoir state.
 

### 2019-04-19 paper/main.tex
Minor changes in abstract

@@
 
-Precoding matrices obtained from the SVD of the wireless MIMO channel matrix can be utilized at the transmitter for optimum power allocation and lower BER transmissions.
-However, a key step that enables this improved performance is feedback of these precoders to the transmitter from the receiver.
-Since bit budget for such channel state information (CSI) feedback is limited, precoders need to be quantized effectively using with very few bits.
-For a $N_T \times N_R$ MIMO system, this amounts to quantizing a $N_T \times N_R$ complex valued matrix.
-This can be simplified by using the underlying manifold structure, and temporal/frequency correlations in the precoders.
-In this work, we introduce a reservoir computing based framework for prediction of the new precoders by observing pastprecoders and utilizing temporal correlations.
-Past methods have primarily exploited the nonlinear geometry endowed by the manifold structure to for precoder interpolation and prediction.
+Precoding matrices obtained from SVD of the MIMO channel matrix (estimated at the receiver) can be utilized at the transmitter for optimum power allocation and lower BER transmissions. 
+A key step enabling this improved performance is the feedback of these precoders to the transmitter from the receiver.
+Since the bit budget for such CSI\footnote{Channel State Info.} feedback is limited, these precoders need to be quantized effectively using just a few bits.
+For a $N_T \times N_R$\footnote{$N_T(R)$: Number of Transmit (Receive) Antennas} MIMO system, this amounts to quantizing a $N_T \times N_R$ complex valued matrix.
+This task is aided by the presence of an underlying manifold structure and temporal/frequency correlations in the precoders. 
+Predictive quantization methods reduce the quantization error by predicting new precoders based on observation of past precoders, and then quantizing the step required to obtain the actual precoder from the predicted value.
+In this work, we introduce a reservoir computing based framework for predictive quantization by exploiting temporal correlations. 
+Past methods have primarily exploited the nonlinear geometry endowed by the manifold structure to for precoder prediction.
 Here, this non-linear relationship is captured using the dynamical reservoir state as part of the training process of the reservoir.
 Simulations reveal that this approach produces reduced quantization error, thereby resulting in lower BER as well as improved achievable rates when compared to earlier work.
-
 \end{abstract}

### 2019-04-19 paper/main.tex
Changes in Introduction

@@
 This task is aided by the presence of an underlying manifold structure and temporal/frequency correlations in the precoders. 
-Predictive quantization methods reduce the quantization error by predicting new precoders based on observation of past precoders, and then quantizing the step required to obtain the actual precoder from the predicted value.
+Predictive quantization methods reduce the quantization error by predicting new precoders based on observation of past precoders, and then quantizing the information required to obtain the actual precoder from the predicted value.
 In this work, we introduce a reservoir computing based framework for predictive quantization by exploiting temporal correlations. 
@@
 The MIMO channel matrix is estimated at the receiver, and the transmitter has no a-priori knowledge of the same.
-Therefore, to obtain the said benefits of SVD precoders, the receiver needs to quantize and feed back the precoders it estimates from the SVD of the MIMO channel matrix.
+Therefore, to obtain the said benefits of SVD precoders, the receiver needs to quantize and feed back the precoders it obtains from the SVD of the MIMO channel matrix.
 To honour the bit budget imposed by limited feedback CSI schemes, the quantization needs to be performed using very few bits.
@@
 % Elaborate on each point (what people have done before) lecunnas
-Past work has used two inherent properties of the precoders to enable effective low-rate precoder feedback.
-First, the precoders are not actually $2\times N_T\times N_R$ dimensional entities, and these have an underlying manifold structure that allows one to work with lower dimensions if one performs operations over the manifold directly.
+Past work has used two inherent properties of the precoders to enable effective quantization of these precoders, with just a few bits.
+First, the precoders are not actually $2\times N_T\times N_R$ dimensional entities, and these have an underlying manifold structure that allows one to work with lower dimensions, if one performs operations over the manifold directly.
 Second, these precoders are correlated in both time and frequency.
-Capturing temporal correlations allows the use off predictive quantization algorithms that improvement of the quantization error with time by effectively utilizing all information.
+Capturing the available correlations allow for predictive quantization algorithms, which enable improvement of the quantization error with time.
+This improvement is obtained because exploiting the available correlations from past fed back precoders allow one to just quantize the extra information required on top of the past available temporal-frequency information, instead of the new precoder information in the entirety.
 Exploiting frequency correlations permits the use of interpolation algorithms, which in turn reduce the feedback overhead in a single OFDM frame, by feeding back CSI information only for certain subcarriers, and interpolating over the others.
-Despite the existence of the underlying manifold structure that possesses effective lower dimensions, most of the na{\"i}ve algorithms that predict and interpolate are limited in their effectiveness, owing to the inherent non-linear structure of the manifold.
-Thus, combining these two properties, viz.
+Thus, combining these two inherent properties, viz.
 the underlying manifold structure and temporal-frequency correlations, requires a generalization of such linear algorithms to the manifold under consideration, by exploiting the differential geometry of the manifold.
@@
 % What is the way ahead
-Manifold based approaches have provided significant performance benefits, given that they work with effective lower dimensions.
+Manifold based approaches for predictive quantization have provided significant performance benefits, given that they work with the effective lower dimensions while framing the manifold operations to predict and quantize.
 However, these approaches are difficult to implement and require some familiarity with manifold geometry for a complete grasp.
 In this paper, we propose a reservoir computing based predictive quantizer to exploit the temporal correlations effectively.
-The proposed scheme offers a cleaner solution to the predictive quantization problem, which brings about both ease of implementability, and improved performance as well, when compared to \cite{6891198}, which proposed a manifold based method of predictive quantization.
+The proposed scheme offers a cleaner solution to the predictive quantization problem, which brings about both ease of implementability, and improved performance as well, when compared to \cite{6891198}, which proposed a manifold based method of predictive quantization by exploiting temporal correlations.
 
 % How to we do this
+\textcolor{blue}{
 Reservoir computing is a computational framework designed for sequential data processing.
@@
 The input features can be efficiently learnt using a simple learning algorithm, since the reservoir non-linearly transforms sequential inputs into a higher dimensional reservoir state.
-Reservoir computing has been successfully used to solve problems like spoken digit recognition \cite{verstraeten2005isolated}, handwritten digit image recognition \cite{jalalvand2015real} and climate prediction \cite{pathak2017using}.
+Reservoir computing has been successfully used to solve problems like spoken digit recognition \cite{verstraeten2005isolated}, handwritten digit image recognition \cite{jalalvand2015real} and climate prediction \cite{pathak2017using}.}
 % Owing to the versatility of reservoir computing, it can deal with any sequential data in principle and hence further expansion of its application fields is widely expected.
 
-Reservoir computing has also been applied to solve problems in the domain of wireless communications \cite{jaeger2004harnessing,mosleh2017brain,shafin2018realizing}.
-\cite{jaeger2004harnessing} used reservoir computing framework to harness channel non-linearities in order for smarter channel equalization.
-\cite{mosleh2017brain,shafin2018realizing} utilized this technique for OFDM symbol detection while accounting for channel and power amplifier non-linearities.
-In our work, we utilize the reservoir computing framework to discover the underlying nonlinear relations between previously observed precoding matrices, in order to predict the next precoder in series.
-Upon vectorizing the precoding matrices, this becomes analogous to time series prediction algorithms, for which the reservoir computing framework has been known to work effectively \cite{mosleh2017brain}.
+\noindent Reservoir computing has also been applied to solve problems in the domain of wireless communications \cite{jaeger2004harnessing,mosleh2017brain,shafin2018realizing}.
+\cite{jaeger2004harnessing} used reservoir computing framework to harness channel non-linearities for smarter channel equalization.
+\cite{mosleh2017brain,shafin2018realizing} utilized the framework for OFDM symbol detection while accounting for channel and power amplifier non-linearities.
+In our work, we utilize the reservoir computing framework to discover the underlying nonlinear relations between previously observed precoders, in order to predict the precoder at next time instant.
+This becomes analogous to time series prediction algorithms, for which the reservoir computing framework has been known to work effectively \cite{mosleh2017brain}.
 

### 2019-04-19 paper/main.tex
Changes in System Model

@@
 \label{section2}
-\noindent We consider a point-to-point MIMO-OFDM wireless system that
-has $N_T$ transmit antennas and $N_R$ receive antennas.
+\noindent We consider a point-to-point $N_T\times N_R$ MIMO-OFDM wireless system.
 The available bandwidth is divided into $N$ subcarriers, so that, individually for each subcarrier, the channel can be assumed to be flat fading.
-The transmitter communicates an $N_s \times 1$ information data vector, where $N_s \leq \text{min}(N_T,N_R)$, and the $N_T \times N_s$ precoding matrix maps the $N_s \times 1$ information data vector onto the $N_T \times 1$ transmit vector emanating out of the transmitter.
-
 In this discussion, we assume that $N_T > N_R$ and $N_s = N_R$.
-Consistent with notation in \cite{6891198,Gupt1905:Predictive}, the $N_R \times 1$ data stream received on the $i$-th subcarrier is denoted by:
+Consistent with notation in \cite{6891198,Gupt1905:Predictive}, the data stream received on the $i$-th subcarrier is denoted by:
 \begin{equation}
@@
 \end{equation}
-$\tilde{\bU}_{i,t} \in \mathbb{C}^{N_T \times N_R}$ represents the precoding matrix, which is a function of quantized CSI fed back by the receiver, $\by_{i,t} \in \mathbb{C}^{N_R \times 1}$ is the received data stream, $\bx_{i,t} \in \mathbb{C}^{N_R \times 1}$ denotes the transmitted signal, $\bH_{i,t} \in \mathbb{C}^{N_T \times N_R}$ denotes the MIMO channel matrix and $\bw_{i,t}$ denotes the i.i.d.
+$\tilde{\bU}_{i,t} \in \mathbb{C}^{N_T \times N_R}$ represents the precoding matrix, which is a function of quantized CSI fed back by the receiver, $\by_{i,t} \in \mathbb{C}^{N_R \times 1}$ is the received data stream, $\bx_{i,t} \in \mathbb{C}^{N_T \times 1}$ denotes the transmitted signal, $\bH_{i,t} \in \mathbb{C}^{N_T \times N_R}$ denotes the MIMO channel matrix and $\bw_{i,t}$ denotes the i.i.d.
 complex Gaussian noise with $\bw_{i,t} \sim \mathcal{N}_{\mathbb{C}}(0,N_0\bI_{N_R})$, $N_0$ being the noise variance.
@@
 
+In this work, we assume that $\bH^{H}_{i,t}$ is estimated error-free at the receiver.
 If an infinite bit budget is available for quantization, the transmitter can directly use the matrices obtained from SVD of $\bH^{H}_{i,t}$ as the precoder $\tilde{\bU}_{i,t}$. 
@@
 Notice that matrices $\bU_{i,t}$ reside on the Stiefel manifold $\text{St}(N_T,N_R)$, since the columns of $\bU_{i,t}$ form a set of $N_R$ orthogonal vectors in $N_T$ dimensions \cite{Gupt1905:Predictive,6891198}.
-Given practical limitations, only limited feedback is available from the receiver, and the objective is to find a `reasonable' estimate of $\bU_{i,t}$, given by $\tilde{\bU}_{i,t}$ using the available feedback bits.
+Given practical limitations, only limited feedback is available from the receiver, and the objective is to find a `reasonable' estimate of $\bU_{i,t}$, given by $\tilde{\bU}_{i,t}$, using the available feedback bits.
 
-Algorithms similar to the Lloyd codebook algorithm have been studied for quantizing $\text{St}(N_T,N_R)$ \cite{6678348}.
-However, this method treats precoders that are close to each other in time or frequency as independent, since it does not exploit any temporal/spectral correlations for quantization.
-Predictive quantization algorithms \cite{Gupt1905:Predictive,6891198} can be utilized to reduce the quantization error with time by utilizing the available correlations.
-
+Independent quantization algorithms analogous to the Lloyd codebook algorithm have been studied for quantizing $\text{St}(N_T,N_R)$ \cite{6678348}.
+However, this method treats precoders that are close to each other in time/frequency as independent, since it does not exploit any temporal/spectral correlations for quantization.
+Predictive quantization algorithms \cite{Gupt1905:Predictive,6891198} can be utilized to reduce the quantization error by utilizing the available correlations.
 We now discuss the basic mathematical model that is central to predictive quantization algorithms for precoding matrices.
 Suppose that we predict the current precoding matrix based on the past $p$ observed precoding matrices, and hence $\tilde{\bU}_{i,t-p},\tilde{\bU}_{i,t-p+1},\ldots,\tilde{\bU}_{i,t-2},\tilde{\bU}_{i,t-1}$ have been fed back and available at the transmitter.
-By using a prediction algorithm  and by exploiting time correlations among precoders at $t-p,t-p+1,\ldots,t-2,t-1$ time instances, the transmitter can predict $\tilde{\bU}_{i,t}$ to be some $\bP_{i,t}=f_P(\tilde{\bU}_{i,t-p},\tilde{\bU}_{i,t-p+1},\ldots,\tilde{\bU}_{i,t-2},\tilde{\bU}_{i,t-1})$, where $f_P: \text{St}(N_T,N_R)^p \to \text{St}(N_T,N_R)$ is a prediction function.
-Now, since the transmitter already possesses a coarse estimate of $\tilde{\bU}_{i,t}$ given by $\bP_{i,t}$, the receiver just quantizes the local space of $\text{St}(N_T,N_R)$ nearby $\bP_{i,t}$ to facilitate the construction of a refined estimate of $\tilde{\bU}_{i,t}$ at the transmitter.
+By using a prediction algorithm and by exploiting time correlations among precoders at $t-p,t-p+1,\ldots,t-2,t-1$ time instances, the transmitter can predict $\bU_{i,t}$ to be some $\bP_{i,t}=f_P(\tilde{\bU}_{i,t-p},\tilde{\bU}_{i,t-p+1},\ldots,\tilde{\bU}_{i,t-2},\tilde{\bU}_{i,t-1})$, where $f_P: \text{St}(N_T,N_R)^p \to \text{St}(N_T,N_R)$ is a prediction function.
+Now, since the transmitter already possesses a coarse estimate of $\bU_{i,t}$ given by $\bP_{i,t}$, the receiver just quantizes the local space of $\text{St}(N_T,N_R)$ nearby $\bP_{i,t}$, instead of the complete $\text{St}(N_T,N_R)$.
+The receiver feeds back this quantized information to the transmitter, enabling estimation of a refined estimate of $\bU_{i,t}$, given by $\tilde{\bU}_{i,t}$.
 That is, the transmitter utilizes a quantization function $q_P:\text{St}(N_T,N_R) \times \mathbb{N} \to \text{St}(N_T,N_R)$, to obtain $\tilde{\bU}_{i,t} \gets q_P(\bP_{i,t},\text{fb}_{i,t})$, where $\text{fb}_{i,t} \in \{1,2\ldots2^{\mathcal{B}}\}$ is the feedback from the receiver for precoder at $i$-th subcarrier and $t$-th time instant, considering bit budget of $\mathcal{B}$ bits.
@@
 Therefore, the quantization error is substantially lower as well.
-However, quantization algorithms that are independent of these specific predictive structures are important for the initialization of these predictive quantization strategies.
+However, independent quantization algorithms are important for smart initialization (instead of a cold start) of the predictive quantization strategies.
 Observe that predictive quantization algorithms for SVD precoders are typically the higher dimensional analogs of the well known approaches to reduce quantization error using linear prediction codes (LPCs) and Delta PCM.
 In both LPCs and Delta PCM, quantization error can be reduced substantially using a linear predictor and quantizing the scalar difference between the predicted and observed value (innovation).
-Analogous to this, for $\text{St}(N_T,N_R)$ quantization error is reduced by quantizing a subspace around the predicted value that is much smaller than the entire manifold.
+Analogous to this, for $\text{St}(N_T,N_R)$, quantization error is reduced by quantizing a subspace around the predicted value that is much smaller than the entire manifold.
 

### 2019-04-19 paper/main.tex
Changes in Section3

@@
 \label{vectorize}
-The reservoir computing framework has inputs and outputs as vectors, and thus, it is necessary to convert the precoder matrices to vectors.
+The traditional reservoir computing framework has inputs and outputs as vectors, and thus, it is necessary to convert the precoder matrices to vectors.
 A precoding matrix $\mathcal{\bM} \in \text{St}(N_T,N_R)$ is a $N_T\times N_R$ matrix with the property $\mathcal{\bM}^H\mathcal{\bM}=\mathbb{I}_{N_R}$.
-For brevity, let us assume that such a matrix $\mathcal{\bM}$ is a \'semi-unitary\' matrix.
+For brevity, we call such a matrix $\mathcal{\bM}$ to be a `semi-unitary' matrix.
 A na{\"i}ve method to vectorize a $N_T\times N_R$ semi-unitary matrix would be to take all it's $N_TN_R$ complex numbers individually and stack them onto a $2N_TN_R$ dimensional real vector.
@@
 Therefore, we can vectorize the $N_T\times N_R$ $\mathcal{\bM}$ into a $2(N_T)+2(N_T-1)+\ldots+2(N_T-N_R+1)= 2N_TN_R-(N_R^2-N_R)$ dimensional vector.
-For any semi-unitary matrix $\mathcal{\bM}$, denote by $\mathcal{\bm}$ the vectorized representation.
+For a semi-unitary matrix $\mathcal{\bM}$, denote by $\mathcal{\bm}$ it's vectorized representation.
 
-Observe here that there is a dimensional penalty; upon vectorizing the semi-unitary $\mathcal{\bM}$,
-$\mathcal{\bM} \in \text{St}(N_T,N_R)$, which is a $2N_TN_R-N_R^2$ dimensional manifold.
-We vectorize $\mathcal{\bM}$ to a $2N_TN_R-N_R^2+N_R$ dimensional vector, corresponding to an overhead of $N_R$ dimensions, since we have not exploited the fact that each column vector is a unit norm vector as well.
-One could attempt to use only $N_T-1$ complex numbers when vectorizing the first column, rather than all $N_T$.
-However, this would lead to a non-unique representation, since there could then be infinitely many values for the missing complex number, all of which yield a unit norm vector.
+Observe here that we incur a dimensional penalty upon vectorizing semi-unitary $\mathcal{\bM}$.
+$\mathcal{\bM} \in \text{St}(N_T,N_R)$, which is a $2N_TN_R-N_R^2$ dimensional manifold, whereas $\mathcal{\bm}$ is a $2N_TN_R-N_R^2+N_R$ dimensional vector.
+This corresponds to an overhead of $N_R$ dimensions, since we have not exploited the fact that each of the $N_R$ column vectors is a unit norm vector as well.
+It looks as if we could just take $N_T-1$ complex numbers when vectorizing the first column, instead of $N_T$, but this would lead to a non-unique representation, since there could then be infinite possibilities of the missing one complex number, such that the vector has a norm 1.
 %Focus on the fact that you don't actually pay a penalty
@@
 
-The input to the reservoir $i$ corresponding to subcarrier $i$ is $\tilde{\bu}_{i,t-1}$, which is the vectorized representation of $\tilde{\bU}_{i,t-1}$.
-Let $D_{\text{in}}=2N_TN_R-N_R^2+N_R$ be the dimension of the input vector to the dimension.
-Using a randomly initialized $D_{\text{in}}\times D_{\text{resv}}$ input coupler matrix $\bW^{\text{in}}_i$, the $D_{\text{in}}$ dimensional input is mapped to a $D_{\text{resv}}$ dimensional vector, where $D_{\text{resv}}$ is the dimension of the reservoir state vector $\br_{i,t}$.
+The input to the reservoir $i$ corresponding to subcarrier $i$ is $\tilde{\bu}_{i,t-1}$, (the vectorized representation of $\tilde{\bU}_{i,t-1}$) with dimensions $D_{\text{in}}=2N_TN_R-N_R^2+N_R$.
+Using a randomly initialized $D_{\text{in}}\times D_{\text{resv}}$ input coupler matrix, $\bW^{\text{in}}_i$, the $D_{\text{in}}$ dimensional input is mapped to a $D_{\text{resv}}$ dimensional vector, where $D_{\text{resv}}$ is the dimension of the reservoir state vector $\br_{i,t}$.
 The reservoir state vector $\br_{i,t}$ is initialized with $D_{\text{resv}}$ zeros, and is updated via the following equation,
@@
 \end{equation}
-where $\bA_i$ is the adjacency matrix that captures the reservoir dynamics and correlates reservoir state across time, and $\text{tanh}$ is applied element wise.
+where $\bA_i$ is the adjacency matrix that captures the reservoir dynamics, and $\text{tanh}$ is applied element wise.
 Typical choices for $\bA_i$ have been Erdos-Renyi graphs with an upper bounded maximum eigen value \cite{mosleh2017brain,pathak2017using}.
@@
 \end{figure*}
-This completes the forward prediction algorithm to obtain $\bP_{i,t}$ using just one past observed $\bU_{i,t-1}$. That is,
+This completes the forward prediction to obtain $\bP_{i,t}$ using only the past observed $\bU_{i,t-1}$ (i.e. $p=1$, Section \ref{section2}). That is,
 \begin{equation}
@@
 A corresponding retraction operation $Y=\texttt{retract}(X,\bT^Y_X)$, $\texttt{retract}: \text{St}(N_T,N_R)\times \mathcal{T}_X \text{St}(N_T,N_R) \to \text{St}(N_T,N_R)$ gives back the manifold point obtained by traversing in the tangent direction given by the second argument.
-In this work, the chosen lifting-retraction operations are the Cayley Exponentials, elaborated in \cite{DBLP:journals/corr/abs-1708-00045}. % and used in \cite{Gupt1905:Predictive}.
+In this work, the chosen lifting-retraction operations are the Cayley Exponentials, discussed in \cite{DBLP:journals/corr/abs-1708-00045,Gupt1905:Predictive}. % and used in \cite{Gupt1905:Predictive}.
 The Cayley exponential lifting operation maps two points in $\text{St}(N_T,N_R)$, to a $N_T\times N_T$ skew Hermitian matrix that represents the tangent from first point to the other.
@@
 The feedback from the receiver indicates the optimum tangent in the $\text{base}^{\mathcal{C}}$, which the transmitter can choose to get closest (in terms of chordal distance metric, $d_s(\bX,\bY)$ for $\bX,\bY \in \text{St}(N_T,N_R)$ detailed in \cite{Gupt1905:Predictive,6891198}) to the actual value $\bU_{i,t}$.
-With the optimum direction chosen, the next step is to determine how much to move in that particular direction, viz. the length of the chosen tangent direction.
+With the optimum direction chosen, the next step is to determine how much to move in that particular chosen direction, viz. the length of the chosen tangent direction.
 For this, we adopt the strategy in \cite{6891198}, which
 controls the magnitude of tangent steps, by having two codebooks
-$T^{\mathcal{C}}_p,T^{\mathcal{C}}_m$ of different spreads $s_p,s_m$, but same $2^{\mathcal{B}-1}$ base vectors from $\text{base}^{\mathcal{C}}$, i.e.
+$T^{\mathcal{C}}_p,T^{\mathcal{C}}_m$ of different spreads $s_p,s_m$, but same $2^{\mathcal{B}-1}$ base vectors in the $\text{base}^{\mathcal{C}}$, i.e.
 $T^{\mathcal{C}}_{\{p/m\}}=s_{\{p/m\}}\text{base}^{\mathcal{C}}$ (All codewords $\in \text{base}^{\mathcal{C}}$ multiplied by $s_{\{p/m\}}$ individually).
@@
 \begin{equation}
-\mathcal{O}_t=\sum_{s=1}^{t}\frac{1}{\lambda^{t-s}}||\bp_{i,t}-\tilde{\bu}_{i,t}||^2=\sum_{s=1}^{t}\frac{1}{\lambda^{t-s}}||\bW_{i,t}^{\text{out}}\br_{i,t}-\tilde{\bu}_{i,t}||^2
+\mathcal{O}_{i,t}=\sum_{s=1}^{t}\frac{1}{\lambda^{t-s}}||\bp_{i,t}-\tilde{\bu}_{i,t}||^2=\sum_{s=1}^{t}\frac{1}{\lambda^{t-s}}||\bW_{i,t}^{\text{out}}\br_{i,t}-\tilde{\bu}_{i,t}||^2
 \end{equation}
@@
 \begin{equation}
-\bW_{i,t}^{\text{out}}\gets\text{argmin}_{\bW_{i,t}^{\text{out}}}(\mathcal{O}_t=\sum_{s=1}^{t}\frac{1}{\lambda^{t-s}}||\bW_{i,t}^{\text{out}}\br_{i,t}-\tilde{\bu}_{i,t}||^2)
+\bW_{i,t}^{\text{out}}\gets\text{argmin}_{\bW_{i,t}^{\text{out}}}(\mathcal{O}_{i,t}=\sum_{s=1}^{t}\frac{1}{\lambda^{t-s}}||\bW_{i,t}^{\text{out}}\br_{i,t}-\tilde{\bu}_{i,t}||^2)
 \end{equation}
-Computing the gradients $\frac{\partial \mathcal{O}_t}{\partial \bW_{i,t}^{\text{out}}}$ and setting it to null gives,
+Computing the gradients $\frac{\partial \mathcal{O}_{i,t}}{\partial \bW_{i,t}^{\text{out}}}$ and setting it to null gives,
 \begin{equation}
@@
 To conclude this section, we will now summarize and touch upon the novel points of the reservoir computing based framework proposed for predictive quantization of SVD precoding.
-The first key advantage of the proposed framework, over the past work in this line \cite{Gupt1905:Predictive,6891198,6545375} is that the prediction function and quantization function are not independent of each other.
-To support the above statement, observe \eqref{res_upd},\eqref{fpqp} to obtain $\bW^{\text{out}}_{i,t}$ from $\tilde{\bu}_{i,t}$, and \eqref{fwd_pred} to obtain $\bP_{i,t+1}$ combinedly,
-\begin{equation*}
-\highlight{\bW_{i,t}^{\text{out}}}=\frac{\frac{\text{num}_{i,t-1}}{\lambda}+\texttt{outer}(\highlight{q_P}(f_P(\tilde{\bu}_{i,t-1}),\text{fb}_{i,t}),\br_{i,t})}{\frac{\text{den}_{i,t-1}}{\lambda}+||\br_{i,t}||^2}
-\end{equation*}
-\begin{equation*}
-\highlight{\bP_{i,t+1}}=f_P(\tilde{\bU}_{i,t})=\highlight{\bW^{\text{out}}_{i,t}}\text{tanh}(\bA_i\br_{i,t}+\bW^{\text{in}}_i\highlight{\tilde{\bu}_{i,t}})
-\end{equation*}
-The dependence between $f_P$ and $q_P$ in our framework is in the sense that the backward pass of the framework ensures that prediction function `'learns' the correlations brought about by $q_P$, in addition to temporal correlations.
+The first key advantage of the proposed framework, over the past work \cite{Gupt1905:Predictive,6891198,6545375} is that the prediction function and quantization function are not independent of each other.
+To support the above statement, observe \eqref{update_Wt1} to obtain $\bW^{\text{out}}_{i,t-1}$ from $\tilde{\bU}_{i,t-1}=q_P(f_P(\tilde{\bU}_{i,t-2}),\text{fb}_{i,t-1})$, and \eqref{pred} to obtain $\bP_{i,t+1}$,
+\begin{equation}
+\highlight{\bW_{i,t-1}^{\text{out}}}=\frac{\frac{\text{num}_{i,t-2}}{\lambda}+\texttt{outer}(\highlight{q_P}(f_P(\tilde{\bU}_{i,t-2}),\text{fb}_{i,t-1}),\br_{i,t-1})}{\frac{\text{den}_{i,t-2}}{\lambda}+||\br_{i,t-1}||^2}
+\label{update_Wt1}
+\end{equation}
+\begin{equation}
+\highlight{\bP_{i,t}}=f_P(\tilde{\bU}_{i,t-1})=\highlight{\bW^{\text{out}}_{i,t-1}}\text{tanh}(\bA_i\br_{i,t-1}+\bW^{\text{in}}_i\highlight{\tilde{\bu}_{i,t-1}})
+\label{pred}
+\end{equation}
+The dependence between $f_P$ and $q_P$ in our framework is in the sense that the backward pass of the framework ensures that prediction function `learns' the correlations brought about by $q_P$, in addition to temporal correlations.
 %Better framing possible
-This is done by optimizing $\bW_{i,t}^{\text{out}}$ such that the prediction output to be as close to the output from $q_P$ (Objective function $\mathcal{O}_t$).
-The updated $\bW_{i,t}^{\text{out}}$ is then used in forward pass to predict $\bP_{i,t+1}$, which is hopefully closer to $\tilde{\bU}_{i,t+1}$ than $\bP_{i,t}$ was to $\tilde{\bU}_{i,t}$ due to optimization of $\mathcal{O}_t$.
+This is done by optimizing $\bW_{i,t}^{\text{out}}$ such that the prediction output to be as close to the output from $q_P$ (Objective function $\mathcal{O}_{i,t}$).
+The updated $\bW_{i,t}^{\text{out}}$ is then used in forward pass to predict $\bP_{i,t+1}$, which is hopefully closer to $\tilde{\bU}_{i,t+1}$ than $\bP_{i,t}$ was to $\tilde{\bU}_{i,t}$ due to optimization of $\mathcal{O}_{i,t}$.
 
@@
 This is a departure from previous schemes \cite{Gupt1905:Predictive,6891198,6545375} which store the past $n$ (which has to be pre-decided) precoders in a $n$ sized cyclic buffer kind-of arrangement.
-Reservoir computing, thus proposes an easier to implement data centric scheme, which is a rarity for typical data centric ML based schemes.
+Reservoir computing, thus proposes an easier to train (data centric) scheme, which is a rarity for typical data centric ML based schemes.
 
@@
 \ref{qtiz_err} it is evident that the reservoir computing based predictive quantizer is able to reduce the quantization error below what was obtained from the existing temporal based predictive quantizer in \cite{6891198}.
-In addition, the quantization error is much more smoother, which can be explained from the fact that the reservoir computing approach optimizes, $\mathcal{O}_t$ which captures the long term dynamics of the channel and hence, is able to correct for jittery variations.
+In addition, the quantization error is much more smoother, which can be explained from the fact that the reservoir computing approach optimizes, $\mathcal{O}_{i,t}$ which captures the long term dynamics of the channel and hence, is able to correct for jittery variations.
 

### 2019-04-19 paper/main.tex
Changes in Section5

@@
 \subsection{Quantization function $q_P$}
+\label{qp}
 Before proceeding, it is critical to describe the quantization function $q_P(\bP_{i,t},\text{fb}_{i,t})$, which is similar to the one used in \cite{6891198,Gupt1905:Predictive,6545375}.
@@
 We just need to store the matrix $\text{num}_{i,t-1}$, a number $\text{den}_{i,t-1}$, and using the current reservoir state $\br_{i,t}$ and obtained $\tilde{\bu}_{i,t}$ from \eqref{fpqp}, one can calculate $\bW_{i,t}^{\text{out}}$ for forward calculation of $\tilde{\bu}_{i,t+1}$.
-This completes our technical discussion for the complete reservoir computing based framework for predictive quantization illustrated in Fig. %Ref Fig.
+This completes our technical discussion for the complete reservoir computing based framework for predictive quantization illustrated in Fig. \ref{res_overview}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \noindent We simulate both our predictive quantization algorithms and the one presented in \cite{6891198} for the IEEE Pedestrian-A channel, with $N_T=4$, $N_R=2$. 
-We simulated our algorithms by using the IT++ library through the Python wrapper py-itpp \cite{ViditPy}, with the channels being generated using Jake’s model for realistic simulations.
-Although in both our work and \cite{6891198}, only temporal correlations are exploited, we compare the BER, quantization error and logsum rate results for the MIMO-OFDM setting with number of subcarriers $N=64$, and evenly spaced $8$ feedback subcarriers, indexed from 0, viz.
+The channel matrices $\bH_{i,t}$ are generated using Jake’s model for realistic simulations, by using the IT++ library through the Python wrapper py-itpp \cite{ViditPy}. 
+Although in both our work and \cite{6891198}, only temporal correlations are exploited, we compare the BER, quantization error and logsum rate results for the complete MIMO-OFDM setting with number of subcarriers $N=64$, and evenly spaced $8$ feedback subcarriers, indexed from 0, viz.
 $\{0,9,\ldots,63\}$ ($\{9k, k \in \{0,1,\ldots,7\}\}$).
@@
 $\bP_{i,t}=\tilde{\bU}_{i,t-1}$) is used for 10 time instances to provide provide the initial training data for the reservoir and for overcoming initial transient response of the reservoir discussed in \cite{mosleh2017brain}.
-A 6 bit base codebook is used for the quantization function $q_P$, generated via vector quantization via $k$-means over a tangent list, comprising of actual tangents from the predicted precoder to the actual precoder obtained from SVD of channel matrix, to guarantee isotropic codewords \cite{Gupt1905:Predictive}.
+A 6 bit base codebook is used for the quantization function $q_P$, generated according to the method presented in Section \ref{qp} and \cite{Gupt1905:Predictive}.
+Hence, for both initialization and subsequent feedback, $\text{fb}_{i,t}$ can be encoded via 6 bits (i.e.
+$\mathcal{B}=6$ Section \ref{section2}).
+The bit budget per OFDM frame is thus 48 bits, for total 8 equally spaced feedback subcarriers $\{9k, k \in \{0,1,\ldots,7\}\}$.
 
@@
 Unlike \cite{Gupt1905:Predictive}, we don't exploit frequency correlations for predictive quantization, and the $8$ reservoirs for prediction of $8$ fed-back subcarriers are kept independent of each other.
-All these 8 resrvoirs are initialized with $\bA_{i\in\{9k\}}$ being an Erdos-Renyi\" graph, with probability of edge connections being $0.2$, $\lambda=2$, $\bW^{\text{out/in}}_{i\in\{9k\},0}$ being randomly assigned, $D_{\text{in}}=D_{\text{out}}=14$ (vectorized representation of $4\times2$ semi-unitary matrix, Section \ref{vectorize}) and $D_{\text{resv}}=60$.
+All these 8 resrvoirs are initialized with $\bA_{i\in\{9k\}}$ being an Erdos-Reny\"i graph, with probability of edge connections being $0.2$, $\lambda=2$, $\bW^{\text{out/in}}_{i\in\{9k\},0}$ being randomly assigned, $D_{\text{in}}=D_{\text{out}}=14$ (vectorized representation of $4\times2$ semi-unitary matrix, Section \ref{vectorize}) and $D_{\text{resv}}=60$.
 
@@
 \centering
-\includegraphics[width=0.5\textwidth]{images/qtizErr.pdf}
+\includegraphics[width=0.45\textwidth]{images/qtizErr.pdf}
 \caption{Quantization Error in terms of chordal distance to the actual precoder $\bU_{\{9k\},t}$ observed at the receiver, from the quantized estimate $\tilde{\bU}_{\{9k\},t}$ at the transmitter, averaged over 8 feedback subcarriers ($\{9k, k \in \{0,1,\ldots,7\}\}$) and 10 independent channel realizations ($f_DT_s=3.5\times10^{-4}$)}

### 2019-04-20 paper/main.tex
made some changes in reservior computuing description and fixed minor grammatical mistakes

@@
 \usepackage{amsmath}
+\usepackage[normalem]{ulem}
 \usepackage[colorinlistoftodos]{todonotes}
@@
 This task is aided by the presence of an underlying manifold structure and temporal/frequency correlations in the precoders. 
-Predictive quantization methods reduce the quantization error by predicting new precoders based on observation of past precoders, and then quantizing the information required to obtain the actual precoder from the predicted value.
+Predictive quantization methods reduce the quantization error by predicting new precoders based on observation of past precoders and then quantizing the information required to obtain the actual precoder from the predicted value.
 In this work, we introduce a reservoir computing based framework for predictive quantization by exploiting temporal correlations. 
-Past methods have primarily exploited the nonlinear geometry endowed by the manifold structure to for precoder prediction.
+Past methods have primarily exploited the nonlinear geometry endowed by the manifold structure \textcolor{red}{\sout{to}} for precoder prediction.
 Here, this non-linear relationship is captured using the dynamical reservoir state as part of the training process of the reservoir.
@@
 To honour the bit budget imposed by limited feedback CSI schemes, the quantization needs to be performed using very few bits.
-Given the high dimensionality of the precoders (which form a $N_T \times N_R$ complex valued matrix, viz.
+Given the high dimensionality of the precoders (which form a $N_T \times N_R$ complex\textcolor{red}{-}valued matrix, viz.
 $2\times N_T\times N_R$ real numbers), effective quantization with just a few bits poses a significant challenge.
@@
 Reservoir computing is a computational framework designed for sequential data processing.
-Its design is inspired from several frameworks of recurrent neural networks \cite{jaeger2004harnessing}, including Liquid State Machines \cite{jalalvand2015real}.
-A reservoir computing system maps the inputs to spatio-temporal patterns in a higher dimensional dynamical reservoir state.
-The pattern analysis over these spatio-temporal patterns is performed by an output coupler that maps the higher dimensional reservoir state back to the output dimension that generally possesses lower dimensionality than the reservoir state.
+Its design is inspired \textcolor{red}{by} several frameworks of recurrent neural networks \cite{jaeger2004harnessing}, including Liquid State Machines \cite{jalalvand2015real}.
+A reservoir computing system maps the inputs to \textcolor{red}{spatiotemporal} patterns in a higher dimensional dynamical reservoir state.
+The reservior states are then lineraly combined to create the output. The only trainable parameters of the system are those of the output coupler. These parameters can be learned by using regression.
 % A important characteristic of reservoir computing is that while training, the input weights and the weights within the reservoir are not kept fixed and the weights of the output coupler are updated.
-The key advantage of a reservoir computing based system is that it is extremely easy to train in comparison to its counterparts like Deep Neural Networks. CITATION NEEDED
-The input features can be efficiently learnt using a simple learning algorithm, since the reservoir non-linearly transforms sequential inputs into a higher dimensional reservoir state.
+The key advantage of a reservoir computing based system is that it is extremely easy to train in comparison to its counterparts like Deep Neural Networks \cite{Schrauwen07anoverview}.
+The input features can be efficiently \textcolor{red}{learned} using a simple learning algorithm since the reservoir non-linearly transforms sequential inputs into a higher dimensional reservoir state.
 Reservoir computing has been successfully used to solve problems like spoken digit recognition \cite{verstraeten2005isolated}, handwritten digit image recognition \cite{jalalvand2015real} and climate prediction \cite{pathak2017using}.}

### 2019-04-25 paper/main.tex
Edits from Prof. Appaiah and Prof. Manoj

--- 2019-04-19 paper/main.tex
@@
 
-Precoding matrices obtained from SVD of the MIMO channel matrix (estimated at the receiver) can be utilized at the transmitter for optimum power allocation and lower BER transmissions. 
+Precoding matrices obtained from SVD of the MIMO channel matrix (which is estimated at the receiver) can be utilized at the transmitter for optimum power allocation and lower BER transmissions. 
 A key step enabling this improved performance is the feedback of these precoders to the transmitter from the receiver.
-Since the bit budget for such CSI\footnote{Channel State Info.} feedback is limited, these precoders need to be quantized effectively using just a few bits.
-For a $N_T \times N_R$\footnote{$N_T(R)$: Number of Transmit (Receive) Antennas} MIMO system, this amounts to quantizing a $N_T \times N_R$ complex valued matrix.
+Since the bit budget for such channel state information (CSI) feedback is limited, these precoders need to be quantized effectively using just a few bits.
+For a $N_T \times N_R$ MIMO system ($N_{\{T/R\}}$: Number of Transmit/Receive Antennas), this amounts to quantizing a $N_T \times N_R$ complex valued matrix.
 This task is aided by the presence of an underlying manifold structure and temporal/frequency correlations in the precoders. 
@@
 Past methods have primarily exploited the nonlinear geometry endowed by the manifold structure to for precoder prediction.
-Here, this non-linear relationship is captured using the dynamical reservoir state as part of the training process of the reservoir.
+Here, this non-linear relationship is captured using the dynamical reservoir state as part of the online training process of the reservoir.
 Simulations reveal that this approach produces reduced quantization error, thereby resulting in lower BER as well as improved achievable rates when compared to earlier work.
@@
 The precoding matrix used to achieve the channel capacity using optimal power allocation is obtained using the SVD of the MIMO channel matrix \cite{love2008overview}.
-The MIMO channel matrix is estimated at the receiver, and the transmitter has no a-priori knowledge of the same.
+The MIMO channel matrix is estimated at the receiver, and the transmitter has no a priori knowledge of the same.
 Therefore, to obtain the said benefits of SVD precoders, the receiver needs to quantize and feed back the precoders it obtains from the SVD of the MIMO channel matrix.
-To honour the bit budget imposed by limited feedback CSI schemes, the quantization needs to be performed using very few bits.
+To respect the bit budget imposed by limited feedback CSI schemes, the quantization needs to be performed using very few bits.
 Given the high dimensionality of the precoders (which form a $N_T \times N_R$ complex valued matrix, viz.
-$2\times N_T\times N_R$ real numbers), effective quantization with just a few bits poses a significant challenge.
+$2N_TN_R$ real numbers), effective quantization with just a few bits poses a significant challenge.
 
@@
 Past work has used two inherent properties of the precoders to enable effective quantization of these precoders, with just a few bits.
-First, the precoders are not actually $2\times N_T\times N_R$ dimensional entities, and these have an underlying manifold structure that allows one to work with lower dimensions, if one performs operations over the manifold directly.
+First, the precoders are not actually $2N_TN_R$ dimensional entities, and these have an underlying manifold structure that allows one to work with lower dimensions, if one performs operations over the manifold directly.
 Second, these precoders are correlated in both time and frequency.
@@
 This improvement is obtained because exploiting the available correlations from past fed back precoders allow one to just quantize the extra information required on top of the past available temporal-frequency information, instead of the new precoder information in the entirety.
-Exploiting frequency correlations permits the use of interpolation algorithms, which in turn reduce the feedback overhead in a single OFDM frame, by feeding back CSI information only for certain subcarriers, and interpolating over the others.
+Exploiting frequency correlations permits the use of interpolation algorithms, which in turn reduces the feedback overhead in a single OFDM frame, by feeding back CSI information only for certain subcarriers, and interpolating over the others.
 Thus, combining these two inherent properties, viz.
 the underlying manifold structure and temporal-frequency correlations, requires a generalization of such linear algorithms to the manifold under consideration, by exploiting the differential geometry of the manifold.
-Relevant past work in this direction has been \cite{Gupt1905:Predictive,6891198,6545375,5671092,Li2016,khaled2005quantized,krishnamachari2013geometry}.
+Relevant past work in this direction has been presented in \cite{Gupt1905:Predictive,6891198,6545375,5671092,Li2016,khaled2005quantized,krishnamachari2013geometry}.
 
@@
 Its design is inspired from several frameworks of recurrent neural networks \cite{jaeger2004harnessing}, including Liquid State Machines \cite{jalalvand2015real}.
-A reservoir computing system maps the inputs to spatio-temporal patterns in a higher dimensional dynamical reservoir state.
-The pattern analysis over these spatio-temporal patterns is performed by an output coupler that maps the higher dimensional reservoir state back to the output dimension that generally possesses lower dimensionality than the reservoir state.
+A reservoir computing system maps the inputs to spatio temporal patterns in a higher dimensional dynamical reservoir state.
+The pattern analysis over these spatio temporal patterns is performed by an output coupler that maps the higher dimensional reservoir state back to the output dimension that generally possesses lower dimensionality than the reservoir state.
 % A important characteristic of reservoir computing is that while training, the input weights and the weights within the reservoir are not kept fixed and the weights of the output coupler are updated.
@@
 \end{equation}
-$\tilde{\bU}_{i,t} \in \mathbb{C}^{N_T \times N_R}$ represents the precoding matrix, which is a function of quantized CSI fed back by the receiver, $\by_{i,t} \in \mathbb{C}^{N_R \times 1}$ is the received data stream, $\bx_{i,t} \in \mathbb{C}^{N_T \times 1}$ denotes the transmitted signal, $\bH_{i,t} \in \mathbb{C}^{N_T \times N_R}$ denotes the MIMO channel matrix and $\bw_{i,t}$ denotes the i.i.d.
+$\tilde{\bU}_{i,t} \in \mathbb{C}^{N_T \times N_R}$ represents the precoding matrix, which is a function of the quantized CSI fed back by the receiver, $\by_{i,t} \in \mathbb{C}^{N_R \times 1}$ is the received data stream, $\bx_{i,t} \in \mathbb{C}^{N_T \times 1}$ denotes the transmitted signal, $\bH_{i,t} \in \mathbb{C}^{N_T \times N_R}$ denotes the MIMO channel matrix and $\bw_{i,t}$ denotes the i.i.d.
 complex Gaussian noise with $\bw_{i,t} \sim \mathcal{N}_{\mathbb{C}}(0,N_0\bI_{N_R})$, $N_0$ being the noise variance.
@@
 
-In this work, we assume that $\bH^{H}_{i,t}$ is estimated error-free at the receiver.
+For this work, we assume that $\bH^{H}_{i,t}$ is estimated exactly, with zero error at the receiver.
 If an infinite bit budget is available for quantization, the transmitter can directly use the matrices obtained from SVD of $\bH^{H}_{i,t}$ as the precoder $\tilde{\bU}_{i,t}$. 
-In particular, if $\text{SVD}(\bH_{i,t}) = \bU_{i,t},\Sigma_{i,t}, \bV_{i,t}$, then $\tilde{\bU}_{i,t} = \bU_{i,t}$.
+That is, if $\text{SVD}(\bH_{i,t}) = \bU_{i,t},\Sigma_{i,t}, \bV_{i,t}$, then $\tilde{\bU}_{i,t} = \bU_{i,t}$.
 Notice that matrices $\bU_{i,t}$ reside on the Stiefel manifold $\text{St}(N_T,N_R)$, since the columns of $\bU_{i,t}$ form a set of $N_R$ orthogonal vectors in $N_T$ dimensions \cite{Gupt1905:Predictive,6891198}.
-Given practical limitations, only limited feedback is available from the receiver, and the objective is to find a `reasonable' estimate of $\bU_{i,t}$, given by $\tilde{\bU}_{i,t}$, using the available feedback bits.
+Given practical limitations, only limited feedback is available from the receiver, and the objective is to estimate $\bU_{i,t}$, via $\tilde{\bU}_{i,t}$, using the available feedback bits.
 
 Independent quantization algorithms analogous to the Lloyd codebook algorithm have been studied for quantizing $\text{St}(N_T,N_R)$ \cite{6678348}.
-However, this method treats precoders that are close to each other in time/frequency as independent, since it does not exploit any temporal/spectral correlations for quantization.
+However, this approach treats precoders that are close to each other in time/frequency as independent, since it does not exploit any temporal/spectral correlations for quantization.
 Predictive quantization algorithms \cite{Gupt1905:Predictive,6891198} can be utilized to reduce the quantization error by utilizing the available correlations.
@@
 Suppose that we predict the current precoding matrix based on the past $p$ observed precoding matrices, and hence $\tilde{\bU}_{i,t-p},\tilde{\bU}_{i,t-p+1},\ldots,\tilde{\bU}_{i,t-2},\tilde{\bU}_{i,t-1}$ have been fed back and available at the transmitter.
-By using a prediction algorithm and by exploiting time correlations among precoders at $t-p,t-p+1,\ldots,t-2,t-1$ time instances, the transmitter can predict $\bU_{i,t}$ to be some $\bP_{i,t}=f_P(\tilde{\bU}_{i,t-p},\tilde{\bU}_{i,t-p+1},\ldots,\tilde{\bU}_{i,t-2},\tilde{\bU}_{i,t-1})$, where $f_P: \text{St}(N_T,N_R)^p \to \text{St}(N_T,N_R)$ is a prediction function.
-Now, since the transmitter already possesses a coarse estimate of $\bU_{i,t}$ given by $\bP_{i,t}$, the receiver just quantizes the local space of $\text{St}(N_T,N_R)$ nearby $\bP_{i,t}$, instead of the complete $\text{St}(N_T,N_R)$.
+By using a prediction algorithm and by exploiting time correlations among precoders at $t-p,t-p+1,\ldots,t-2,t-1$ time instances, the transmitter can obtain a prediction (coarse estimate) of $\bU_{i,t}$, as $\bP_{i,t}=f_P(\tilde{\bU}_{i,t-p},\tilde{\bU}_{i,t-p+1},\ldots,\tilde{\bU}_{i,t-2},\tilde{\bU}_{i,t-1})$, where $f_P: \text{St}(N_T,N_R)\times\ldots\{p-\text{times}\}\ldots\times\text{St}(N_T,N_R) \to \text{St}(N_T,N_R)$ is a prediction function.
+Now, since the transmitter already possesses a coarse estimate $\bP_{i,t}$ of $\bU_{i,t}$, the receiver just quantizes the local space of $\text{St}(N_T,N_R)$ nearby $\bP_{i,t}$, instead of the complete $\text{St}(N_T,N_R)$.
 The receiver feeds back this quantized information to the transmitter, enabling estimation of a refined estimate of $\bU_{i,t}$, given by $\tilde{\bU}_{i,t}$.
@@
 However, independent quantization algorithms are important for smart initialization (instead of a cold start) of the predictive quantization strategies.
-Observe that predictive quantization algorithms for SVD precoders are typically the higher dimensional analogs of the well known approaches to reduce quantization error using linear prediction codes (LPCs) and Delta PCM.
+Observe that predictive quantization algorithms for SVD precoders are typically the higher dimensional analogues of the well known approaches to reduce quantization error using linear prediction codes (LPCs) and Delta PCM.
 In both LPCs and Delta PCM, quantization error can be reduced substantially using a linear predictor and quantizing the scalar difference between the predicted and observed value (innovation).
@@
 The traditional reservoir computing framework has inputs and outputs as vectors, and thus, it is necessary to convert the precoder matrices to vectors.
-A precoding matrix $\mathcal{\bM} \in \text{St}(N_T,N_R)$ is a $N_T\times N_R$ matrix with the property $\mathcal{\bM}^H\mathcal{\bM}=\mathbb{I}_{N_R}$.
+A precoding matrix $\mathcal{\bM} \in \text{St}(N_T,N_R)$ is a $N_T\times N_R$ matrix with the property $\mathcal{\bM}^H\mathcal{\bM}=\text{\textbf{1}}_{N_R}$.
 For brevity, we call such a matrix $\mathcal{\bM}$ to be a `semi-unitary' matrix.
 A na{\"i}ve method to vectorize a $N_T\times N_R$ semi-unitary matrix would be to take all it's $N_TN_R$ complex numbers individually and stack them onto a $2N_TN_R$ dimensional real vector.
-However, a more efficient approach would be to use the $\mathcal{\bM}^H\mathcal{\bM}=\mathbb{I}_{N_R}$ property, which implies that each vector representing the columns of $\mathcal{\bM}$ is orthogonal to other columns.
+However, a more efficient approach would be to use the $\mathcal{\bM}^H\mathcal{\bM}=\text{\textbf{1}}_{N_R}$ property, which implies that each vector representing the columns of $\mathcal{\bM}$ is orthogonal to the other columns.
 For the first column, we take its $N_T$ complex numbers and stack them onto a $2N_T$ vector.
@@
 Therefore, the output of the reservoir is also a $D_{\text{in}}$ dimensional vector ($D_{\text{out}}=D_{\text{in}}$).
-The output $\bp_{i,t}$ is obtained via matrix transformation of the reservoir state $\br_{i,t}$ via the $D_{\text{resv}}\times D_{\text{out}}$ output coupler matrix $\bW^{\text{out}}_{i,t-1}$\footnote{Why it is $t-1$ and not $t$ would surface up in Section \ref{train}}, viz.
+The output $\bp_{i,t}$ is obtained using a matrix transformation of the reservoir state $\br_{i,t}$ with the $D_{\text{resv}}\times D_{\text{out}}$ output coupler matrix $\bW^{\text{out}}_{i,t-1}$ viz.
 \begin{equation}
@@
 with $s[0]=0$.
-Intuitively, the algorithm reduces/increases the spread of the codebook till the operation of reduction/increase is no longer beneficial, i.e.
+Intuitively, the algorithm reduces/increases the spread of the codebook till the reduction/increase of spread is no longer beneficial, i.e.
 the optimum codeword lies in the higher/lower spread codebook instead.
-The scheme used by us to obtain $\text{base}^{\mathcal{C}}$ is similar to the one presented in \cite{Gupt1905:Predictive}, which performs a $k$-means ($k=2^{\mathcal{B}-1}$) clustering on a collection of tangents to obtain an isotropic collection of $2^{\mathcal{B}-1}$ tangent codewords.
+The scheme used to obtain $\text{base}^{\mathcal{C}}$ is similar to the one presented in \cite{Gupt1905:Predictive}, which performs a $k$-means ($k=2^{\mathcal{B}-1}$) clustering on a collection of tangents to obtain an isotropic collection of $2^{\mathcal{B}-1}$ tangent codewords.
 This completes the discussion on the quantization function $q_P$ to obtain $\tilde{\bU}_{i,t}=q_P(\bP_{i,t},\text{fb}_{i,t})$ from $\bP_{i,t},\text{fb}_{i,t}$.
@@
 \end{equation}
-The key idea here is that as the predicted matrix $\bP_{i,t}$, which is basically the coarse estimate for $\bU_{i,t}$, gets closer to the refined estimate $\tilde{\bU}_{i,t}$, the receiver has to quantize even smaller subspaces and can thus provide an even refined estimate via it's feedback $\text{fb}_{i,t}$.
+The key idea here is that as the predicted matrix $\bP_{i,t}$ (the coarse estimate), gets closer to $\tilde{\bU}_{i,t}$ (the refined estimate), the receiver has to quantize even smaller subspaces and can thus provide a more refined estimate from the feedback $\text{fb}_{i,t}$.
 Hence, for the time instant $t\geq1$, we train the reservoir output coupler such that the following objective function is optimized,
@@
 \end{equation}
-here $\lambda>1$ is the history parameter.
-We wish to perform the following optimization in order to find the optimum $\bW_{i,t}^{\text{out}}$ from whatever we have observed about $\tilde{\bu}_{i,t}$ uptill now,
+here $\lambda>1$ is the history parameter. We wish to perform the following optimization in order to find the optimum $\bW_{i,t}^{\text{out}}$ from our observations till time $t$,
 \begin{equation}
@@
 \end{equation}
-Computing the gradients $\frac{\partial \mathcal{O}_{i,t}}{\partial \bW_{i,t}^{\text{out}}}$ and setting it to null gives,
+Computing the gradient $\frac{\partial \mathcal{O}_{i,t}}{\partial \bW_{i,t}^{\text{out}}}$, setting it to null matrix gives,
 \begin{equation}
@@
 \end{equation}
-where $\texttt{outer}(\bx,\by)$ is the outer product between $N_x$ dimensional vector $\bx$ and $N_y$ dimensional vector $\by$ to give a $N_x\times N_y$ matrix.
-Let $\sum_{s=1}^{t}\frac{1}{\lambda^{t-s}}\texttt{outer}(\tilde{\bu}_{i,s},\br_{i,s})$ be $\text{num}_{i,t}$ and $\sum_{s=1}^{t}\frac{1}{\lambda^{t-s}}||\br_{i,s}||^2$ be $\text{den}_{i,t}$, with $\bW_{i,t}^{\text{out}}=\frac{\text{num}_{i,t}}{\text{den}_{i,t}}$.
+where $\texttt{outer}(\bx,\by)$ is the outer product between $N_x$ dimensional vector $\bx$ and $N_y$ dimensional vector $\by$ to yield a $N_x\times N_y$ matrix.
+Let $\sum_{s=1}^{t}\frac{1}{\lambda^{t-s}}\texttt{outer}(\tilde{\bu}_{i,s},\br_{i,s})$ be $\text{\textbf{num}}_{i,t}$ and $\sum_{s=1}^{t}\frac{1}{\lambda^{t-s}}||\br_{i,s}||^2$ be $\text{den}_{i,t}$, with $\bW_{i,t}^{\text{out}}=\frac{\text{\textbf{num}}_{i,t}}{\text{den}_{i,t}}$.
 Observe that,
 \begin{equation}
-\bW_{i,t}^{\text{out}}=\frac{\frac{\text{num}_{i,t-1}}{\lambda}+\texttt{outer}(\tilde{\bu}_{i,t},\br_{i,t})}{\frac{\text{den}_{i,t-1}}{\lambda}+||\br_{i,t}||^2}
+\bW_{i,t}^{\text{out}}=\frac{\frac{\text{\textbf{num}}_{i,t-1}}{\lambda}+\texttt{outer}(\tilde{\bu}_{i,t},\br_{i,t})}{\frac{\text{den}_{i,t-1}}{\lambda}+||\br_{i,t}||^2}
 \label{wout_upd}
@@
 \eqref{wout_upd} makes training of the reservoir easy to implement, and of low complexity as well.
-We just need to store the matrix $\text{num}_{i,t-1}$, a number $\text{den}_{i,t-1}$, and using the current reservoir state $\br_{i,t}$ and obtained $\tilde{\bu}_{i,t}$ from \eqref{fpqp}, one can calculate $\bW_{i,t}^{\text{out}}$ for forward calculation of $\tilde{\bu}_{i,t+1}$.
-This completes our technical discussion for the complete reservoir computing based framework for predictive quantization illustrated in Fig. \ref{res_overview}
+We only need to store the matrix $\text{\textbf{num}}_{i,t-1}$, a number $\text{den}_{i,t-1}$, and using the current reservoir state $\br_{i,t}$ and $\tilde{\bu}_{i,t}$ obtained from \eqref{fpqp}, $\bW_{i,t}^{\text{out}}$ can be calculated, to obtain predicted coarse estimate of $\tilde{\bu}_{i,t+1}$.
+This completes our technical discussion for the reservoir computing based framework for predictive quantization illustrated in Fig. \ref{res_overview}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-To conclude this section, we will now summarize and touch upon the novel points of the reservoir computing based framework proposed for predictive quantization of SVD precoding.
+To conclude this section, we now summarize and highlight the novel points of the reservoir computing based framework proposed for predictive quantization of SVD precoding.
 The first key advantage of the proposed framework, over the past work \cite{Gupt1905:Predictive,6891198,6545375} is that the prediction function and quantization function are not independent of each other.
-To support the above statement, observe \eqref{update_Wt1} to obtain $\bW^{\text{out}}_{i,t-1}$ from $\tilde{\bU}_{i,t-1}=q_P(f_P(\tilde{\bU}_{i,t-2}),\text{fb}_{i,t-1})$, and \eqref{pred} to obtain $\bP_{i,t+1}$,
+To see this, observe \eqref{update_Wt1} to obtain $\bW^{\text{out}}_{i,t-1}$ from $\tilde{\bU}_{i,t-1}=q_P(f_P(\tilde{\bU}_{i,t-2}),\text{fb}_{i,t-1})$, and \eqref{pred} to obtain $\bP_{i,t+1}$,
 \begin{equation}
@@
 
-The second key advantage of the proposed scheme comes from the ease of training the reservoir, entailed by \eqref{res_upd}.
-By storing just one matrix $\text{num}_{i,t}$ and a number $\text{den}_{i,t}$, we can capture the enitre history of the precoding matrices, with past values weighted by $\lambda$.
+\textcolor{blue}{The second key advantage of the proposed scheme comes from the ease of training the reservoir, entailed by \eqref{res_upd}.
+By storing just one matrix $\text{\textbf{num}}_{i,t}$ and a number $\text{den}_{i,t}$, we can capture the enitre history of the precoding matrices, with past values weighted by $\lambda$.
 This is a departure from previous schemes \cite{Gupt1905:Predictive,6891198,6545375} which store the past $n$ (which has to be pre-decided) precoders in a $n$ sized cyclic buffer kind-of arrangement.
-Reservoir computing, thus proposes an easier to train (data centric) scheme, which is a rarity for typical data centric ML based schemes.
+Reservoir computing, thus proposes an easier to train (data centric) scheme, which is not typical for typical data centric ML based schemes.}
 
@@
 The channel matrices $\bH_{i,t}$ are generated using Jake’s model for realistic simulations, by using the IT++ library through the Python wrapper py-itpp \cite{ViditPy}. 
-Although in both our work and \cite{6891198}, only temporal correlations are exploited, we compare the BER, quantization error and logsum rate results for the complete MIMO-OFDM setting with number of subcarriers $N=64$, and evenly spaced $8$ feedback subcarriers, indexed from 0, viz.
+Although in both our work and \cite{6891198}, only temporal correlations are exploited, we compare the BER, quantization error and logsum rate results for the complete MIMO-OFDM setting with number of subcarriers $N=64$, and evenly spaced $8$ fed back subcarriers, indexed from 0, viz.
 $\{0,9,\ldots,63\}$ ($\{9k, k \in \{0,1,\ldots,7\}\}$).
@@
 $\mathcal{B}=6$ Section \ref{section2}).
-The bit budget per OFDM frame is thus 48 bits, for total 8 equally spaced feedback subcarriers $\{9k, k \in \{0,1,\ldots,7\}\}$.
+The bit budget per OFDM frame is thus 48 bits, for total 8 equally spaced fed back subcarriers $\{9k, k \in \{0,1,\ldots,7\}\}$.
 
-For prediction of each of the $8$ fed-back subcarriers, we consider $8$ separate reservoirs, each of them evolved separately, with $i\in\{9k, k \in \{0,1,\ldots,7\}\}$ in both the forward pass prediction and quantization ($f_P,q_P$) \eqref{fpqp} and backward pass to update $\bW_{i,t}^{\text{out}}$ \eqref{backpass}.
-Unlike \cite{Gupt1905:Predictive}, we don't exploit frequency correlations for predictive quantization, and the $8$ reservoirs for prediction of $8$ fed-back subcarriers are kept independent of each other.
-All these 8 resrvoirs are initialized with $\bA_{i\in\{9k\}}$ being an Erdos-Reny\"i graph, with probability of edge connections being $0.2$, $\lambda=2$, $\bW^{\text{out/in}}_{i\in\{9k\},0}$ being randomly assigned, $D_{\text{in}}=D_{\text{out}}=14$ (vectorized representation of $4\times2$ semi-unitary matrix, Section \ref{vectorize}) and $D_{\text{resv}}=60$.
+For predicting each of the $8$ fed-back subcarriers, we consider $8$ separate reservoirs, each of them evolved separately, with $i\in\{9k, k \in \{0,1,\ldots,7\}\}$ in both the forward pass prediction and quantization ($f_P,q_P$) \eqref{fpqp} and backward pass to update $\bW_{i,t}^{\text{out}}$ \eqref{backpass}.
+Unlike \cite{Gupt1905:Predictive}, we do not exploit frequency correlations for predictive quantization, and the $8$ reservoirs for prediction of $8$ fed-back subcarriers are kept independent of each other.
+All these 8 reservoirs are initialized with $\bA_{i\in\{9k\}}$ being an Erdos-Reny\"i graph, with probability of edge connections being $0.2$, $\lambda=2$, $\bW^{\text{out/in}}_{i\in\{9k\},0}$ being randomly assigned, $D_{\text{in}}=D_{\text{out}}=14$ (vectorized representation of $4\times2$ semi-unitary matrix, Section \ref{vectorize}) and $D_{\text{resv}}=60$.r
 
@@
 
-\subsection{Quantization Error, BER and Achievable Rate Results}
+\subsection{Quantization error, BER and Achievable Rate Results}
 \label{res}{}
@@
 \includegraphics[width=0.45\textwidth]{images/qtizErr.pdf}
-\caption{Quantization Error in terms of chordal distance to the actual precoder $\bU_{\{9k\},t}$ observed at the receiver, from the quantized estimate $\tilde{\bU}_{\{9k\},t}$ at the transmitter, averaged over 8 feedback subcarriers ($\{9k, k \in \{0,1,\ldots,7\}\}$) and 10 independent channel realizations ($f_DT_s=3.5\times10^{-4}$)}
+\caption{Quantization error in terms of chordal distance to the actual precoder $\bU_{\{9k\},t}$ observed at the receiver, from the quantized estimate $\tilde{\bU}_{\{9k\},t}$ at the transmitter, averaged over 8 fed back subcarriers ($\{9k, k \in \{0,1,\ldots,7\}\}$) and 10 independent channel realizations ($f_DT_s=3.5\times10^{-4}$)}
 \label{qtiz_err}
@@
 From Fig.
-\ref{qtiz_err} it is evident that the reservoir computing based predictive quantizer is able to reduce the quantization error below what was obtained from the existing temporal based predictive quantizer in \cite{6891198}.
-In addition, the quantization error is much more smoother, which can be explained from the fact that the reservoir computing approach optimizes, $\mathcal{O}_{i,t}$ which captures the long term dynamics of the channel and hence, is able to correct for jittery variations.
+\ref{qtiz_err} it is evident that the reservoir computing based predictive quantizer is able to reduce the quantization error below what was obtained from the existing temporal correlations based predictive quantizer in \cite{6891198}.
+In addition, the quantization error is much smoother, which can be explained from the fact that the reservoir computing approach optimizes, $\mathcal{O}_{i,t}$ that captures the long term dynamics of the channel and hence, is able to correct for jittery variations.
 
@@
 \ref{BER} that reservoir computing framework is able to achieve substantial imporvements in $\text{E}_\text{b}\text{N}_0$ levels at $\text{BER}\leq 10^{-3}$.
-Particularly, observe, for $\text{BER}=10^{-4}$ we observe around 5dB improvement.
-Also, notice the substanial improvement which both the predictive quantization schemes offer from the independent quantization scheme with Lloyd codebook for precoders \cite{6678348}, using the same number of bits.
+Particularly, observe, for $\text{BER}=10^{-4}$ we observe around $5$ dB improvement.
+Also, notice the substantial improvement which both the predictive quantization schemes offer from the independent quantization scheme with Lloyd codebook for precoders \cite{6678348}, using the same number of bits.
 
@@
 \ref{achievrate} that the reservoir computing framework offers signicant improvement in achievable rate for $f_DT_s=10^{-4}$.
-Since the temporal variations for $f_DT_s=10^{-2}, 10^{-1}$ are higher, the resrvoir computing framework has to learn a faster-varying function, and hence the degradation in performance.
+Since the temporal variations for $f_DT_s=10^{-2}, 10^{-1}$ are higher, the reservoir computing framework has to learn a faster-varying function, and hence the degradation in performance.
 However, it still matches the performance of the predictive quantizer in \cite{6891198} for $f_DT_s=10^{-2}$ and performs slightly better for $f_DT_s=10^{-1}$.
@@
 \label{section5}
-In this paper, we presented a reservoir computing framework to exploit temporal correlations for predictive quantization of SVD based precoders.
+In this paper, we have presented a reservoir computing framework to exploit temporal correlations for predictive quantization of SVD based precoders.
 The simulations reveal reduced quantization error, improved BER performance, and higher achievable rate from the proposed framework.

### 2019-04-26 paper/main.tex
Adding modified system diagram
Adding caption to system figure

@@
 \usepackage{xcolor}
-\setlength{\belowcaptionskip}{-10pt}
+\setlength{\belowcaptionskip}{-12pt}
 \newcommand{\highlight}[1]{%
@@
 \centering
-\includegraphics[width=0.8\textwidth]{images/system.pdf}
-\caption{An overview of the reservoir computing framework proposed for predictive quantization of $\bu_{i,t}$}
+\includegraphics[width=0.8\textwidth]{images/system2.pdf}
+\caption{System Overview: The reservoir computing framework takes the precoder estimate at $t-1$ (viz.
+$\tilde{\bu_{i,t-1}}$) as input, and executes the forward pass of the predictive quantization framework, shaded in green, to obtain $\tilde{\bu_{i,t}}$.
+Both the transmitter and receiver utilize the same reservoir (initialized identically), with a minute difference indicated by the cyan shaded block.
+In the cyan shaded block, receiver finds the appropriate codeword for the $q_P$ function by comparing the prediction with the actual $\bU_{i,t}$, and communicates $\text{fb}_{i,t}$ to allow estimation of $\tilde{\bu}_{i,t}$ at the transmitter.
+Then, both the receiver and transmitter execute the backward pass (shaded in blue) to optimize $\mathcal{O}_{i,t}$ \eqref{oit}, to ensure identical evolution of both the reservoirs}
 \label{res_overview}
+\vspace{-10pt}
 \end{figure*}
@@
 \mathcal{O}_{i,t}=\sum_{s=1}^{t}\frac{1}{\lambda^{t-s}}||\bp_{i,t}-\tilde{\bu}_{i,t}||^2=\sum_{s=1}^{t}\frac{1}{\lambda^{t-s}}||\bW_{i,t}^{\text{out}}\br_{i,t}-\tilde{\bu}_{i,t}||^2
+\label{oit}
 \end{equation}
@@
 \label{table}
+\vspace{-8pt}
 \end{figure}
@@
 \centering
-\includegraphics[width=0.5\textwidth]{images/BER_res.pdf}
+\includegraphics[width=0.45\textwidth]{images/BER_res.pdf}
 \caption{BER results after obtaining non fed back $\tilde{\bU}_{i\neq\{9k\},t}$ from $\tilde{\bU}_{\{9k\},t}$ via Cayley interpolation \cite{Gupt1905:Predictive}, averaged over 10 independent channel realizations, 100 channel evolutions each ($f_DT_s=3.5\times10^{-4}$)}
 \label{BER}
+\vspace{-8pt}
 \end{figure}
@@
 \centering
-\includegraphics[width=0.5\textwidth]{images/achievRate.pdf}
+\includegraphics[width=0.45\textwidth]{images/achievRate.pdf}
 \caption{Achievable Rate results for the two predictive quantization methods considered.
@@
 \label{achievrate}
+\vspace{-13pt}
 \end{figure}
@@
 \label{section5}
+\vspace{-3pt}
 In this paper, we have presented a reservoir computing framework to exploit temporal correlations for predictive quantization of SVD based precoders.
@@
 This motivates further study into the framework as well, and future lines of work here would be a generalization of the framework to capture frequency correlations as well for predictive quantization, and a detailed analysis of impact on performance caused by choice of certain reservoir parameters like $\bA,\text{tanh}(\cdot)$, number of dimensions of the reservoir state.
+\vspace{-5pt}
 

### 2019-04-28 paper/main.tex
Adding delay mitigation citation

@@
 \subsection{Forward Prediction $f_P$ function}
-\noindent The vector representation of semi-unitary matrices allows us to proceed with the discussion on reservoir computing framework for predictive quantization of SVD precoders.
-Consider the reservoir computing framework shown in Fig. \ref{res_overview} %Ref Fig. Reservoir Pic
+\noindent The vector representation of semi-unitary matrices allows to proceed with our discussion on reservoir computing framework.
+Consider the reservoir computing framework in Fig. \ref{res_overview} %Ref Fig. Reservoir Pic
 
-The input to the reservoir $i$ corresponding to subcarrier $i$ is $\tilde{\bu}_{i,t-1}$, (the vectorized representation of $\tilde{\bU}_{i,t-1}$) with dimensions $D_{\text{in}}=2N_TN_R-N_R^2+N_R$.
-Using a randomly initialized $D_{\text{in}}\times D_{\text{resv}}$ input coupler matrix, $\bW^{\text{in}}_i$, the $D_{\text{in}}$ dimensional input is mapped to a $D_{\text{resv}}$ dimensional vector, where $D_{\text{resv}}$ is the dimension of the reservoir state vector $\br_{i,t}$.
-The reservoir state vector $\br_{i,t}$ is initialized with $D_{\text{resv}}$ zeros, and is updated via the following equation,
+The input to the reservoir $i$ corresponding to subcarrier $i$ is $\tilde{\bu}_{i,t-1}$, (vectorized representation of $\tilde{\bU}_{i,t-1}$) with dimensions $D_{\text{in}}=2N_TN_R-N_R^2+N_R$.
+Using a randomly initialized $D_{\text{in}}\times D_{\text{resv}}$ input coupler matrix, $\bW^{\text{in}}_i$, the $D_{\text{in}}$ dimensional input is mapped to a $D_{\text{resv}}(>D_{\text{in}})$ dimensional vector, where $D_{\text{resv}}$ is the dimension of the reservoir state vector $\br_{i,t}$.
+$\br_{i,t}$ is initialized with $D_{\text{resv}}$ zeros, and is updated via the following equation,
 \begin{equation}
@@
 \caption{System Overview: The reservoir computing framework takes the precoder estimate at $t-1$ (viz.
-$\tilde{\bu_{i,t-1}}$) as input, and executes the forward pass of the predictive quantization framework, shaded in green, to obtain $\tilde{\bu_{i,t}}$.
+$\tilde{\bu}_{i,t-1}$) as input, and executes the forward pass of the predictive quantization framework, shaded in green, to obtain $\tilde{\bu}_{i,t}$.
 Both the transmitter and receiver utilize the same reservoir (initialized identically), with a minute difference indicated by the cyan shaded block.
@@
 
-$\text{fb}_{i,t}$ is also used to update the spread of the codebooks $T^{\mathcal{C}}_p,T^{\mathcal{C}}_m$.
+\noindent $\text{fb}_{i,t}$ is also used to update the spread of the codebooks $T^{\mathcal{C}}_p,T^{\mathcal{C}}_m$.
 Depending on whether $\text{fb}_{i,t} \geq 2^{\mathcal{B}-1}$,
@@
 $T^{\mathcal{C}}_m$, the scale parameter $s[k]$, which in turn
-controls values of $s_p, s_m$, is updated in the following manner,
+controls values of $s_p, s_m$, is updated accordingly,
 $$s_p=g^{\text{min}(s[k-1]+1,0)}, s_m = g^{s[k-1]-1}$$
@@
 \label{train}
-Armed with the descriptions of $f_P, q_P$ we are now ready to describe the training process for the reservoir.
+\noindent Having described the technicalities of $f_P,q_P$, we are now ready to describe the training process for the reservoir.
 Recall that to obtain $\tilde{\bU}_{i,t}$ from  $\tilde{\bU}_{i,t-1}$, we have,
@@
 \end{equation}
-here $\lambda>1$ is the history parameter. We wish to perform the following optimization in order to find the optimum $\bW_{i,t}^{\text{out}}$ from our observations till time $t$,
+here $\lambda>1$ is the history parameter. We wish to perform the following optimization in order to find the optimum $\bW_{i,t}^{\text{out}}$ from the available estimates till time $t$,
 \begin{equation}
@@
 
-To conclude this section, we now summarize and highlight the novel points of the reservoir computing based framework proposed for predictive quantization of SVD precoding.
+To conclude this section, we now summarize and highlight the novel points of the proposed framework for predictive quantization.
 The first key advantage of the proposed framework, over the past work \cite{Gupt1905:Predictive,6891198,6545375} is that the prediction function and quantization function are not independent of each other.
@@
 \end{equation}
-The dependence between $f_P$ and $q_P$ in our framework is in the sense that the backward pass of the framework ensures that prediction function `learns' the correlations brought about by $q_P$, in addition to temporal correlations.
+The dependence between $f_P$ and $q_P$ in our framework is in the sense that the backward pass ensures that prediction function `learns' the correlations brought about by $q_P$, in addition to temporal correlations.
 %Better framing possible
@@
 
-\textcolor{blue}{The second key advantage of the proposed scheme comes from the ease of training the reservoir, entailed by \eqref{res_upd}.
-By storing just one matrix $\text{\textbf{num}}_{i,t}$ and a number $\text{den}_{i,t}$, we can capture the enitre history of the precoding matrices, with past values weighted by $\lambda$.
+\textcolor{blue}{Another advantage of the proposed scheme comes from the ease of training the reservoir, entailed by \eqref{res_upd}.
+By storing just one matrix $\text{\textbf{num}}_{i,t}$ and a number $\text{den}_{i,t}$, we capture the entire history of the precoding matrices, with past values weighted by $\lambda$.
 This is a departure from previous schemes \cite{Gupt1905:Predictive,6891198,6545375} which store the past $n$ (which has to be pre-decided) precoders in a $n$ sized cyclic buffer kind-of arrangement.
@@
 \label{setting}
-\noindent We simulate both our predictive quantization algorithms and the one presented in \cite{6891198} for the IEEE Pedestrian-A channel, with $N_T=4$, $N_R=2$. 
-The channel matrices $\bH_{i,t}$ are generated using Jake’s model for realistic simulations, by using the IT++ library through the Python wrapper py-itpp \cite{ViditPy}. 
+\noindent We simulate both our predictive quantization algorithm and the one presented in \cite{6891198} for the IEEE Pedestrian-A channel, with $N_T=4$, $N_R=2$. 
+The channel matrices $\bH_{i,t}$ are generated using Jake’s model for realistic simulations, from the IT++ library through the python wrapper py-itpp \cite{ViditPy}. 
 Although in both our work and \cite{6891198}, only temporal correlations are exploited, we compare the BER, quantization error and logsum rate results for the complete MIMO-OFDM setting with number of subcarriers $N=64$, and evenly spaced $8$ fed back subcarriers, indexed from 0, viz.
@@
 \caption{The transmitter obtains feedback for $\{0,9,\ldots,63\}$ ($\{9k, k \in \{0,1,\ldots,7\}\}$ subcarriers, and uses $\tilde{\bU}_{i,t-1}$, alongwith $f_P,q_P$ \eqref{fpqp} to obtain $\tilde{\bU}_{i,t}$, illustrated in the figure via cyan arrows.
-For each time instant, the transmitter uses the Cayley mehtod to interpolate $\tilde{\bU}_{i,t}$ at $i\neq\{9k\}$ subcarriers}
+For each time instant, the transmitter uses the Cayley method to interpolate $\tilde{\bU}_{i,t}$ at $i\neq\{9k\}$ subcarriers}
 \label{table}
@@
 \includegraphics[width=0.45\textwidth]{images/qtizErr.pdf}
-\caption{Quantization error in terms of chordal distance to the actual precoder $\bU_{\{9k\},t}$ observed at the receiver, from the quantized estimate $\tilde{\bU}_{\{9k\},t}$ at the transmitter, averaged over 8 fed back subcarriers ($\{9k, k \in \{0,1,\ldots,7\}\}$) and 10 independent channel realizations ($f_DT_s=3.5\times10^{-4}$)}
+\caption{Quantization error in terms of chordal distance to the actual precoder $\bU_{\{9k\},t}$ observed at the receiver, from the quantized estimate $\tilde{\bU}_{\{9k\},t}$ at the transmitter, averaged over 8 fed back subcarriers ($\{9k, k \in \{0,1,\ldots,7\}\}$) and 10 independent channel realizations ($f_DT_s=10^{-4}$)}
 \label{qtiz_err}
@@
 Observe from Fig.
-\ref{BER} that reservoir computing framework is able to achieve substantial imporvements in $\text{E}_\text{b}\text{N}_0$ levels at $\text{BER}\leq 10^{-3}$.
+\ref{BER} that reservoir computing framework is able to achieve substantial improvements in $\text{E}_\text{b}\text{N}_0$ levels at $\text{BER}\leq 10^{-3}$.
 Particularly, observe, for $\text{BER}=10^{-4}$ we observe around $5$ dB improvement.
@@
 \includegraphics[width=0.45\textwidth]{images/BER_res.pdf}
-\caption{BER results after obtaining non fed back $\tilde{\bU}_{i\neq\{9k\},t}$ from $\tilde{\bU}_{\{9k\},t}$ via Cayley interpolation \cite{Gupt1905:Predictive}, averaged over 10 independent channel realizations, 100 channel evolutions each ($f_DT_s=3.5\times10^{-4}$)}
+\caption{BER results after obtaining non fed back $\tilde{\bU}_{i\neq\{9k\},t}$ from $\tilde{\bU}_{\{9k\},t}$ via Cayley interpolation \cite{Gupt1905:Predictive}, averaged over 10 independent channel realizations, 100 channel evolutions each ($f_DT_s=10^{-4}$)}
 \label{BER}
-\vspace{-8pt}
 \end{figure}
@@
 \centering
-\includegraphics[width=0.45\textwidth]{images/achievRate.pdf}
+\includegraphics[width=0.45\textwidth]{images/hopRate.pdf}
 \caption{Achievable Rate results for the two predictive quantization methods considered.
-The results are presented as a perecentage of the ideal acheivable rate obtained when the transmitter has the accurate (unquantized) and non-interpolated estimates of $\bU_{i,t}$ for each subcarrier and each time instant.
+The results are presented as a percentage of the ideal achievable rate obtained when the transmitter has the accurate (unquantized) and non-interpolated estimates of $\bU_{i,t}$ for each subcarrier and each time instant.
 The results have been averaged over 10 independent channel realizations, 100 channel evolutions each, for each $f_DT_s$}
 \label{achievrate}
-\vspace{-13pt}
 \end{figure}
@@
 This motivates further study into the framework as well, and future lines of work here would be a generalization of the framework to capture frequency correlations as well for predictive quantization, and a detailed analysis of impact on performance caused by choice of certain reservoir parameters like $\bA,\text{tanh}(\cdot)$, number of dimensions of the reservoir state.
+The reservoir computing framework can also be used to predict the future precoders at the receiver, so as to mitigate against the delay in feedback, on the lines of \cite{chang2011adaptive}, which forms another exciting line for future work.
 \vspace{-5pt}

### 2019-04-28 eval.py

@@ -13,10 +13,10 @@ signal.signal(signal.SIGINT, sigint_handler)
 # np.random.seed(0)
 np.random.seed(1)
 norm=1
-U_data=np.load("./BER_Data/ped_10_100_4_2.npy")
-qt_U_data=np.load("./BER_Data/qt_ped_10_100_4_2.npy")
-H_data=np.load("./BER_Data/ped_10_100_4_2_H.npy")
-sigma_data=np.load("./BER_Data/ped_10_100_4_2_sigma.npy")
+U_data=np.load("./Fin_Data/0.1/ped_10_100_4_2.npy")
+qt_U_data=np.load("./Fin_Data/0.1/qt_ped_10_100_4_2.npy")
+H_data=np.load("./Fin_Data/0.1/ped_10_100_4_2_H.npy")
+sigma_data=np.load("./Fin_Data/0.1/ped_10_100_4_2_sigma.npy")
 num_chans=10
 num_evols=100
 Nt=4
@@ -34,20 +34,21 @@ Eb_N0_dB=np.arange(-3,22,2)
 resBER_QPSK=np.zeros(Eb_N0_dB.shape[0])
 otBER_QPSK=np.zeros(Eb_N0_dB.shape[0])
 unqtBER_QPSK=np.zeros(Eb_N0_dB.shape[0])
+unqt_interpBER_QPSK=np.zeros(Eb_N0_dB.shape[0])
 indqtBER_QPSK=np.zeros(Eb_N0_dB.shape[0])
 count=0
-sil_BER=0
-sil_cap=1
+sil_BER=1
+sil_cap=0
 # qtiz_U=np.load('./Intmd_Res/qtiz_U0.npy')
 # cmp_qtiz_U=np.load('./Intmd_Res/cmp_qtiz_U0.npy')
 # cmp_qtiz_err=np.load('./Intmd_Res/cmp_qtiz_err0.npy')
 # qtiz_err=np.load('./Intmd_Res/qtiz_err0.npy')
 # fin_qt_U=np.load('./Intmd_Res/fin_qt_U0.npy')
-qtiz_U=np.load('./BER_Data2/qtiz_U_norm.npy')
-cmp_qtiz_U=np.load('./BER_Data2/cmp_qtiz_U_norm.npy')
-cmp_qtiz_err=np.load('./BER_Data2/cmp_qtiz_err_norm.npy')
[…]

### 2019-04-28 main.py

@@ -52,9 +52,9 @@ class reservoir:
 signal.signal(signal.SIGINT, sigint_handler)
 # np.random.seed(0)
 np.random.seed(1)
-norm=4
-data=np.load("./BER_Data/ped_10_100_4_2_norm"+str(norm)+".npy")
-ind_qt_data=np.load("./BER_Data/qt_ped_10_100_4_2_norm"+str(norm)+".npy")
+norm=3.5*1e-4
+data=np.load("./Fin_Data/BER/ped_10_100_4_2.npy")
+ind_qt_data=np.load("./Fin_Data/BER/qt_ped_10_100_4_2.npy")
 num_chans=10
 num_evols=100
 Nt=4
@@ -75,7 +75,7 @@ cmp_qtiz_err=np.zeros((num_chans,num_evols-1,feedback_subc))
 time_vals=4
 for chan_inst in range(num_chans):
 	print("--------------------------------------------------")
-	print("Starting Channel Instance: "+str(chan_inst))
+	print("Starting Channel Instance: "+str(chan_inst)+ " For Norm: "+str(norm))
 	print("--------------------------------------------------")
 
 	#Initialise with independent quantization
@@ -112,11 +112,11 @@ for chan_inst in range(num_chans):
 
 pdb.set_trace()
 
-# np.save('./BER_Data2/cmp_qtiz_U_10_100_norm'+str(norm)+'.npy',cmp_qtiz_U)
-# np.save('./BER_Data2/cmp_qtiz_err_10_100_norm'+str(norm)+'.npy',cmp_qtiz_err)
-# np.save('./BER_Data2/fin_qt_U_10_100_norm'+str(norm)+'.npy',fin_qt_U)
-# np.save('./BER_Data2/qtiz_err_10_100_norm'+str(norm)+'.npy',qtiz_err)
-# np.save('./BER_Data2/qtiz_U_10_100_norm'+str(norm)+'.npy',qtiz_U)
+# np.save('./Fin_Data/0.1/cmp_qtiz_U_10_100.npy',cmp_qtiz_U)
+# np.save('./Fin_Data/0.1/cmp_qtiz_err_10_100.npy',cmp_qtiz_err)
+# np.save('./Fin_Data/0.1/fin_qt_U_10_100.npy',fin_qt_U)
+# np.save('./Fin_Data/0.1/qtiz_err_10_100.npy',qtiz_err)
[…]

### 2019-04-28 paper/main.tex
Add changes

@@
 % Broad summary of your work, come to your problem definition.
-In MIMO wireless systems, precoding matrices are used for transformation of an $N_S$-dimensional ($N_S \leq \text{min}(N_T,N_R))$ information vector onto an $N_T$-dimensional transmit vector that corresponds to the signal emanating out of the $N_T$ antennas of the transmitter.
+In MIMO wireless systems, precoding matrices are used for transformation of an $N_S$-dimensional ($N_S \leq \text{min}(N_T,N_R))$ information vector onto an $N_T$-dimensional transmit vector that corresponds to the signal emanating from the $N_T$ antennas of the transmitter.
 The precoding matrix used to achieve the channel capacity using optimal power allocation is obtained using the SVD of the MIMO channel matrix \cite{love2008overview}.
@@
 Second, these precoders are correlated in both time and frequency.
-Capturing the available correlations allow for predictive quantization algorithms, which enable improvement of the quantization error with time.
+Capturing the available correlations permit the use of predictive quantization algorithms, which enable improvement of the quantization error with time.
 This improvement is obtained because exploiting the available correlations from past fed back precoders allow one to just quantize the extra information required on top of the past available temporal-frequency information, instead of the new precoder information in the entirety.
-Exploiting frequency correlations permits the use of interpolation algorithms, which in turn reduces the feedback overhead in a single OFDM frame, by feeding back CSI information only for certain subcarriers, and interpolating over the others.
+Exploiting frequency correlations permits the use of interpolation algorithms, which in turn reduce the feedback overhead in a single OFDM frame, by feeding back CSI information only for certain subcarriers, and interpolating over the others.
 Thus, combining these two inherent properties, viz.
@@
 Manifold based approaches for predictive quantization have provided significant performance benefits, given that they work with the effective lower dimensions while framing the manifold operations to predict and quantize.
-However, these approaches are difficult to implement and require some familiarity with manifold geometry for a complete grasp.
+However, these approaches are difficult to implement and require some operations on the manifold structure.
 In this paper, we propose a reservoir computing based predictive quantizer to exploit the temporal correlations effectively.
-The proposed scheme offers a cleaner solution to the predictive quantization problem, which brings about both ease of implementability, and improved performance as well, when compared to \cite{6891198}, which proposed a manifold based method of predictive quantization by exploiting temporal correlations.
+The proposed scheme offers a simple solution to the predictive quantization problem, which brings about both ease of implementation, and improved performance as well, when compared to \cite{6891198}, which proposed a manifold based method of predictive quantization by exploiting temporal correlations.
 
@@
 \cite{mosleh2017brain,shafin2018realizing} utilized the framework for OFDM symbol detection while accounting for channel and power amplifier non-linearities.
-In our work, we utilize the reservoir computing framework to discover the underlying nonlinear relations between previously observed precoders, in order to predict the precoder at next time instant.
+In our work, we utilize the reservoir computing framework to capture the underlying nonlinear relations between previously observed precoders, in order to predict the precoder at next time instant.
 This becomes analogous to time series prediction algorithms, for which the reservoir computing framework has been known to work effectively \cite{mosleh2017brain}.
@@
 \label{section2}
-\noindent We consider a point-to-point $N_T\times N_R$ MIMO-OFDM wireless system.
+We consider a point-to-point $N_T\times N_R$ MIMO-OFDM wireless system.
 The available bandwidth is divided into $N$ subcarriers, so that, individually for each subcarrier, the channel can be assumed to be flat fading.
-In this discussion, we assume that $N_T > N_R$ and $N_s = N_R$.
-Consistent with notation in \cite{6891198,Gupt1905:Predictive}, the data stream received on the $i$-th subcarrier is denoted by:
+In this discussion, we assume that $N_T > N_R$ and $N_s = N_R$. Consistent with notation in \cite{6891198,Gupt1905:Predictive}, the data stream received on the $i$-th subcarrier is denoted by:
 \begin{equation}

### 2019-04-28 paper/main.tex
More minor fixes in lines

@@
 Suppose that we predict the current precoding matrix based on the past $p$ observed precoding matrices, and hence $\tilde{\bU}_{i,t-p},\tilde{\bU}_{i,t-p+1},\ldots,\tilde{\bU}_{i,t-2},\tilde{\bU}_{i,t-1}$ have been fed back and available at the transmitter.
-By using a prediction algorithm and by exploiting time correlations among precoders at $t-p,t-p+1,\ldots,t-2,t-1$ time instances, the transmitter can obtain a prediction (coarse estimate) of $\bU_{i,t}$, as $\bP_{i,t}=f_P(\tilde{\bU}_{i,t-p},\tilde{\bU}_{i,t-p+1},\ldots,\tilde{\bU}_{i,t-2},\tilde{\bU}_{i,t-1})$, where $f_P: \text{St}(N_T,N_R)\times\ldots\{p-\text{times}\}\ldots\times\text{St}(N_T,N_R) \to \text{St}(N_T,N_R)$ is a prediction function.
+By using a prediction algorithm and by exploiting time correlations among precoders at time instances $t-p,t-p+1,\ldots,t-2,t-1$, the transmitter can obtain a prediction (coarse estimate) of $\bU_{i,t}$, as $\bP_{i,t}=f_P(\tilde{\bU}_{i,t-p},\tilde{\bU}_{i,t-p+1},\ldots,\tilde{\bU}_{i,t-2},\tilde{\bU}_{i,t-1})$, where $f_P: \text{St}(N_T,N_R)\times\ldots\{p-\text{times}\}\ldots\times\text{St}(N_T,N_R) \to \text{St}(N_T,N_R)$ is a prediction function.
 Now, since the transmitter already possesses a coarse estimate $\bP_{i,t}$ of $\bU_{i,t}$, the receiver just quantizes the local space of $\text{St}(N_T,N_R)$ nearby $\bP_{i,t}$, instead of the complete $\text{St}(N_T,N_R)$.
@@
 
-When using predictive quantization scheme, the quantization is performed on a smaller subspace when compared to the entire manifold in case of independent quantization.
+When using the predictive quantization scheme, the quantization is performed on a smaller subspace when compared to the entire manifold in case of independent quantization.
 Therefore, the quantization error is substantially lower as well.
 However, independent quantization algorithms are important for smart initialization (instead of a cold start) of the predictive quantization strategies.
-Observe that predictive quantization algorithms for SVD precoders are typically the higher dimensional analogues of the well known approaches to reduce quantization error using linear prediction codes (LPCs) and Delta PCM.
+Observe that predictive quantization algorithms for SVD precoders are typically the higher dimensional analogues of well known approaches to reduce quantization error using linear prediction codes (LPCs) and Delta PCM.
 In both LPCs and Delta PCM, quantization error can be reduced substantially using a linear predictor and quantizing the scalar difference between the predicted and observed value (innovation).

### 2019-04-28 paper/main.tex
Minor changes by Kumar

@@
 A precoding matrix $\mathcal{\bM} \in \text{St}(N_T,N_R)$ is a $N_T\times N_R$ matrix with the property $\mathcal{\bM}^H\mathcal{\bM}=\text{\textbf{1}}_{N_R}$.
-For brevity, we call such a matrix $\mathcal{\bM}$ to be a `semi-unitary' matrix.
-A na{\"i}ve method to vectorize a $N_T\times N_R$ semi-unitary matrix would be to take all it's $N_TN_R$ complex numbers individually and stack them onto a $2N_TN_R$ dimensional real vector.
-However, a more efficient approach would be to use the $\mathcal{\bM}^H\mathcal{\bM}=\text{\textbf{1}}_{N_R}$ property, which implies that each vector representing the columns of $\mathcal{\bM}$ is orthogonal to the other columns.
+For brevity, we call such a matrix $\mathcal{\bM}$ a `semi-unitary' matrix.
+A na{\"i}ve method to vectorize a $N_T\times N_R$ semi-unitary matrix would be to take all its $N_TN_R$ complex numbers individually and stack them onto a $2N_TN_R$ dimensional real vector.
+However, a more efficient approach would be to use the $\mathcal{\bM}^H\mathcal{\bM}=\text{\textbf{1}}_{N_R}$ property, which implies that each vector that represents the columns of $\mathcal{\bM}$ is orthogonal to the other columns.
 For the first column, we take its $N_T$ complex numbers and stack them onto a $2N_T$ vector.
@@
 Therefore, we can vectorize the $N_T\times N_R$ $\mathcal{\bM}$ into a $2(N_T)+2(N_T-1)+\ldots+2(N_T-N_R+1)= 2N_TN_R-(N_R^2-N_R)$ dimensional vector.
-For a semi-unitary matrix $\mathcal{\bM}$, denote by $\mathcal{\bm}$ it's vectorized representation.
+For a semi-unitary matrix $\mathcal{\bM}$, we denote by $\mathcal{\bm}$ its vectorized representation.
 
@@
 This corresponds to an overhead of $N_R$ dimensions, since we have not exploited the fact that each of the $N_R$ column vectors is a unit norm vector as well.
-It looks as if we could just take $N_T-1$ complex numbers when vectorizing the first column, instead of $N_T$, but this would lead to a non-unique representation, since there could then be infinite possibilities of the missing one complex number, such that the vector has a norm 1.
+It looks as if we could just take $N_T-1$ complex numbers when vectorizing the first column, instead of $N_T$, but this would lead to a non-unique representation, since there could then be infinite possibile values that the lone missing complex number can take, so that the vector has unit norm.
 %Focus on the fact that you don't actually pay a penalty
@@
 
-The input to the reservoir $i$ corresponding to subcarrier $i$ is $\tilde{\bu}_{i,t-1}$, (vectorized representation of $\tilde{\bU}_{i,t-1}$) with dimensions $D_{\text{in}}=2N_TN_R-N_R^2+N_R$.
+The input to the reservoir $i$ that corresponds to subcarrier $i$ is $\tilde{\bu}_{i,t-1}$, (vectorized representation of $\tilde{\bU}_{i,t-1}$) with dimensions $D_{\text{in}}=2N_TN_R-N_R^2+N_R$.
 Using a randomly initialized $D_{\text{in}}\times D_{\text{resv}}$ input coupler matrix, $\bW^{\text{in}}_i$, the $D_{\text{in}}$ dimensional input is mapped to a $D_{\text{resv}}(>D_{\text{in}})$ dimensional vector, where $D_{\text{resv}}$ is the dimension of the reservoir state vector $\br_{i,t}$.
-$\br_{i,t}$ is initialized with $D_{\text{resv}}$ zeros, and is updated via the following equation,
+$\br_{i,t}$ is initialized with $D_{\text{resv}}$ zeros, and is updated via the following equation:
 \begin{equation}
@@
 where $\bA_i$ is the adjacency matrix that captures the reservoir dynamics, and $\text{tanh}$ is applied element wise.
-Typical choices for $\bA_i$ have been Erdos-Renyi graphs with an upper bounded maximum eigen value \cite{mosleh2017brain,pathak2017using}.
+Typical choices for $\bA_i$ have been Erdos-Renyi graphs with an upper bounded maximum eigenvalue \cite{mosleh2017brain,pathak2017using}.
 

### 2019-04-28 paper/main.tex
Add changes

@@
 \label{qp}
-Before proceeding, it is critical to describe the quantization function $q_P(\bP_{i,t},\text{fb}_{i,t})$, which is similar to the one used in \cite{6891198,Gupt1905:Predictive,6545375}.
+We now describe the quantization function $q_P(\bP_{i,t},\text{fb}_{i,t})$, which is similar to the one used in \cite{6891198,Gupt1905:Predictive,6545375}.
 Central to the quantization algorithm is the fact that tangent spaces local to a point in manifold are linear vector spaces.
@@
 A corresponding retraction operation $Y=\texttt{retract}(X,\bT^Y_X)$, $\texttt{retract}: \text{St}(N_T,N_R)\times \mathcal{T}_X \text{St}(N_T,N_R) \to \text{St}(N_T,N_R)$ gives back the manifold point obtained by traversing in the tangent direction given by the second argument.
-In this work, the chosen lifting-retraction operations are the Cayley Exponentials, discussed in \cite{DBLP:journals/corr/abs-1708-00045,Gupt1905:Predictive}. % and used in \cite{Gupt1905:Predictive}.
+In this work, the chosen lifting-retraction operations are the Cayley exponentials, discussed in \cite{DBLP:journals/corr/abs-1708-00045,Gupt1905:Predictive}. % and used in \cite{Gupt1905:Predictive}.
 The Cayley exponential lifting operation maps two points in $\text{St}(N_T,N_R)$, to a $N_T\times N_T$ skew Hermitian matrix that represents the tangent from first point to the other.
@@
 With the optimum direction chosen, the next step is to determine how much to move in that particular chosen direction, viz. the length of the chosen tangent direction.
-For this, we adopt the strategy in \cite{6891198}, which
-controls the magnitude of tangent steps, by having two codebooks
-$T^{\mathcal{C}}_p,T^{\mathcal{C}}_m$ of different spreads $s_p,s_m$, but same $2^{\mathcal{B}-1}$ base vectors in the $\text{base}^{\mathcal{C}}$, i.e.
+For this, we adopt the strategy in \cite{6891198}, which controls the magnitude of tangent steps, by having two codebooks $T^{\mathcal{C}}_p,T^{\mathcal{C}}_m$ of different spreads $s_p,s_m$, but same $2^{\mathcal{B}-1}$ base vectors in the $\text{base}^{\mathcal{C}}$, i.e.
 $T^{\mathcal{C}}_{\{p/m\}}=s_{\{p/m\}}\text{base}^{\mathcal{C}}$ (All codewords $\in \text{base}^{\mathcal{C}}$ multiplied by $s_{\{p/m\}}$ individually).
@@
 \end{equation}
-
-\noindent $\text{fb}_{i,t}$ is also used to update the spread of the codebooks $T^{\mathcal{C}}_p,T^{\mathcal{C}}_m$.
-Depending on whether $\text{fb}_{i,t} \geq 2^{\mathcal{B}-1}$,
-i.e. whether the optimum codeword is in $T^{\mathcal{C}}_p$ or
-$T^{\mathcal{C}}_m$, the scale parameter $s[k]$, which in turn
-controls values of $s_p, s_m$, is updated accordingly,
+$\text{fb}_{i,t}$ is also used to update the spread of the codebooks $T^{\mathcal{C}}_p,T^{\mathcal{C}}_m$.
+Depending on whether $\text{fb}_{i,t} \geq 2^{\mathcal{B}-1}$, i.e.
+whether the optimum codeword is in $T^{\mathcal{C}}_p$ or $T^{\mathcal{C}}_m$, the scale parameter $s[k]$, which in turn controls values of $s_p, s_m$, is updated accordingly, as
 $$s_p=g^{\text{min}(s[k-1]+1,0)}, s_m = g^{s[k-1]-1}$$
@@
 \label{train}
-\noindent Having described the technicalities of $f_P,q_P$, we are now ready to describe the training process for the reservoir.
-Recall that to obtain $\tilde{\bU}_{i,t}$ from  $\tilde{\bU}_{i,t-1}$, we have,
+\noindent Having described the technicalities of $f_P,q_P$, we now describe the training process for the reservoir.
+Recall that, to obtain $\tilde{\bU}_{i,t}$ from  $\tilde{\bU}_{i,t-1}$, we have
 \begin{equation}
@@
 \end{equation}
-The key idea here is that as the predicted matrix $\bP_{i,t}$ (the coarse estimate), gets closer to $\tilde{\bU}_{i,t}$ (the refined estimate), the receiver has to quantize even smaller subspaces and can thus provide a more refined estimate from the feedback $\text{fb}_{i,t}$.
-Hence, for the time instant $t\geq1$, we train the reservoir output coupler such that the following objective function is optimized,
+The key idea here is that, as the predicted matrix $\bP_{i,t}$ (the coarse estimate), gets closer to $\tilde{\bU}_{i,t}$ (the refined estimate), the receiver has to quantize even smaller subspaces, and can thus provide a more refined estimate from the feedback $\text{fb}_{i,t}$.
+So, for the time instant $t\geq 1$, we train the reservoir output coupler such that the following objective function is optimized:
 \begin{equation}
@@
 \end{equation}
-here $\lambda>1$ is the history parameter. We wish to perform the following optimization in order to find the optimum $\bW_{i,t}^{\text{out}}$ from the available estimates till time $t$,
+Here $\lambda>1$ is the history parameter.
+We wish to perform the following optimization in order to find the optimum $\bW_{i,t}^{\text{out}}$ from the available estimates till time $t$:
 \begin{equation}
@@
 \end{equation}
-Computing the gradient $\frac{\partial \mathcal{O}_{i,t}}{\partial \bW_{i,t}^{\text{out}}}$, setting it to null matrix gives,
+Computing the gradient $\frac{\partial \mathcal{O}_{i,t}}{\partial \bW_{i,t}^{\text{out}}}$ and setting it to the null matrix yields
 \begin{equation}
@@
 Let $\sum_{s=1}^{t}\frac{1}{\lambda^{t-s}}\texttt{outer}(\tilde{\bu}_{i,s},\br_{i,s})$ be $\text{\textbf{num}}_{i,t}$ and $\sum_{s=1}^{t}\frac{1}{\lambda^{t-s}}||\br_{i,s}||^2$ be $\text{den}_{i,t}$, with $\bW_{i,t}^{\text{out}}=\frac{\text{\textbf{num}}_{i,t}}{\text{den}_{i,t}}$.
-Observe that,
+Observe that
 \begin{equation}
@@
 \end{equation}
-\eqref{wout_upd} makes training of the reservoir easy to implement, and of low complexity as well.
-We only need to store the matrix $\text{\textbf{num}}_{i,t-1}$, a number $\text{den}_{i,t-1}$, and using the current reservoir state $\br_{i,t}$ and $\tilde{\bu}_{i,t}$ obtained from \eqref{fpqp}, $\bW_{i,t}^{\text{out}}$ can be calculated, to obtain predicted coarse estimate of $\tilde{\bu}_{i,t+1}$.
-This completes our technical discussion for the reservoir computing based framework for predictive quantization illustrated in Fig. \ref{res_overview}
+\eqref{wout_upd} makes training of the reservoir easy to implement with low complexity.
+We only need to store the matrix $\text{\textbf{num}}_{i,t-1}$, a number $\text{den}_{i,t-1}$.
+Then, using the current reservoir state $\br_{i,t}$ and $\tilde{\bu}_{i,t}$ obtained from \eqref{fpqp}, $\bW_{i,t}^{\text{out}}$ can be calculated to obtain the predicted coarse estimate of $\tilde{\bu}_{i,t+1}$.
+This completes our technical discussion for the reservoir computing based framework for predictive quantization illustrated in Fig. \ref{res_overview}.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-To conclude this section, we now summarize and highlight the novel points of the proposed framework for predictive quantization.
-The first key advantage of the proposed framework, over the past work \cite{Gupt1905:Predictive,6891198,6545375} is that the prediction function and quantization function are not independent of each other.
-To see this, observe \eqref{update_Wt1} to obtain $\bW^{\text{out}}_{i,t-1}$ from $\tilde{\bU}_{i,t-1}=q_P(f_P(\tilde{\bU}_{i,t-2}),\text{fb}_{i,t-1})$, and \eqref{pred} to obtain $\bP_{i,t+1}$,
+Finally, we summarize and highlight the novel aspects of the proposed framework for predictive quantization.
+The first key advantage of the proposed approach over the past work \cite{Gupt1905:Predictive,6891198,6545375} is that the prediction function and quantization function are not independent of each other.
+To see this, observe \eqref{update_Wt1} to obtain $\bW^{\text{out}}_{i,t-1}$ from $\tilde{\bU}_{i,t-1}=q_P(f_P(\tilde{\bU}_{i,t-2}),\text{fb}_{i,t-1})$, and \eqref{pred} to obtain $\bP_{i,t+1}$
 \begin{equation}
@@
 This is done by optimizing $\bW_{i,t}^{\text{out}}$ such that the prediction output to be as close to the output from $q_P$ (Objective function $\mathcal{O}_{i,t}$).
-The updated $\bW_{i,t}^{\text{out}}$ is then used in forward pass to predict $\bP_{i,t+1}$, which is hopefully closer to $\tilde{\bU}_{i,t+1}$ than $\bP_{i,t}$ was to $\tilde{\bU}_{i,t}$ due to optimization of $\mathcal{O}_{i,t}$.
+The updated $\bW_{i,t}^{\text{out}}$ is then used in the forward pass to predict $\bP_{i,t+1}$, which is likely closer to $\tilde{\bU}_{i,t+1}$ than $\bP_{i,t}$ was to $\tilde{\bU}_{i,t}$ due to optimization of $\mathcal{O}_{i,t}$.
 
-\textcolor{blue}{Another advantage of the proposed scheme comes from the ease of training the reservoir, entailed by \eqref{res_upd}.
+\textcolor{blue}{Another advantage of the proposed scheme is the ease of training the reservoir, captured in \eqref{res_upd}.
 By storing just one matrix $\text{\textbf{num}}_{i,t}$ and a number $\text{den}_{i,t}$, we capture the entire history of the precoding matrices, with past values weighted by $\lambda$.
-This is a departure from previous schemes \cite{Gupt1905:Predictive,6891198,6545375} which store the past $n$ (which has to be pre-decided) precoders in a $n$ sized cyclic buffer kind-of arrangement.
-Reservoir computing, thus proposes an easier to train (data centric) scheme, which is not typical for typical data centric ML based schemes.}
+This is a departure from previous schemes \cite{Gupt1905:Predictive,6891198,6545375} which store the past $n$ precoders precoders in a $n$ sized cyclic buffer ($n$ also has to be pre-decided).
+Reservoir computing, thus proposes an easier to train (data centric) scheme, which is not typical in data centric ML based schemes.}
 
@@
 \noindent We simulate both our predictive quantization algorithm and the one presented in \cite{6891198} for the IEEE Pedestrian-A channel, with $N_T=4$, $N_R=2$. 
-The channel matrices $\bH_{i,t}$ are generated using Jake’s model for realistic simulations, from the IT++ library through the python wrapper py-itpp \cite{ViditPy}. 
-Although in both our work and \cite{6891198}, only temporal correlations are exploited, we compare the BER, quantization error and logsum rate results for the complete MIMO-OFDM setting with number of subcarriers $N=64$, and evenly spaced $8$ fed back subcarriers, indexed from 0, viz.
+The channel matrices $\bH_{i,t}$ are generated using Jake's model for realistic simulations, from the IT++ library through the python wrapper py-itpp \cite{ViditPy}. 
+Although in both our work and \cite{6891198}, only temporal correlations are exploited, we compare the BER, quantization error and logsum rate results for the complete MIMO-OFDM setting with $N=64$ of subcarriers, and channels are fed back for $8$ evenly spaced subcarriers, indexed starting at 0, viz.
 $\{0,9,\ldots,63\}$ ($\{9k, k \in \{0,1,\ldots,7\}\}$).
-The precoding matrices at non fedback subcarriers ($i\neq\{9k\}$) are estimated via the Cayley Interpolation method presented in \cite{Gupt1905:Predictive}.
-Feedback is available for $i=\{9k\}$ subcarriers (i.e.
-transmitter obtains $\text{fb}_{\{9k\},t}$) for predictive quantization.
-The setting is visually illustrated in Fig.
-\ref{table}.
-A 6 bit codebook generated via Lloyd codebook algorithm for the Stiefel Manifold in \cite{6678348} is used to feedback $\tilde{\bU}_{\{9k\},0}$ and differential quantization (i.e.
-$\bP_{i,t}=\tilde{\bU}_{i,t-1}$) is used for 10 time instances to provide provide the initial training data for the reservoir and for overcoming initial transient response of the reservoir discussed in \cite{mosleh2017brain}.
-A 6 bit base codebook is used for the quantization function $q_P$, generated according to the method presented in Section \ref{qp} and \cite{Gupt1905:Predictive}.
-Hence, for both initialization and subsequent feedback, $\text{fb}_{i,t}$ can be encoded via 6 bits (i.e.
-$\mathcal{B}=6$ Section \ref{section2}).
+The precoding matrices at subcarriers were channels are not fed back ($i\neq\{9k\}$) are estimated via the Cayley Interpolation method presented in \cite{Gupt1905:Predictive}.
+Feedback is available for $i=\{9k\}$ subcarriers (i.e. transmitter obtains $\text{fb}_{\{9k\},t}$) for predictive quantization.
+The setting is visually illustrated in Fig. \ref{table}.
+A 6 bit codebook generated using the Lloyd codebook algorithm for the Stiefel Manifold in \cite{6678348} is used to feedback $\tilde{\bU}_{\{9k\},0}$ and differential quantization (i.e.
+$\bP_{i,t}=\tilde{\bU}_{i,t-1}$) is used for 10 time instances to provide provide the initial training data for the reservoir and for overcoming initial transient response of the reservoir, as discussed in \cite{mosleh2017brain}.
+A 6 bit base codebook that is used for the quantization function $q_P$ is generated according to the method presented in Section \ref{qp} and \cite{Gupt1905:Predictive}.
+Hence, for both initialization and subsequent feedback, $\text{fb}_{i,t}$ can be encoded using 6 bits (i.e. $\mathcal{B}=6$ Section \ref{section2}).
 The bit budget per OFDM frame is thus 48 bits, for total 8 equally spaced fed back subcarriers $\{9k, k \in \{0,1,\ldots,7\}\}$.
 
-For predicting each of the $8$ fed-back subcarriers, we consider $8$ separate reservoirs, each of them evolved separately, with $i\in\{9k, k \in \{0,1,\ldots,7\}\}$ in both the forward pass prediction and quantization ($f_P,q_P$) \eqref{fpqp} and backward pass to update $\bW_{i,t}^{\text{out}}$ \eqref{backpass}.
+For predicting channels at each of the $8$ fed-back subcarriers, we consider $8$ separate reservoirs, each of them evolved separately, with $i\in\{9k, k \in \{0,1,\ldots,7\}\}$ in both the forward pass prediction and quantization ($f_P,q_P$) \eqref{fpqp} and backward pass to update $\bW_{i,t}^{\text{out}}$ \eqref{backpass}.
 Unlike \cite{Gupt1905:Predictive}, we do not exploit frequency correlations for predictive quantization, and the $8$ reservoirs for prediction of $8$ fed-back subcarriers are kept independent of each other.
-All these 8 reservoirs are initialized with $\bA_{i\in\{9k\}}$ being an Erdos-Reny\"i graph, with probability of edge connections being $0.2$, $\lambda=2$, $\bW^{\text{out/in}}_{i\in\{9k\},0}$ being randomly assigned, $D_{\text{in}}=D_{\text{out}}=14$ (vectorized representation of $4\times2$ semi-unitary matrix, Section \ref{vectorize}) and $D_{\text{resv}}=60$.r
+All these 8 reservoirs are initialized with $\bA_{i\in\{9k\}}$ being an Erdos-Reny\"i graph, with probability of edge connections being $0.2$, $\lambda=2$, $\bW^{\text{out/in}}_{i\in\{9k\},0}$ being randomly assigned, $D_{\text{in}}=D_{\text{out}}=14$ (vectorized representation of $4\times2$ semi-unitary matrix, Section \ref{vectorize}) and $D_{\text{resv}}=60$.
 
@@
 \includegraphics[width=0.5\textwidth]{images/table.pdf}
-\caption{The transmitter obtains feedback for $\{0,9,\ldots,63\}$ ($\{9k, k \in \{0,1,\ldots,7\}\}$ subcarriers, and uses $\tilde{\bU}_{i,t-1}$, alongwith $f_P,q_P$ \eqref{fpqp} to obtain $\tilde{\bU}_{i,t}$, illustrated in the figure via cyan arrows.
-For each time instant, the transmitter uses the Cayley method to interpolate $\tilde{\bU}_{i,t}$ at $i\neq\{9k\}$ subcarriers}
+\caption{The transmitter obtains feedback for $\{0,9,\ldots,63\}$ ($\{9k, k \in \{0,1,\ldots,7\}\}$ subcarriers, and uses $\tilde{\bU}_{i,t-1}$, along with $f_P,q_P$ \eqref{fpqp} to obtain $\tilde{\bU}_{i,t}$, illustrated in the figure via cyan arrows.
+For each time instant, the transmitter uses the Cayley method to interpolate $\tilde{\bU}_{i,t}$ at $i\neq\{9k\}$ subcarriers.}
 \label{table}
@@
 \label{res}{}
-Considering mitigation against randomly appearing drastic events in wireless channels, like sudden interferences, and dynamic environment, only 100 channel evolutions are considered for the simulations.
-Averaging is done over 10 independent channel realizations, to ensure that the simulation results hold in general for the chosen IEEE Pedestrian A channel profile.
-Hence, the quantization error, BER and achievable rate results are simulated for 1000 channel instances, with 100 channel evolutions of 10 independent channel realizations.
-
+To mitigate errors in tracking in the presence of randomly appearing drastic events in wireless channels, such as sudden interferences and dynamic environments, only 100 channel evolutions are considered for the simulations.
+Averaging is performed over 10 independent channel realizations, to ensure that the simulation results hold in general for the chosen IEEE Pedestrian A channel profile.
+Therefore, the quantization error, BER and achievable rate results are averaged over 1000 channel instances, with 100 channel evolutions of 10 independent channel realizations.
 \begin{figure}[h]
@@
 \includegraphics[width=0.45\textwidth]{images/qtizErr.pdf}
-\caption{Quantization error in terms of chordal distance to the actual precoder $\bU_{\{9k\},t}$ observed at the receiver, from the quantized estimate $\tilde{\bU}_{\{9k\},t}$ at the transmitter, averaged over 8 fed back subcarriers ($\{9k, k \in \{0,1,\ldots,7\}\}$) and 10 independent channel realizations ($f_DT_s=10^{-4}$)}
+\caption{Quantization error in terms of chordal distance to the actual precoder $\bU_{\{9k\},t}$ observed at the receiver, from the quantized estimate $\tilde{\bU}_{\{9k\},t}$ at the transmitter, averaged over 8 fed back subcarriers ($\{9k, k \in \{0,1,\ldots,7\}\}$) and 10 independent channel realizations (normalized Doppler $f_DT_s=10^{-4}$).}
 \label{qtiz_err}
 \end{figure}
-
 From Fig.
-\ref{qtiz_err} it is evident that the reservoir computing based predictive quantizer is able to reduce the quantization error below what was obtained from the existing temporal correlations based predictive quantizer in \cite{6891198}.
+\ref{qtiz_err} it is evident that the reservoir computing based predictive quantizer is able to reduce the quantization error to below what was obtained from the existing temporal correlation based predictive quantizer in \cite{6891198}.
 In addition, the quantization error is much smoother, which can be explained from the fact that the reservoir computing approach optimizes, $\mathcal{O}_{i,t}$ that captures the long term dynamics of the channel and hence, is able to correct for jittery variations.
@@
 We simulate the (uncoded QPSK) BER performance for precoders obtained after interpolation ($\tilde{\bU}_{i\neq\{9k\},t}$) and quantization ($\tilde{\bU}_{\{9k\},t}$), for all the 63 subcarriers.
-Observe from Fig.
-\ref{BER} that reservoir computing framework is able to achieve substantial improvements in $\text{E}_\text{b}\text{N}_0$ levels at $\text{BER}\leq 10^{-3}$.
-Particularly, observe, for $\text{BER}=10^{-4}$ we observe around $5$ dB improvement.
-Also, notice the substantial improvement which both the predictive quantization schemes offer from the independent quantization scheme with Lloyd codebook for precoders \cite{6678348}, using the same number of bits.
+Observe from Fig. \ref{BER} that reservoir computing framework is able to achieve substantial improvements in $\text{E}_\text{b}\text{N}_0$ levels at $\text{BER}\leq 10^{-3}$.
+Particularly, for $\text{BER}=10^{-4}$, we observe around $5$ dB improvement.
+In addition, substantial improvement is obtained with both the predictive quantization schemes over the independent quantization scheme with Lloyd codebook for precoders \cite{6678348}, using the same number of bits.
 
-For simulating the achievable rate for the point-to-point MIMO system considered, we quantize the sigma values ($\Sigma_{i,t}$ obtained from SVD of $\bH_{i,t}$) using a 2 bit vector quantizer ($k$-means), and feed them back to the transmitter for fed back subcarriers ($\{9k, k \in \{0,1,\ldots,7\}\}$).
-For the non-fed back subcarriers, they are interpolated via nai\"ve linear interpolation method as in \cite{Gupt1905:Predictive}.
-Observe from Fig.
-\ref{achievrate} that the reservoir computing framework offers signicant improvement in achievable rate for $f_DT_s=10^{-4}$.
-Since the temporal variations for $f_DT_s=10^{-2}, 10^{-1}$ are higher, the reservoir computing framework has to learn a faster-varying function, and hence the degradation in performance.
-However, it still matches the performance of the predictive quantizer in \cite{6891198} for $f_DT_s=10^{-2}$ and performs slightly better for $f_DT_s=10^{-1}$.
+For simulating the achievable rate for the point-to-point MIMO system, we quantize the channel matrix singular values ($\Sigma_{i,t}$ obtained from SVD of $\bH_{i,t}$) using a 2 bit vector quantizer ($k$-means), and feed them back to the transmitter for fed back subcarriers ($\{9k, k \in \{0,1,\ldots,7\}\}$).
+For the non-fed back subcarriers, they are interpolated by nai\"ve linear interpolation, as in \cite{Gupt1905:Predictive}.
+Observe from Fig. \ref{achievrate} that the reservoir computing framework offers significant improvement in achievable rate for normalized Doppler $f_DT_s=10^{-4}$.
+Since temporal variations for normalized Doppler $f_DT_s=10^{-2}, 10^{-1}$ are higher, the reservoir computing framework has to learn a faster-varying function, and hence the degradation in performance.
+However, it still matches the performance of the predictive quantizer in \cite{6891198} for normalized Doppler $f_DT_s=10^{-2}$ and slightly outperforms slightly for $f_DT_s=10^{-1}$.
 \begin{figure}[h]
@@
 \includegraphics[width=0.45\textwidth]{images/BER_res.pdf}
-\caption{BER results after obtaining non fed back $\tilde{\bU}_{i\neq\{9k\},t}$ from $\tilde{\bU}_{\{9k\},t}$ via Cayley interpolation \cite{Gupt1905:Predictive}, averaged over 10 independent channel realizations, 100 channel evolutions each ($f_DT_s=10^{-4}$)}
+\caption{BER results after obtaining non fed back $\tilde{\bU}_{i\neq\{9k\},t}$ from $\tilde{\bU}_{\{9k\},t}$ via Cayley interpolation \cite{Gupt1905:Predictive}, averaged over 10 independent channel realizations, 100 channel evolutions each (normalized Doppler $f_DT_s=10^{-4}$).}
 \label{BER}
@@
 \includegraphics[width=0.45\textwidth]{images/hopRate.pdf}
-\caption{Achievable Rate results for the two predictive quantization methods considered.
+\caption{Achievable rate results for the two predictive quantization methods considered.
 The results are presented as a percentage of the ideal achievable rate obtained when the transmitter has the accurate (unquantized) and non-interpolated estimates of $\bU_{i,t}$ for each subcarrier and each time instant.
-The results have been averaged over 10 independent channel realizations, 100 channel evolutions each, for each $f_DT_s$}
+The results have been averaged over 10 independent channel realizations, 100 channel evolutions each, for each normalized Doppler value ($f_DT_s$).}
 \label{achievrate}
@@
 \vspace{-3pt}
-In this paper, we have presented a reservoir computing framework to exploit temporal correlations for predictive quantization of SVD based precoders.
-The simulations reveal reduced quantization error, improved BER performance, and higher achievable rate from the proposed framework.
-This motivates further study into the framework as well, and future lines of work here would be a generalization of the framework to capture frequency correlations as well for predictive quantization, and a detailed analysis of impact on performance caused by choice of certain reservoir parameters like $\bA,\text{tanh}(\cdot)$, number of dimensions of the reservoir state.
-The reservoir computing framework can also be used to predict the future precoders at the receiver, so as to mitigate against the delay in feedback, on the lines of \cite{chang2011adaptive}, which forms another exciting line for future work.
+In this paper, we have presented a reservoir computing framework that exploits temporal correlations for predictive quantization of SVD based precoders.
+The simulations reveal that reduced quantization error reduces significantly, and BER improves significantly, and achievable rates are higher in when using the proposed framework.
+This motivates further study into the framework as well, and future work  would involve a generalization of the framework to capture frequency correlations as well for predictive quantization, and a detailed analysis of impact on performance caused by choice of different reservoir parameters like $\bA,\text{tanh}(\cdot)$, and number of dimensions of the reservoir state.
+The reservoir computing framework can also be used to predict the future precoders at the receiver, so as to mitigate issues caused by delay in feedback, on the lines of \cite{chang2011adaptive}, which forms another interesting path for future enhancements.
 \vspace{-5pt}

### 2019-04-30 paper/main.tex
Changes in result section

--- 2019-04-28 paper/main.tex
@@
 % Broad summary of your work, come to your problem definition.
-In MIMO wireless systems, precoding matrices are used for transformation of an $N_S$-dimensional ($N_S \leq \text{min}(N_T,N_R))$ information vector onto an $N_T$-dimensional transmit vector that corresponds to the signal emanating from the $N_T$ antennas of the transmitter.
+In MIMO wireless systems, precoding matrices are used for transformation of an $N_S$-dimensional ($N_S \leq \text{min}(N_T,N_R))$ information vector onto an $N_T$-dimensional transmit vector that corresponds to the signal emanating out of the $N_T$ antennas of the transmitter.
 The precoding matrix used to achieve the channel capacity using optimal power allocation is obtained using the SVD of the MIMO channel matrix \cite{love2008overview}.
@@
 Second, these precoders are correlated in both time and frequency.
-Capturing the available correlations permit the use of predictive quantization algorithms, which enable improvement of the quantization error with time.
+Capturing the available correlations allow for predictive quantization algorithms, which enable improvement of the quantization error with time.
 This improvement is obtained because exploiting the available correlations from past fed back precoders allow one to just quantize the extra information required on top of the past available temporal-frequency information, instead of the new precoder information in the entirety.
-Exploiting frequency correlations permits the use of interpolation algorithms, which in turn reduce the feedback overhead in a single OFDM frame, by feeding back CSI information only for certain subcarriers, and interpolating over the others.
+Exploiting frequency correlations permits the use of interpolation algorithms, which in turn reduces the feedback overhead in a single OFDM frame, by feeding back CSI information only for certain subcarriers, and interpolating over the others.
 Thus, combining these two inherent properties, viz.
@@
 Manifold based approaches for predictive quantization have provided significant performance benefits, given that they work with the effective lower dimensions while framing the manifold operations to predict and quantize.
-However, these approaches are difficult to implement and require some operations on the manifold structure.
+However, these approaches are difficult to implement and require some familiarity with manifold geometry for a complete grasp.
 In this paper, we propose a reservoir computing based predictive quantizer to exploit the temporal correlations effectively.
-The proposed scheme offers a simple solution to the predictive quantization problem, which brings about both ease of implementation, and improved performance as well, when compared to \cite{6891198}, which proposed a manifold based method of predictive quantization by exploiting temporal correlations.
+The proposed scheme offers a cleaner solution to the predictive quantization problem, which brings about both ease of implementability, and improved performance as well, when compared to \cite{6891198}, which proposed a manifold based method of predictive quantization by exploiting temporal correlations.
 
@@
 \cite{mosleh2017brain,shafin2018realizing} utilized the framework for OFDM symbol detection while accounting for channel and power amplifier non-linearities.
-In our work, we utilize the reservoir computing framework to capture the underlying nonlinear relations between previously observed precoders, in order to predict the precoder at next time instant.
+In our work, we utilize the reservoir computing framework to discover the underlying nonlinear relations between previously observed precoders, in order to predict the precoder at next time instant.
 This becomes analogous to time series prediction algorithms, for which the reservoir computing framework has been known to work effectively \cite{mosleh2017brain}.
@@
 \label{section2}
-We consider a point-to-point $N_T\times N_R$ MIMO-OFDM wireless system.
+\noindent We consider a point-to-point $N_T\times N_R$ MIMO-OFDM wireless system.
 The available bandwidth is divided into $N$ subcarriers, so that, individually for each subcarrier, the channel can be assumed to be flat fading.
-In this discussion, we assume that $N_T > N_R$ and $N_s = N_R$. Consistent with notation in \cite{6891198,Gupt1905:Predictive}, the data stream received on the $i$-th subcarrier is denoted by:
+In this discussion, we assume that $N_T > N_R$ and $N_s = N_R$.
+Consistent with notation in \cite{6891198,Gupt1905:Predictive}, the data stream received on the $i$-th subcarrier is denoted by:
 \begin{equation}
@@
 Suppose that we predict the current precoding matrix based on the past $p$ observed precoding matrices, and hence $\tilde{\bU}_{i,t-p},\tilde{\bU}_{i,t-p+1},\ldots,\tilde{\bU}_{i,t-2},\tilde{\bU}_{i,t-1}$ have been fed back and available at the transmitter.
-By using a prediction algorithm and by exploiting time correlations among precoders at time instances $t-p,t-p+1,\ldots,t-2,t-1$, the transmitter can obtain a prediction (coarse estimate) of $\bU_{i,t}$, as $\bP_{i,t}=f_P(\tilde{\bU}_{i,t-p},\tilde{\bU}_{i,t-p+1},\ldots,\tilde{\bU}_{i,t-2},\tilde{\bU}_{i,t-1})$, where $f_P: \text{St}(N_T,N_R)\times\ldots\{p-\text{times}\}\ldots\times\text{St}(N_T,N_R) \to \text{St}(N_T,N_R)$ is a prediction function.
+By using a prediction algorithm and by exploiting time correlations among precoders at $t-p,t-p+1,\ldots,t-2,t-1$ time instances, the transmitter can obtain a prediction (coarse estimate) of $\bU_{i,t}$, as $\bP_{i,t}=f_P(\tilde{\bU}_{i,t-p},\tilde{\bU}_{i,t-p+1},\ldots,\tilde{\bU}_{i,t-2},\tilde{\bU}_{i,t-1})$, where $f_P: \text{St}(N_T,N_R)\times\ldots\{p-\text{times}\}\ldots\times\text{St}(N_T,N_R) \to \text{St}(N_T,N_R)$ is a prediction function.
 Now, since the transmitter already possesses a coarse estimate $\bP_{i,t}$ of $\bU_{i,t}$, the receiver just quantizes the local space of $\text{St}(N_T,N_R)$ nearby $\bP_{i,t}$, instead of the complete $\text{St}(N_T,N_R)$.
@@
 
-When using the predictive quantization scheme, the quantization is performed on a smaller subspace when compared to the entire manifold in case of independent quantization.
+When using predictive quantization scheme, the quantization is performed on a smaller subspace when compared to the entire manifold in case of independent quantization.
 Therefore, the quantization error is substantially lower as well.
 However, independent quantization algorithms are important for smart initialization (instead of a cold start) of the predictive quantization strategies.
-Observe that predictive quantization algorithms for SVD precoders are typically the higher dimensional analogues of well known approaches to reduce quantization error using linear prediction codes (LPCs) and Delta PCM.
+Observe that predictive quantization algorithms for SVD precoders are typically the higher dimensional analogues of the well known approaches to reduce quantization error using linear prediction codes (LPCs) and Delta PCM.
 In both LPCs and Delta PCM, quantization error can be reduced substantially using a linear predictor and quantizing the scalar difference between the predicted and observed value (innovation).
@@
 Observe from Fig.
-\ref{BER} that reservoir computing framework is able to achieve substantial improvements in $\text{E}_\text{b}\text{N}_0$ levels at $\text{BER}\leq 10^{-3}$.
-Particularly, observe, for $\text{BER}=10^{-4}$ we observe around $5$ dB improvement.
-Also, notice the substantial improvement which both the predictive quantization schemes offer from the independent quantization scheme with Lloyd codebook for precoders \cite{6678348}, using the same number of bits.
+\ref{BER} that reservoir computing framework is able to achieve substantial improvements in $\text{E}_\text{b}\text{N}_0$ levels at $\text{BER}\leq 10^{-4}$.
+Particularly, observe, for $\text{BER}=10^{-5}$ we observe around $5$ dB improvement.
 

### 2019-04-30 paper/main.tex

--- 2019-04-28 paper/main.tex
@@
 \end{figure}
+
 From Fig.
-\ref{qtiz_err} it is evident that the reservoir computing based predictive quantizer is able to reduce the quantization error to below what was obtained from the existing temporal correlation based predictive quantizer in \cite{6891198}.
+\ref{qtiz_err} it is evident that the reservoir computing based predictive quantizer is able to reduce the quantization error below what was obtained from the existing temporal correlations based predictive quantizer in \cite{6891198}.
 In addition, the quantization error is much smoother, which can be explained from the fact that the reservoir computing approach optimizes, $\mathcal{O}_{i,t}$ that captures the long term dynamics of the channel and hence, is able to correct for jittery variations.
@@
 We simulate the (uncoded QPSK) BER performance for precoders obtained after interpolation ($\tilde{\bU}_{i\neq\{9k\},t}$) and quantization ($\tilde{\bU}_{\{9k\},t}$), for all the 63 subcarriers.
-Observe from Fig. \ref{BER} that reservoir computing framework is able to achieve substantial improvements in $\text{E}_\text{b}\text{N}_0$ levels at $\text{BER}\leq 10^{-3}$.
-Particularly, for $\text{BER}=10^{-4}$, we observe around $5$ dB improvement.
-In addition, substantial improvement is obtained with both the predictive quantization schemes over the independent quantization scheme with Lloyd codebook for precoders \cite{6678348}, using the same number of bits.
+Observe from Fig.
+\ref{BER} that reservoir computing framework is able to achieve substantial improvements in $\text{E}_\text{b}\text{N}_0$ levels at $\text{BER}\leq 10^{-4}$.
+Particularly, observe, for $\text{BER}=10^{-5}$ we observe around $5$ dB improvement.
 
-For simulating the achievable rate for the point-to-point MIMO system, we quantize the channel matrix singular values ($\Sigma_{i,t}$ obtained from SVD of $\bH_{i,t}$) using a 2 bit vector quantizer ($k$-means), and feed them back to the transmitter for fed back subcarriers ($\{9k, k \in \{0,1,\ldots,7\}\}$).
-For the non-fed back subcarriers, they are interpolated by nai\"ve linear interpolation, as in \cite{Gupt1905:Predictive}.
-Observe from Fig. \ref{achievrate} that the reservoir computing framework offers significant improvement in achievable rate for normalized Doppler $f_DT_s=10^{-4}$.
-Since temporal variations for normalized Doppler $f_DT_s=10^{-2}, 10^{-1}$ are higher, the reservoir computing framework has to learn a faster-varying function, and hence the degradation in performance.
-However, it still matches the performance of the predictive quantizer in \cite{6891198} for normalized Doppler $f_DT_s=10^{-2}$ and slightly outperforms slightly for $f_DT_s=10^{-1}$.
+For simulating the achievable rate for the point-to-point MIMO system considered, we quantize the sigma values ($\Sigma_{i,t}$ obtained from SVD of $\bH_{i,t}$) using a 2 bit vector quantizer ($k$-means), and feed them back to the transmitter for fed back subcarriers ($\{9k, k \in \{0,1,\ldots,7\}\}$).
+For the non-fed back subcarriers, they are interpolated via nai\"ve linear interpolation method as in \cite{Gupt1905:Predictive}.
+Observe from Fig.
+\ref{achievrate} that the reservoir computing framework offers signicant improvement in achievable rate for $f_DT_s=10^{-4}$.
+Since the temporal variations for $f_DT_s=10^{-2}, 10^{-1}$ are higher, the reservoir computing framework has to learn a faster-varying function, and hence the degradation in performance.
+However, it still matches the performance of the predictive quantizer in \cite{6891198} for $f_DT_s=10^{-2}$ and performs slightly better for $f_DT_s=10^{-1}$.
+
 \begin{figure}[h]

### 2019-04-30 paper/main.tex
Adding changes in Section4

@@
 Since the bit budget for such channel state information (CSI) feedback is limited, these precoders need to be quantized effectively using just a few bits.
-For a $N_T \times N_R$ MIMO system ($N_{\{T/R\}}$: Number of Transmit/Receive Antennas), this amounts to quantizing a $N_T \times N_R$ complex valued matrix.
+For a $N_T \times N_R$ MIMO system ($N_{\{T/R\}}$: Number of Transmit/Receive Antennas), this amounts to quantizing a $N_T \times N_R$ complex-valued matrix.
 This task is aided by the presence of an underlying manifold structure and temporal/frequency correlations in the precoders. 
@@
 In this work, we introduce a reservoir computing based framework for predictive quantization by exploiting temporal correlations. 
-Past methods have primarily exploited the nonlinear geometry endowed by the manifold structure to for precoder prediction.
+Past methods have primarily exploited the nonlinear geometry endowed by the manifold structure for precoder prediction.
 Here, this non-linear relationship is captured using the dynamical reservoir state as part of the online training process of the reservoir.
@@
 To respect the bit budget imposed by limited feedback CSI schemes, the quantization needs to be performed using very few bits.
-Given the high dimensionality of the precoders (which form a $N_T \times N_R$ complex valued matrix, viz.
+Given the high dimensionality of the precoders (which form a $N_T \times N_R$ complex-valued matrix, viz.
 $2N_TN_R$ real numbers), effective quantization with just a few bits poses a significant challenge.
@@
 % How to we do this
-\textcolor{blue}{
+%\textcolor{blue}
+{
 Reservoir computing is a computational framework designed for sequential data processing.
@@
 % A important characteristic of reservoir computing is that while training, the input weights and the weights within the reservoir are not kept fixed and the weights of the output coupler are updated.
-The key advantage of a reservoir computing based system is that it is extremely easy to train in comparison to its counterparts like Deep Neural Networks. CITATION NEEDED
+The key advantage of a reservoir computing based system is that it is easy to train in comparison to its counterparts like Deep Neural Networks \cite{mosleh2017brain}.
 The input features can be efficiently learnt using a simple learning algorithm, since the reservoir non-linearly transforms sequential inputs into a higher dimensional reservoir state.
-Reservoir computing has been successfully used to solve problems like spoken digit recognition \cite{verstraeten2005isolated}, handwritten digit image recognition \cite{jalalvand2015real} and climate prediction \cite{pathak2017using}.}
+Reservoir computing has been successfully used to solve problems like handwritten digit image recognition \cite{jalalvand2015real}, spoken digit recognition \cite{verstraeten2005isolated}, and climate prediction \cite{pathak2017using}.
+}
 % Owing to the versatility of reservoir computing, it can deal with any sequential data in principle and hence further expansion of its application fields is widely expected.
 
-\noindent Reservoir computing has also been applied to solve problems in the domain of wireless communications \cite{jaeger2004harnessing,mosleh2017brain,shafin2018realizing}.
+Reservoir computing has also been applied to solve problems in the domain of wireless communications \cite{jaeger2004harnessing,mosleh2017brain,shafin2018realizing}.
 \cite{jaeger2004harnessing} used reservoir computing framework to harness channel non-linearities for smarter channel equalization.
@@
 \label{res_overview}
-\vspace{-10pt}
+\vspace{-5pt}
 \end{figure*}
@@
 \bW_{i,t}^{\text{out}}\gets\text{argmin}_{\bW_{i,t}^{\text{out}}}(\mathcal{O}_{i,t}=\sum_{s=1}^{t}\frac{1}{\lambda^{t-s}}||\bW_{i,t}^{\text{out}}\br_{i,t}-\tilde{\bu}_{i,t}||^2)
+\label{getsOpt}
 \end{equation}
-Computing the gradient $\frac{\partial \mathcal{O}_{i,t}}{\partial \bW_{i,t}^{\text{out}}}$ and setting it to the null matrix yields
+Computing the gradient $\frac{\partial \mathcal{O}_{i,t}}{\partial \bW_{i,t}^{\text{out}}}$ and setting it to null yields,
 \begin{equation}
@@
 
-Finally, we summarize and highlight the novel aspects of the proposed framework for predictive quantization.
-The first key advantage of the proposed approach over the past work \cite{Gupt1905:Predictive,6891198,6545375} is that the prediction function and quantization function are not independent of each other.
-To see this, observe \eqref{update_Wt1} to obtain $\bW^{\text{out}}_{i,t-1}$ from $\tilde{\bU}_{i,t-1}=q_P(f_P(\tilde{\bU}_{i,t-2}),\text{fb}_{i,t-1})$, and \eqref{pred} to obtain $\bP_{i,t+1}$
-\begin{equation}
-\highlight{\bW_{i,t-1}^{\text{out}}}=\frac{\frac{\text{num}_{i,t-2}}{\lambda}+\texttt{outer}(\highlight{q_P}(f_P(\tilde{\bU}_{i,t-2}),\text{fb}_{i,t-1}),\br_{i,t-1})}{\frac{\text{den}_{i,t-2}}{\lambda}+||\br_{i,t-1}||^2}
-\label{update_Wt1}
-\end{equation}
-\begin{equation}
-\highlight{\bP_{i,t}}=f_P(\tilde{\bU}_{i,t-1})=\highlight{\bW^{\text{out}}_{i,t-1}}\text{tanh}(\bA_i\br_{i,t-1}+\bW^{\text{in}}_i\highlight{\tilde{\bu}_{i,t-1}})
-\label{pred}
-\end{equation}
-The dependence between $f_P$ and $q_P$ in our framework is in the sense that the backward pass ensures that prediction function `learns' the correlations brought about by $q_P$, in addition to temporal correlations.
-%Better framing possible
-This is done by optimizing $\bW_{i,t}^{\text{out}}$ such that the prediction output to be as close to the output from $q_P$ (Objective function $\mathcal{O}_{i,t}$).
+To conclude this section, we summarize and highlight the novel aspects of the proposed framework.
+The first key advantage of the proposed approach over the past work \cite{Gupt1905:Predictive,6891198,6545375} is that the prediction function is not uncoupled with the quantization function.
+Past work for predictive quantization has largely kept $f_P,q_P$ uncoupled in the sense that, the obtained precoder is just composite function of previous $p$ estimates ($p$ defined in Section \ref{section2}) $q_P(f_P(\cdot))$.
+In the proposed framework, $f_P$ changes with time due to the update equation of $\bW_{i,t}^{\text{out}}$ \eqref{wout_upd}.
+Recall that $\bW_{i,t}^{\text{out}}$ update equation is obtained from optimizing \eqref{oit}, which minimizes the norm error between the prediction $\bp_{i,t}$ (the coarse estimate) and the quantized value $\tilde{\bu}_{i,t}$ (the refined estimate).
+Hence, backward pass ensures that coarse estimate provided by $f_P$ gets more refined with time, since optimizing $\bW_{i,t}^{\text{out}}$ to minimize $\mathcal{O}_{i,t}$ brings the predicted estimates $\bp_{i,s\leq t}$ closer to the quantized estimates $\tilde{\bu}_{i,s\leq t}$.
 The updated $\bW_{i,t}^{\text{out}}$ is then used in the forward pass to predict $\bP_{i,t+1}$, which is likely closer to $\tilde{\bU}_{i,t+1}$ than $\bP_{i,t}$ was to $\tilde{\bU}_{i,t}$ due to optimization of $\mathcal{O}_{i,t}$.
+This enables $q_P$ to quantize even smaller subspaces, since the coarse estimate itself has improved, which in turn brings about lower quantization error, and thus improved performance.
 
-\textcolor{blue}{Another advantage of the proposed scheme is the ease of training the reservoir, captured in \eqref{res_upd}.
+% To see this, observe \eqref{update_Wt1} to obtain $\bW^{\text{out}}_{i,t-1}$ from $\tilde{\bU}_{i,t-1}=q_P(f_P(\tilde{\bU}_{i,t-2}),\text{fb}_{i,t-1})$, and \eqref{pred} to obtain $\bP_{i,t+1}$
+% \begin{equation}
+% \highlight{\bW_{i,t-1}^{\text{out}}}=\frac{\frac{\text{num}_{i,t-2}}{\lambda}+\texttt{outer}(\highlight{q_P}(f_P(\tilde{\bU}_{i,t-2}),\text{fb}_{i,t-1}),\br_{i,t-1})}{\frac{\text{den}_{i,t-2}}{\lambda}+||\br_{i,t-1}||^2}
+% \label{update_Wt1}
+% \end{equation}
+% \begin{equation}
+% \highlight{\bP_{i,t}}=f_P(\tilde{\bU}_{i,t-1})=\highlight{\bW^{\text{out}}_{i,t-1}}\text{tanh}(\bA_i\br_{i,t-1}+\bW^{\text{in}}_i\highlight{\tilde{\bu}_{i,t-1}})
+% \label{pred}
+% \end{equation}
+
+%\textcolor{blue}
+{Another advantage of the proposed scheme is the ease of training the reservoir, captured in \eqref{res_upd}.
 By storing just one matrix $\text{\textbf{num}}_{i,t}$ and a number $\text{den}_{i,t}$, we capture the entire history of the precoding matrices, with past values weighted by $\lambda$.
-This is a departure from previous schemes \cite{Gupt1905:Predictive,6891198,6545375} which store the past $n$ precoders precoders in a $n$ sized cyclic buffer ($n$ also has to be pre-decided).
-Reservoir computing, thus proposes an easier to train (data centric) scheme, which is not typical in data centric ML based schemes.}
+This is a departure from previous schemes \cite{Gupt1905:Predictive,6891198,6545375} which store the past $p$ precoders precoders in a $p$ sized cyclic buffer ($p$ also has to be pre-decided).
+Reservoir computing, thus proposes an easier to train (data centric) scheme, which is not typical in data centric ML based schemes.
+}
 
+\vspace{-4pt}
 \section{Simulation Results}
@@
 \label{setting}
-\noindent We simulate both our predictive quantization algorithm and the one presented in \cite{6891198} for the IEEE Pedestrian-A channel, with $N_T=4$, $N_R=2$. 
+\noindent The simulations have been performed for the IEEE Pedestrian-A channel, with $N_T=4$, $N_R=2$.
 The channel matrices $\bH_{i,t}$ are generated using Jake's model for realistic simulations, from the IT++ library through the python wrapper py-itpp \cite{ViditPy}.
-Although in both our work and \cite{6891198}, only temporal correlations are exploited, we compare the BER, quantization error and logsum rate results for the complete MIMO-OFDM setting with $N=64$ of subcarriers, and channels are fed back for $8$ evenly spaced subcarriers, indexed starting at 0, viz.
+We compare the results obtained by our framework, with the work presented in \cite{6891198}, which also utilized temporal correlations for predictive quantization.
+The forward prediction function $f_P$ of the proposed framework, has $p$ (Section \ref{section2}) to be $1$ \eqref{fpqp}, whereas the backward pass $p$ for time instant $t$ is $t$ (Observe the framing of $\mathcal{O}_{i,t}$).
+We keep $p=4$ for the $f_P$ presented in \cite{6891198}.
+The quantization function $q_P$ is kept to be same, as described in \cite{6545375,6891198,Gupt1905:Predictive} for both the approaches.
+Although in both our work and \cite{6891198}, only temporal correlations are exploited, we compare the BER, quantization error and achievable rate results for the complete MIMO-OFDM setting with $N=64$ of subcarriers, and channels are fed back for $8$ evenly spaced subcarriers, indexed starting at 0, viz.
 $\{0,9,\ldots,63\}$ ($\{9k, k \in \{0,1,\ldots,7\}\}$).
-The precoding matrices at subcarriers were channels are not fed back ($i\neq\{9k\}$) are estimated via the Cayley Interpolation method presented in \cite{Gupt1905:Predictive}.
-Feedback is available for $i=\{9k\}$ subcarriers (i.e. transmitter obtains $\text{fb}_{\{9k\},t}$) for predictive quantization.
+Hence, the feedback is available only for $i=\{9k\}$ subcarriers (i.e.
+transmitter obtains only $\text{fb}_{\{9k\},t}$).
+The precoding matrices at subcarriers where feedback is not available ($i\neq\{9k\}$) are estimated via the Cayley Interpolation method presented in \cite{Gupt1905:Predictive}.
 The setting is visually illustrated in Fig. \ref{table}.
-A 6 bit codebook generated using the Lloyd codebook algorithm for the Stiefel Manifold in \cite{6678348} is used to feedback $\tilde{\bU}_{\{9k\},0}$ and differential quantization (i.e.
-$\bP_{i,t}=\tilde{\bU}_{i,t-1}$) is used for 10 time instances to provide provide the initial training data for the reservoir and for overcoming initial transient response of the reservoir, as discussed in \cite{mosleh2017brain}.
-A 6 bit base codebook that is used for the quantization function $q_P$ is generated according to the method presented in Section \ref{qp} and \cite{Gupt1905:Predictive}.
-Hence, for both initialization and subsequent feedback, $\text{fb}_{i,t}$ can be encoded using 6 bits (i.e. $\mathcal{B}=6$ Section \ref{section2}).
+
+A 6 bit codebook generated using the Lloyd codebook algorithm for the Stiefel Manifold presented in \cite{6678348} is used for initial feedback ($\tilde{\bU}_{\{9k\},0}$) and differential quantization (i.e.
+$\bP_{i,t}=\tilde{\bU}_{i,t-1}$) is used for 10 time instances to provide the initial training data for the reservoir and to overcome the initial transient response of the reservoir (also discussed in \cite{mosleh2017brain}).
+A 6 bit base codebook is used for the quantization function $q_P$ and is generated according to the method presented in Section \ref{qp}, similar to \cite{Gupt1905:Predictive}.
+Hence, both initialization and subsequent feedback, $\text{fb}_{i,t}$ can be encoded using 6 bits (i.e. $\mathcal{B}=6$ Section \ref{section2}).
 The bit budget per OFDM frame is thus 48 bits, for total 8 equally spaced fed back subcarriers $\{9k, k \in \{0,1,\ldots,7\}\}$.
@@
 Unlike \cite{Gupt1905:Predictive}, we do not exploit frequency correlations for predictive quantization, and the $8$ reservoirs for prediction of $8$ fed-back subcarriers are kept independent of each other.
-All these 8 reservoirs are initialized with $\bA_{i\in\{9k\}}$ being an Erdos-Reny\"i graph, with probability of edge connections being $0.2$, $\lambda=2$, $\bW^{\text{out/in}}_{i\in\{9k\},0}$ being randomly assigned, $D_{\text{in}}=D_{\text{out}}=14$ (vectorized representation of $4\times2$ semi-unitary matrix, Section \ref{vectorize}) and $D_{\text{resv}}=60$.
+All these 8 reservoirs are initialized with $\bA_{i\in\{9k\}}$ being an Erdos-Reny\"i graph, with probability of edge connections being $0.2$, $\lambda=2$, $\bW^{\text{out/in}}_{i\in\{9k\},0}$ are initialized randomly, and $D_{\text{in}}=D_{\text{out}}=14$ (vectorized representation of $4\times2$ semi-unitary matrix, Section \ref{vectorize}) and $D_{\text{resv}}=60$.
 
@@
 \label{res}{}
-To mitigate errors in tracking in the presence of randomly appearing drastic events in wireless channels, such as sudden interferences and dynamic environments, only 100 channel evolutions are considered for the simulations.
-Averaging is performed over 10 independent channel realizations, to ensure that the simulation results hold in general for the chosen IEEE Pedestrian A channel profile.
+% To mitigate errors in prediction upon the presence of randomly appearing drastic events in wireless channels, such as sudden interferences and dynamic environments, only 100 channel evolutions are considered for the simulations, and the algorithm is re-starte.
+\noindent Averaging is performed over 10 independent channel realizations, to ensure that the simulation results hold in general for the chosen IEEE Pedestrian A channel profile.
 Therefore, the quantization error, BER and achievable rate results are averaged over 1000 channel instances, with 100 channel evolutions of 10 independent channel realizations.
@@
 \centering
-\includegraphics[width=0.45\textwidth]{images/qtizErr.pdf}
-\caption{Quantization error in terms of chordal distance to the actual precoder $\bU_{\{9k\},t}$ observed at the receiver, from the quantized estimate $\tilde{\bU}_{\{9k\},t}$ at the transmitter, averaged over 8 fed back subcarriers ($\{9k, k \in \{0,1,\ldots,7\}\}$) and 10 independent channel realizations (normalized Doppler $f_DT_s=10^{-4}$).}
+\includegraphics[width=0.4\textwidth]{images/qtizErr.pdf}
+\caption{Quantization error in terms of chordal distance to the actual precoder $\bU_{\{9k\},t}$ observed at the receiver, from the quantized estimate $\tilde{\bU}_{\{9k\},t}$, averaged over 8 fed back subcarriers ($\{9k, k \in \{0,1,\ldots,7\}\}$) and 10 independent channel realizations (normalized Doppler $f_DT_s=10^{-4}$).}
 \label{qtiz_err}
@@
 From Fig.
-\ref{qtiz_err} it is evident that the reservoir computing based predictive quantizer is able to reduce the quantization error below what was obtained from the existing temporal correlations based predictive quantizer in \cite{6891198}.
-In addition, the quantization error is much smoother, which can be explained from the fact that the reservoir computing approach optimizes, $\mathcal{O}_{i,t}$ that captures the long term dynamics of the channel and hence, is able to correct for jittery variations.
-
-We simulate the (uncoded QPSK) BER performance for precoders obtained after interpolation ($\tilde{\bU}_{i\neq\{9k\},t}$) and quantization ($\tilde{\bU}_{\{9k\},t}$), for all the 63 subcarriers.
+\ref{qtiz_err} it is evident that the proposed framework is able to reduce the quantization error below what was obtained from the existing temporal correlations based predictive quantizer in \cite{6891198}.
+In addition, the quantization error plot is much smoother as well, which can be explained from the fact that the reservoir computing approach optimizes $\mathcal{O}_{i,t}$, that captures the long term dynamics of the channel and hence, does not face jittery variations.
+We simulate (uncoded QPSK) BER performance for all the 64 subcarriers' precoders obtained after interpolation ($\tilde{\bU}_{i\neq\{9k\},t}$) and quantization ($\tilde{\bU}_{\{9k\},t}$).
 Observe from Fig.
 \ref{BER} that reservoir computing framework is able to achieve substantial improvements in $\text{E}_\text{b}\text{N}_0$ levels at $\text{BER}\leq 10^{-4}$.
-Particularly, observe, for $\text{BER}=10^{-5}$ we observe around $5$ dB improvement.
+Particularly, for $\text{BER}=10^{-5}$ we observe around $5$ dB improvement.
 
-For simulating the achievable rate for the point-to-point MIMO system considered, we quantize the sigma values ($\Sigma_{i,t}$ obtained from SVD of $\bH_{i,t}$) using a 2 bit vector quantizer ($k$-means), and feed them back to the transmitter for fed back subcarriers ($\{9k, k \in \{0,1,\ldots,7\}\}$).
-For the non-fed back subcarriers, they are interpolated via nai\"ve linear interpolation method as in \cite{Gupt1905:Predictive}.
+We hypothesize that the key reason for the improved performance for both quantization error and BER in the reservoir computing approach, $f_P,q_P$ are coupled via the backward pass framework (explained towards the end of Section \ref{train}).
+Also, observe from Fig.
+\ref{BER} that the proposed framework BER curve (yellow) comes very close to the ideal $8$ feedback curve (green).
+This can be explained due to the fact that the semi-unitary precoder basically rotates the data vector via it's matrix transformation.
+For QPSK, we get some reasonable error margin for this rotation, which becomes more stringent as the simulated BER is reduced.
+Hence, we match the ideal curve for high BER region, and for low BER region, as the margin of error reduces, the curves diverge.
+
+\noindent For simulating the achievable rate, we quantize the sigma values ($\Sigma_{i,t}$ from SVD of $\bH_{i,t}$) using a 2 bit vector quantizer ($k$-means), and feed them back to the transmitter for fed back subcarriers ($\{9k, k \in \{0,1,\ldots,7\}\}$).
+For the non-fed back subcarriers, they are interpolated via a simple convex combination interpolation method as in \cite{Gupt1905:Predictive}.
 Observe from Fig.
-\ref{achievrate} that the reservoir computing framework offers signicant improvement in achievable rate for $f_DT_s=10^{-4}$.
+\ref{achievrate} that the reservoir computing framework offers improvement in achievable rate for $f_DT_s=10^{-4}$.
 Since the temporal variations for $f_DT_s=10^{-2}, 10^{-1}$ are higher, the reservoir computing framework has to learn a faster-varying function, and hence the degradation in performance.
 However, it still matches the performance of the predictive quantizer in \cite{6891198} for $f_DT_s=10^{-2}$ and performs slightly better for $f_DT_s=10^{-1}$.
+\vspace{-3pt}
 
@@
 \centering
-\includegraphics[width=0.45\textwidth]{images/BER_res.pdf}
-\caption{BER results after obtaining non fed back $\tilde{\bU}_{i\neq\{9k\},t}$ from $\tilde{\bU}_{\{9k\},t}$ via Cayley interpolation \cite{Gupt1905:Predictive}, averaged over 10 independent channel realizations, 100 channel evolutions each (normalized Doppler $f_DT_s=10^{-4}$).}
+\includegraphics[width=0.44\textwidth]{images/BER_res.pdf}
+\caption{BER results: Here, red curve is the most ideal case considering exact $\bU_{i,t}$ for all 64 subcarriers, at each time instant are available at the transmitter.
+The \{green/yellow/blue\} curves corresponds to the case in which \{$\bU_{9k,t}$/$\tilde{\bU}_{9k,t}$ from reservoir method/$\tilde{\bU}_{9k,t}$ from \cite{6891198}\} is available for each time instant, and non fed back precoders are interpolated via Cayley method.
+Observe that the proposed framework BER curve (provides significant improvement in $\text{E}_\text{b}\text{N}_0$ levels over the work presented in \cite{6891198} (blue).}
 \label{BER}
+\vspace{-5pt}
 \end{figure}
@@
 \centering
-\includegraphics[width=0.45\textwidth]{images/hopRate.pdf}
-\caption{Achievable rate results for the two predictive quantization methods considered.
-The results are presented as a percentage of the ideal achievable rate obtained when the transmitter has the accurate (unquantized) and non-interpolated estimates of $\bU_{i,t}$ for each subcarrier and each time instant.
-The results have been averaged over 10 independent channel realizations, 100 channel evolutions each, for each normalized Doppler value ($f_DT_s$).}
+\includegraphics[width=0.44\textwidth]{images/hopRate.pdf}
+\caption{The results are presented as a percentage of the ideal achievable rate obtained when the transmitter has the accurate (unquantized) and non-interpolated estimates of $\bU_{i,t}$ for each subcarrier and each time instant.}
 \label{achievrate}
+\vspace{-5pt}
 \end{figure}
@@
 \vspace{-3pt}
-In this paper, we have presented a reservoir computing framework that exploits temporal correlations for predictive quantization of SVD based precoders.
-The simulations reveal that reduced quantization error reduces significantly, and BER improves significantly, and achievable rates are higher in when using the proposed framework.
-This motivates further study into the framework as well, and future work  would involve a generalization of the framework to capture frequency correlations as well for predictive quantization, and a detailed analysis of impact on performance caused by choice of different reservoir parameters like $\bA,\text{tanh}(\cdot)$, and number of dimensions of the reservoir state.
-The reservoir computing framework can also be used to predict the future precoders at the receiver, so as to mitigate issues caused by delay in feedback, on the lines of \cite{chang2011adaptive}, which forms another interesting path for future enhancements.
+In this paper, we have presented a reservoir computing framework for temporal-correlations based predictive quantization of SVD precoders.
+The simulations reveal significant improvement in quantization error and BER, along with an increase in achievable rate for IEEE Pedestrian-A channel model with normalized Doppler $f_DT_s=10^{-4}$.
+This motivates further study into the framework, and future work would involve generalization of the framework to capture temporal-frequency correlations jointly for predictive quantization, and a detailed analysis of impact on performance caused by choice of different reservoir parameters like $\bA,\text{tanh}(\cdot),$ and $D_{\text{resv}}$.
+The reservoir computing framework can also be used to predict the future precoders at the receiver, to mitigate issues caused by delay in feedback, on the lines of \cite{chang2011adaptive}, which forms another interesting path for future enhancements.
 \vspace{-5pt}

### 2019-04-30 paper/main.tex
Minor changes suggested by Sankhe

@@
 Capturing the available correlations permit the use of predictive quantization algorithms, which enable improvement of the quantization error with time.
-This improvement is obtained because exploiting the available correlations from past fed back precoders allow one to just quantize the extra information required on top of the past available temporal-frequency information, instead of the new precoder information in the entirety.
+This improvement is obtained because exploiting the available correlations allow for quantization of just the small extra information needed on top of the past fed back estimates, instead of quantizing the complete new precoder information in the entirety.
 Exploiting frequency correlations permits the use of interpolation algorithms, which in turn reduce the feedback overhead in a single OFDM frame, by feeding back CSI information only for certain subcarriers, and interpolating over the others.
@@
 Manifold based approaches for predictive quantization have provided significant performance benefits, given that they work with the effective lower dimensions while framing the manifold operations to predict and quantize.
-However, these approaches are difficult to implement and require some operations on the manifold structure.
+However, these approaches are non-trivial, since they require specific operations over the non-linear manifold differential geometry.
 In this paper, we propose a reservoir computing based predictive quantizer to exploit the temporal correlations effectively.
@@
 Reservoir computing is a computational framework designed for sequential data processing.
-Its design is inspired from several frameworks of recurrent neural networks \cite{jaeger2004harnessing}, including Liquid State Machines \cite{jalalvand2015real}.
-A reservoir computing system maps the inputs to spatio temporal patterns in a higher dimensional dynamical reservoir state.
-The pattern analysis over these spatio temporal patterns is performed by an output coupler that maps the higher dimensional reservoir state back to the output dimension that generally possesses lower dimensionality than the reservoir state.
+Its design is inspired from several frameworks of recurrent neural networks \cite{jaeger2004harnessing}, including Liquid State Machines \cite{jalalvand2015real} and Echo State Networks \cite{mosleh2017brain,pathak2017using}.
+The reservoir computing framework represents the non-linear relationships in the data via the higher dimensional dynamical reservoir state vector, which is transformed (using
+matrices, referred to as `couplers') to the lower dimensional input/output vectors
+% A reservoir computing system maps the inputs to temporal patterns in a higher dimensional dynamical reservoir state.
+% The pattern analysis over these temporal patterns is performed by an output coupler that maps the higher dimensional reservoir state back to the output dimension that generally possesses lower dimensionality than the reservoir state.
 % A important characteristic of reservoir computing is that while training, the input weights and the weights within the reservoir are not kept fixed and the weights of the output coupler are updated.
-The key advantage of a reservoir computing based system is that it is easy to train in comparison to its counterparts like Deep Neural Networks \cite{mosleh2017brain}.
-The input features can be efficiently learnt using a simple learning algorithm, since the reservoir non-linearly transforms sequential inputs into a higher dimensional reservoir state.
-Reservoir computing has been successfully used to solve problems like handwritten digit image recognition \cite{jalalvand2015real}, spoken digit recognition \cite{verstraeten2005isolated}, and climate prediction \cite{pathak2017using}.
+The key advantage of a reservoir computing framework is that it is easy to train in comparison to its counterparts like Deep Neural Networks \cite{mosleh2017brain}.
+Reservoir computing has been successfully used to solve problems like handwritten digit image recognition \cite{jalalvand2015real}, climate prediction \cite{pathak2017using} and spoken digit recognition \cite{verstraeten2005isolated}.
 }
 % Owing to the versatility of reservoir computing, it can deal with any sequential data in principle and hence further expansion of its application fields is widely expected.
-
-Reservoir computing has also been applied to solve problems in the domain of wireless communications \cite{jaeger2004harnessing,mosleh2017brain,shafin2018realizing}.
-\cite{jaeger2004harnessing} used reservoir computing framework to harness channel non-linearities for smarter channel equalization.
+Reservoir computing frameworks have also been applied to solve problems in the domain of wireless communications \cite{jaeger2004harnessing,mosleh2017brain,shafin2018realizing}.
+\cite{jaeger2004harnessing} used reservoir computing framework to harness channel non-linearities for improved channel equalization.
 \cite{mosleh2017brain,shafin2018realizing} utilized the framework for OFDM symbol detection while accounting for channel and power amplifier non-linearities.
 In our work, we utilize the reservoir computing framework to capture the underlying nonlinear relations between previously observed precoders, in order to predict the precoder at next time instant.
-This becomes analogous to time series prediction algorithms, for which the reservoir computing framework has been known to work effectively \cite{mosleh2017brain}.
+This becomes analogous to time series prediction algorithms, for which the reservoir computing framework has been cited to work effectively \cite{mosleh2017brain}.
 
@@
 The proposed reservoir computing scheme is evaluated against the temporal predictive quantization scheme in \cite{6891198}, and the simulation results are discussed in Section \ref{section4}.
-Finally, Section \ref{section5} concludes and presents future lines of work.
+Finally, Section \ref{section5} concludes the proposed framework and presents future lines of work.
 
@@
 The input to the reservoir $i$ that corresponds to subcarrier $i$ is $\tilde{\bu}_{i,t-1}$, (vectorized representation of $\tilde{\bU}_{i,t-1}$) with dimensions $D_{\text{in}}=2N_TN_R-N_R^2+N_R$.
-Using a randomly initialized $D_{\text{in}}\times D_{\text{resv}}$ input coupler matrix, $\bW^{\text{in}}_i$, the $D_{\text{in}}$ dimensional input is mapped to a $D_{\text{resv}}(>D_{\text{in}})$ dimensional vector, where $D_{\text{resv}}$ is the dimension of the reservoir state vector $\br_{i,t}$.
+Using a randomly initialized $D_{\text{in}}\times D_{\text{resv}}$ input coupler matrix, $\bW^{\text{in}}_i$, the $D_{\text{in}}$ dimensional input is mapped to a $D_{\text{resv}}(>>D_{\text{in}})$ dimensional vector, where $D_{\text{resv}}$ is the dimension of the reservoir state vector $\br_{i,t}$.
 $\br_{i,t}$ is initialized with $D_{\text{resv}}$ zeros, and is updated via the following equation:
@@
 Depending on whether $\text{fb}_{i,t} \geq 2^{\mathcal{B}-1}$, i.e.
-whether the optimum codeword is in $T^{\mathcal{C}}_p$ or $T^{\mathcal{C}}_m$, the scale parameter $s[k]$, which in turn controls values of $s_p, s_m$, is updated accordingly, as
+whether the optimum codeword is in $T^{\mathcal{C}}_p$ or $T^{\mathcal{C}}_m$, the scale parameter $s[k]$, which in turn controls values of $s_p, s_m$, is updated as,
 $$s_p=g^{\text{min}(s[k-1]+1,0)}, s_m = g^{s[k-1]-1}$$

### 2019-05-01 paper/main.tex
Slight changes due to EDAS warnings

@@
 \DeclareMathOperator*{\argmin}{argmin}
+% \usepackage{titlesec}
+
+% \titlespacing*{\section}{0pt}{1pt plus 2p}{1ex}
+% \titleformat*{\section}{\fontsize{12}{12}\bfseries}
+
 \begin{document}
@@
 
-\vspace{-4pt}
 \section{Simulation Results}
 \label{section4}
+
 \subsection{Simulation setting considered}
 \label{setting}
+
 \noindent The simulations have been performed for the IEEE Pedestrian-A channel, with $N_T=4$, $N_R=2$.
@@
 We compare the results obtained by our framework, with the work presented in \cite{6891198}, which also utilized temporal correlations for predictive quantization.
-The forward prediction function $f_P$ of the proposed framework, has $p$ (Section \ref{section2}) to be $1$ \eqref{fpqp}, whereas the backward pass $p$ for time instant $t$ is $t$ (Observe the framing of $\mathcal{O}_{i,t}$).
+% The forward prediction function $f_P$ of the proposed framework, has $p$ (Section \ref{section2}) to be $1$ \eqref{fpqp}, whereas the backward pass $p$ for time instant $t$ is $t$ (Observe the framing of $\mathcal{O}_{i,t}$).
 We keep $p=4$ for the $f_P$ presented in \cite{6891198}.
@@
 All these 8 reservoirs are initialized with $\bA_{i\in\{9k\}}$ being an Erdos-Reny\"i graph, with probability of edge connections being $0.2$, $\lambda=2$, $\bW^{\text{out/in}}_{i\in\{9k\},0}$ are initialized randomly, and $D_{\text{in}}=D_{\text{out}}=14$ (vectorized representation of $4\times2$ semi-unitary matrix, Section \ref{vectorize}) and $D_{\text{resv}}=60$.
-
+% All these 8 reservoirs are initialized with $\bA_{i\in\{9k\}}$ being an Erdos-Reny\"i graph, with 
 \begin{figure}
@@
 \label{table}
-\vspace{-8pt}
+\vspace{5pt}
 \end{figure}
@@
 Therefore, the quantization error, BER and achievable rate results are averaged over 1000 channel instances, with 100 channel evolutions of 10 independent channel realizations.
-\begin{figure}[h]
+\begin{figure}
 \centering
@@
 \label{qtiz_err}
+\vspace{-10pt}
 \end{figure}
@@
 
-We hypothesize that the key reason for the improved performance for both quantization error and BER in the reservoir computing approach, $f_P,q_P$ are coupled via the backward pass framework (explained towards the end of Section \ref{train}).
+We hypothesize that the key reason for the improved performance for both quantization error and BER in the reservoir computing approach, is the fact that $f_P,q_P$ are coupled via the backward pass framework (explained towards the end of Section \ref{train}).
 Also, observe from Fig.
 \ref{BER} that the proposed framework BER curve (yellow) comes very close to the ideal $8$ feedback curve (green).
-This can be explained due to the fact that the semi-unitary precoder basically rotates the data vector via it's matrix transformation.
+This can be explained due to the fact that the semi-unitary precoder basically rotates the data vector via its matrix transformation.
 For QPSK, we get some reasonable error margin for this rotation, which becomes more stringent as the simulated BER is reduced.
@@
 
-\begin{figure}[h]
+\begin{figure}
 \centering
@@
 \label{BER}
-\vspace{-5pt}
 \end{figure}
 
-\begin{figure}[h]
+\begin{figure}
 \centering
@@
 \label{achievrate}
-\vspace{-5pt}
+\vspace{-10pt}
 \end{figure}
@@
 \label{section5}
-\vspace{-3pt}
-In this paper, we have presented a reservoir computing framework for temporal-correlations based predictive quantization of SVD precoders.
-The simulations reveal significant improvement in quantization error and BER, along with an increase in achievable rate for IEEE Pedestrian-A channel model with normalized Doppler $f_DT_s=10^{-4}$.
-This motivates further study into the framework, and future work would involve generalization of the framework to capture temporal-frequency correlations jointly for predictive quantization, and a detailed analysis of impact on performance caused by choice of different reservoir parameters like $\bA,\text{tanh}(\cdot),$ and $D_{\text{resv}}$.
+In this paper, we have presented a reservoir computing framework for temporal correlations based predictive quantization of SVD precoders.
+The simulations reveal significant improvement in quantization error and BER, along with an increase in achievable rate for IEEE Pedestrian-A channel model with normalized Doppler, $10^{-4}$.
+This motivates further study into the framework, and future work would involve generalization of the framework to capture temporal-frequency correlations jointly (as presented in \cite{Gupt1905:Predictive}) for predictive quantization, and a detailed analysis of impact on performance caused by choice of different reservoir parameters like $\bA,\text{tanh}(\cdot),$ and $D_{\text{resv}}$.
 The reservoir computing framework can also be used to predict the future precoders at the receiver, to mitigate issues caused by delay in feedback, on the lines of \cite{chang2011adaptive}, which forms another interesting path for future enhancements.

### 2019-05-01 paper/main.tex
Adding changes in Intro

@@
 In MIMO wireless systems, precoding matrices are used for transformation of an $N_S$-dimensional ($N_S \leq \text{min}(N_T,N_R))$ information vector onto an $N_T$-dimensional transmit vector that corresponds to the signal emanating from the $N_T$ antennas of the transmitter.
-The precoding matrix used to achieve the channel capacity using optimal power allocation is obtained using the SVD of the MIMO channel matrix \cite{love2008overview}.
+The precoding matrix used to achieve the channel capacity using optimal power allocation is obtained via the SVD of the MIMO channel matrix \cite{love2008overview}.
 The MIMO channel matrix is estimated at the receiver, and the transmitter has no a priori knowledge of the same.
-Therefore, to obtain the said benefits of SVD precoders, the receiver needs to quantize and feed back the precoders it obtains from the SVD of the MIMO channel matrix.
+Therefore, to obtain the said benefits of SVD precoders at the transmitter, the receiver needs to quantize and feed back the precoders it obtains from the SVD of MIMO channel matrix.
 To respect the bit budget imposed by limited feedback CSI schemes, the quantization needs to be performed using very few bits.
-Given the high dimensionality of the precoders (which form a $N_T \times N_R$ complex-valued matrix, viz.
+Given the high dimensionality of precoders (which form a $N_T \times N_R$ complex-valued matrix, viz.
 $2N_TN_R$ real numbers), effective quantization with just a few bits poses a significant challenge.
@@
 % Elaborate on each point (what people have done before) lecunnas
-Past work has used two inherent properties of the precoders to enable effective quantization of these precoders, with just a few bits.
-First, the precoders are not actually $2N_TN_R$ dimensional entities, and these have an underlying manifold structure that allows one to work with lower dimensions, if one performs operations over the manifold directly.
+Past work has used two inherent properties of the precoders to enable effective quantization with just a few bits.
+First, the precoders are not actually $2N_TN_R$ dimensional entities, but have an underlying manifold structure that allows to work with lower dimensions, when performing operations over the manifold directly.
 Second, these precoders are correlated in both time and frequency.
-Capturing the available correlations permit the use of predictive quantization algorithms, which enable improvement of the quantization error with time.
-This improvement is obtained because exploiting the available correlations allow for quantization of just the small extra information needed on top of the past fed back estimates, instead of quantizing the complete new precoder information in the entirety.
-Exploiting frequency correlations permits the use of interpolation algorithms, which in turn reduce the feedback overhead in a single OFDM frame, by feeding back CSI information only for certain subcarriers, and interpolating over the others.
-Thus, combining these two inherent properties, viz.
-the underlying manifold structure and temporal-frequency correlations, requires a generalization of such linear algorithms to the manifold under consideration, by exploiting the differential geometry of the manifold.
+Utilizing these correlations permit the use of predictive quantization algorithms, which enable improvement of the quantization error with time.
+This improvement is obtained because utilizing the available correlations allow for quantization of just the small extra information needed on top of the past fed back estimates, for estimation of the new precoder, as compared to quantization of the complete new precoder information in the entirety.
+Exploiting frequency correlations permits the use of interpolation algorithms, which reduce the feedback overhead in a single OFDM frame, by feeding back CSI only for certain subcarriers, and interpolating over the others.
+Combining the two inherent properties (viz.
+manifold structure and correlations), requires a generalization of various well known linear algorithms for prediction, quantization and interpolation, to the manifold structure under consideration.
+This is done by exploiting the underlying non-linear differential geometry of the manifold.
 Relevant past work in this direction has been presented in \cite{Gupt1905:Predictive,6891198,6545375,5671092,Li2016,khaled2005quantized,krishnamachari2013geometry}.
@@
 In this paper, we propose a reservoir computing based predictive quantizer to exploit the temporal correlations effectively.
-The proposed scheme offers a simple solution to the predictive quantization problem, which brings about both ease of implementation, and improved performance as well, when compared to \cite{6891198}, which proposed a manifold based method of predictive quantization by exploiting temporal correlations.
+The proposed scheme offers a simple solution to the predictive quantization problem, which brings about ease of implementation, and improved performance as well, when compared to \cite{6891198}, which proposed a manifold based method of predictive quantization by exploiting temporal correlations.
 

### 2019-05-01 paper/main.tex
Slight changes in section2

@@
 We consider a point-to-point $N_T\times N_R$ MIMO-OFDM wireless system. 
+In this discussion, we assume that $N_T > N_R$ and $N_s = N_R$.
 The available bandwidth is divided into $N$ subcarriers, so that, individually for each subcarrier, the channel can be assumed to be flat fading.
-In this discussion, we assume that $N_T > N_R$ and $N_s = N_R$. Consistent with notation in \cite{6891198,Gupt1905:Predictive}, the data stream received on the $i$-th subcarrier is denoted by:
+Consistent with notation in \cite{6891198,Gupt1905:Predictive}, the data stream received on the $i$-th subcarrier, $t$-th time instant (or the $t$-th OFDM frame) is denoted by:
 \begin{equation}
@@
 \end{equation}
-$\tilde{\bU}_{i,t} \in \mathbb{C}^{N_T \times N_R}$ represents the precoding matrix, which is a function of the quantized CSI fed back by the receiver, $\by_{i,t} \in \mathbb{C}^{N_R \times 1}$ is the received data stream, $\bx_{i,t} \in \mathbb{C}^{N_T \times 1}$ denotes the transmitted signal, $\bH_{i,t} \in \mathbb{C}^{N_T \times N_R}$ denotes the MIMO channel matrix and $\bw_{i,t}$ denotes the i.i.d.
+Here, $\tilde{\bU}_{i,t} \in \mathbb{C}^{N_T \times N_R}$ is the quantized estimate of precoding matrix, $\by_{i,t} \in \mathbb{C}^{N_R \times 1}$ is the received data stream, $\bx_{i,t} \in \mathbb{C}^{N_T \times 1}$ denotes the transmitted signal, $\bH_{i,t} \in \mathbb{C}^{N_T \times N_R}$ denotes the MIMO channel matrix and $\bw_{i,t}$ denotes the i.i.d.
 complex Gaussian noise with $\bw_{i,t} \sim \mathcal{N}_{\mathbb{C}}(0,N_0\bI_{N_R})$, $N_0$ being the noise variance.
+For this work, we assume that $\bH^{H}_{i,t}$ is estimated exactly, with zero error at the receiver.
 
@@
 
-For this work, we assume that $\bH^{H}_{i,t}$ is estimated exactly, with zero error at the receiver.
-If an infinite bit budget is available for quantization, the transmitter can directly use the matrices obtained from SVD of $\bH^{H}_{i,t}$ as the precoder $\tilde{\bU}_{i,t}$. 
+If an infinite bit budget is available for precoder quantization, the transmitter can directly use the matrices obtained from SVD of $\bH^{H}_{i,t}$ as the precoder $\tilde{\bU}_{i,t}$. 
 That is, if $\text{SVD}(\bH_{i,t}) = \bU_{i,t},\Sigma_{i,t}, \bV_{i,t}$, then $\tilde{\bU}_{i,t} = \bU_{i,t}$.
@@
 Given practical limitations, only limited feedback is available from the receiver, and the objective is to estimate $\bU_{i,t}$, via $\tilde{\bU}_{i,t}$, using the available feedback bits.
-
 Independent quantization algorithms analogous to the Lloyd codebook algorithm have been studied for quantizing $\text{St}(N_T,N_R)$ \cite{6678348}.
 However, this approach treats precoders that are close to each other in time/frequency as independent, since it does not exploit any temporal/spectral correlations for quantization.
+
 Predictive quantization algorithms \cite{Gupt1905:Predictive,6891198} can be utilized to reduce the quantization error by utilizing the available correlations.
 We now discuss the basic mathematical model that is central to predictive quantization algorithms for precoding matrices.
-Suppose that we predict the current precoding matrix based on the past $p$ observed precoding matrices, and hence $\tilde{\bU}_{i,t-p},\tilde{\bU}_{i,t-p+1},\ldots,\tilde{\bU}_{i,t-2},\tilde{\bU}_{i,t-1}$ have been fed back and available at the transmitter.
-By using a prediction algorithm and by exploiting time correlations among precoders at time instances $t-p,t-p+1,\ldots,t-2,t-1$, the transmitter can obtain a prediction (coarse estimate) of $\bU_{i,t}$, as $\bP_{i,t}=f_P(\tilde{\bU}_{i,t-p},\tilde{\bU}_{i,t-p+1},\ldots,\tilde{\bU}_{i,t-2},\tilde{\bU}_{i,t-1})$, where $f_P: \text{St}(N_T,N_R)\times\ldots\{p-\text{times}\}\ldots\times\text{St}(N_T,N_R) \to \text{St}(N_T,N_R)$ is a prediction function.
+Suppose that we predict the current precoding matrix based on the past $p$ observed precoding matrices.
+For this, assume that $\tilde{\bU}_{i,t-p},\tilde{\bU}_{i,t-p+1},\ldots,\tilde{\bU}_{i,t-2},\tilde{\bU}_{i,t-1}$ have been fed back and available at the transmitter.
+By using a prediction algorithm and by exploiting time correlations among precoders at time instances $t-p,t-p+1,\ldots,t-2,t-1$, the transmitter can obtain a prediction (viz.
+a coarse estimate) of $\bU_{i,t}$, given by $\bP_{i,t}=f_P(\tilde{\bU}_{i,t-p},\tilde{\bU}_{i,t-p+1},\ldots,\tilde{\bU}_{i,t-2},\tilde{\bU}_{i,t-1})$, where $f_P: \text{St}(N_T,N_R)\times\ldots\{p-\text{times}\}\ldots\times\text{St}(N_T,N_R) \to \text{St}(N_T,N_R)$ is a prediction function.
 Now, since the transmitter already possesses a coarse estimate $\bP_{i,t}$ of $\bU_{i,t}$, the receiver just quantizes the local space of $\text{St}(N_T,N_R)$ nearby $\bP_{i,t}$, instead of the complete $\text{St}(N_T,N_R)$.
-The receiver feeds back this quantized information to the transmitter, enabling estimation of a refined estimate of $\bU_{i,t}$, given by $\tilde{\bU}_{i,t}$.
+The receiver feeds back this quantized information, enabling a refined estimate of $\bU_{i,t}$, given by $\tilde{\bU}_{i,t}$ at the transmitter.
 That is, the transmitter utilizes a quantization function $q_P:\text{St}(N_T,N_R) \times \mathbb{N} \to \text{St}(N_T,N_R)$, to obtain $\tilde{\bU}_{i,t} \gets q_P(\bP_{i,t},\text{fb}_{i,t})$, where $\text{fb}_{i,t} \in \{1,2\ldots2^{\mathcal{B}}\}$ is the feedback from the receiver for precoder at $i$-th subcarrier and $t$-th time instant, considering bit budget of $\mathcal{B}$ bits.
@@
 
-In our work, we propose a reservoir computing based prediction framework that predicts the new precoders by utilizing temporal correlations that are captured from past observed precoders ($f_P$).
+In our work, we propose a reservoir computing based prediction framework that predicts the new precoders by utilizing temporal correlations that are captured from past observed precoders (via $f_P$).
 We reuse the $q_P$ algorithm from \cite{Gupt1905:Predictive,6891198}.
 However, by incorporating the $q_P$ in the prediction framework, as discussed in subsequent sections, the $f_P$ function also exploits correlations in $q_P$ (codebook locality correlations), along with temporal correlations.
-Previous work \cite{Gupt1905:Predictive,6891198} has considered $f_P$ and $q_P$ to be independent of each other.
+Previous work \cite{Gupt1905:Predictive,6891198} has considered $f_P$ and $q_P$ to be uncoupled with each other.
 A detailed discussion on the reservoir computing based model for $f_P$ and $q_P$ is presented in Section \ref{section3}.

### 2019-05-01 paper/main.tex
Slight changes in section3,4

@@
 We reuse the $q_P$ algorithm from \cite{Gupt1905:Predictive,6891198}.
-However, by incorporating the $q_P$ in the prediction framework, as discussed in subsequent sections, the $f_P$ function also exploits correlations in $q_P$ (codebook locality correlations), along with temporal correlations.
+However, by incorporating the $q_P$ in the reservoir framework, $f_P$ and $q_P$ get coupled in the sense that $f_P$ is optimized via online training of the reservoir by minimizing the norm difference between $\bP_{i,t}=f_P(\cdot)$ and $\tilde{\bU}_{i,t}=q_P(f_P(\cdot),\text{fb}_{i,t})$.
 Previous work \cite{Gupt1905:Predictive,6891198} has considered $f_P$ and $q_P$ to be uncoupled with each other.
@@
 The proposed reservoir computing scheme is evaluated against the temporal predictive quantization scheme in \cite{6891198}, and the simulation results are discussed in Section \ref{section4}.
-Finally, Section \ref{section5} concludes the proposed framework and presents future lines of work.
 
@@
 \label{vectorize}
-The traditional reservoir computing framework has inputs and outputs as vectors, and thus, it is necessary to convert the precoder matrices to vectors.
-A precoding matrix $\mathcal{\bM} \in \text{St}(N_T,N_R)$ is a $N_T\times N_R$ matrix with the property $\mathcal{\bM}^H\mathcal{\bM}=\text{\textbf{1}}_{N_R}$.
+The reservoir computing framework has inputs and outputs as real vectors, and thus, it is necessary to convert the precoding matrices to vectors.
+A precoding matrix $\mathcal{\bM} \in \text{St}(N_T,N_R)$ is a $\mathbb{C}^{N_T \times N_R}$ matrix with the property $\mathcal{\bM}^H\mathcal{\bM}=\text{\textbf{1}}_{N_R}$.
 For brevity, we call such a matrix $\mathcal{\bM}$ a `semi-unitary' matrix.
-A na{\"i}ve method to vectorize a $N_T\times N_R$ semi-unitary matrix would be to take all its $N_TN_R$ complex numbers individually and stack them onto a $2N_TN_R$ dimensional real vector.
+A na{\"i}ve method to vectorize a $\mathbb{C}^{N_T \times N_R}$ semi-unitary matrix would be to take all its $N_TN_R$ complex numbers individually and stack them onto a $2N_TN_R$ dimensional real vector.
 However, a more efficient approach would be to use the $\mathcal{\bM}^H\mathcal{\bM}=\text{\textbf{1}}_{N_R}$ property, which implies that each vector that represents the columns of $\mathcal{\bM}$ is orthogonal to the other columns.
 For the first column, we take its $N_T$ complex numbers and stack them onto a $2N_T$ vector.
-For the second column, we take only the first $N_T-1$ complex numbers, since the last number can be determined by utilizing orthogonality with the first vector.
+For the second column, we take only the first $N_T-1$ complex numbers and concatenate, since the last number can be determined by utilizing orthogonality with the first column.
 For the third column, we take only the first $N_T-2$ complex numbers, and so on.
-Therefore, we can vectorize the $N_T\times N_R$ $\mathcal{\bM}$ into a $2(N_T)+2(N_T-1)+\ldots+2(N_T-N_R+1)= 2N_TN_R-(N_R^2-N_R)$ dimensional vector.
-For a semi-unitary matrix $\mathcal{\bM}$, we denote by $\mathcal{\bm}$ its vectorized representation.
+Therefore, we vectorize a $\mathbb{C}^{N_T \times N_R}$ semi-unitary matrix into a $2(N_T)+2(N_T-1)+\ldots+2(N_T-N_R+1)= 2N_TN_R-N_R^2+N_R$ dimensional vector.
 
-Observe here that we incur a dimensional penalty upon vectorizing semi-unitary $\mathcal{\bM}$.
-$\mathcal{\bM} \in \text{St}(N_T,N_R)$, which is a $2N_TN_R-N_R^2$ dimensional manifold, whereas $\mathcal{\bm}$ is a $2N_TN_R-N_R^2+N_R$ dimensional vector.
+Observe here that we incur a dimensional penalty upon vectorizing semi-unitary matrices.
+$\mathcal{\bM} \in \text{St}(N_T,N_R)$, which is a $2N_TN_R-N_R^2$ dimensional manifold, whereas we get a $2N_TN_R-N_R^2+N_R$ dimensional vector representation.
 This corresponds to an overhead of $N_R$ dimensions, since we have not exploited the fact that each of the $N_R$ column vectors is a unit norm vector as well.
-It looks as if we could just take $N_T-1$ complex numbers when vectorizing the first column, instead of $N_T$, but this would lead to a non-unique representation, since there could then be infinite possibile values that the lone missing complex number can take, so that the vector has unit norm.
+It looks as if utilizing the norm 1 property, we could just take $N_T-1$ complex numbers when vectorizing the first column, instead of $N_T$.
+However, this would lead to non-unique representations, since there could then be infinite possible values that the lone missing complex number can take, so that the vector has unit norm.
+Hence, we vectorize a semi-unitary $\mathbb{C}^{N_T \times N_R}$ $\mathcal{\bM}$ into $2N_TN_R-N_R^2+N_R$ dimensional vector, denoted as $\bm$.
 %Focus on the fact that you don't actually pay a penalty
@@
 The input to the reservoir $i$ that corresponds to subcarrier $i$ is $\tilde{\bu}_{i,t-1}$, (vectorized representation of $\tilde{\bU}_{i,t-1}$) with dimensions $D_{\text{in}}=2N_TN_R-N_R^2+N_R$.
-Using a randomly initialized $D_{\text{in}}\times D_{\text{resv}}$ input coupler matrix, $\bW^{\text{in}}_i$, the $D_{\text{in}}$ dimensional input is mapped to a $D_{\text{resv}}(>>D_{\text{in}})$ dimensional vector, where $D_{\text{resv}}$ is the dimension of the reservoir state vector $\br_{i,t}$.
+Using a randomly initialized $D_{\text{in}}\times D_{\text{resv}}$ input coupler matrix $\bW^{\text{in}}_i$, the $D_{\text{in}}$ dimensional input is mapped to a $D_{\text{resv}}(>>D_{\text{in}})$ dimensional vector, where $D_{\text{resv}}$ is the dimension of the reservoir state vector $\br_{i,t}$.
 $\br_{i,t}$ is initialized with $D_{\text{resv}}$ zeros, and is updated via the following equation:
@@
 Typical choices for $\bA_i$ have been Erdos-Renyi graphs with an upper bounded maximum eigenvalue \cite{mosleh2017brain,pathak2017using}.
-
-The output of the reservoir is $\bp_{i,t}$, a vectorized representation of $\bP_{i,t}$.
+The output of the reservoir is $\bp_{i,t}$, a vectorized representation of $\bP_{i,t}$, which denotes the predicted precoder at $i$-th subcarrier,$t$-th time instant.
 Therefore, the output of the reservoir is also a $D_{\text{in}}$ dimensional vector ($D_{\text{out}}=D_{\text{in}}$).
@@
 \end{equation}
-However, a complete discussion of the prediction algorithm also involves a backward pass, involving the updation of output couplers $\bW^{\text{out}}_{i,t}$, which would follow subsequently.
+However, a complete discussion of the framework also involves a backward pass training of the reservoir, involving the updation of $\bW^{\text{out}}_{i,t}$, which would follow subsequently.
 \subsection{Quantization function $q_P$}
 \label{qp}
-We now describe the quantization function $q_P(\bP_{i,t},\text{fb}_{i,t})$, which is similar to the one used in \cite{6891198,Gupt1905:Predictive,6545375}.
+We now describe the quantization function $q_P(\bP_{i,t},\text{fb}_{i,t})$, which is similar to the schemes used in \cite{6891198,Gupt1905:Predictive,6545375}.
 Central to the quantization algorithm is the fact that tangent spaces local to a point in manifold are linear vector spaces.
 Given two points $\bX$ and $\bY$ in $\text{St}(N_T,N_R)$, a lifting operation $\bT^Y_X=\texttt{lift}(\bX,\bY)$, $\texttt{lift}:\text{St}(N_T,N_R)\times \text{St}(N_T,N_R) \to \mathcal{T}_X \text{St}(N_T,N_R)$ yields a tangent from $X$ to $Y$, denoted as $\bT^Y_X \in \mathcal{T}_X \text{St}(N_T,N_R)$, where $\mathcal{T}_X \text{St}(N_T,N_R)$ is the local tangent space at $\bX$.
-A corresponding retraction operation $Y=\texttt{retract}(X,\bT^Y_X)$, $\texttt{retract}: \text{St}(N_T,N_R)\times \mathcal{T}_X \text{St}(N_T,N_R) \to \text{St}(N_T,N_R)$ gives back the manifold point obtained by traversing in the tangent direction given by the second argument.
-In this work, the chosen lifting-retraction operations are the Cayley exponentials, discussed in \cite{DBLP:journals/corr/abs-1708-00045,Gupt1905:Predictive}. % and used in \cite{Gupt1905:Predictive}.
+A corresponding retraction operation $Y=\texttt{retract}(X,\bT^Y_X)$, $\texttt{retract}: \text{St}(N_T,N_R)\times \mathcal{T}_X \text{St}(N_T,N_R) \to \text{St}(N_T,N_R)$ gives back the manifold point obtained by traversing in the tangent direction given by the second argument ($\bT^Y_X$).
+In this work, the chosen lifting-retraction pairs are the Cayley exponentials, discussed in \cite{DBLP:journals/corr/abs-1708-00045,Gupt1905:Predictive}. % and used in \cite{Gupt1905:Predictive}.
 The Cayley exponential lifting operation maps two points in $\text{St}(N_T,N_R)$, to a $N_T\times N_T$ skew Hermitian matrix that represents the tangent from first point to the other.
@@
 The codebook for $\mathcal{T}_{\bP_{i,t}} \text{St}(N_T,N_R)$ corresponds to a collection of codewords that represent the different directions (tangents) in $\mathcal{T}_{\bP_{i,t}} \text{St}(N_T,N_R)$.
-This codebook is also referred to as the base codebook ($\text{base}^{\mathcal{C}}$) for the quantization function.
-The feedback from the receiver indicates the optimum tangent in the $\text{base}^{\mathcal{C}}$, which the transmitter can choose to get closest (in terms of chordal distance metric, $d_s(\bX,\bY)$ for $\bX,\bY \in \text{St}(N_T,N_R)$ detailed in \cite{Gupt1905:Predictive,6891198}) to the actual value $\bU_{i,t}$.
+This codebook is subsequently referred to as the base codebook ($\text{base}^{\mathcal{C}}$) for the quantization function.
+The feedback from the receiver indicates the codeword corresponding to the optimum tangent in the $\text{base}^{\mathcal{C}}$, which the transmitter can choose to get closest (in terms of chordal distance metric, $d_s(\bX,\bY)$ for $\bX,\bY \in \text{St}(N_T,N_R)$ detailed in \cite{Gupt1905:Predictive,6891198}) to the actual value $\bU_{i,t}$.
 With the optimum direction chosen, the next step is to determine how much to move in that particular chosen direction, viz. the length of the chosen tangent direction.
+
 For this, we adopt the strategy in \cite{6891198}, which controls the magnitude of tangent steps, by having two codebooks $T^{\mathcal{C}}_p,T^{\mathcal{C}}_m$ of different spreads $s_p,s_m$, but same $2^{\mathcal{B}-1}$ base vectors in the $\text{base}^{\mathcal{C}}$, i.e.
@@
 \label{train}
-\noindent Having described the technicalities of $f_P,q_P$, we now describe the training process for the reservoir.
+\noindent Having described the technicalities of $f_P,q_P$, we now describe the training process for the reservoir, which couples $f_P$ with $q_P$.
 Recall that, to obtain $\tilde{\bU}_{i,t}$ from  $\tilde{\bU}_{i,t-1}$, we have
@@
 \end{equation}
-The key idea here is that, as the predicted matrix $\bP_{i,t}$ (the coarse estimate), gets closer to $\tilde{\bU}_{i,t}$ (the refined estimate), the receiver has to quantize even smaller subspaces, and can thus provide a more refined estimate from the feedback $\text{fb}_{i,t}$.
-So, for the time instant $t\geq 1$, we train the reservoir output coupler such that the following objective function is optimized:
+The key idea for reservoir training is that, as the predicted matrix $\bP_{i,t}$ (the coarse estimate), gets closer to $\tilde{\bU}_{i,t}$ (the refined estimate), the receiver has to quantize even smaller subspaces, and can thus provide a more refined estimate from the feedback $\text{fb}_{i,t}$.
+Hence, we train the reservoir output coupler such that the following objective function is optimized:
 \begin{equation}
@@
 We only need to store the matrix $\text{\textbf{num}}_{i,t-1}$, a number $\text{den}_{i,t-1}$.
-Then, using the current reservoir state $\br_{i,t}$ and $\tilde{\bu}_{i,t}$ obtained from \eqref{fpqp}, $\bW_{i,t}^{\text{out}}$ can be calculated to obtain the predicted coarse estimate of $\tilde{\bu}_{i,t+1}$.
-This completes our technical discussion for the reservoir computing based framework for predictive quantization illustrated in Fig. \ref{res_overview}.
+Then, using the current reservoir state $\br_{i,t}$ and $\tilde{\bu}_{i,t}$ obtained from \eqref{res_upd}, \eqref{fpqp} respectively, $\bW_{i,t}^{\text{out}}$ can be calculated to obtain the predicted coarse estimate, $\tilde{\bu}_{i,t+1}$.
+This completes the technical discussion for the reservoir computing based framework for predictive quantization illustrated in Fig. \ref{res_overview}.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 The first key advantage of the proposed approach over the past work \cite{Gupt1905:Predictive,6891198,6545375} is that the prediction function is not uncoupled with the quantization function.
-Past work for predictive quantization has largely kept $f_P,q_P$ uncoupled in the sense that, the obtained precoder is just composite function of previous $p$ estimates ($p$ defined in Section \ref{section2}) $q_P(f_P(\cdot))$.
+Past work for predictive quantization has largely kept $f_P,q_P$ uncoupled in the sense that, the obtained precoder is just composite function of $q_P,f_P$ applied to previous $p$ precoder estimates viz.
+$q_P(f_P(\cdot))$ (Section \ref{section2}).
 In the proposed framework, $f_P$ changes with time due to the update equation of $\bW_{i,t}^{\text{out}}$ \eqref{wout_upd}.
@@
 This is a departure from previous schemes \cite{Gupt1905:Predictive,6891198,6545375} which store the past $p$ precoders precoders in a $p$ sized cyclic buffer ($p$ also has to be pre-decided).
-Reservoir computing, thus proposes an easier to train (data centric) scheme, which is not typical in data centric ML based schemes.
+Reservoir computing, thus proposes an easy to train data centric scheme, which is not typical for data centric ML based schemes.
 }

### 2019-05-01 paper/main.tex
Changes in section 5

@@
 \usepackage{amsmath}
+% \usepackage{titlesec}
 \usepackage[colorinlistoftodos]{todonotes}
@@
 % \titleformat*{\section}{\fontsize{12}{12}\bfseries}
+% \titleformat{\section}
+%        {\normalfont\fontfamily{phv}\fontsize{12}{17}\bfseries}{\thesection}{1em}{}
+
+% \titleformat{\subsection}
+%        {\normalfont\fontfamily{phv}\fontsize{12}{17}\bfseries\itshape}{\thesubsection}{1em}{}
 
@@
 
-\section{Introduction}
+\section{\textbf{Introduction}}
 \label{intro}
@@
 This is done by exploiting the underlying non-linear differential geometry of the manifold.
-Relevant past work in this direction has been presented in \cite{Gupt1905:Predictive,6891198,6545375,5671092,Li2016,khaled2005quantized,krishnamachari2013geometry}.
+Relevant past work in this direction has been presented in \cite{Gupt1905:Predictive,6891198,6545375,5671092,Li2016,khaled2005quantized,krishnamachari2013geometry,chang2011adaptive}.
 
@@
 
-\section{System Model}
+\section{\textbf{System Model}}
 \label{section2}
@@
 %Explain prediction and quantization steps here itself ! (succintly)
-\section{Reservoir model for Predictive Quantization}
+\section{\textbf{Reservoir model for Predictive Quantization}}
 \label{section3}
-\subsection{Vectorizing matrices in Stiefel Manifold}
+\subsection{\textbf{Vectorizing matrices in Stiefel Manifold}}
 \label{vectorize}
@@
 %The thing to quantize remains on the Stiefel Manifold
-\subsection{Forward Prediction $f_P$ function}
+\subsection{\textbf{Forward Prediction $f_P$ function}}
 \noindent The vector representation of semi-unitary matrices allows to proceed with our discussion on reservoir computing framework.
@@
 However, a complete discussion of the framework also involves a backward pass training of the reservoir, involving the updation of $\bW^{\text{out}}_{i,t}$, which would follow subsequently.
-\subsection{Quantization function $q_P$}
+\subsection{\textbf{Quantization function $q_P$}}
 \label{qp}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Reservoir Training Procedure, the backward pass}
+\subsection{\textbf{Reservoir Training Procedure, the backward pass}}
 \label{train}
@@
 
-\section{Simulation Results}
+\section{\textbf{Simulation Results}}
 \label{section4}
 
-\subsection{Simulation setting considered}
+\subsection{\textbf{Simulation setting considered}}
 \label{setting}
@@
 
-\subsection{Quantization error, BER and Achievable Rate Results}
+\subsection{\textbf{Quantization error, BER and Achievable Rate Results}}
 \label{res}{}
@@
 \centering
-\includegraphics[width=0.44\textwidth]{images/BER_res.pdf}
+\includegraphics[width=0.43\textwidth]{images/BER_res.pdf}
+\vspace{-5pt}
 \caption{BER results: Here, red curve is the most ideal case considering exact $\bU_{i,t}$ for all 64 subcarriers, at each time instant are available at the transmitter.
@@
 \centering
-\includegraphics[width=0.44\textwidth]{images/hopRate.pdf}
+\includegraphics[width=0.43\textwidth]{images/hopRate.pdf}
+\vspace{-5pt}
 \caption{The results are presented as a percentage of the ideal achievable rate obtained when the transmitter has the accurate (unquantized) and non-interpolated estimates of $\bU_{i,t}$ for each subcarrier and each time instant.}
@@
 %Achievable rat
-\section{Conclusions and Future Work}
+
+\section{\textbf{Conclusions and Future Work}}
 \label{section5}
-In this paper, we have presented a reservoir computing framework for temporal correlations based predictive quantization of SVD precoders.
-The simulations reveal significant improvement in quantization error and BER, along with an increase in achievable rate for IEEE Pedestrian-A channel model with normalized Doppler, $10^{-4}$.
-This motivates further study into the framework, and future work would involve generalization of the framework to capture temporal-frequency correlations jointly (as presented in \cite{Gupt1905:Predictive}) for predictive quantization, and a detailed analysis of impact on performance caused by choice of different reservoir parameters like $\bA,\text{tanh}(\cdot),$ and $D_{\text{resv}}$.
-The reservoir computing framework can also be used to predict the future precoders at the receiver, to mitigate issues caused by delay in feedback, on the lines of \cite{chang2011adaptive}, which forms another interesting path for future enhancements.
-\vspace{-5pt}
+
+In this paper, we have presented a reservoir computing framework for predictive quantization of SVD precoders.
+The simulations reveal significant improvement in quantization error, BER, and achievable rate for IEEE Pedestrian-A channel model with normalized Doppler $10^{-4}$. 
+The novelty enabling these improvements lies in the training method for the reservoir framework, which refines the predicted coarse estimates as the reservoir evolves.
+If the simulation results hold in the hardware implementation, the proposed framework would be able to communicate at significantly lower power levels for the same BER, as illustrated in Fig.
+\ref{BER}.
+Note that these results have been obtained by exploiting just the temporal correlations for predictive quantization, and can potentially improve if temporal-frequency correlations are exploited jointly.
+This motivates further study into the reservoir framework, and a detailed analysis of impact on performance caused by choice of different reservoir parameters like $\bA,\text{tanh}(\cdot),$ and $D_{\text{resv}}$.
+\vspace{-4pt}
 

### 2019-05-01 paper/main.tex
Changes in section 4

@@
 To conclude this section, we summarize and highlight the novel aspects of the proposed framework.
-The first key advantage of the proposed approach over the past work \cite{Gupt1905:Predictive,6891198,6545375} is that the prediction function is not uncoupled with the quantization function.
-Past work for predictive quantization has largely kept $f_P,q_P$ uncoupled in the sense that, the obtained precoder is just composite function of $q_P,f_P$ applied to previous $p$ precoder estimates viz.
+The first key advantage of the proposed approach over the past work \cite{Gupt1905:Predictive,6891198,6545375} is that here the prediction function, $f_P$ is coupled with the quantization function, $q_P$.
+Past work for predictive quantization has largely kept $f_P$ and $q_P$ uncoupled in the sense that, the obtained precoder is just composite function of $f_P$ and $q_P$, applied to the previous $p$ precoder estimates i.e.
 $q_P(f_P(\cdot))$ (Section \ref{section2}).
@@
 Recall that $\bW_{i,t}^{\text{out}}$ update equation is obtained from optimizing \eqref{oit}, which minimizes the norm error between the prediction $\bp_{i,t}$ (the coarse estimate) and the quantized value $\tilde{\bu}_{i,t}$ (the refined estimate).
-Hence, backward pass ensures that coarse estimate provided by $f_P$ gets more refined with time, since optimizing $\bW_{i,t}^{\text{out}}$ to minimize $\mathcal{O}_{i,t}$ brings the predicted estimates $\bp_{i,s\leq t}$ closer to the quantized estimates $\tilde{\bu}_{i,s\leq t}$.
-The updated $\bW_{i,t}^{\text{out}}$ is then used in the forward pass to predict $\bP_{i,t+1}$, which is likely closer to $\tilde{\bU}_{i,t+1}$ than $\bP_{i,t}$ was to $\tilde{\bU}_{i,t}$ due to optimization of $\mathcal{O}_{i,t}$.
+Hence, backward pass ensures that the coarse estimate provided by $f_P$ gets more refined with time, since optimizing $\bW_{i,t}^{\text{out}}$ to minimize $\mathcal{O}_{i,t}$ brings the predicted estimates $\bp_{i,s\leq t}$ closer to the quantized estimates $\tilde{\bu}_{i,s\leq t}$.
+The updated $\bW_{i,t}^{\text{out}}$ is then used to obtain $\bP_{i,t+1}$, which is likely to be closer to $\tilde{\bU}_{i,t+1}$, than $\bP_{i,t}$ was to $\tilde{\bU}_{i,t}$, due to optimization of $\mathcal{O}_{i,t}$.
 This enables $q_P$ to quantize even smaller subspaces, since the coarse estimate itself has improved, which in turn brings about lower quantization error, and thus improved performance.

### 2019-05-01 paper/main.tex
Changes in section 3 caption

@@
 \cite{mosleh2017brain,shafin2018realizing} utilized the framework for OFDM symbol detection while accounting for channel and power amplifier non-linearities.
-In our work, we utilize the reservoir computing framework to capture the underlying nonlinear relations between previously observed precoders, in order to predict the precoder at next time instant.
+In our work, we utilize the reservoir computing framework to capture the underlying nonlinear relations between previously obtained quantized precoders, in order to predict the precoder at next time instant.
 This becomes analogous to time series prediction algorithms, for which the reservoir computing framework has been cited to work effectively \cite{mosleh2017brain}.
@@
 \includegraphics[width=0.8\textwidth]{images/system2.pdf}
-\caption{System Overview: The reservoir computing framework takes the precoder estimate at $t-1$ (viz.
+% \caption{System Overview: The reservoir computing framework takes the precoder estimate at $t-1$ (viz.
 $\tilde{\bu}_{i,t-1}$) as input, and executes the forward pass of the predictive quantization framework, shaded in green, to obtain $\tilde{\bu}_{i,t}$.
@@
 Then, both the receiver and transmitter execute the backward pass (shaded in blue) to optimize $\mathcal{O}_{i,t}$ \eqref{oit}, to ensure identical evolution of both the reservoirs}
+\caption{Forward Prediction (Green): Both the transmitter and receiver utilize identical reservoirs and quantized precoder estimate at $t-1$ (i.e.
+$\tilde{\bu}_{i,t-1}$, top left of figure) to obtain $\bP_{i,t}$ via \eqref{fwd_pred}.
+The transmitter estimates the quantized precoder at $t$ (i.e.
+$\tilde{\bu}_{i,t}$, top right of figure) using receiver feedback $\text{fb}_{i,t}$ via $q_P$ \eqref{eqn:cn2}.
+\\Feedback Estimation (Cyan): The Receiver estimates the ideal $\text{fb}_{i,t}$ using the exact precoders $\bU_{i,t}$ via \eqref{eqn:cn1}.
+The transmitter observes only the feedback $\text{fb}_{i,t}$\\ Backward Pass (Blue): $\bW^{\text{out}}_{i,t}$ is updated via \eqref{wout_upd} for optimizing $\mathcal{O}_{i,t}$.
+This is done at both transmitter and receiver to ensure identical evolution of the reservoirs}
 \label{res_overview}
@@
 %\textcolor{blue}
-{Another advantage of the proposed scheme is the ease of training the reservoir, captured in \eqref{res_upd}.
-By storing just one matrix $\text{\textbf{num}}_{i,t}$ and a number $\text{den}_{i,t}$, we capture the entire history of the precoding matrices, with past values weighted by $\lambda$.
+{\noindent Another advantage of the proposed scheme is the ease of training the reservoir, captured in \eqref{res_upd}.
+By storing just one matrix $\text{\textbf{num}}_{i,t}$ and a number $\text{den}_{i,t}$, we capture the entire history of the obtained quantized precoders, with past values weighted by $\lambda$ in $\mathcal{O}_{i,t}$ \eqref{oit}.
 This is a departure from previous schemes \cite{Gupt1905:Predictive,6891198,6545375} which store the past $p$ precoders precoders in a $p$ sized cyclic buffer ($p$ also has to be pre-decided).

### 2019-05-01 paper/main.tex
Minor changes suggested by Dad

@@
 A key step enabling this improved performance is the feedback of these precoders to the transmitter from the receiver.
-Since the bit budget for such channel state information (CSI) feedback is limited, these precoders need to be quantized effectively using just a few bits.
+Since the bit budget for such Channel State Information (CSI) feedback is limited, these precoders need to be quantized effectively using just a few bits.
 For a $N_T \times N_R$ MIMO system ($N_{\{T/R\}}$: Number of Transmit/Receive Antennas), this amounts to quantizing a $N_T \times N_R$ complex-valued matrix.
@@
 
-\section{\textbf{Introduction}}
+\section{Introduction}
 \label{intro}
@@
 The precoding matrix used to achieve the channel capacity using optimal power allocation is obtained via the SVD of the MIMO channel matrix \cite{love2008overview}.
-The MIMO channel matrix is estimated at the receiver, and the transmitter has no a priori knowledge of the same.
+The MIMO channel matrix is estimated at the receiver, and the transmitter has no a-priori knowledge of the same.
 Therefore, to obtain the said benefits of SVD precoders at the transmitter, the receiver needs to quantize and feed back the precoders it obtains from the SVD of MIMO channel matrix.
@@
 Utilizing these correlations permit the use of predictive quantization algorithms, which enable improvement of the quantization error with time.
-This improvement is obtained because utilizing the available correlations allow for quantization of just the small extra information needed on top of the past fed back estimates, for estimation of the new precoder, as compared to quantization of the complete new precoder information in the entirety.
+This improvement is obtained because utilizing the correlations for estimation of the new precoder, allows for quantization of just the small extra information needed on top of the past fed back precoders, as compared to the new precoder information in the entirety.
 Exploiting frequency correlations permits the use of interpolation algorithms, which reduce the feedback overhead in a single OFDM frame, by feeding back CSI only for certain subcarriers, and interpolating over the others.
 Combining the two inherent properties (viz.
-manifold structure and correlations), requires a generalization of various well known linear algorithms for prediction, quantization and interpolation, to the manifold structure under consideration.
+manifold structure and correlations), requires generalization of various well known linear algorithms for prediction, quantization and interpolation, to the manifold structure.
 This is done by exploiting the underlying non-linear differential geometry of the manifold.
@@
 However, these approaches are non-trivial, since they require specific operations over the non-linear manifold differential geometry.
-In this paper, we propose a reservoir computing based predictive quantizer to exploit the temporal correlations effectively.
-The proposed scheme offers a simple solution to the predictive quantization problem, which brings about ease of implementation, and improved performance as well, when compared to \cite{6891198}, which proposed a manifold based method of predictive quantization by exploiting temporal correlations.
+In this paper, we aim to capture the above non-linear relations using a reservoir computing based predictive quantizer to exploit the temporal correlations effectively.
+The proposed framework offers a simple solution to the predictive quantization problem, which brings about ease of implementation, along with improved performance, when compared to \cite{6891198}, which proposed a manifold based method of predictive quantization by exploiting temporal correlations as well.
 
@@
 
-\section{\textbf{System Model}}
+\section{System Model}
 \label{section2}
@@
 %Explain prediction and quantization steps here itself ! (succintly)
-\section{\textbf{Reservoir model for Predictive Quantization}}
+\section{Reservoir Framework for Predictive Quantization}
 \label{section3}
-\subsection{\textbf{Vectorizing matrices in Stiefel Manifold}}
+\subsection{Vectorizing matrices in Stiefel Manifold}
 \label{vectorize}
@@
 %The thing to quantize remains on the Stiefel Manifold
-\subsection{\textbf{Forward Prediction $f_P$ function}}
+\subsection{Forward Prediction $f_P$}
 \noindent The vector representation of semi-unitary matrices allows to proceed with our discussion on reservoir computing framework.
@@
 However, a complete discussion of the framework also involves a backward pass training of the reservoir, involving the updation of $\bW^{\text{out}}_{i,t}$, which would follow subsequently.
-\subsection{\textbf{Quantization function $q_P$}}
+\subsection{Quantization function $q_P$}
 \label{qp}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{\textbf{Reservoir Training Procedure, the backward pass}}
+\subsection{Reservoir Training Procedure, the backward pass}
 \label{train}
@@
 \end{equation}
-The key idea for reservoir training is that, as the predicted matrix $\bP_{i,t}$ (the coarse estimate), gets closer to $\tilde{\bU}_{i,t}$ (the refined estimate), the receiver has to quantize even smaller subspaces, and can thus provide a more refined estimate from the feedback $\text{fb}_{i,t}$.
+The key idea for reservoir training is that, as the predicted matrix $\bP_{i,t}$ (the coarse estimate) gets closer to $\tilde{\bU}_{i,t}$ (the refined estimate), the receiver has to quantize even smaller subspaces, and can thus provide a more refined estimate from the feedback $\text{fb}_{i,t}$.
 Hence, we train the reservoir output coupler such that the following objective function is optimized:
@@
 By storing just one matrix $\text{\textbf{num}}_{i,t}$ and a number $\text{den}_{i,t}$, we capture the entire history of the obtained quantized precoders, with past values weighted by $\lambda$ in $\mathcal{O}_{i,t}$ \eqref{oit}.
-This is a departure from previous schemes \cite{Gupt1905:Predictive,6891198,6545375} which store the past $p$ precoders precoders in a $p$ sized cyclic buffer ($p$ also has to be pre-decided).
+This is a departure from previous schemes \cite{Gupt1905:Predictive,6891198,6545375} which store the past $p$ precoders in a $p$ sized cyclic buffer ($p$ also has to be pre-decided).
 Reservoir computing, thus proposes an easy to train data centric scheme, which is not typical for data centric ML based schemes.
@@
 
-\section{\textbf{Simulation Results}}
+\section{Simulation Results}
 \label{section4}
 
-\subsection{\textbf{Simulation setting considered}}
+\subsection{Simulation setting considered}
 \label{setting}
@@
 \includegraphics[width=0.5\textwidth]{images/table.pdf}
-\caption{The transmitter obtains feedback for $\{0,9,\ldots,63\}$ ($\{9k, k \in \{0,1,\ldots,7\}\}$ subcarriers, and uses $\tilde{\bU}_{i,t-1}$, along with $f_P,q_P$ \eqref{fpqp} to obtain $\tilde{\bU}_{i,t}$, illustrated in the figure via cyan arrows.
-For each time instant, the transmitter uses the Cayley method to interpolate $\tilde{\bU}_{i,t}$ at $i\neq\{9k\}$ subcarriers.}
+\caption{The transmitter obtains feedback for $\{9k, k \in \{0,1,\ldots,7\}$ subcarriers, and uses $\tilde{\bU}_{i,t-1}$, along with $f_P,q_P$ \eqref{fpqp} to obtain $\tilde{\bU}_{i,t}$, illustrated in the figure via cyan arrows.
+For each time instant, the transmitter uses the Cayley method to interpolate $\tilde{\bU}_{i,t}$ at $i\neq\{9k\}$ non fed back subcarriers (green arrows).}
 \label{table}
@@
 
-\subsection{\textbf{Quantization error, BER and Achievable Rate Results}}
+\subsection{Quantization error, BER and Achievable Rate Results}
 \label{res}{}
 % To mitigate errors in prediction upon the presence of randomly appearing drastic events in wireless channels, such as sudden interferences and dynamic environments, only 100 channel evolutions are considered for the simulations, and the algorithm is re-starte.
-\noindent Averaging is performed over 10 independent channel realizations, to ensure that the simulation results hold in general for the chosen IEEE Pedestrian A channel profile.
+\noindent To ensure that the simulation results hold in general for the chosen IEEE Pedestrian A channel profile, we perform averaging over 10 independent channel realizations.
 Therefore, the quantization error, BER and achievable rate results are averaged over 1000 channel instances, with 100 channel evolutions of 10 independent channel realizations.
@@
 The \{green/yellow/blue\} curves corresponds to the case in which \{$\bU_{9k,t}$/$\tilde{\bU}_{9k,t}$ from reservoir method/$\tilde{\bU}_{9k,t}$ from \cite{6891198}\} is available for each time instant, and non fed back precoders are interpolated via Cayley method.
-Observe that the proposed framework BER curve (provides significant improvement in $\text{E}_\text{b}\text{N}_0$ levels over the work presented in \cite{6891198} (blue).}
+Observe that the proposed framework BER curve provides significant improvement in $\text{E}_\text{b}\text{N}_0$ levels over \cite{6891198} (normalized Doppler $f_DT_s=10^{-4}$).}
+\vspace{5pt}
 \label{BER}
@@
 
-\section{\textbf{Conclusions and Future Work}}
+\section{Conclusions and Future Work}
 \label{section5}
 
-In this paper, we have presented a reservoir computing framework for predictive quantization of SVD precoders.
+In this paper, we have presented a reservoir computing framework for predictive quantization of SVD precoders by exploiting temporal correlations.
 The simulations reveal significant improvement in quantization error, BER, and achievable rate for IEEE Pedestrian-A channel model with normalized Doppler $10^{-4}$. 
-The novelty enabling these improvements lies in the training method for the reservoir framework, which refines the predicted coarse estimates as the reservoir evolves.
-If the simulation results hold in the hardware implementation, the proposed framework would be able to communicate at significantly lower power levels for the same BER, as illustrated in Fig.
-\ref{BER}.
+The novelty that enables these improvements lies in the training method for the reservoir framework, which refines the predicted coarse estimates as the reservoir evolves.
+The simulation results indicate that the proposed framework would be able to communicate at significantly lower power levels for the same BER, as illustrated in Fig. \ref{BER}.
 Note that these results have been obtained by exploiting just the temporal correlations for predictive quantization, and can potentially improve if temporal-frequency correlations are exploited jointly.

### 2019-05-11 paper/main.tex
Some changes before 10 May Deadline

@@
 This task is aided by the presence of an underlying manifold structure and temporal/frequency correlations in the precoders. 
-Predictive quantization methods reduce the quantization error by predicting new precoders based on observation of past precoders, and then quantizing the information required to obtain the actual precoder from the predicted value.
-In this work, we introduce a reservoir computing based framework for predictive quantization by exploiting temporal correlations. 
-Past methods have primarily exploited the nonlinear geometry endowed by the manifold structure for precoder prediction.
+Predictive quantization methods exploit the available correlations in the previously estimated precoders to predict new precoders, and then quantize just the additional information required to obtain the actual precoder from the predicted value, yielding a refined estimate.
+In this work, we introduce a reservoir computing framework for predictive quantization by exploiting temporal correlations. 
+Past methods have primarily exploited the nonlinear geometry of the underlying manifold structure for precoder prediction.
 Here, this non-linear relationship is captured using the dynamical reservoir state as part of the online training process of the reservoir.
-Simulations reveal that this approach produces reduced quantization error, thereby resulting in lower BER as well as improved achievable rates when compared to earlier work.
+Simulations reveal that this approach produces reduced quantization error, which results in lower BER as well as improved achievable rates when compared to earlier work.
 \end{abstract}
@@
 Reservoir computing is a computational framework designed for sequential data processing.
-Its design is inspired from several frameworks of recurrent neural networks \cite{jaeger2004harnessing}, including Liquid State Machines \cite{jalalvand2015real} and Echo State Networks \cite{mosleh2017brain,pathak2017using}.
+Its design is inspired from several frameworks of Recurrent Neural Networks \cite{jaeger2004harnessing}, including Liquid State Machines \cite{jalalvand2015real} and Echo State Networks \cite{mosleh2017brain,pathak2017using}.
 The reservoir computing framework represents the non-linear relationships in the data via the higher dimensional dynamical reservoir state vector, which is transformed (using
@@
 % A important characteristic of reservoir computing is that while training, the input weights and the weights within the reservoir are not kept fixed and the weights of the output coupler are updated.
-The key advantage of a reservoir computing framework is that it is easy to train in comparison to its counterparts like Deep Neural Networks \cite{mosleh2017brain}.
+% Key advantages of reservoir computing framework include ease of training in comparison to its counterparts like Deep Neural Networks \cite{mosleh2017brain}.
 Reservoir computing has been successfully used to solve problems like handwritten digit image recognition \cite{jalalvand2015real}, climate prediction \cite{pathak2017using} and spoken digit recognition \cite{verstraeten2005isolated}.
@@
 \cite{mosleh2017brain,shafin2018realizing} utilized the framework for OFDM symbol detection while accounting for channel and power amplifier non-linearities.
-In our work, we utilize the reservoir computing framework to capture the underlying nonlinear relations between previously obtained quantized precoders, in order to predict the precoder at next time instant.
+In our work, we utilize a reservoir computing framework similar to one presented in \cite{pathak2017using} to capture the underlying nonlinear relations between previously obtained quantized precoders, in order to predict the precoder at next time instant.
 This becomes analogous to time series prediction algorithms, for which the reservoir computing framework has been cited to work effectively \cite{mosleh2017brain}.
@@
 We reuse the $q_P$ algorithm from \cite{Gupt1905:Predictive,6891198}.
-However, by incorporating the $q_P$ in the reservoir framework, $f_P$ and $q_P$ get coupled in the sense that $f_P$ is optimized via online training of the reservoir by minimizing the norm difference between $\bP_{i,t}=f_P(\cdot)$ and $\tilde{\bU}_{i,t}=q_P(f_P(\cdot),\text{fb}_{i,t})$.
+However, by incorporating the $q_P$ in the reservoir framework, $f_P$ and $q_P$ get coupled in the sense that $f_P$ is optimized via online training of the reservoir by minimizing the norm difference between $\bP_{i,t}=f_P(\cdot)$, and $\tilde{\bU}_{i,t}=q_P(f_P(\cdot),\text{fb}_{i,t})$.
 Previous work \cite{Gupt1905:Predictive,6891198} has considered $f_P$ and $q_P$ to be uncoupled with each other.
@@
 \label{section3}
-\subsection{Vectorizing matrices in Stiefel Manifold}
+\subsection{Vectorizing matrices in the Stiefel Manifold}
 \label{vectorize}
@@
 Observe here that we incur a dimensional penalty upon vectorizing semi-unitary matrices.
-$\mathcal{\bM} \in \text{St}(N_T,N_R)$, which is a $2N_TN_R-N_R^2$ dimensional manifold, whereas we get a $2N_TN_R-N_R^2+N_R$ dimensional vector representation.
+$\text{St}(N_T,N_R)$ is a $2N_TN_R-N_R^2$ dimensional manifold, whereas the proposed vectorization yields a $2N_TN_R-N_R^2+N_R$ dimensional vector representation.
 This corresponds to an overhead of $N_R$ dimensions, since we have not exploited the fact that each of the $N_R$ column vectors is a unit norm vector as well.
@@
 
-The input to the reservoir $i$ that corresponds to subcarrier $i$ is $\tilde{\bu}_{i,t-1}$, (vectorized representation of $\tilde{\bU}_{i,t-1}$) with dimensions $D_{\text{in}}=2N_TN_R-N_R^2+N_R$.
+The input to the reservoir $i$ that corresponds to subcarrier $i$ is $\tilde{\bu}_{i,t-1}$ (vectorized representation of $\tilde{\bU}_{i,t-1}$), with dimensions $D_{\text{in}}=2N_TN_R-N_R^2+N_R$.
 Using a randomly initialized $D_{\text{in}}\times D_{\text{resv}}$ input coupler matrix $\bW^{\text{in}}_i$, the $D_{\text{in}}$ dimensional input is mapped to a $D_{\text{resv}}(>>D_{\text{in}})$ dimensional vector, where $D_{\text{resv}}$ is the dimension of the reservoir state vector $\br_{i,t}$.
@@
 Typical choices for $\bA_i$ have been Erdos-Renyi graphs with an upper bounded maximum eigenvalue \cite{mosleh2017brain,pathak2017using}.
-The output of the reservoir is $\bp_{i,t}$, a vectorized representation of $\bP_{i,t}$, which denotes the predicted precoder at $i$-th subcarrier,$t$-th time instant.
-Therefore, the output of the reservoir is also a $D_{\text{in}}$ dimensional vector ($D_{\text{out}}=D_{\text{in}}$).
-The output $\bp_{i,t}$ is obtained using a matrix transformation of the reservoir state $\br_{i,t}$ with the $D_{\text{resv}}\times D_{\text{out}}$ output coupler matrix $\bW^{\text{out}}_{i,t-1}$ viz.
+The output of the reservoir is $\bp_{i,t}$, a vectorized representation of $\bP_{i,t}$, which denotes the predicted precoder at $i$-th subcarrier, $t$-th time instant.
+Therefore, the output of the reservoir is also a $D_{\text{in}}$ dimensional vector (viz. $D_{\text{out}}=D_{\text{in}}$).
+The output $\bp_{i,t}$ is obtained using a matrix transformation of the reservoir state $\br_{i,t}$ with the $D_{\text{resv}}\times D_{\text{out}}$ output coupler matrix $\bW^{\text{out}}_{i,t-1}$,
 \begin{equation}
@@
 \end{equation}
-However, a complete discussion of the framework also involves a backward pass training of the reservoir, involving the updation of $\bW^{\text{out}}_{i,t}$, which would follow subsequently.
+However, a complete discussion of the framework involves a backward pass for reservoir training, which estimates optimum $\bW^{\text{out}}_{i,t}$.
+This would follow subsequently after $q_P(\cdot)$ is described.
 \subsection{Quantization function $q_P$}
@@
 We now describe the quantization function $q_P(\bP_{i,t},\text{fb}_{i,t})$, which is similar to the schemes used in \cite{6891198,Gupt1905:Predictive,6545375}.
-Central to the quantization algorithm is the fact that tangent spaces local to a point in manifold are linear vector spaces.
+Central to the quantization algorithm is the fact that tangent spaces local to a point in manifold are vector spaces.
 Given two points $\bX$ and $\bY$ in $\text{St}(N_T,N_R)$, a lifting operation $\bT^Y_X=\texttt{lift}(\bX,\bY)$, $\texttt{lift}:\text{St}(N_T,N_R)\times \text{St}(N_T,N_R) \to \mathcal{T}_X \text{St}(N_T,N_R)$ yields a tangent from $X$ to $Y$, denoted as $\bT^Y_X \in \mathcal{T}_X \text{St}(N_T,N_R)$, where $\mathcal{T}_X \text{St}(N_T,N_R)$ is the local tangent space at $\bX$.
@@
 
-The quantization algorithm exploits the linear vector space property of the tangent space and quantizes the local tangent space at the predicted precoder $\bP_{i,t}$, viz $\mathcal{T}_{\bP_{i,t}} \text{St}(N_T,N_R)$.
-The codebook for $\mathcal{T}_{\bP_{i,t}} \text{St}(N_T,N_R)$ corresponds to a collection of codewords that represent the different directions (tangents) in $\mathcal{T}_{\bP_{i,t}} \text{St}(N_T,N_R)$.
+The quantization algorithm exploits the vector space property of the tangent space and quantizes the local tangent space at the predicted precoder $\bP_{i,t}$, viz $\mathcal{T}_{\bP_{i,t}} \text{St}(N_T,N_R)$.
+The codebook for $\mathcal{T}_{\bP_{i,t}} \text{St}(N_T,N_R)$ corresponds to a collection of $\mathcal{B}-1$ codewords that represent the different directions (tangents) in $\mathcal{T}_{\bP_{i,t}} \text{St}(N_T,N_R)$.
 This codebook is subsequently referred to as the base codebook ($\text{base}^{\mathcal{C}}$) for the quantization function.
@@
 
-For this, we adopt the strategy in \cite{6891198}, which controls the magnitude of tangent steps, by having two codebooks $T^{\mathcal{C}}_p,T^{\mathcal{C}}_m$ of different spreads $s_p,s_m$, but same $2^{\mathcal{B}-1}$ base vectors in the $\text{base}^{\mathcal{C}}$, i.e.
-$T^{\mathcal{C}}_{\{p/m\}}=s_{\{p/m\}}\text{base}^{\mathcal{C}}$ (All codewords $\in \text{base}^{\mathcal{C}}$ multiplied by $s_{\{p/m\}}$ individually).
-The two codebooks are concatenated to form a $2^\mathcal{B}$ length codebook $T^\mathcal{C}$.
+For this, we adopt the strategy in \cite{6891198}, which controls the magnitude of tangent steps, by having two codebooks $T^{\mathcal{C}}_p,T^{\mathcal{C}}_m$ of different spreads $s_p,s_m$, but the same $2^{\mathcal{B}-1}$ base vectors in the $\text{base}^{\mathcal{C}}$, i.e.
+$T^{\mathcal{C}}_{\{p/m\}}=s_{\{p/m\}}\text{base}^{\mathcal{C}}$ (i.e.
+All codewords $\in \text{base}^{\mathcal{C}}$ multiplied by $s_{\{p/m\}}$ individually).
+The two codebooks are concatenated to form a $2^\mathcal{B}$ length codebook, $T^\mathcal{C}$.
 The receiver finds the optimal index $\text{fb}_{i,t} \in \{1,2,\ldots,2^{\mathcal{B}}\}$ in $T^\mathcal{C}$ by comparing the chordal distance metric ($d_s$), of each codeword to the actual precoder $\bU_{i,t}$ obtained from the SVD of the channel matrix, using \eqref{eqn:cn1}.
@@
 \end{equation}
-Here $\lambda>1$ is the history parameter.
+Here $\lambda>1$ is the history parameter, and $||\cdot||$ is $\mathcal{L}^2$ norm.
 We wish to perform the following optimization in order to find the optimum $\bW_{i,t}^{\text{out}}$ from the available estimates till time $t$:
@@
 \eqref{wout_upd} makes training of the reservoir easy to implement with low complexity.
-We only need to store the matrix $\text{\textbf{num}}_{i,t-1}$, a number $\text{den}_{i,t-1}$.
-Then, using the current reservoir state $\br_{i,t}$ and $\tilde{\bu}_{i,t}$ obtained from \eqref{res_upd}, \eqref{fpqp} respectively, $\bW_{i,t}^{\text{out}}$ can be calculated to obtain the predicted coarse estimate, $\tilde{\bu}_{i,t+1}$.
-This completes the technical discussion for the reservoir computing based framework for predictive quantization illustrated in Fig. \ref{res_overview}.
+We only need to store a matrix $\text{\textbf{num}}_{i,t-1}$, and a number $\text{den}_{i,t-1}$.
+Then, using the current reservoir state $\br_{i,t}$ and $\tilde{\bu}_{i,t}$ obtained from \eqref{res_upd}, \eqref{fpqp} respectively, optimum $\bW_{i,t}^{\text{out}}$ can be estimated.
+The optimum $\bW_{i,t}^{\text{out}}$ can then be used to obtain $\tilde{\bP}_{i,t+1}$, and so on.
+This completes the discussion of the proposed reservoir computing framework illustrated in Fig. \ref{res_overview}.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %\textcolor{blue}
-{\noindent Another advantage of the proposed scheme is the ease of training the reservoir, captured in \eqref{res_upd}.
-By storing just one matrix $\text{\textbf{num}}_{i,t}$ and a number $\text{den}_{i,t}$, we capture the entire history of the obtained quantized precoders, with past values weighted by $\lambda$ in $\mathcal{O}_{i,t}$ \eqref{oit}.
+{\noindent Another advantage of the proposed scheme is the ease of training of the reservoir, entailed by \eqref{wout_upd}.
+Reservoir computing, thus proposes an easy to train data centric scheme, which is not typical for data centric ML based schemes.
+Also, by storing just one matrix $\text{\textbf{num}}_{i,t}$ and a number $\text{den}_{i,t}$, we capture the entire history of the obtained quantized precoders, with past values weighted by $\lambda$ in $\mathcal{O}_{i,t}$ \eqref{oit}.
 This is a departure from previous schemes \cite{Gupt1905:Predictive,6891198,6545375} which store the past $p$ precoders in a $p$ sized cyclic buffer ($p$ also has to be pre-decided).
-Reservoir computing, thus proposes an easy to train data centric scheme, which is not typical for data centric ML based schemes.
+
 }
@@
 \noindent The simulations have been performed for the IEEE Pedestrian-A channel, with $N_T=4$, $N_R=2$.
-The channel matrices $\bH_{i,t}$ are generated using Jake's model for realistic simulations, from the IT++ library through the python wrapper py-itpp \cite{ViditPy}.
-We compare the results obtained by our framework, with the work presented in \cite{6891198}, which also utilized temporal correlations for predictive quantization.
+The channel matrices $\bH_{i,t}$ are generated using Jake's model via IT++ library through the python wrapper py-itpp \cite{ViditPy}.
+We compare the results obtained by our framework with \cite{6891198}, which presented a manifold geometry method to exploit temporal correlations for predictive quantization.
 % The forward prediction function $f_P$ of the proposed framework, has $p$ (Section \ref{section2}) to be $1$ \eqref{fpqp}, whereas the backward pass $p$ for time instant $t$ is $t$ (Observe the framing of $\mathcal{O}_{i,t}$).
@@
 The quantization function $q_P$ is kept to be same, as described in \cite{6545375,6891198,Gupt1905:Predictive} for both the approaches.
-Although in both our work and \cite{6891198}, only temporal correlations are exploited, we compare the BER, quantization error and achievable rate results for the complete MIMO-OFDM setting with $N=64$ of subcarriers, and channels are fed back for $8$ evenly spaced subcarriers, indexed starting at 0, viz.
+Although in both our work and \cite{6891198}, only temporal correlations are exploited, we compare the simulation results for the complete MIMO-OFDM setting (visually illustrated in Fig.
+2) with $N=64$ subcarriers.
+Channels are fed back for $8$ evenly spaced subcarriers indexed from 0, viz.
 $\{0,9,\ldots,63\}$ ($\{9k, k \in \{0,1,\ldots,7\}\}$).
-Hence, the feedback is available only for $i=\{9k\}$ subcarriers (i.e.
-transmitter obtains only $\text{fb}_{\{9k\},t}$).
-The precoding matrices at subcarriers where feedback is not available ($i\neq\{9k\}$) are estimated via the Cayley Interpolation method presented in \cite{Gupt1905:Predictive}.
-The setting is visually illustrated in Fig. \ref{table}.
+Hence, the transmitter obtains only $\text{fb}_{\{9k\},t}$.
+For non fed back subcarriers $i\neq 9k$, $9n < i < 9(n+1)$, the Cayley method \cite{Gupt1905:Predictive} is used to interpolate $\tilde{\bU}_{i,t}$, from available estimates, $\tilde{\bU}_{9n,t}$ and $\tilde{\bU}_{9(n+1), t}$
+\begin{equation}
+\label{eqn:cayley_i1_i2}
+  \tilde{\bU}_{i,t} =  \text{Exp}_{\tilde{\bU}_{9n, t}}\left((i/9-n)\text{Exp}^{-1}_{\tilde{\bU}_{9n, t}}\left(\tilde{\bU}_{9(n+1),t}\right)\right)
+%\text{Exp}^{-1}_{\tilde{\bU}_{i_1,t}}(\tilde{\bU}_{i_2,t}
+%\Lambda)\right)
+\end{equation}
+For a detailed treatment on $\text{Exp}, \text{Exp}^{-1}$, refer \cite{DBLP:journals/corr/abs-1708-00045}.
 
@@
 $\bP_{i,t}=\tilde{\bU}_{i,t-1}$) is used for 10 time instances to provide the initial training data for the reservoir and to overcome the initial transient response of the reservoir (also discussed in \cite{mosleh2017brain}).
-A 6 bit base codebook is used for the quantization function $q_P$ and is generated according to the method presented in Section \ref{qp}, similar to \cite{Gupt1905:Predictive}.
+A 5 bit base codebook is used for the quantization function $q_P$ and is generated according to the method presented in Section \ref{qp}, similar to \cite{Gupt1905:Predictive}.
 Hence, both initialization and subsequent feedback, $\text{fb}_{i,t}$ can be encoded using 6 bits (i.e. $\mathcal{B}=6$ Section \ref{section2}).
@@
 Unlike \cite{Gupt1905:Predictive}, we do not exploit frequency correlations for predictive quantization, and the $8$ reservoirs for prediction of $8$ fed-back subcarriers are kept independent of each other.
-All these 8 reservoirs are initialized with $\bA_{i\in\{9k\}}$ being an Erdos-Reny\"i graph, with probability of edge connections being $0.2$, $\lambda=2$, $\bW^{\text{out/in}}_{i\in\{9k\},0}$ are initialized randomly, and $D_{\text{in}}=D_{\text{out}}=14$ (vectorized representation of $4\times2$ semi-unitary matrix, Section \ref{vectorize}) and $D_{\text{resv}}=60$.
+All these 8 reservoirs are initialized with $\bA_{i\in\{9k\}}$ being an Erdos-Reny\"i graph, with probability of edge connections being $0.2$, $\lambda=2$, $\bW^{\text{out/in}}_{i\in\{9k\},0}$ initialized randomly, $D_{\text{in}}=D_{\text{out}}=14$ (vectorized representation of $4\times2$ semi-unitary matrix, Section \ref{vectorize}) and $D_{\text{resv}}=60$.
 % All these 8 reservoirs are initialized with $\bA_{i\in\{9k\}}$ being an Erdos-Reny\"i graph, with 
@@
 \caption{The transmitter obtains feedback for $\{9k, k \in \{0,1,\ldots,7\}$ subcarriers, and uses $\tilde{\bU}_{i,t-1}$, along with $f_P,q_P$ \eqref{fpqp} to obtain $\tilde{\bU}_{i,t}$, illustrated in the figure via cyan arrows.
-For each time instant, the transmitter uses the Cayley method to interpolate $\tilde{\bU}_{i,t}$ at $i\neq\{9k\}$ non fed back subcarriers (green arrows).}
+For each time instant, the transmitter uses the Cayley method  \eqref{eqn:cayley_i1_i2} to interpolate $\tilde{\bU}_{i,t}$ at $i\neq\{9k\}$ non fed back subcarriers (green arrows}
 \label{table}
@@
 \includegraphics[width=0.4\textwidth]{images/qtizErr.pdf}
-\caption{Quantization error in terms of chordal distance to the actual precoder $\bU_{\{9k\},t}$ observed at the receiver, from the quantized estimate $\tilde{\bU}_{\{9k\},t}$, averaged over 8 fed back subcarriers ($\{9k, k \in \{0,1,\ldots,7\}\}$) and 10 independent channel realizations (normalized Doppler $f_DT_s=10^{-4}$).}
+\caption{Quantization error in terms of chordal distance to the actual precoder $\bU_{\{9k\},t}$ observed at the receiver, from the quantized estimate $\tilde{\bU}_{\{9k\},t}$ averaged over $\{9k\}$ fed back subcarriers $\Big($ viz.
+$\frac{\Sigma_{i \in 9k}d_S(\tilde{\bU}_{i,t}, \bU_{i,t})}{8}$ $\Big)$ and 10 independent channel realizations (normalized Doppler $f_DT_s=10^{-4}$).}
 \label{qtiz_err}

### 2019-09-08 paper/main.tex
Shortening abstract

@@
 
-Precoding matrices obtained from SVD of the MIMO channel matrix (which is estimated at the receiver) can be utilized at the transmitter for optimum power allocation and lower BER transmissions. 
-A key step enabling this improved performance is the feedback of these precoders to the transmitter from the receiver.
-Since the bit budget for such Channel State Information (CSI) feedback is limited, these precoders need to be quantized effectively using just a few bits.
-For a $N_T \times N_R$ MIMO system ($N_{\{T/R\}}$: Number of Transmit/Receive Antennas), this amounts to quantizing a $N_T \times N_R$ complex-valued matrix.
+SVD based precoding matrices have been theoretically proven to perform optimum power allocation and lower BER transmissions in MIMO wireless systems. 
+% A key step enabling this improved performance is the feedback of these precoders to the transmitter from the receiver.
+% Gievn the limited bit budget for such Channel State Information (CSI) feedback, these precoders need to be quantized effectively using just a few bits.
+However, in a practical setting, for a $N_T \times N_R$ MIMO system ($N_{\{T/R\}}$: Number of Transmit/Receive Antennas), the receiver needs to quantize and feedback the $N_T \times N_R$ precoding matrix obtained from SVD of the channel matrix, with just a few bits to respect the limited bit budget constraint.
 This task is aided by the presence of an underlying manifold structure and temporal/frequency correlations in the precoders. 
-Predictive quantization methods exploit the available correlations in the previously estimated precoders to predict new precoders, and then quantize just the additional information required to obtain the actual precoder from the predicted value, yielding a refined estimate.
+Predictive quantization methods exploit the correlations in the previously fed back precoders for prediction, followed by quantization of the incremental information required to obtain the actual precoder from the predicted value.
 In this work, we introduce a reservoir computing framework for predictive quantization by exploiting temporal correlations. 
@@
 {
-Reservoir computing is a computational framework designed for sequential data processing.
+Reservoir computing (RC) is a computational framework designed for sequential data processing.
 Its design is inspired from several frameworks of Recurrent Neural Networks \cite{jaeger2004harnessing}, including Liquid State Machines \cite{jalalvand2015real} and Echo State Networks \cite{mosleh2017brain,pathak2017using}.
-The reservoir computing framework represents the non-linear relationships in the data via the higher dimensional dynamical reservoir state vector, which is transformed (using
+The RC framework represents the non-linear relationships in the data via the higher dimensional dynamical reservoir state vector, which is transformed (using
 matrices, referred to as `couplers') to the lower dimensional input/output vectors
@@
 % Key advantages of reservoir computing framework include ease of training in comparison to its counterparts like Deep Neural Networks \cite{mosleh2017brain}.
-Reservoir computing has been successfully used to solve problems like handwritten digit image recognition \cite{jalalvand2015real}, climate prediction \cite{pathak2017using} and spoken digit recognition \cite{verstraeten2005isolated}.
+RC has been successfully used to solve problems like handwritten digit image recognition \cite{jalalvand2015real}, climate prediction \cite{pathak2017using} and spoken digit recognition \cite{verstraeten2005isolated}.
 }
 % Owing to the versatility of reservoir computing, it can deal with any sequential data in principle and hence further expansion of its application fields is widely expected.
-Reservoir computing frameworks have also been applied to solve problems in the domain of wireless communications \cite{jaeger2004harnessing,mosleh2017brain,shafin2018realizing}.
-\cite{jaeger2004harnessing} used reservoir computing framework to harness channel non-linearities for improved channel equalization.
+RC frameworks have also been applied to solve problems in the domain of wireless communications \cite{jaeger2004harnessing,mosleh2017brain,shafin2018realizing}.
+\cite{jaeger2004harnessing} used RC framework to harness channel non-linearities for improved channel equalization.
 \cite{mosleh2017brain,shafin2018realizing} utilized the framework for OFDM symbol detection while accounting for channel and power amplifier non-linearities.
-In our work, we utilize a reservoir computing framework similar to one presented in \cite{pathak2017using} to capture the underlying nonlinear relations between previously obtained quantized precoders, in order to predict the precoder at next time instant.
-This becomes analogous to time series prediction algorithms, for which the reservoir computing framework has been cited to work effectively \cite{mosleh2017brain}.
+In our work, we utilize a RC framework similar to one presented in \cite{pathak2017using} to capture the underlying nonlinear relations between previously obtained quantized precoders, in order to predict the precoder at next time instant.
+This becomes analogous to time series prediction algorithms, for which the RC framework has been cited to work effectively \cite{mosleh2017brain}.
 
@@
 
-When using the predictive quantization scheme, the quantization is performed on a smaller subspace when compared to the entire manifold in case of independent quantization.
-Therefore, the quantization error is substantially lower as well.
-However, independent quantization algorithms are important for smart initialization (instead of a cold start) of the predictive quantization strategies.
-Observe that predictive quantization algorithms for SVD precoders are typically the higher dimensional analogues of well known approaches to reduce quantization error using linear prediction codes (LPCs) and Delta PCM.
-In both LPCs and Delta PCM, quantization error can be reduced substantially using a linear predictor and quantizing the scalar difference between the predicted and observed value (innovation).
-Analogous to this, for $\text{St}(N_T,N_R)$, quantization error is reduced by quantizing a subspace around the predicted value that is much smaller than the entire manifold.
+% When using the predictive quantization scheme, the quantization is performed on a smaller subspace when compared to the entire manifold in case of independent quantization.
+% Therefore, the quantization error is substantially lower as well.
+% However, independent quantization algorithms are important for smart initialization (instead of a cold start) of the predictive quantization strategies.
+% Observe that predictive quantization algorithms for SVD precoders are typically the higher dimensional analogues of well known approaches to reduce quantization error using linear prediction codes (LPCs) and Delta PCM.
+% In both LPCs and Delta PCM, quantization error can be reduced substantially using a linear predictor and quantizing the scalar difference between the predicted and observed value (innovation).
+% Analogous to this, for $\text{St}(N_T,N_R)$, quantization error is reduced by quantizing a subspace around the predicted value that is much smaller than the entire manifold.
 
-In our work, we propose a reservoir computing based prediction framework that predicts the new precoders by utilizing temporal correlations that are captured from past observed precoders (via $f_P$).
+In our work, we propose a RC based prediction framework that predicts the new precoders by utilizing temporal correlations that are captured from past observed precoders (via $f_P$).
 We reuse the $q_P$ algorithm from \cite{Gupt1905:Predictive,6891198}.
@@
 Previous work \cite{Gupt1905:Predictive,6891198} has considered $f_P$ and $q_P$ to be uncoupled with each other.
-A detailed discussion on the reservoir computing based model for $f_P$ and $q_P$ is presented in Section \ref{section3}.
-The proposed reservoir computing scheme is evaluated against the temporal predictive quantization scheme in \cite{6891198}, and the simulation results are discussed in Section \ref{section4}.
+% A detailed discussion on the RC based model for $f_P$ and $q_P$ is presented in Section \ref{section3}.
+% The proposed RC scheme is evaluated against the temporal predictive quantization scheme in \cite{6891198}, and the simulation results are discussed in Section \ref{section4}.
 
@@
 \label{vectorize}
-The reservoir computing framework has inputs and outputs as real vectors, and thus, it is necessary to convert the precoding matrices to vectors.
+The RC framework has inputs and outputs as real vectors, and thus, it is necessary to convert the precoding matrices to vectors.
 A precoding matrix $\mathcal{\bM} \in \text{St}(N_T,N_R)$ is a $\mathbb{C}^{N_T \times N_R}$ matrix with the property $\mathcal{\bM}^H\mathcal{\bM}=\text{\textbf{1}}_{N_R}$.
@@
 For the third column, we take only the first $N_T-2$ complex numbers, and so on.
-Therefore, we vectorize a $\mathbb{C}^{N_T \times N_R}$ semi-unitary matrix into a $2(N_T)+2(N_T-1)+\ldots+2(N_T-N_R+1)= 2N_TN_R-N_R^2+N_R$ dimensional vector.
+Therefore, we vectorize a $\mathbb{C}^{N_T \times N_R}$ semi-unitary matrix $\mathcal{\bM}$ into a $2(N_T)+2(N_T-1)+\ldots+2(N_T-N_R+1)= 2N_TN_R-N_R^2+N_R$ dimensional vector, denoted as $\bm$.
 
-Observe here that we incur a dimensional penalty upon vectorizing semi-unitary matrices.
-$\text{St}(N_T,N_R)$ is a $2N_TN_R-N_R^2$ dimensional manifold, whereas the proposed vectorization yields a $2N_TN_R-N_R^2+N_R$ dimensional vector representation.
-This corresponds to an overhead of $N_R$ dimensions, since we have not exploited the fact that each of the $N_R$ column vectors is a unit norm vector as well.
-It looks as if utilizing the norm 1 property, we could just take $N_T-1$ complex numbers when vectorizing the first column, instead of $N_T$.
+% Observe here that we incur a dimensional penalty upon vectorizing semi-unitary matrices.
+% $\text{St}(N_T,N_R)$ is a $2N_TN_R-N_R^2$ dimensional manifold, whereas the proposed vectorization yields a $2N_TN_R-N_R^2+N_R$ dimensional vector representation.
+% This corresponds to an overhead of $N_R$ dimensions, since we have not exploited the fact that each of the $N_R$ column vectors is a unit norm vector as well.
+% It looks as if utilizing the norm 1 property, we could just take $N_T-1$ complex numbers when vectorizing the first column, instead of $N_T$.
 However, this would lead to non-unique representations, since there could then be infinite possible values that the lone missing complex number can take, so that the vector has unit norm.
-Hence, we vectorize a semi-unitary $\mathbb{C}^{N_T \times N_R}$ $\mathcal{\bM}$ into $2N_TN_R-N_R^2+N_R$ dimensional vector, denoted as $\bm$.
+ % Hence, we vectorize a semi-unitary $\mathbb{C}^{N_T \times N_R}$ $\mathcal{\bM}$ into $2N_TN_R-N_R^2+N_R$ dimensional vector, denoted as $\bm$.
 %Focus on the fact that you don't actually pay a penalty
@@
 \subsection{Forward Prediction $f_P$}
-\noindent The vector representation of semi-unitary matrices allows to proceed with our discussion on reservoir computing framework.
-Consider the reservoir computing framework in Fig. \ref{res_overview} %Ref Fig. Reservoir Pic
+\noindent The vector representation of semi-unitary matrices allows to proceed with our discussion on RC framework.
+Consider the RC framework in Fig. \ref{res_overview} %Ref Fig. Reservoir Pic
 
 The input to the reservoir $i$ that corresponds to subcarrier $i$ is $\tilde{\bu}_{i,t-1}$ (vectorized representation of $\tilde{\bU}_{i,t-1}$), with dimensions $D_{\text{in}}=2N_TN_R-N_R^2+N_R$.
-Using a randomly initialized $D_{\text{in}}\times D_{\text{resv}}$ input coupler matrix $\bW^{\text{in}}_i$, the $D_{\text{in}}$ dimensional input is mapped to a $D_{\text{resv}}(>>D_{\text{in}})$ dimensional vector, where $D_{\text{resv}}$ is the dimension of the reservoir state vector $\br_{i,t}$.
+Using a randomly initialized $D_{\text{resv}}\times D_{\text{in}}$ input coupler matrix $\bW^{\text{in}}_i$, the $D_{\text{in}}$ dimensional input is mapped to a $D_{\text{resv}}(>>D_{\text{in}})$ dimensional vector, where $D_{\text{resv}}$ is the dimension of the reservoir state vector $\br_{i,t}$.
 $\br_{i,t}$ is initialized with $D_{\text{resv}}$ zeros, and is updated via the following equation:
@@
 Therefore, the output of the reservoir is also a $D_{\text{in}}$ dimensional vector (viz. $D_{\text{out}}=D_{\text{in}}$).
-The output $\bp_{i,t}$ is obtained using a matrix transformation of the reservoir state $\br_{i,t}$ with the $D_{\text{resv}}\times D_{\text{out}}$ output coupler matrix $\bW^{\text{out}}_{i,t-1}$,
+The output $\bp_{i,t}$ is obtained using a matrix transformation of the reservoir state $\br_{i,t}$ with the $D_{\text{out}}\times D_{\text{resv}}$ output coupler matrix $\bW^{\text{out}}_{i,t-1}$,
 \begin{equation}
@@
 \includegraphics[width=0.8\textwidth]{images/system2.pdf}
-% \caption{System Overview: The reservoir computing framework takes the precoder estimate at $t-1$ (viz.
+% \caption{System Overview: The RC framework takes the precoder estimate at $t-1$ (viz.
 $\tilde{\bu}_{i,t-1}$) as input, and executes the forward pass of the predictive quantization framework, shaded in green, to obtain $\tilde{\bu}_{i,t}$.
@@
 Central to the quantization algorithm is the fact that tangent spaces local to a point in manifold are vector spaces.
-Given two points $\bX$ and $\bY$ in $\text{St}(N_T,N_R)$, a lifting operation $\bT^Y_X=\texttt{lift}(\bX,\bY)$, $\texttt{lift}:\text{St}(N_T,N_R)\times \text{St}(N_T,N_R) \to \mathcal{T}_X \text{St}(N_T,N_R)$ yields a tangent from $X$ to $Y$, denoted as $\bT^Y_X \in \mathcal{T}_X \text{St}(N_T,N_R)$, where $\mathcal{T}_X \text{St}(N_T,N_R)$ is the local tangent space at $\bX$.
-A corresponding retraction operation $Y=\texttt{retract}(X,\bT^Y_X)$, $\texttt{retract}: \text{St}(N_T,N_R)\times \mathcal{T}_X \text{St}(N_T,N_R) \to \text{St}(N_T,N_R)$ gives back the manifold point obtained by traversing in the tangent direction given by the second argument ($\bT^Y_X$).
-In this work, the chosen lifting-retraction pairs are the Cayley exponentials, discussed in \cite{DBLP:journals/corr/abs-1708-00045,Gupt1905:Predictive}. % and used in \cite{Gupt1905:Predictive}.
-The Cayley exponential lifting operation maps two points in $\text{St}(N_T,N_R)$, to a $N_T\times N_T$ skew Hermitian matrix that represents the tangent from first point to the other.
+% Given two points $\bX$ and $\bY$ in $\text{St}(N_T,N_R)$, a lifting operation $\bT^Y_X=\texttt{lift}(\bX,\bY)$, $\texttt{lift}:\text{St}(N_T,N_R)\times \text{St}(N_T,N_R) \to \mathcal{T}_X \text{St}(N_T,N_R)$ yields a tangent from $X$ to $Y$, denoted as $\bT^Y_X \in \mathcal{T}_X \text{St}(N_T,N_R)$, where $\mathcal{T}_X \text{St}(N_T,N_R)$ is the local tangent space at $\bX$.
+% A corresponding retraction operation $Y=\texttt{retract}(X,\bT^Y_X)$, $\texttt{retract}: \text{St}(N_T,N_R)\times \mathcal{T}_X \text{St}(N_T,N_R) \to \text{St}(N_T,N_R)$ gives back the manifold point obtained by traversing in the tangent direction given by the second argument ($\bT^Y_X$).
+% In this work, the chosen lifting-retraction pairs are the Cayley exponentials, discussed in \cite{DBLP:journals/corr/abs-1708-00045,Gupt1905:Predictive}. % and used in \cite{Gupt1905:Predictive}.
+% The Cayley exponential lifting operation maps two points in $\text{St}(N_T,N_R)$, to a $N_T\times N_T$ skew Hermitian matrix that represents the tangent from first point to the other.
 
 The quantization algorithm exploits the vector space property of the tangent space and quantizes the local tangent space at the predicted precoder $\bP_{i,t}$, viz $\mathcal{T}_{\bP_{i,t}} \text{St}(N_T,N_R)$.
-The codebook for $\mathcal{T}_{\bP_{i,t}} \text{St}(N_T,N_R)$ corresponds to a collection of $\mathcal{B}-1$ codewords that represent the different directions (tangents) in $\mathcal{T}_{\bP_{i,t}} \text{St}(N_T,N_R)$.
-This codebook is subsequently referred to as the base codebook ($\text{base}^{\mathcal{C}}$) for the quantization function.
-The feedback from the receiver indicates the codeword corresponding to the optimum tangent in the $\text{base}^{\mathcal{C}}$, which the transmitter can choose to get closest (in terms of chordal distance metric, $d_s(\bX,\bY)$ for $\bX,\bY \in \text{St}(N_T,N_R)$ detailed in \cite{Gupt1905:Predictive,6891198}) to the actual value $\bU_{i,t}$.
-With the optimum direction chosen, the next step is to determine how much to move in that particular chosen direction, viz. the length of the chosen tangent direction.
-
-For this, we adopt the strategy in \cite{6891198}, which controls the magnitude of tangent steps, by having two codebooks $T^{\mathcal{C}}_p,T^{\mathcal{C}}_m$ of different spreads $s_p,s_m$, but the same $2^{\mathcal{B}-1}$ base vectors in the $\text{base}^{\mathcal{C}}$, i.e.
-$T^{\mathcal{C}}_{\{p/m\}}=s_{\{p/m\}}\text{base}^{\mathcal{C}}$ (i.e.
-All codewords $\in \text{base}^{\mathcal{C}}$ multiplied by $s_{\{p/m\}}$ individually).
-The two codebooks are concatenated to form a $2^\mathcal{B}$ length codebook, $T^\mathcal{C}$.
-The receiver finds the optimal index $\text{fb}_{i,t} \in \{1,2,\ldots,2^{\mathcal{B}}\}$ in $T^\mathcal{C}$ by comparing the chordal distance metric ($d_s$), of each codeword to the actual precoder $\bU_{i,t}$ obtained from the SVD of the channel matrix, using \eqref{eqn:cn1}.
+% The codebook for $\mathcal{T}_{\bP_{i,t}} \text{St}(N_T,N_R)$ corresponds to a collection of $\mathcal{B}-1$ codewords that represent the different directions (tangents) in $\mathcal{T}_{\bP_{i,t}} \text{St}(N_T,N_R)$.
+% This codebook is subsequently referred to as the base codebook ($\text{base}^{\mathcal{C}}$) for the quantization function.
+The feedback from the receiver indicates the codeword corresponding to the optimum tangent in $\mathcal{T}_{\bP_{i,t}} \text{St}(N_T,N_R)$, which the transmitter can choose to get closest (in terms of chordal distance metric, $d_s(\bX,\bY)$ for $\bX,\bY \in \text{St}(N_T,N_R)$ detailed in \cite{Gupt1905:Predictive,6891198}) to the actual value $\bU_{i,t}$.
+With the optimum direction chosen, the next step is to determine how much to move in that particular chosen direction, viz.
+the length of the chosen tangent direction.
+For this, we adopt the strategy in \cite{6891198}, which controls the magnitude of tangent steps, by having two codebooks of different spreads, but the same $2^{\mathcal{B}-1}$ base vectors.
+% The two codebooks are concatenated to form a $2^\mathcal{B}$ length codebook, $T^\mathcal{C}$.
+% The receiver finds the optimal index $\text{fb}_{i,t} \in \{1,2,\ldots,2^{\mathcal{B}}\}$ in $T^\mathcal{C}$ by comparing the chordal distance metric ($d_s$), of each codeword to the actual precoder $\bU_{i,t}$ obtained from the SVD of the channel matrix, using \eqref{eqn:cn1}.
 The receiver then feeds back $\text{fb}_{i,t}$ to the transmitter using $\mathcal{B}$ bits.
 The transmitter uses the fed back $\text{fb}_{i,t}$ and \eqref{eqn:cn2} to calculate $\tilde{\bU}_{i,t}$,
-\begin{equation}
-\label{eqn:cn1}
-\text{fb}_{i,t} \gets \text{argmin}_{i \in \{1,2,\ldots,2^{\mathcal{B}}\}}\left (d_s\left (\bU_{i,t},\text{retract}(\bP_{i,t},T^\mathcal{C}[i])\right ) \right)
-\end{equation}
-\begin{equation}
-\tilde{\bU}_{i,t}=q_P(\bP_{i,t},\text{fb}_{i,t})=\text{retract}(\bP_{i,t},T^\mathcal{C}[\text{fb}_{i,t}])
-\label{eqn:cn2}
-\end{equation}
-$\text{fb}_{i,t}$ is also used to update the spread of the codebooks $T^{\mathcal{C}}_p,T^{\mathcal{C}}_m$.
-Depending on whether $\text{fb}_{i,t} \geq 2^{\mathcal{B}-1}$, i.e.
+% \begin{equation}
+% \label{eqn:cn1}
+% \text{fb}_{i,t} \gets \text{argmin}_{i \in \{1,2,\ldots,2^{\mathcal{B}}\}}\left (d_s\left (\bU_{i,t},\text{retract}(\bP_{i,t},T^\mathcal{C}[i])\right ) \right)
+% \end{equation}
+% \begin{equation}
+% \tilde{\bU}_{i,t}=q_P(\bP_{i,t},\text{fb}_{i,t})=\text{retract}(\bP_{i,t},T^\mathcal{C}[\text{fb}_{i,t}])
+% \label{eqn:cn2}
+% \end{equation}
+% $\text{fb}_{i,t}$ is also used to update the spread of the codebooks $T^{\mathcal{C}}_p,T^{\mathcal{C}}_m$.
+% Depending on whether $\text{fb}_{i,t} \geq 2^{\mathcal{B}-1}$, i.e.
 whether the optimum codeword is in $T^{\mathcal{C}}_p$ or $T^{\mathcal{C}}_m$, the scale parameter $s[k]$, which in turn controls values of $s_p, s_m$, is updated as,
-$$s_p=g^{\text{min}(s[k-1]+1,0)}, s_m = g^{s[k-1]-1}$$
-$$
-s[k]=
-\begin{cases}
-\text{min}(s[k-1]+1,0), \text{ for } \text{fb}_{i,t} \in T^{\mathcal{C}}_p\\
-s[k-1]-1, \text{otherwise}\\
-\end{cases}
-$$
-with $s[0]=0$.
-Intuitively, the algorithm reduces/increases the spread of the codebook till the reduction/increase of spread is no longer beneficial, i.e.
+% $$s_p=g^{\text{min}(s[k-1]+1,0)}, s_m = g^{s[k-1]-1}$$
+% $$
+% s[k]=
+% \begin{cases}
+% \text{min}(s[k-1]+1,0), \text{ for } \text{fb}_{i,t} \in T^{\mathcal{C}}_p\\
+% s[k-1]-1, \text{otherwise}\\
+% \end{cases}
+% $$
+% with $s[0]=0$.
+% Intuitively, the algorithm reduces/increases the spread of the codebook till the reduction/increase of spread is no longer beneficial, i.e.
 the optimum codeword lies in the higher/lower spread codebook instead.
-The scheme used to obtain $\text{base}^{\mathcal{C}}$ is similar to the one presented in \cite{Gupt1905:Predictive}, which performs a $k$-means ($k=2^{\mathcal{B}-1}$) clustering on a collection of tangents to obtain an isotropic collection of $2^{\mathcal{B}-1}$ tangent codewords.
+% The scheme used to obtain $\text{base}^{\mathcal{C}}$ is similar to the one presented in \cite{Gupt1905:Predictive}, which performs a $k$-means ($k=2^{\mathcal{B}-1}$) clustering on a collection of tangents to obtain an isotropic collection of $2^{\mathcal{B}-1}$ tangent codewords.
 This completes the discussion on the quantization function $q_P$ to obtain $\tilde{\bU}_{i,t}=q_P(\bP_{i,t},\text{fb}_{i,t})$ from $\bP_{i,t},\text{fb}_{i,t}$.
@@
 The optimum $\bW_{i,t}^{\text{out}}$ can then be used to obtain $\tilde{\bP}_{i,t+1}$, and so on.
-This completes the discussion of the proposed reservoir computing framework illustrated in Fig. \ref{res_overview}.
+This completes the discussion of the proposed RC framework illustrated in Fig. \ref{res_overview}.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %\textcolor{blue}
-{\noindent Another advantage of the proposed scheme is the ease of training of the reservoir, entailed by \eqref{wout_upd}.
-Reservoir computing, thus proposes an easy to train data centric scheme, which is not typical for data centric ML based schemes.
-Also, by storing just one matrix $\text{\textbf{num}}_{i,t}$ and a number $\text{den}_{i,t}$, we capture the entire history of the obtained quantized precoders, with past values weighted by $\lambda$ in $\mathcal{O}_{i,t}$ \eqref{oit}.
-This is a departure from previous schemes \cite{Gupt1905:Predictive,6891198,6545375} which store the past $p$ precoders in a $p$ sized cyclic buffer ($p$ also has to be pre-decided).
+% {\noindent Another advantage of the proposed scheme is the ease of training of the reservoir, entailed by \eqref{wout_upd}.
+% RC, thus proposes an easy to train data centric scheme, which is not typical for data centric ML based schemes.
+% Also, by storing just one matrix $\text{\textbf{num}}_{i,t}$ and a number $\text{den}_{i,t}$, we capture the entire history of the obtained quantized precoders, with past values weighted by $\lambda$ in $\mathcal{O}_{i,t}$ \eqref{oit}.
+% This is a departure from previous schemes \cite{Gupt1905:Predictive,6891198,6545375} which store the past $p$ precoders in a $p$ sized cyclic buffer ($p$ also has to be pre-decided).
 
-}
+% }
 
@@
 \ref{qtiz_err} it is evident that the proposed framework is able to reduce the quantization error below what was obtained from the existing temporal correlations based predictive quantizer in \cite{6891198}.
-In addition, the quantization error plot is much smoother as well, which can be explained from the fact that the reservoir computing approach optimizes $\mathcal{O}_{i,t}$, that captures the long term dynamics of the channel and hence, does not face jittery variations.
+In addition, the quantization error plot is much smoother as well, which can be explained from the fact that the RC approach optimizes $\mathcal{O}_{i,t}$, that captures the long term dynamics of the channel and hence, does not face jittery variations.
 We simulate (uncoded QPSK) BER performance for all the 64 subcarriers' precoders obtained after interpolation ($\tilde{\bU}_{i\neq\{9k\},t}$) and quantization ($\tilde{\bU}_{\{9k\},t}$).
 Observe from Fig.
-\ref{BER} that reservoir computing framework is able to achieve substantial improvements in $\text{E}_\text{b}\text{N}_0$ levels at $\text{BER}\leq 10^{-4}$.
+\ref{BER} that RC framework is able to achieve substantial improvements in $\text{E}_\text{b}\text{N}_0$ levels at $\text{BER}\leq 10^{-4}$.
 Particularly, for $\text{BER}=10^{-5}$ we observe around $5$ dB improvement.
 
-We hypothesize that the key reason for the improved performance for both quantization error and BER in the reservoir computing approach, is the fact that $f_P,q_P$ are coupled via the backward pass framework (explained towards the end of Section \ref{train}).
+We hypothesize that the key reason for the improved performance for both quantization error and BER in the RC approach, is the fact that $f_P,q_P$ are coupled via the backward pass framework (explained towards the end of Section \ref{train}).
 Also, observe from Fig.
@@
 Observe from Fig.
-\ref{achievrate} that the reservoir computing framework offers improvement in achievable rate for $f_DT_s=10^{-4}$.
-Since the temporal variations for $f_DT_s=10^{-2}, 10^{-1}$ are higher, the reservoir computing framework has to learn a faster-varying function, and hence the degradation in performance.
+\ref{achievrate} that the RC framework offers improvement in achievable rate for $f_DT_s=10^{-4}$.
+Since the temporal variations for $f_DT_s=10^{-2}, 10^{-1}$ are higher, the RC framework has to learn a faster-varying function, and hence the degradation in performance.
 However, it still matches the performance of the predictive quantizer in \cite{6891198} for $f_DT_s=10^{-2}$ and performs slightly better for $f_DT_s=10^{-1}$.
@@
 \centering
-\includegraphics[width=0.43\textwidth]{images/hopRate.pdf}
+\includegraphics[width=0.43\textwidth]{images/hopRate2.pdf}
 \vspace{-5pt}

### 2019-09-08 eval.py

@@ -37,8 +37,8 @@ unqtBER_QPSK=np.zeros(Eb_N0_dB.shape[0])
 unqt_interpBER_QPSK=np.zeros(Eb_N0_dB.shape[0])
 indqtBER_QPSK=np.zeros(Eb_N0_dB.shape[0])
 count=0
-sil_BER=1
-sil_cap=0
+sil_BER=0
+sil_cap=1
 # qtiz_U=np.load('./Intmd_Res/qtiz_U0.npy')
 # cmp_qtiz_U=np.load('./Intmd_Res/cmp_qtiz_U0.npy')
 # cmp_qtiz_err=np.load('./Intmd_Res/cmp_qtiz_err0.npy')

### 2019-09-08 paper/main.tex
Introduction shortened to one page

@@
 % Broad summary of your work, come to your problem definition.
-In MIMO wireless systems, precoding matrices are used for transformation of an $N_S$-dimensional ($N_S \leq \text{min}(N_T,N_R))$ information vector onto an $N_T$-dimensional transmit vector that corresponds to the signal emanating from the $N_T$ antennas of the transmitter.
-The precoding matrix used to achieve the channel capacity using optimal power allocation is obtained via the SVD of the MIMO channel matrix \cite{love2008overview}.
-The MIMO channel matrix is estimated at the receiver, and the transmitter has no a-priori knowledge of the same.
-Therefore, to obtain the said benefits of SVD precoders at the transmitter, the receiver needs to quantize and feed back the precoders it obtains from the SVD of MIMO channel matrix.
-To respect the bit budget imposed by limited feedback CSI schemes, the quantization needs to be performed using very few bits.
+% Can remove MIMO wireless systems
+In MIMO wireless systems, precoding matrices are used for transformation of an $N_S$-dimensional ($N_S \leq \text{min}(N_T,N_R))$ data stream onto an $N_T$-dimensional transmit vector that corresponds to the signal emanating from the $N_T$ transmit antennas.
+The precoding matrix used to maximize the achievable rate using optimal power allocation is obtained via the SVD of the MIMO channel matrix \cite{love2008overview}.
+However, since the MIMO channel matrix is estimated at the receiver, the transmitter requires receiver feedback for optimal precoding.
+Therefore, the receiver needs to quantize and feed back the precoders while respecting the bit budget imposed by limited feedback schemes.
 Given the high dimensionality of precoders (which form a $N_T \times N_R$ complex-valued matrix, viz.
@@
 Past work has used two inherent properties of the precoders to enable effective quantization with just a few bits.
-First, the precoders are not actually $2N_TN_R$ dimensional entities, but have an underlying manifold structure that allows to work with lower dimensions, when performing operations over the manifold directly.
-Second, these precoders are correlated in both time and frequency.
-Utilizing these correlations permit the use of predictive quantization algorithms, which enable improvement of the quantization error with time.
-This improvement is obtained because utilizing the correlations for estimation of the new precoder, allows for quantization of just the small extra information needed on top of the past fed back precoders, as compared to the new precoder information in the entirety.
-Exploiting frequency correlations permits the use of interpolation algorithms, which reduce the feedback overhead in a single OFDM frame, by feeding back CSI only for certain subcarriers, and interpolating over the others.
+First, the optimum precoders are not actually $2N_TN_R$ dimensional entities, but have an underlying manifold structure that allows to work with lower dimensions, when performing operations over the manifold directly \cite{pitaval2013codebooks}.
+Second, these precoders are correlated in both time and frequency \cite{Gupt1905:Predictive}.
+Utilizing the available correlations permit the use of predictive quantization algorithms, which enable improvement of the quantization error with time.
+This improvement is obtained because of feeding back just the small extra information needed on top of the past fed back precoders, as compared to the new precoder information in the entirety.
+% Exploiting frequency correlations permits the use of interpolation algorithms, which reduce the feedback overhead in a single OFDM frame, by feeding back CSI only for certain subcarriers, and interpolating over the others.
+
 Combining the two inherent properties (viz.
-manifold structure and correlations), requires generalization of various well known linear algorithms for prediction, quantization and interpolation, to the manifold structure.
-This is done by exploiting the underlying non-linear differential geometry of the manifold.
-Relevant past work in this direction has been presented in \cite{Gupt1905:Predictive,6891198,6545375,5671092,Li2016,khaled2005quantized,krishnamachari2013geometry,chang2011adaptive}.
-
-% What is the way ahead
+manifold structure and correlations) to frame manifold based predictive quantization algorithms, require a generalization of various well known linear algorithms for prediction, quantization and interpolation, to the underlying non-linear manifold structure.
+This is typically done by exploiting the differential geometry of the manifold and relevant past work in this direction has been presented in \cite{Gupt1905:Predictive,6891198,6545375,5671092,Li2016,krishnamachari2013geometry,chang2011adaptive}.
 Manifold based approaches for predictive quantization have provided significant performance benefits, given that they work with the effective lower dimensions while framing the manifold operations to predict and quantize.
@@
 In this paper, we aim to capture the above non-linear relations using a reservoir computing based predictive quantizer to exploit the temporal correlations effectively.
-The proposed framework offers a simple solution to the predictive quantization problem, which brings about ease of implementation, along with improved performance, when compared to \cite{6891198}, which proposed a manifold based method of predictive quantization by exploiting temporal correlations as well.
+The proposed framework offers a simple solution to the predictive quantization problem, which brings about ease of implementation, along with improved performance, when compared to \cite{6891198}, which proposed a corresponding manifold based method to the problem considered in this paper.
 
@@
 Reservoir computing (RC) is a computational framework designed for sequential data processing.
-Its design is inspired from several frameworks of Recurrent Neural Networks \cite{jaeger2004harnessing}, including Liquid State Machines \cite{jalalvand2015real} and Echo State Networks \cite{mosleh2017brain,pathak2017using}.
-The RC framework represents the non-linear relationships in the data via the higher dimensional dynamical reservoir state vector, which is transformed (using
-matrices, referred to as `couplers') to the lower dimensional input/output vectors
+% Its design is inspired from several frameworks of Recurrent Neural Networks \cite{jaeger2004harnessing}, including Liquid State Machines \cite{jalalvand2015real} and Echo State Networks \cite{mosleh2017brain,pathak2017using}.
+The RC framework represents the non-linear relationships in the data via the higher dimensional dynamical reservoir state vector, which is transformed (using matrices, referred to as `couplers') to the lower dimensional input/output vectors.
+The couplers are learnt over time to map the transformations from reservoir state to the output, optimally.
 % A reservoir computing system maps the inputs to temporal patterns in a higher dimensional dynamical reservoir state.
@@
 % Key advantages of reservoir computing framework include ease of training in comparison to its counterparts like Deep Neural Networks \cite{mosleh2017brain}.
-RC has been successfully used to solve problems like handwritten digit image recognition \cite{jalalvand2015real}, climate prediction \cite{pathak2017using} and spoken digit recognition \cite{verstraeten2005isolated}.
-}
-% Owing to the versatility of reservoir computing, it can deal with any sequential data in principle and hence further expansion of its application fields is widely expected.
-RC frameworks have also been applied to solve problems in the domain of wireless communications \cite{jaeger2004harnessing,mosleh2017brain,shafin2018realizing}.
+RC has been successfully used to solve problems like handwritten digit image recognition \cite{jalalvand2015real}, climate prediction \cite{pathak2017using}, as well as problems in the domain of wireless communications \cite{jaeger2004harnessing,mosleh2017brain,shafin2018realizing}.
 \cite{jaeger2004harnessing} used RC framework to harness channel non-linearities for improved channel equalization.
 \cite{mosleh2017brain,shafin2018realizing} utilized the framework for OFDM symbol detection while accounting for channel and power amplifier non-linearities.
-In our work, we utilize a RC framework similar to one presented in \cite{pathak2017using} to capture the underlying nonlinear relations between previously obtained quantized precoders, in order to predict the precoder at next time instant.
+In our work, we utilize a RC framework to capture the underlying nonlinear relations between the previously fed back precoders and the precoder at next time instant, for predictive quantization.
 This becomes analogous to time series prediction algorithms, for which the RC framework has been cited to work effectively \cite{mosleh2017brain}.

### 2019-09-08 paper/main.tex
System Model fit to 0.5 page

@@
 \label{section2}
-We consider a point-to-point $N_T\times N_R$ MIMO-OFDM wireless system. 
-In this discussion, we assume that $N_T > N_R$ and $N_s = N_R$.
-The available bandwidth is divided into $N$ subcarriers, so that, individually for each subcarrier, the channel can be assumed to be flat fading.
-Consistent with notation in \cite{6891198,Gupt1905:Predictive}, the data stream received on the $i$-th subcarrier, $t$-th time instant (or the $t$-th OFDM frame) is denoted by:
+We consider a $N_T\times N_R$ MIMO-OFDM wireless system with $N$ subcarriers, and assume $N_T > N_R$ and $N_s = N_R$.
+Consistent with notation in \cite{6891198,Gupt1905:Predictive}, the data stream received on the $i$-th subcarrier, $t$-th time instant (or the $t$-th OFDM frame) is,
+\vspace{-5pt}
 \begin{equation}
@@
 \end{equation}
-Here, $\tilde{\bU}_{i,t} \in \mathbb{C}^{N_T \times N_R}$ is the quantized estimate of precoding matrix, $\by_{i,t} \in \mathbb{C}^{N_R \times 1}$ is the received data stream, $\bx_{i,t} \in \mathbb{C}^{N_T \times 1}$ denotes the transmitted signal, $\bH_{i,t} \in \mathbb{C}^{N_T \times N_R}$ denotes the MIMO channel matrix and $\bw_{i,t}$ denotes the i.i.d.
+Here, $\tilde{\bU}_{i,t} \in \mathbb{C}^{N_T \times N_R}$ is the quantized estimate of precoding matrix, $\by_{i,t} \in \mathbb{C}^{N_R \times 1}$ is the received data stream, $\bx_{i,t} \in \mathbb{C}^{N_T \times 1}$ denotes the transmitted signal, $\bH_{i,t} \in \mathbb{C}^{N_T \times N_R}$ denotes the point-to-point MIMO channel matrix and $\bw_{i,t}$ denotes the i.i.d.
 complex Gaussian noise with $\bw_{i,t} \sim \mathcal{N}_{\mathbb{C}}(0,N_0\bI_{N_R})$, $N_0$ being the noise variance.
@@
 
-If an infinite bit budget is available for precoder quantization, the transmitter can directly use the matrices obtained from SVD of $\bH^{H}_{i,t}$ as the precoder $\tilde{\bU}_{i,t}$. 
+Given infinite bit budget, the transmitter can directly use the matrices obtained from SVD of $\bH^{H}_{i,t}$ as the precoder $\tilde{\bU}_{i,t}$. 
 That is, if $\text{SVD}(\bH_{i,t}) = \bU_{i,t},\Sigma_{i,t}, \bV_{i,t}$, then $\tilde{\bU}_{i,t} = \bU_{i,t}$.
-Notice that matrices $\bU_{i,t}$ reside on the Stiefel manifold $\text{St}(N_T,N_R)$, since the columns of $\bU_{i,t}$ form a set of $N_R$ orthogonal vectors in $N_T$ dimensions \cite{Gupt1905:Predictive,6891198}.
+The matrices $\bU_{i,t}$ reside on the Stiefel manifold $\text{St}(N_T,N_R)$, since the columns of $\bU_{i,t}$ form a set of $N_R$ orthogonal vectors in $N_T$ dimensions \cite{Gupt1905:Predictive,6891198}.
 Given practical limitations, only limited feedback is available from the receiver, and the objective is to estimate $\bU_{i,t}$, via $\tilde{\bU}_{i,t}$, using the available feedback bits.
-Independent quantization algorithms analogous to the Lloyd codebook algorithm have been studied for quantizing $\text{St}(N_T,N_R)$ \cite{6678348}.
-However, this approach treats precoders that are close to each other in time/frequency as independent, since it does not exploit any temporal/spectral correlations for quantization.
+Independent quantization algorithms analogous to the Lloyd codebook algorithm have been studied for quantizing the complete $\text{St}(N_T,N_R)$ \cite{6678348}.
+However, this approach treats precoders close to each other in time/frequency as independent, since it does not exploit any temporal/frequency correlations.
 
-Predictive quantization algorithms \cite{Gupt1905:Predictive,6891198} can be utilized to reduce the quantization error by utilizing the available correlations.
+Predictive quantization algorithms \cite{Gupt1905:Predictive,6891198} can be utilized to reduce the quantization error by utilizing correlations.
 We now discuss the basic mathematical model that is central to predictive quantization algorithms for precoding matrices.
 Suppose that we predict the current precoding matrix based on the past $p$ observed precoding matrices.
-For this, assume that $\tilde{\bU}_{i,t-p},\tilde{\bU}_{i,t-p+1},\ldots,\tilde{\bU}_{i,t-2},\tilde{\bU}_{i,t-1}$ have been fed back and available at the transmitter.
-By using a prediction algorithm and by exploiting time correlations among precoders at time instances $t-p,t-p+1,\ldots,t-2,t-1$, the transmitter can obtain a prediction (viz.
-a coarse estimate) of $\bU_{i,t}$, given by $\bP_{i,t}=f_P(\tilde{\bU}_{i,t-p},\tilde{\bU}_{i,t-p+1},\ldots,\tilde{\bU}_{i,t-2},\tilde{\bU}_{i,t-1})$, where $f_P: \text{St}(N_T,N_R)\times\ldots\{p-\text{times}\}\ldots\times\text{St}(N_T,N_R) \to \text{St}(N_T,N_R)$ is a prediction function.
-Now, since the transmitter already possesses a coarse estimate $\bP_{i,t}$ of $\bU_{i,t}$, the receiver just quantizes the local space of $\text{St}(N_T,N_R)$ nearby $\bP_{i,t}$, instead of the complete $\text{St}(N_T,N_R)$.
-The receiver feeds back this quantized information, enabling a refined estimate of $\bU_{i,t}$, given by $\tilde{\bU}_{i,t}$ at the transmitter.
-That is, the transmitter utilizes a quantization function $q_P:\text{St}(N_T,N_R) \times \mathbb{N} \to \text{St}(N_T,N_R)$, to obtain $\tilde{\bU}_{i,t} \gets q_P(\bP_{i,t},\text{fb}_{i,t})$, where $\text{fb}_{i,t} \in \{1,2\ldots2^{\mathcal{B}}\}$ is the feedback from the receiver for precoder at $i$-th subcarrier and $t$-th time instant, considering bit budget of $\mathcal{B}$ bits.
-In \cite{Gupt1905:Predictive,6891198,6545375}, $\text{fb}_{i,t}$ denotes the codeword index for the codebook obtained for quantizing the local tangent space at $\bP_{i,t}$.
+For this, assume that $\tilde{\bU}_{i,t-p},\ldots,\tilde{\bU}_{i,t-1}$ have been fed back to the transmitter.
+By using a prediction algorithm to exploit the time correlations among precoders at time instances $t-p,\ldots,t-1$, the transmitter can obtain a prediction (viz.
+a coarse estimate) of $\bU_{i,t}$, given by $\bP_{i,t}=f_P(\tilde{\bU}_{i,t-p},\ldots,\tilde{\bU}_{i,t-1})$, where $f_P(\cdot)$ is a prediction function.
+Now, since the transmitter already possesses a coarse estimate $\bP_{i,t}$ of $\bU_{i,t}$, the receiver just quantizes the local space of $\text{St}(N_T,N_R)$ nearby $\bP_{i,t}$.
+The receiver feeds back this quantized information, enabling a refined estimate of $\bU_{i,t}$, given by $\tilde{\bU}_{i,t}$.
+That is, the transmitter utilizes a quantization function $q_P(\cdot)$, to obtain $\tilde{\bU}_{i,t} \gets q_P(\bP_{i,t},\text{fb}_{i,t})$, where $\text{fb}_{i,t} \in \{1,2\ldots2^{\mathcal{B}}\}$ is feedback for the precoder at $i$-th subcarrier, $t$-th time instant, considering bit budget of $\mathcal{B}$ bits.
+In \cite{Gupt1905:Predictive,6891198,6545375}, $\text{fb}_{i,t}$ denotes the codeword index for the codebook obtained by quantizing the local tangent space at $\bP_{i,t}$.
 
@@
 
-In our work, we propose a RC based prediction framework that predicts the new precoders by utilizing temporal correlations that are captured from past observed precoders (via $f_P$).
+In our work, we propose a RC framework which implements the prediction function $f_p(\cdot)$.
 We reuse the $q_P$ algorithm from \cite{Gupt1905:Predictive,6891198}.

### 2019-09-08 paper/main.tex
Playing around with vspace

@@
 
-\title{Predictive Quantization for MIMO-OFDM SVD Precoders using Reservoir Computing Framework}
+\title{Predictive Quantization for MIMO-OFDM SVD Precoders using Reservoir Computing Framework \vspace{-10pt}}
 
@@
  \authorblockA{Department of Electrical Engineering, Indian Institute of Technology Bombay\\
- \{agrim,pranavs,akumar,manojg\}@ee.iitb.ac.in}
+ \{agrim,pranavs,akumar,manojg\}@ee.iitb.ac.in \vspace{-15pt}}
 % \thanks{Parts of this work was supported by the Bharti Centre for Communication in
@@
 
+\vspace{-6pt}
 \section{Introduction}
+\vspace{-6pt}
 \label{intro}
@@
 Consistent with notation in \cite{6891198,Gupt1905:Predictive}, the data stream received on the $i$-th subcarrier, $t$-th time instant (or the $t$-th OFDM frame) is,
-\vspace{-5pt}
 \begin{equation}
@@
 %Explain prediction and quantization steps here itself ! (succintly)
-\section{Reservoir Framework for Predictive Quantization}
+\section{Reservoir Framework for Pred. Qtizn.}
 \label{section3}

### 2019-09-22 paper/main.tex
System model and into on first page

@@
 
-\title{Predictive Quantization for MIMO-OFDM SVD Precoders using Reservoir Computing Framework \vspace{-10pt}}
+\title{\vspace{-10pt}Predictive Quantization for MIMO-OFDM SVD Precoders using Reservoir Computing Framework \vspace{-17pt}}
 
@@
  \authorblockA{Department of Electrical Engineering, Indian Institute of Technology Bombay\\
- \{agrim,pranavs,akumar,manojg\}@ee.iitb.ac.in \vspace{-15pt}}
+ \{agrim,pranavs,akumar,manojg\}@ee.iitb.ac.in \vspace{-18pt}}
 % \thanks{Parts of this work was supported by the Bharti Centre for Communication in
@@
   % approaches.
+
 \begin{abstract}
@@
 
-\vspace{-6pt}
+\vspace{-5pt}
 \section{Introduction}
-\vspace{-6pt}
+\vspace{-5pt}
 \label{intro}
@@
 % Can remove MIMO wireless systems
-In MIMO wireless systems, precoding matrices are used for transformation of an $N_S$-dimensional ($N_S \leq \text{min}(N_T,N_R))$ data stream onto an $N_T$-dimensional transmit vector that corresponds to the signal emanating from the $N_T$ transmit antennas.
+In MIMO wireless systems, precoding matrices are used for transformation of an $N_S$-dimensional ($N_S \leq \text{min}(N_T,N_R))$ data stream onto an $N_T$-dimensional transmit signal.
 The precoding matrix used to maximize the achievable rate using optimal power allocation is obtained via the SVD of the MIMO channel matrix \cite{love2008overview}.
@@
 % Elaborate on each point (what people have done before) lecunnas
-Past work has used two inherent properties of the precoders to enable effective quantization with just a few bits.
-First, the optimum precoders are not actually $2N_TN_R$ dimensional entities, but have an underlying manifold structure that allows to work with lower dimensions, when performing operations over the manifold directly \cite{pitaval2013codebooks}.
+Past work has used two inherent properties of the optimal precoders to enable effective quantization with just a few bits.
+First, the optimum precoders are not actually $2N_TN_R$ dimensional entities, but have an underlying manifold structure that allows to work with effective lower dimensions, when performing operations over the manifold directly \cite{pitaval2013codebooks}.
 Second, these precoders are correlated in both time and frequency \cite{Gupt1905:Predictive}.
@@
 
+\vspace{-3pt}
 \section{System Model}

### 2019-09-22 paper/main.tex
Minimizing the quantization function description

@@
 
-\title{\vspace{-10pt}Predictive Quantization for MIMO-OFDM SVD Precoders using Reservoir Computing Framework \vspace{-17pt}}
+\title{\vspace{-10pt}Predictive Quantization for MIMO-OFDM SVD Precoders using Reservoir Computing Framework \vspace{-10pt}}
 
@@
 
-\vspace{-3pt}
+\vspace{-1pt}
 \section{System Model}
 \label{section2}
+\vspace{-1pt}
 We consider a $N_T\times N_R$ MIMO-OFDM wireless system with $N$ subcarriers, and assume $N_T > N_R$ and $N_s = N_R$.
 Consistent with notation in \cite{6891198,Gupt1905:Predictive}, the data stream received on the $i$-th subcarrier, $t$-th time instant (or the $t$-th OFDM frame) is,
+\vspace{-1pt}
 \begin{equation}
@@
 \end{equation}
+\vspace{-1pt}
 Here, $\tilde{\bU}_{i,t} \in \mathbb{C}^{N_T \times N_R}$ is the quantized estimate of precoding matrix, $\by_{i,t} \in \mathbb{C}^{N_R \times 1}$ is the received data stream, $\bx_{i,t} \in \mathbb{C}^{N_T \times 1}$ denotes the transmitted signal, $\bH_{i,t} \in \mathbb{C}^{N_T \times N_R}$ denotes the point-to-point MIMO channel matrix and $\bw_{i,t}$ denotes the i.i.d.
@@
 \label{section3}
-\subsection{Vectorizing matrices in the Stiefel Manifold}
-\label{vectorize}
+% \subsection{Vectorizing matrices in the Stiefel Manifold}
+% \label{vectorize}
 The RC framework has inputs and outputs as real vectors, and thus, it is necessary to convert the precoding matrices to vectors.
@@
 %The thing to quantize remains on the Stiefel Manifold
-\subsection{Forward Prediction $f_P$}
-\noindent The vector representation of semi-unitary matrices allows to proceed with our discussion on RC framework.
-Consider the RC framework in Fig. \ref{res_overview} %Ref Fig. Reservoir Pic
+% \subsection{Forward Prediction $f_P$}
 
@@
 Typical choices for $\bA_i$ have been Erdos-Renyi graphs with an upper bounded maximum eigenvalue \cite{mosleh2017brain,pathak2017using}.
-The output of the reservoir is $\bp_{i,t}$, a vectorized representation of $\bP_{i,t}$, which denotes the predicted precoder at $i$-th subcarrier, $t$-th time instant.
+The output of the reservoir is $\bp_{i,t}$ (vectorized representation of $\bP_{i,t}$), which denotes the predicted precoder at $i$-th subcarrier, $t$-th time instant.
 Therefore, the output of the reservoir is also a $D_{\text{in}}$ dimensional vector (viz. $D_{\text{out}}=D_{\text{in}}$).
-The output $\bp_{i,t}$ is obtained using a matrix transformation of the reservoir state $\br_{i,t}$ with the $D_{\text{out}}\times D_{\text{resv}}$ output coupler matrix $\bW^{\text{out}}_{i,t-1}$,
+The output $\bp_{i,t}$ is obtained using a matrix transformation of the reservoir state $\br_{i,t}$ with $D_{\text{out}}\times D_{\text{resv}}$ output coupler matrix $\bW^{\text{out}}_{i,t-1}$, which forms the prediction function $f_P(\cdot)$ with $\tilde{\bU}_{i,t-1}$ as its argument, for the RC framework
 \begin{equation}
-\bp_{i,t}=\bW^{\text{out}}_{i,t-1}\br_{i,t}
+\bp_{i,t}=\bW^{\text{out}}_{i,t-1}\br_{i,t}=f_P(\tilde{\bU}_{i,t-1})
 \label{pred_op}
 \end{equation}
+
 \begin{figure*}[ht]
@@
 Then, both the receiver and transmitter execute the backward pass (shaded in blue) to optimize $\mathcal{O}_{i,t}$ \eqref{oit}, to ensure identical evolution of both the reservoirs}
-\caption{Forward Prediction (Green): Both the transmitter and receiver utilize identical reservoirs and quantized precoder estimate at $t-1$ (i.e.
-$\tilde{\bu}_{i,t-1}$, top left of figure) to obtain $\bP_{i,t}$ via \eqref{fwd_pred}.
+\caption{RC Framework Overview: Forward Prediction (Green): Both TX and RX utilize identical RCs and quantized precoder estimate at $t-1$ (i.e.
+$\tilde{\bu}_{i,t-1}$, top left of fig.) to obtain $\bP_{i,t}$ via \eqref{pred_op}.
 The transmitter estimates the quantized precoder at $t$ (i.e.
-$\tilde{\bu}_{i,t}$, top right of figure) using receiver feedback $\text{fb}_{i,t}$ via $q_P$ \eqref{eqn:cn2}.
+$\tilde{\bu}_{i,t}$, top right of fig.) using receiver feedback $\text{fb}_{i,t}$ via $q_P$ \eqref{eqn:cn2}.
 \\Feedback Estimation (Cyan): The Receiver estimates the ideal $\text{fb}_{i,t}$ using the exact precoders $\bU_{i,t}$ via \eqref{eqn:cn1}.
 The transmitter observes only the feedback $\text{fb}_{i,t}$\\ Backward Pass (Blue): $\bW^{\text{out}}_{i,t}$ is updated via \eqref{wout_upd} for optimizing $\mathcal{O}_{i,t}$.
-This is done at both transmitter and receiver to ensure identical evolution of the reservoirs}
+This is done at both TX and RX to ensure identical evolution of the reservoirs}
 \label{res_overview}
@@
 \end{figure*}
-This completes the forward prediction to obtain $\bP_{i,t}$ using only the past observed $\bU_{i,t-1}$ (i.e. $p=1$, Section \ref{section2}). That is,
+% \begin{equation}
+% \bP_{i,t}=f_P(\tilde{\bU}_{i,t-1})=\bW^{\text{out}}_{i,t-1}\text{tanh}(\bA_i\br_{i,t-1}+\bW^{\text{in}}_i\tilde{\bu}_{i,t-1})\footnote{For brevity, $\bp_{i,t}$ and $\bP_{i,t}$ are treated to be one and the same}
+% \label{fwd_pred}
+% \end{equation}
+% However, a complete discussion of the framework involves a backward pass for reservoir training, which estimates optimum $\bW^{\text{out}}_{i,t}$.
+This would follow subsequently after $q_P(\cdot)$ is described.
+
+We now describe the quantization function $q_P(\cdot)$ which is essentially the same as considered in \cite{Gupt1905:Predictive,6891198}, that exploits the fact that tangent spaces local to a point in manifold are vector spaces.
+To do so, the quantization algorithm quantizes the local tangent space at the predicted precoder $\bP_{i,t}$ to get a codebook, $T^\mathcal{C}$ having $2^{\mathcal{B}}$ codeword tangents in the tangent space.
+The quantized precoders are obtained by traversing along the `codeword tangents' from the predicted precoder $\bP_{i,t}$, using a retraction map (denoted by $\text{retract}(\cdot)$).
+The receiver conveys the feedback $\text{fb}_{i,t}$ to the transmitter, which minimizes the chordal distance metric ($d_s(\bX,\bY)$ for $\bX,\bY \in \text{St}(N_T,N_R)$ detailed in \cite{Gupt1905:Predictive,6891198}) between the quantized precoders and the ideal precoder $\bU_{i,t}$ estimated from SVD of $\bH_{i,t}$ \eqref{eqn:cn1}
  \begin{equation}
-\bP_{i,t}=f_P(\tilde{\bU}_{i,t-1})=\bW^{\text{out}}_{i,t-1}\text{tanh}(\bA_i\br_{i,t-1}+\bW^{\text{in}}_i\tilde{\bu}_{i,t-1})\footnote{For brevity, $\bp_{i,t}$ and $\bP_{i,t}$ are treated to be one and the same}
-\label{fwd_pred}
+\label{eqn:cn1}
+\text{fb}_{i,t} \gets \text{argmin}_{i \in \{1,2,\ldots,2^{\mathcal{B}}\}}\left (d_s\left (\bU_{i,t},\text{retract}(\bP_{i,t},T^\mathcal{C}[i])\right ) \right)
 \end{equation}
-However, a complete discussion of the framework involves a backward pass for reservoir training, which estimates optimum $\bW^{\text{out}}_{i,t}$.
-This would follow subsequently after $q_P(\cdot)$ is described.
-\subsection{Quantization function $q_P$}
-\label{qp}
-We now describe the quantization function $q_P(\bP_{i,t},\text{fb}_{i,t})$, which is similar to the schemes used in \cite{6891198,Gupt1905:Predictive,6545375}.
-Central to the quantization algorithm is the fact that tangent spaces local to a point in manifold are vector spaces.
+The transmitter utilizes the above quantization function $q_P$ to obtain $\tilde{\bU}_{i,t}=q_P(\bp_{i,t},\text{fb}_{i,t})$ from $\bp_{i,t},\text{fb}_{i,t}$.
+\begin{equation}
+\tilde{\bU}_{i,t}=q_P(\bP_{i,t},\text{fb}_{i,t})=\text{retract}(\bP_{i,t},T^\mathcal{C}[\text{fb}_{i,t}])
+\label{eqn:cn2}
+\end{equation}
 % Given two points $\bX$ and $\bY$ in $\text{St}(N_T,N_R)$, a lifting operation $\bT^Y_X=\texttt{lift}(\bX,\bY)$, $\texttt{lift}:\text{St}(N_T,N_R)\times \text{St}(N_T,N_R) \to \mathcal{T}_X \text{St}(N_T,N_R)$ yields a tangent from $X$ to $Y$, denoted as $\bT^Y_X \in \mathcal{T}_X \text{St}(N_T,N_R)$, where $\mathcal{T}_X \text{St}(N_T,N_R)$ is the local tangent space at $\bX$.
@@
 
-The quantization algorithm exploits the vector space property of the tangent space and quantizes the local tangent space at the predicted precoder $\bP_{i,t}$, viz $\mathcal{T}_{\bP_{i,t}} \text{St}(N_T,N_R)$.
 % The codebook for $\mathcal{T}_{\bP_{i,t}} \text{St}(N_T,N_R)$ corresponds to a collection of $\mathcal{B}-1$ codewords that represent the different directions (tangents) in $\mathcal{T}_{\bP_{i,t}} \text{St}(N_T,N_R)$.
 % This codebook is subsequently referred to as the base codebook ($\text{base}^{\mathcal{C}}$) for the quantization function.
-The feedback from the receiver indicates the codeword corresponding to the optimum tangent in $\mathcal{T}_{\bP_{i,t}} \text{St}(N_T,N_R)$, which the transmitter can choose to get closest (in terms of chordal distance metric, $d_s(\bX,\bY)$ for $\bX,\bY \in \text{St}(N_T,N_R)$ detailed in \cite{Gupt1905:Predictive,6891198}) to the actual value $\bU_{i,t}$.
-With the optimum direction chosen, the next step is to determine how much to move in that particular chosen direction, viz.
+% The feedback from the receiver indicates the codeword corresponding to the optimum tangent in $\mathcal{T}_{\bP_{i,t}} \text{St}(N_T,N_R)$, which the transmitter can choose to get closest (in terms of chordal distance metric, $d_s(\bX,\bY)$ for $\bX,\bY \in \text{St}(N_T,N_R)$ detailed in \cite{Gupt1905:Predictive,6891198}) to the actual value $\bU_{i,t}$.
+% With the optimum direction chosen, the next step is to determine how much to move in that particular chosen direction, viz.
 the length of the chosen tangent direction.
-For this, we adopt the strategy in \cite{6891198}, which controls the magnitude of tangent steps, by having two codebooks of different spreads, but the same $2^{\mathcal{B}-1}$ base vectors.
+For this, we adopt the same strategy in \cite{,Gupt1905:Predictive,6891198}, which controls the magnitude of tangent steps, by having two codebooks of different spreads, but the same $2^{\mathcal{B}-1}$ base vectors.
 % The two codebooks are concatenated to form a $2^\mathcal{B}$ length codebook, $T^\mathcal{C}$.
@@
 The transmitter uses the fed back $\text{fb}_{i,t}$ and \eqref{eqn:cn2} to calculate $\tilde{\bU}_{i,t}$,
-% \begin{equation}
-% \label{eqn:cn1}
-% \text{fb}_{i,t} \gets \text{argmin}_{i \in \{1,2,\ldots,2^{\mathcal{B}}\}}\left (d_s\left (\bU_{i,t},\text{retract}(\bP_{i,t},T^\mathcal{C}[i])\right ) \right)
-% \end{equation}
-% \begin{equation}
-% \tilde{\bU}_{i,t}=q_P(\bP_{i,t},\text{fb}_{i,t})=\text{retract}(\bP_{i,t},T^\mathcal{C}[\text{fb}_{i,t}])
-% \label{eqn:cn2}
-% \end{equation}
+
 % $\text{fb}_{i,t}$ is also used to update the spread of the codebooks $T^{\mathcal{C}}_p,T^{\mathcal{C}}_m$.
@@
 % The scheme used to obtain $\text{base}^{\mathcal{C}}$ is similar to the one presented in \cite{Gupt1905:Predictive}, which performs a $k$-means ($k=2^{\mathcal{B}-1}$) clustering on a collection of tangents to obtain an isotropic collection of $2^{\mathcal{B}-1}$ tangent codewords.
-This completes the discussion on the quantization function $q_P$ to obtain $\tilde{\bU}_{i,t}=q_P(\bP_{i,t},\text{fb}_{i,t})$ from $\bP_{i,t},\text{fb}_{i,t}$.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Reservoir Training Procedure, the backward pass}
-\label{train}
+% \subsection{Reservoir Training Procedure, the backward pass}
+% \label{train}
 \noindent Having described the technicalities of $f_P,q_P$, we now describe the training process for the reservoir, which couples $f_P$ with $q_P$.

### 2019-09-22 paper/main.tex
Shortening Section 3

@@
 \noindent Having described the technicalities of $f_P,q_P$, we now describe the training process for the reservoir, which couples $f_P$ with $q_P$.
-Recall that, to obtain $\tilde{\bU}_{i,t}$ from  $\tilde{\bU}_{i,t-1}$, we have
-\begin{equation}
-\tilde{\bU}_{i,t}=q_P(\bP_{i,t},\text{fb}_{i,t})=q_P(f_P(\tilde{\bU}_{i,t-1}),\text{fb}_{i,t})
-\label{fpqp}
-\end{equation}
 The key idea for reservoir training is that, as the predicted matrix $\bP_{i,t}$ (the coarse estimate) gets closer to $\tilde{\bU}_{i,t}$ (the refined estimate), the receiver has to quantize even smaller subspaces, and can thus provide a more refined estimate from the feedback $\text{fb}_{i,t}$.
@@
 \eqref{wout_upd} makes training of the reservoir easy to implement with low complexity.
-We only need to store a matrix $\text{\textbf{num}}_{i,t-1}$, and a number $\text{den}_{i,t-1}$.
-Then, using the current reservoir state $\br_{i,t}$ and $\tilde{\bu}_{i,t}$ obtained from \eqref{res_upd}, \eqref{fpqp} respectively, optimum $\bW_{i,t}^{\text{out}}$ can be estimated.
-The optimum $\bW_{i,t}^{\text{out}}$ can then be used to obtain $\tilde{\bP}_{i,t+1}$, and so on.
-This completes the discussion of the proposed RC framework illustrated in Fig. \ref{res_overview}.
+We only need to store a matrix $\text{\textbf{num}}_{i,t-1}$, and a number $\text{den}_{i,t-1}$ from $t-1$ time instant to calculate optimum output coupler for $t$-th time instant.
+This completes the discussion of the proposed RC framework (Fig.
+\ref{res_overview}).
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 In this paper, we have presented a reservoir computing framework for predictive quantization of SVD precoders by exploiting temporal correlations.
-The simulations reveal significant improvement in quantization error, BER, and achievable rate for IEEE Pedestrian-A channel model with normalized Doppler $10^{-4}$. 
+The simulations reveal significant improvement in quantization error, BER, and achievable rate.
 The novelty that enables these improvements lies in the training method for the reservoir framework, which refines the predicted coarse estimates as the reservoir evolves.
-The simulation results indicate that the proposed framework would be able to communicate at significantly lower power levels for the same BER, as illustrated in Fig. \ref{BER}.
 Note that these results have been obtained by exploiting just the temporal correlations for predictive quantization, and can potentially improve if temporal-frequency correlations are exploited jointly.

### 2019-09-23 paper/main.tex
Add new abstract

@@
 
-SVD based precoding matrices have been theoretically proven to perform optimum power allocation and lower BER transmissions in MIMO wireless systems. 
-% A key step enabling this improved performance is the feedback of these precoders to the transmitter from the receiver.
-% Gievn the limited bit budget for such Channel State Information (CSI) feedback, these precoders need to be quantized effectively using just a few bits.
-However, in a practical setting, for a $N_T \times N_R$ MIMO system ($N_{\{T/R\}}$: Number of Transmit/Receive Antennas), the receiver needs to quantize and feedback the $N_T \times N_R$ precoding matrix obtained from SVD of the channel matrix, with just a few bits to respect the limited bit budget constraint.
-This task is aided by the presence of an underlying manifold structure and temporal/frequency correlations in the precoders. 
-Predictive quantization methods exploit the correlations in the previously fed back precoders for prediction, followed by quantization of the incremental information required to obtain the actual precoder from the predicted value.
-In this work, we introduce a reservoir computing framework for predictive quantization by exploiting temporal correlations. 
-Past methods have primarily exploited the nonlinear geometry of the underlying manifold structure for precoder prediction.
-Here, this non-linear relationship is captured using the dynamical reservoir state as part of the online training process of the reservoir.
-Simulations reveal that this approach produces reduced quantization error, which results in lower BER as well as improved achievable rates when compared to earlier work.
+  Precoding in MIMO wireless systems is essential for achieving
+  channel capacity. However, the receiver should quantize and feed
+  back the precoder using very few bits of overhead. The precoder's
+  underlying manifold structure aids this feedback and allows the use
+  of channel temporal/frequency correlation for predictive
+  quantization. We introduce a reservoir computing framework for
+  predictive quantization by exploiting temporal correlations. Past
+  methods primarily use the geometry of the underlying manifold for
+  precoder prediction.  We, instead, use a dynamical reservoir state
+  as part of the online training process of the reservoir.
+  Simulations reveal reduces quantization error, lower BER and
+  improved achievable rates.
 \end{abstract}
@@
 
-\begin{figure*}[ht]
+\begin{figure}[ht]
 \centering
-\includegraphics[width=0.8\textwidth]{images/system2.pdf}
+\includegraphics[width=0.5\textwidth]{images/system2.pdf}
 % \caption{System Overview: The RC framework takes the precoder estimate at $t-1$ (viz.
@@
 $\tilde{\bu}_{i,t}$, top right of fig.) using receiver feedback $\text{fb}_{i,t}$ via $q_P$ \eqref{eqn:cn2}.
-\\Feedback Estimation (Cyan): The Receiver estimates the ideal $\text{fb}_{i,t}$ using the exact precoders $\bU_{i,t}$ via \eqref{eqn:cn1}.
+Feedback Estimation (Cyan): The Receiver estimates the ideal $\text{fb}_{i,t}$ using the exact precoders $\bU_{i,t}$ via \eqref{eqn:cn1}.
 The transmitter observes only the feedback $\text{fb}_{i,t}$\\ Backward Pass (Blue): $\bW^{\text{out}}_{i,t}$ is updated via \eqref{wout_upd} for optimizing $\mathcal{O}_{i,t}$.
@@
 \label{res_overview}
-\vspace{-5pt}
-\end{figure*}
+\end{figure}
 % \begin{equation}
@@
 \centering
-\includegraphics[width=0.4\textwidth]{images/qtizErr.pdf}
+\includegraphics[width=0.37\textwidth]{images/qtizErr.pdf}
 \caption{Quantization error in terms of chordal distance to the actual precoder $\bU_{\{9k\},t}$ observed at the receiver, from the quantized estimate $\tilde{\bU}_{\{9k\},t}$ averaged over $\{9k\}$ fed back subcarriers $\Big($ viz.
@@
 \label{qtiz_err}
-\vspace{-10pt}
 \end{figure}
@@
 \centering
-\includegraphics[width=0.43\textwidth]{images/BER_res.pdf}
+\includegraphics[width=0.37\textwidth]{images/BER_res.pdf}
 \vspace{-5pt}
@@
 \centering
-\includegraphics[width=0.43\textwidth]{images/hopRate2.pdf}
+\includegraphics[width=0.37\textwidth]{images/hopRate2.pdf}
 \vspace{-5pt}

### 2019-09-23 paper/main.tex
Minor optimizations

@@
 % Can remove MIMO wireless systems
-In MIMO wireless systems, precoding matrices are used for transformation of an $N_S$-dimensional ($N_S \leq \text{min}(N_T,N_R))$ data stream onto an $N_T$-dimensional transmit signal.
+In MIMO wireless systems, precoding matrices are used to transform of an $N_S$-dimensional ($N_S \leq \text{min}(N_T,N_R))$ data stream onto an $N_T$-dimensional transmit signal.
 The precoding matrix used to maximize the achievable rate using optimal power allocation is obtained via the SVD of the MIMO channel matrix \cite{love2008overview}.
@@
 % Analogous to this, for $\text{St}(N_T,N_R)$, quantization error is reduced by quantizing a subspace around the predicted value that is much smaller than the entire manifold.
-
 In our work, we propose a RC framework which implements the prediction function $f_p(\cdot)$.
@@
 \centering
-\includegraphics[width=0.37\textwidth]{images/qtizErr.pdf}
+\includegraphics[width=0.35\textwidth]{images/qtizErr.pdf}
 \caption{Quantization error in terms of chordal distance to the actual precoder $\bU_{\{9k\},t}$ observed at the receiver, from the quantized estimate $\tilde{\bU}_{\{9k\},t}$ averaged over $\{9k\}$ fed back subcarriers $\Big($ viz.
@@
 \centering
-\includegraphics[width=0.37\textwidth]{images/BER_res.pdf}
+\includegraphics[width=0.35\textwidth]{images/BER_res.pdf}
 \vspace{-5pt}
@@
 \centering
-\includegraphics[width=0.37\textwidth]{images/hopRate2.pdf}
+\includegraphics[width=0.35\textwidth]{images/hopRate2.pdf}
 \vspace{-5pt}
@@
 
-In this paper, we have presented a reservoir computing framework for predictive quantization of SVD precoders by exploiting temporal correlations.
-The simulations reveal significant improvement in quantization error, BER, and achievable rate.
-The novelty that enables these improvements lies in the training method for the reservoir framework, which refines the predicted coarse estimates as the reservoir evolves.
-Note that these results have been obtained by exploiting just the temporal correlations for predictive quantization, and can potentially improve if temporal-frequency correlations are exploited jointly.
-This motivates further study into the reservoir framework, and a detailed analysis of impact on performance caused by choice of different reservoir parameters like $\bA,\text{tanh}(\cdot),$ and $D_{\text{resv}}$.
+We have presented a reservoir computing framework for predictive quantization of MIMO precoders by exploiting temporal correlations.
+Simulations reveal significant improvement in quantization error, BER, and achievable rate.
+The novelty that enables these improvements is the training method for the reservoir framework, which refines the predicted coarse estimates as the reservoir evolves.
+Our results have been obtained by exploiting only temporal correlations for predictive quantization, and can potentially improve if frequency correlations are also exploited simultaneously..
+Future work would focus on better reservoir frameworks, and a detailed analysis of impact on performance caused by choice of different reservoir parameters like $\bA,\text{tanh}(\cdot),$ and $D_{\text{resv}}$.
 \vspace{-4pt}

### 2019-09-30 paper/main.tex
Further minor optimizations

@@
 % Elaborate on each point (what people have done before) lecunnas
-Past work has used two inherent properties of the optimal precoders to enable effective quantization with just a few bits.
-First, the optimum precoders are not actually $2N_TN_R$ dimensional entities, but have an underlying manifold structure that allows to work with effective lower dimensions, when performing operations over the manifold directly \cite{pitaval2013codebooks}.
+Past approaches have generally utilized the fact that the optimum precoders are not actually $2N_TN_R$ dimensional entities, but have an underlying manifold structure that allows to work with effective lower dimensions for transformations \cite{pitaval2013codebooks}.
 Second, these precoders are correlated in both time and frequency \cite{Gupt1905:Predictive}.
-Utilizing the available correlations permit the use of predictive quantization algorithms, which enable improvement of the quantization error with time.
-This improvement is obtained because of feeding back just the small extra information needed on top of the past fed back precoders, as compared to the new precoder information in the entirety.
-% Exploiting frequency correlations permits the use of interpolation algorithms, which reduce the feedback overhead in a single OFDM frame, by feeding back CSI only for certain subcarriers, and interpolating over the others.
-
-Combining the two inherent properties (viz.
-manifold structure and correlations) to frame manifold based predictive quantization algorithms, require a generalization of various well known linear algorithms for prediction, quantization and interpolation, to the underlying non-linear manifold structure.
+Utilizing the available correlations permit the use of predictive quantization algorithms, which improve the quantization error with time.
+This improvement is obtained because of feeding back only incremental information needed over the past fed back precoders, as compared to the new precoder in its entirety.
+Combining these two inherent properties (viz.
+manifold structure and correlations) to perform manifold based predictive quantization requires a generalization of various linear algorithms for prediction, quantization and interpolation to the non-linear manifold structure.
 This is typically done by exploiting the differential geometry of the manifold and relevant past work in this direction has been presented in \cite{Gupt1905:Predictive,6891198,6545375,5671092,Li2016,krishnamachari2013geometry,chang2011adaptive}.
-Manifold based approaches for predictive quantization have provided significant performance benefits, given that they work with the effective lower dimensions while framing the manifold operations to predict and quantize.
-However, these approaches are non-trivial, since they require specific operations over the non-linear manifold differential geometry.
-In this paper, we aim to capture the above non-linear relations using a reservoir computing based predictive quantizer to exploit the temporal correlations effectively.
-The proposed framework offers a simple solution to the predictive quantization problem, which brings about ease of implementation, along with improved performance, when compared to \cite{6891198}, which proposed a corresponding manifold based method to the problem considered in this paper.
+Such approaches for predictive quantization have provided significant performance benefits, since they operate using lower effective dimensions for prediction and quantization.
+However, these approaches require specific complicated operations over the non-linear manifold differential geometry.
+In this paper, we aim to capture the above non-linear relations using a reservoir computing based predictive quantizer to exploit channel temporal correlations.
+This framework offers a simple solution to the predictive quantization problem that is easy to implement while also improving performance, when compared to corresponding manifold based approach.
 

### 2019-09-30 paper/main.tex
Add changes

@@
 % Its design is inspired from several frameworks of Recurrent Neural Networks \cite{jaeger2004harnessing}, including Liquid State Machines \cite{jalalvand2015real} and Echo State Networks \cite{mosleh2017brain,pathak2017using}.
-The RC framework represents the non-linear relationships in the data via the higher dimensional dynamical reservoir state vector, which is transformed (using matrices, referred to as `couplers') to the lower dimensional input/output vectors.
-The couplers are learnt over time to map the transformations from reservoir state to the output, optimally.
+The RC framework represents the non-linear relationships in data using the higher dimensional dynamical reservoir state vector, which is transformed (using matrices, referred to as `couplers') to the lower dimensional input/output vectors.
+The couplers are learnt over time to optimally map the transformations from the reservoir state to the output.
 % A reservoir computing system maps the inputs to temporal patterns in a higher dimensional dynamical reservoir state.
@@
 % Key advantages of reservoir computing framework include ease of training in comparison to its counterparts like Deep Neural Networks \cite{mosleh2017brain}.
-RC has been successfully used to solve problems like handwritten digit image recognition \cite{jalalvand2015real}, climate prediction \cite{pathak2017using}, as well as problems in the domain of wireless communications \cite{jaeger2004harnessing,mosleh2017brain,shafin2018realizing}.
-\cite{jaeger2004harnessing} used RC framework to harness channel non-linearities for improved channel equalization.
-\cite{mosleh2017brain,shafin2018realizing} utilized the framework for OFDM symbol detection while accounting for channel and power amplifier non-linearities.
-In our work, we utilize a RC framework to capture the underlying nonlinear relations between the previously fed back precoders and the precoder at next time instant, for predictive quantization.
-This becomes analogous to time series prediction algorithms, for which the RC framework has been cited to work effectively \cite{mosleh2017brain}.
+RC has been successfully used to solve problems like handwritten digit image recognition \cite{jalalvand2015real}, climate prediction \cite{pathak2017using}, and problems in the domain of wireless communications \cite{jaeger2004harnessing,mosleh2017brain,shafin2018realizing}.
+\cite{jaeger2004harnessing} used the RC framework to harness channel non-linearities for improved channel equalization.
+\cite{mosleh2017brain,shafin2018realizing} demonstrates a framework for OFDM symbol detection that accounts for channel and power amplifier non-linearities.
+In our work, we utilize a RC framework to capture the underlying nonlinear relations between the previously fed back precoders and the precoder at next time instant for predictive quantization.
+This is analogous to time series prediction algorithms, for which the RC framework has been shown to work effectively \cite{mosleh2017brain}.
 
@@
 The matrices $\bU_{i,t}$ reside on the Stiefel manifold $\text{St}(N_T,N_R)$, since the columns of $\bU_{i,t}$ form a set of $N_R$ orthogonal vectors in $N_T$ dimensions \cite{Gupt1905:Predictive,6891198}.
-Given practical limitations, only limited feedback is available from the receiver, and the objective is to estimate $\bU_{i,t}$, via $\tilde{\bU}_{i,t}$, using the available feedback bits.
+Practically, only limited feedback is available from the receiver, and the objective is to estimate $\bU_{i,t}$, via $\tilde{\bU}_{i,t}$, using the available feedback bits.
 Independent quantization algorithms analogous to the Lloyd codebook algorithm have been studied for quantizing the complete $\text{St}(N_T,N_R)$ \cite{6678348}.
-However, this approach treats precoders close to each other in time/frequency as independent, since it does not exploit any temporal/frequency correlations.
+However, this treats precoders close to each other in time/frequency as independent, and does not exploit any temporal/frequency correlations.
 
@@
 %Explain prediction and quantization steps here itself ! (succintly)
-\section{Reservoir Framework for Pred. Qtizn.}
+\section{RC for Predictive Quantization}
 \label{section3}
@@
 
-\subsection{Simulation setting considered}
-\label{setting}
-
-\noindent The simulations have been performed for the IEEE Pedestrian-A channel, with $N_T=4$, $N_R=2$.
-The channel matrices $\bH_{i,t}$ are generated using Jake's model via IT++ library through the python wrapper py-itpp \cite{ViditPy}.
+\noindent The simulations have been performed for the IEEE Pedestrian-A channel, with $N_T=4$, $N_R=2$.  The channel matrices $\bH_{i,t}$ are generated using Jake's model.
 We compare the results obtained by our framework with \cite{6891198}, which presented a manifold geometry method to exploit temporal correlations for predictive quantization.
@@
 \centering
-\includegraphics[width=0.5\textwidth]{images/table.pdf}
+\includegraphics[width=0.4\textwidth]{images/table.pdf}
 \caption{The transmitter obtains feedback for $\{9k, k \in \{0,1,\ldots,7\}$ subcarriers, and uses $\tilde{\bU}_{i,t-1}$, along with $f_P,q_P$ \eqref{fpqp} to obtain $\tilde{\bU}_{i,t}$, illustrated in the figure via cyan arrows.
@@
 
-\subsection{Quantization error, BER and Achievable Rate Results}
-\label{res}{}
 % To mitigate errors in prediction upon the presence of randomly appearing drastic events in wireless channels, such as sudden interferences and dynamic environments, only 100 channel evolutions are considered for the simulations, and the algorithm is re-starte.
@@
 \centering
-\includegraphics[width=0.35\textwidth]{images/qtizErr.pdf}
-\caption{Quantization error in terms of chordal distance to the actual precoder $\bU_{\{9k\},t}$ observed at the receiver, from the quantized estimate $\tilde{\bU}_{\{9k\},t}$ averaged over $\{9k\}$ fed back subcarriers $\Big($ viz.
-$\frac{\Sigma_{i \in 9k}d_S(\tilde{\bU}_{i,t}, \bU_{i,t})}{8}$ $\Big)$ and 10 independent channel realizations (normalized Doppler $f_DT_s=10^{-4}$).}
+\includegraphics[width=0.3\textwidth]{images/qtizErr.pdf}
+\caption{Quantization error in terms of chordal distance to the actual precoder $\bU_{\{9k\},t}$ observed at the receiver, from the quantized estimate $\tilde{\bU}_{\{9k\},t}$ averaged over $\{9k\}$ fed back subcarriers, viz.
+$\frac{1}{8}\Sigma_{i \in 9k}d_S(\tilde{\bU}_{i,t}, \bU_{i,t})$ and 10 independent channel realizations (normalized Doppler $f_DT_s=10^{-4}$).}
 \label{qtiz_err}
@@
 
-We hypothesize that the key reason for the improved performance for both quantization error and BER in the RC approach, is the fact that $f_P,q_P$ are coupled via the backward pass framework (explained towards the end of Section \ref{train}).
-Also, observe from Fig.
-\ref{BER} that the proposed framework BER curve (yellow) comes very close to the ideal $8$ feedback curve (green).
-This can be explained due to the fact that the semi-unitary precoder basically rotates the data vector via its matrix transformation.
-For QPSK, we get some reasonable error margin for this rotation, which becomes more stringent as the simulated BER is reduced.
-Hence, we match the ideal curve for high BER region, and for low BER region, as the margin of error reduces, the curves diverge.
+The improved performance for both quantization error and BER in the RC approach could be due to the fact that $f_P,q_P$ are coupled via the backward pass framework (see Section \ref{train}).
+Also, from from Fig.
+\ref{BER}, the proposed framework BER curve (yellow) performs close to the ideal $8$ feedback curve (green), since the semi-unitary precoder rotates the data vector using its matrix transformation.
+For QPSK, we observe a reasonable error margin for this rotation, which becomes more stringent as the simulated BER is reduced.
+Thus, we match the ideal curve for high BER region, and for the low BER region, as the margin of error reduces, the curves diverge.
 
-\noindent For simulating the achievable rate, we quantize the sigma values ($\Sigma_{i,t}$ from SVD of $\bH_{i,t}$) using a 2 bit vector quantizer ($k$-means), and feed them back to the transmitter for fed back subcarriers ($\{9k, k \in \{0,1,\ldots,7\}\}$).
-For the non-fed back subcarriers, they are interpolated via a simple convex combination interpolation method as in \cite{Gupt1905:Predictive}.
+\noindent For simulating the achievable rate, we quantize the sigma values ($\Sigma_{i,t}$ from SVD of $\bH_{i,t}$) using a 2 bit vector quantizer ($k$-means), and feed them back to the transmitter for subcarriers ($\{9k, k \in \{0,1,\ldots,7\}\}$).
+For the non-fed back subcarriers, they are interpolated using a convex combination interpolation as in \cite{Gupt1905:Predictive}.
 Observe from Fig.
 \ref{achievrate} that the RC framework offers improvement in achievable rate for $f_DT_s=10^{-4}$.
-Since the temporal variations for $f_DT_s=10^{-2}, 10^{-1}$ are higher, the RC framework has to learn a faster-varying function, and hence the degradation in performance.
-However, it still matches the performance of the predictive quantizer in \cite{6891198} for $f_DT_s=10^{-2}$ and performs slightly better for $f_DT_s=10^{-1}$.
+Since the temporal variations for $f_DT_s=10^{-2}, 10^{-1}$ are higher, the RC framework has to learn faster varying functions thus degrading performance.
+However, it still matches the performance of the predictive quantizer in \cite{6891198} for $f_DT_s=10^{-2}$ and slightly outperforms it for $f_DT_s=10^{-1}$.
 \vspace{-3pt}
@@
 \centering
-\includegraphics[width=0.35\textwidth]{images/BER_res.pdf}
+\includegraphics[width=0.3\textwidth]{images/BER_res.pdf}
 \vspace{-5pt}
-\caption{BER results: Here, red curve is the most ideal case considering exact $\bU_{i,t}$ for all 64 subcarriers, at each time instant are available at the transmitter.
-The \{green/yellow/blue\} curves corresponds to the case in which \{$\bU_{9k,t}$/$\tilde{\bU}_{9k,t}$ from reservoir method/$\tilde{\bU}_{9k,t}$ from \cite{6891198}\} is available for each time instant, and non fed back precoders are interpolated via Cayley method.
-Observe that the proposed framework BER curve provides significant improvement in $\text{E}_\text{b}\text{N}_0$ levels over \cite{6891198} (normalized Doppler $f_DT_s=10^{-4}$).}
+\caption{The red curve is the ideal case, with exact $\bU_{i,t}$ for all 64 subcarriers available at each time instant at the transmitter.
+The \{green/yellow/blue\} curves corresponds to the case in which \{$\bU_{9k,t}$/$\tilde{\bU}_{9k,t}$ from reservoir method/$\tilde{\bU}_{9k,t}$ from \cite{6891198}\} is available at each time instant, and non fed back precoders are interpolated via the Cayley method.
+The BER for the proposed framework BER provides significant improvement in $E_b/N_0$ levels over \cite{6891198} (normalized Doppler $f_DT_s=10^{-4}$).}
 \vspace{5pt}
@@
 \centering
-\includegraphics[width=0.35\textwidth]{images/hopRate2.pdf}
+\includegraphics[width=0.32\textwidth]{images/hopRate2.pdf}
 \vspace{-5pt}
-\caption{The results are presented as a percentage of the ideal achievable rate obtained when the transmitter has the accurate (unquantized) and non-interpolated estimates of $\bU_{i,t}$ for each subcarrier and each time instant.}
+\caption{The percentage of the ideal achievable rate obtained when the transmitter has the accurate (unquantized) and non-interpolated estimates of $\bU_{i,t}$ for each subcarrier and each time instant.}
 \label{achievrate}
@@
 
-We have presented a reservoir computing framework for predictive quantization of MIMO precoders by exploiting temporal correlations.
+We have presented a reservoir computing framework for predictive quantization of MIMO precoders that exploits temporal correlations.
 Simulations reveal significant improvement in quantization error, BER, and achievable rate.
-The novelty that enables these improvements is the training method for the reservoir framework, which refines the predicted coarse estimates as the reservoir evolves.
-Our results have been obtained by exploiting only temporal correlations for predictive quantization, and can potentially improve if frequency correlations are also exploited simultaneously..
+These improvements are due to the training method for the reservoir framework, which refines the predicted coarse estimates as the reservoir evolves.
+Our results use only temporal correlations for predictive quantization, and could improve if frequency correlations are also xexploited simultaneously..
 Future work would focus on better reservoir frameworks, and a detailed analysis of impact on performance caused by choice of different reservoir parameters like $\bA,\text{tanh}(\cdot),$ and $D_{\text{resv}}$.

### 2019-10-05 paper/main.tex
Add changes

@@
 Then, both the receiver and transmitter execute the backward pass (shaded in blue) to optimize $\mathcal{O}_{i,t}$ \eqref{oit}, to ensure identical evolution of both the reservoirs}
-\caption{RC Framework Overview: Forward Prediction (Green): Both TX and RX utilize identical RCs and quantized precoder estimate at $t-1$ (i.e.
-$\tilde{\bu}_{i,t-1}$, top left of fig.) to obtain $\bP_{i,t}$ via \eqref{pred_op}.
-The transmitter estimates the quantized precoder at $t$ (i.e.
-$\tilde{\bu}_{i,t}$, top right of fig.) using receiver feedback $\text{fb}_{i,t}$ via $q_P$ \eqref{eqn:cn2}.
-Feedback Estimation (Cyan): The Receiver estimates the ideal $\text{fb}_{i,t}$ using the exact precoders $\bU_{i,t}$ via \eqref{eqn:cn1}.
-The transmitter observes only the feedback $\text{fb}_{i,t}$\\ Backward Pass (Blue): $\bW^{\text{out}}_{i,t}$ is updated via \eqref{wout_upd} for optimizing $\mathcal{O}_{i,t}$.
-This is done at both TX and RX to ensure identical evolution of the reservoirs}
+\caption{RC Framework Overview: Forward Prediction (Green):
+  Transmitter and receiver utilize identical RCs and quantized
+  precoder estimate at $t-1$ (i.e. $\tilde{\bu}_{i,t-1}$, top left) to
+  obtain $\bP_{i,t}$ using Equation \eqref{pred_op}. The transmitter
+  estimates the quantized precoder at $t$ (i.e. $\tilde{\bu}_{i,t}$,
+  top right) using feedback $\text{fb}_{i,t}$ via $q_P$
+  \eqref{eqn:cn2}. Feedback Estimation (Cyan): Receiver estimates
+  the ideal $\text{fb}_{i,t}$ using exact precoders $\bU_{i,t}$ using
+  Equation \eqref{eqn:cn1}. The transmitter observes only feedback
+  $\text{fb}_{i,t}$.
+Backward Pass (Blue): $\bW^{\text{out}}_{i,t}$ is updated using Equation~\eqref{wout_upd} for optimizing $\mathcal{O}_{i,t}$.
+This is done at both TX and RX to ensure identical evolution of the reservoirs.}
 \label{res_overview}
@@
 Unlike \cite{Gupt1905:Predictive}, we do not exploit frequency correlations for predictive quantization, and the $8$ reservoirs for prediction of $8$ fed-back subcarriers are kept independent of each other.
-All these 8 reservoirs are initialized with $\bA_{i\in\{9k\}}$ being an Erdos-Reny\"i graph, with probability of edge connections being $0.2$, $\lambda=2$, $\bW^{\text{out/in}}_{i\in\{9k\},0}$ initialized randomly, $D_{\text{in}}=D_{\text{out}}=14$ (vectorized representation of $4\times2$ semi-unitary matrix, Section \ref{vectorize}) and $D_{\text{resv}}=60$.
+All these 8 reservoirs are initialized with $\bA_{i\in\{9k\}}$ being an Erdos-Reny\"i graph, with probability of edge connections being $0.2$, $\lambda=2$, $\bW^{\text{out/in}}_{i\in\{9k\},0}$ initialized randomly, $D_{\text{in}}=D_{\text{out}}=14$ (vectorized representation of $4\times2$ semi-unitary matrix, Section \ref{section3}) and $D_{\text{resv}}=60$.
 % All these 8 reservoirs are initialized with $\bA_{i\in\{9k\}}$ being an Erdos-Reny\"i graph, with
@@
 \includegraphics[width=0.4\textwidth]{images/table.pdf}
-\caption{The transmitter obtains feedback for $\{9k, k \in \{0,1,\ldots,7\}$ subcarriers, and uses $\tilde{\bU}_{i,t-1}$, along with $f_P,q_P$ \eqref{fpqp} to obtain $\tilde{\bU}_{i,t}$, illustrated in the figure via cyan arrows.
-For each time instant, the transmitter uses the Cayley method  \eqref{eqn:cayley_i1_i2} to interpolate $\tilde{\bU}_{i,t}$ at $i\neq\{9k\}$ non fed back subcarriers (green arrows}
+\caption{The transmitter obtains feedback for $\{9k, k \in \{0,1,\ldots,7\}$ subcarriers, and uses $\tilde{\bU}_{i,t-1}$, with $f_P,q_P$ to obtain $\tilde{\bU}_{i,t}$, illustrated in the figure via cyan arrows.
+For each time instant, the transmitter uses the Cayley method (Equation~\eqref{eqn:cayley_i1_i2}) for $\tilde{\bU}_{i,t}$ at $i\neq\{9k\}$ non fed back subcarriers (green arrows).}
 \label{table}

### 2019-10-05 paper/main.tex
More changes

@@
 %package list
-\documentclass[conference]{IEEEtran}
+\documentclass[conference,10pt]{IEEEtran}
 \IEEEoverridecommandlockouts
@@
 Past approaches have generally utilized the fact that the optimum precoders are not actually $2N_TN_R$ dimensional entities, but have an underlying manifold structure that allows to work with effective lower dimensions for transformations \cite{pitaval2013codebooks}.
-Second, these precoders are correlated in both time and frequency \cite{Gupt1905:Predictive}.
-Utilizing the available correlations permit the use of predictive quantization algorithms, which improve the quantization error with time.
-This improvement is obtained because of feeding back only incremental information needed over the past fed back precoders, as compared to the new precoder in its entirety.
-Combining these two inherent properties (viz.
-manifold structure and correlations) to perform manifold based predictive quantization requires a generalization of various linear algorithms for prediction, quantization and interpolation to the non-linear manifold structure.
-This is typically done by exploiting the differential geometry of the manifold and relevant past work in this direction has been presented in \cite{Gupt1905:Predictive,6891198,6545375,5671092,Li2016,krishnamachari2013geometry,chang2011adaptive}.
+These precoders are also correlated in both time and frequency \cite{5946308,khaled2005quantized}.
+Predictive quantization can utilize these correlations by needing to feed back only incremental information needed over the past fed back precoders, as compared to the complete new precoder.
+Such a an approach to predictive quantization requires generalization of various linear prediction, quantization and interpolation to the non-linear manifold structure.
+This is typically done by exploiting the differential geometry of the manifold and relevant past work in this direction has been presented in \cite{6891198,6545375,5671092,Li2016,krishnamachari2013geometry,chang2011adaptive}.
 Such approaches for predictive quantization have provided significant performance benefits, since they operate using lower effective dimensions for prediction and quantization.
@@
 We consider a $N_T\times N_R$ MIMO-OFDM wireless system with $N$ subcarriers, and assume $N_T > N_R$ and $N_s = N_R$.
-Consistent with notation in \cite{6891198,Gupt1905:Predictive}, the data stream received on the $i$-th subcarrier, $t$-th time instant (or the $t$-th OFDM frame) is,
+Consistent with notation in \cite{6891198}, the data stream received on the $i$-th subcarrier, $t$-th time instant (or the $t$-th OFDM frame) is,
 \vspace{-1pt}
@@
 That is, if $\text{SVD}(\bH_{i,t}) = \bU_{i,t},\Sigma_{i,t}, \bV_{i,t}$, then $\tilde{\bU}_{i,t} = \bU_{i,t}$.
-The matrices $\bU_{i,t}$ reside on the Stiefel manifold $\text{St}(N_T,N_R)$, since the columns of $\bU_{i,t}$ form a set of $N_R$ orthogonal vectors in $N_T$ dimensions \cite{Gupt1905:Predictive,6891198}.
+The matrices $\bU_{i,t}$ reside on the Stiefel manifold $\text{St}(N_T,N_R)$, since the columns of $\bU_{i,t}$ form a set of $N_R$ orthogonal vectors in $N_T$ dimensions \cite{6891198}.
 Practically, only limited feedback is available from the receiver, and the objective is to estimate $\bU_{i,t}$, via $\tilde{\bU}_{i,t}$, using the available feedback bits.
@@
 
-Predictive quantization algorithms \cite{Gupt1905:Predictive,6891198} can be utilized to reduce the quantization error by utilizing correlations.
+Predictive quantization algorithms \cite{6891198} can be utilized to reduce the quantization error by utilizing correlations.
 We now discuss the basic mathematical model that is central to predictive quantization algorithms for precoding matrices.
@@
 That is, the transmitter utilizes a quantization function $q_P(\cdot)$, to obtain $\tilde{\bU}_{i,t} \gets q_P(\bP_{i,t},\text{fb}_{i,t})$, where $\text{fb}_{i,t} \in \{1,2\ldots2^{\mathcal{B}}\}$ is feedback for the precoder at $i$-th subcarrier, $t$-th time instant, considering bit budget of $\mathcal{B}$ bits.
-In \cite{Gupt1905:Predictive,6891198,6545375}, $\text{fb}_{i,t}$ denotes the codeword index for the codebook obtained by quantizing the local tangent space at $\bP_{i,t}$.
+In \cite{6891198,6545375}, $\text{fb}_{i,t}$ denotes the codeword index for the codebook obtained by quantizing the local tangent space at $\bP_{i,t}$.
 
@@
 In our work, we propose a RC framework which implements the prediction function $f_p(\cdot)$.
-We reuse the $q_P$ algorithm from \cite{Gupt1905:Predictive,6891198}.
+We reuse the $q_P$ algorithm from \cite{6891198}.
 However, by incorporating the $q_P$ in the reservoir framework, $f_P$ and $q_P$ get coupled in the sense that $f_P$ is optimized via online training of the reservoir by minimizing the norm difference between $\bP_{i,t}=f_P(\cdot)$, and $\tilde{\bU}_{i,t}=q_P(f_P(\cdot),\text{fb}_{i,t})$.
-Previous work \cite{Gupt1905:Predictive,6891198} has considered $f_P$ and $q_P$ to be uncoupled with each other.
+Previous work \cite{6891198} has considered $f_P$ and $q_P$ to be uncoupled with each other.
 % A detailed discussion on the RC based model for $f_P$ and $q_P$ is presented in Section \ref{section3}.
@@
 The input to the reservoir $i$ that corresponds to subcarrier $i$ is $\tilde{\bu}_{i,t-1}$ (vectorized representation of $\tilde{\bU}_{i,t-1}$), with dimensions $D_{\text{in}}=2N_TN_R-N_R^2+N_R$.
-Using a randomly initialized $D_{\text{resv}}\times D_{\text{in}}$ input coupler matrix $\bW^{\text{in}}_i$, the $D_{\text{in}}$ dimensional input is mapped to a $D_{\text{resv}}(>>D_{\text{in}})$ dimensional vector, where $D_{\text{resv}}$ is the dimension of the reservoir state vector $\br_{i,t}$.
+Using a randomly initialized $D_{\text{resv}}\times D_{\text{in}}$ input coupler matrix $\bW^{\text{in}}_i$, the $D_{\text{in}}$ dimensional input is mapped to a $D_{\text{resv}}(\gg D_{\text{in}})$ dimensional vector, where $D_{\text{resv}}$ is the dimension of the reservoir state vector $\br_{i,t}$.
 $\br_{i,t}$ is initialized with $D_{\text{resv}}$ zeros, and is updated via the following equation:
@@
 
-We now describe the quantization function $q_P(\cdot)$ which is essentially the same as considered in \cite{Gupt1905:Predictive,6891198}, that exploits the fact that tangent spaces local to a point in manifold are vector spaces.
+We now describe the quantization function $q_P(\cdot)$ which is essentially the same as considered in \cite{6891198}, that exploits the fact that tangent spaces local to a point in manifold are vector spaces.
 To do so, the quantization algorithm quantizes the local tangent space at the predicted precoder $\bP_{i,t}$ to get a codebook, $T^\mathcal{C}$ having $2^{\mathcal{B}}$ codeword tangents in the tangent space.
 The quantized precoders are obtained by traversing along the `codeword tangents' from the predicted precoder $\bP_{i,t}$, using a retraction map (denoted by $\text{retract}(\cdot)$).
-The receiver conveys the feedback $\text{fb}_{i,t}$ to the transmitter, which minimizes the chordal distance metric ($d_s(\bX,\bY)$ for $\bX,\bY \in \text{St}(N_T,N_R)$ detailed in \cite{Gupt1905:Predictive,6891198}) between the quantized precoders and the ideal precoder $\bU_{i,t}$ estimated from SVD of $\bH_{i,t}$ \eqref{eqn:cn1}
+The receiver conveys the feedback $\text{fb}_{i,t}$ to the transmitter, which minimizes the chordal distance metric ($d_s(\bX,\bY)$ for $\bX,\bY \in \text{St}(N_T,N_R)$ detailed in \cite{6891198}) between the quantized precoders and the ideal precoder $\bU_{i,t}$ estimated from SVD of $\bH_{i,t}$ \eqref{eqn:cn1}
  \begin{equation}
@@
 % A corresponding retraction operation $Y=\texttt{retract}(X,\bT^Y_X)$, $\texttt{retract}: \text{St}(N_T,N_R)\times \mathcal{T}_X \text{St}(N_T,N_R) \to \text{St}(N_T,N_R)$ gives back the manifold point obtained by traversing in the tangent direction given by the second argument ($\bT^Y_X$).
-% In this work, the chosen lifting-retraction pairs are the Cayley exponentials, discussed in \cite{DBLP:journals/corr/abs-1708-00045,Gupt1905:Predictive}. % and used in \cite{Gupt1905:Predictive}.
+% In this work, the chosen lifting-retraction pairs are the Cayley exponentials, discussed in \cite{DBLP:journals/corr/abs-1708-00045}. % and used in \cite{}.
 % The Cayley exponential lifting operation maps two points in $\text{St}(N_T,N_R)$, to a $N_T\times N_T$ skew Hermitian matrix that represents the tangent from first point to the other.
@@
 % This codebook is subsequently referred to as the base codebook ($\text{base}^{\mathcal{C}}$) for the quantization function.
-% The feedback from the receiver indicates the codeword corresponding to the optimum tangent in $\mathcal{T}_{\bP_{i,t}} \text{St}(N_T,N_R)$, which the transmitter can choose to get closest (in terms of chordal distance metric, $d_s(\bX,\bY)$ for $\bX,\bY \in \text{St}(N_T,N_R)$ detailed in \cite{Gupt1905:Predictive,6891198}) to the actual value $\bU_{i,t}$.
+% The feedback from the receiver indicates the codeword corresponding to the optimum tangent in $\mathcal{T}_{\bP_{i,t}} \text{St}(N_T,N_R)$, which the transmitter can choose to get closest (in terms of chordal distance metric, $d_s(\bX,\bY)$ for $\bX,\bY \in \text{St}(N_T,N_R)$ detailed in \cite{6891198}) to the actual value $\bU_{i,t}$.
 % With the optimum direction chosen, the next step is to determine how much to move in that particular chosen direction, viz.
 the length of the chosen tangent direction.
-For this, we adopt the same strategy in \cite{,Gupt1905:Predictive,6891198}, which controls the magnitude of tangent steps, by having two codebooks of different spreads, but the same $2^{\mathcal{B}-1}$ base vectors.
+For this, we adopt the same strategy in \cite{6891198}, which controls the magnitude of tangent steps, by having two codebooks of different spreads, but the same $2^{\mathcal{B}-1}$ base vectors.
 % The two codebooks are concatenated to form a $2^\mathcal{B}$ length codebook, $T^\mathcal{C}$.
@@
 the optimum codeword lies in the higher/lower spread codebook instead.
-% The scheme used to obtain $\text{base}^{\mathcal{C}}$ is similar to the one presented in \cite{Gupt1905:Predictive}, which performs a $k$-means ($k=2^{\mathcal{B}-1}$) clustering on a collection of tangents to obtain an isotropic collection of $2^{\mathcal{B}-1}$ tangent codewords.
+% The scheme used to obtain $\text{base}^{\mathcal{C}}$ is similar to the one presented in \cite{}, which performs a $k$-means ($k=2^{\mathcal{B}-1}$) clustering on a collection of tangents to obtain an isotropic collection of $2^{\mathcal{B}-1}$ tangent codewords.
 
@@
 \noindent Having described the technicalities of $f_P,q_P$, we now describe the training process for the reservoir, which couples $f_P$ with $q_P$.
-The key idea for reservoir training is that, as the predicted matrix $\bP_{i,t}$ (the coarse estimate) gets closer to $\tilde{\bU}_{i,t}$ (the refined estimate), the receiver has to quantize even smaller subspaces, and can thus provide a more refined estimate from the feedback $\text{fb}_{i,t}$.
-Hence, we train the reservoir output coupler such that the following objective function is optimized:
+For reservoir training, as the predicted matrix $\bP_{i,t}$ (the coarse estimate) gets closer to $\tilde{\bU}_{i,t}$ (the refined estimate), the receiver quantizes smaller subspaces, and can thus provide a more refined estimate from the feedback $\text{fb}_{i,t}$.
+We thus train the reservoir output coupler to minimize the following:
 \begin{equation}
@@
 \end{equation}
-Computing the gradient $\frac{\partial \mathcal{O}_{i,t}}{\partial \bW_{i,t}^{\text{out}}}$ and setting it to null yields,
+Computing the gradient $\frac{\partial \mathcal{O}_{i,t}}{\partial \bW_{i,t}^{\text{out}}}$ and setting it to null yields
 \begin{equation}
@@
 \end{equation}
-\eqref{wout_upd} makes training of the reservoir easy to implement with low complexity.
-We only need to store a matrix $\text{\textbf{num}}_{i,t-1}$, and a number $\text{den}_{i,t-1}$ from $t-1$ time instant to calculate optimum output coupler for $t$-th time instant.
-This completes the discussion of the proposed RC framework (Fig.
-\ref{res_overview}).
+This simplifies the reservoir training, since we only need to store a matrix $\text{\textbf{num}}_{i,t-1}$, and a number $\text{den}_{i,t-1}$ from time $t-1$ to calculate optimum output coupler for time $t$.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 To conclude this section, we summarize and highlight the novel aspects of the proposed framework.
-The first key advantage of the proposed approach over the past work \cite{Gupt1905:Predictive,6891198,6545375} is that here the prediction function, $f_P$ is coupled with the quantization function, $q_P$.
+The first key advantage of the proposed approach over the past work \cite{6891198,6545375} is that here the prediction function, $f_P$ is coupled with the quantization function, $q_P$.
 Past work for predictive quantization has largely kept $f_P$ and $q_P$ uncoupled in the sense that, the obtained precoder is just composite function of $f_P$ and $q_P$, applied to the previous $p$ precoder estimates i.e.
@@
 % Also, by storing just one matrix $\text{\textbf{num}}_{i,t}$ and a number $\text{den}_{i,t}$, we capture the entire history of the obtained quantized precoders, with past values weighted by $\lambda$ in $\mathcal{O}_{i,t}$ \eqref{oit}.
-% This is a departure from previous schemes \cite{Gupt1905:Predictive,6891198,6545375} which store the past $p$ precoders in a $p$ sized cyclic buffer ($p$ also has to be pre-decided).
+% This is a departure from previous schemes \cite{,6891198,6545375} which store the past $p$ precoders in a $p$ sized cyclic buffer ($p$ also has to be pre-decided).
 
@@
 We compare the results obtained by our framework with \cite{6891198}, which presented a manifold geometry method to exploit temporal correlations for predictive quantization.
-% The forward prediction function $f_P$ of the proposed framework, has $p$ (Section \ref{section2}) to be $1$ \eqref{fpqp}, whereas the backward pass $p$ for time instant $t$ is $t$ (Observe the framing of $\mathcal{O}_{i,t}$).
+% The forward prediction function $f_P$ of the proposed framework, has $p$ (Section \ref{section2}) to be $1$, whereas the backward pass $p$ for time instant $t$ is $t$ (Observe the framing of $\mathcal{O}_{i,t}$).
 We keep $p=4$ for the $f_P$ presented in \cite{6891198}.
-The quantization function $q_P$ is kept to be same, as described in \cite{6545375,6891198,Gupt1905:Predictive} for both the approaches.
+The quantization function $q_P$ is kept to be same, as described in \cite{6545375,6891198} for both the approaches.
 Although in both our work and \cite{6891198}, only temporal correlations are exploited, we compare the simulation results for the complete MIMO-OFDM setting (visually illustrated in Fig.
@@
 Hence, the transmitter obtains only $\text{fb}_{\{9k\},t}$.
-For non fed back subcarriers $i\neq 9k$, $9n < i < 9(n+1)$, the Cayley method \cite{Gupt1905:Predictive} is used to interpolate $\tilde{\bU}_{i,t}$, from available estimates, $\tilde{\bU}_{9n,t}$ and $\tilde{\bU}_{9(n+1), t}$
+For non fed back subcarriers $i\neq 9k$, $9n < i < 9(n+1)$, the Cayley method \cite{} is used to interpolate $\tilde{\bU}_{i,t}$, from available estimates, $\tilde{\bU}_{9n,t}$ and $\tilde{\bU}_{9(n+1), t}$
 \begin{equation}
@@
 $\bP_{i,t}=\tilde{\bU}_{i,t-1}$) is used for 10 time instances to provide the initial training data for the reservoir and to overcome the initial transient response of the reservoir (also discussed in \cite{mosleh2017brain}).
-A 5 bit base codebook is used for the quantization function $q_P$ and is generated according to the method presented in Section \ref{qp}, similar to \cite{Gupt1905:Predictive}.
+A 5 bit base codebook is used for the quantization function $q_P$ and is generated according to the method presented in Section \ref{section3}.
 Hence, both initialization and subsequent feedback, $\text{fb}_{i,t}$ can be encoded using 6 bits (i.e. $\mathcal{B}=6$ Section \ref{section2}).
@@
 
-For predicting channels at each of the $8$ fed-back subcarriers, we consider $8$ separate reservoirs, each of them evolved separately, with $i\in\{9k, k \in \{0,1,\ldots,7\}\}$ in both the forward pass prediction and quantization ($f_P,q_P$) \eqref{fpqp} and backward pass to update $\bW_{i,t}^{\text{out}}$ \eqref{backpass}.
-Unlike \cite{Gupt1905:Predictive}, we do not exploit frequency correlations for predictive quantization, and the $8$ reservoirs for prediction of $8$ fed-back subcarriers are kept independent of each other.
+For predicting channels at each of the $8$ fed-back subcarriers, we consider $8$ separate reservoirs, each of them evolved separately, with $i\in\{9k, k \in \{0,1,\ldots,7\}\}$ in both the forward pass prediction and quantization ($f_P,q_P$) and backward pass to update $\bW_{i,t}^{\text{out}}$ \eqref{backpass}.
+Unlike \cite{}, we do not exploit frequency correlations for predictive quantization, and the $8$ reservoirs for prediction of $8$ fed-back subcarriers are kept independent of each other.
 All these 8 reservoirs are initialized with $\bA_{i\in\{9k\}}$ being an Erdos-Reny\"i graph, with probability of edge connections being $0.2$, $\lambda=2$, $\bW^{\text{out/in}}_{i\in\{9k\},0}$ initialized randomly, $D_{\text{in}}=D_{\text{out}}=14$ (vectorized representation of $4\times2$ semi-unitary matrix, Section \ref{section3}) and $D_{\text{resv}}=60$.
@@
 Observe from Fig.
-\ref{BER} that RC framework is able to achieve substantial improvements in $\text{E}_\text{b}\text{N}_0$ levels at $\text{BER}\leq 10^{-4}$.
+\ref{BER} that RC framework is able to achieve substantial improvements in ${E}_{b}/{N}_0$ levels at $\text{BER}\leq 10^{-4}$.
 Particularly, for $\text{BER}=10^{-5}$ we observe around $5$ dB improvement.
-
-The improved performance for both quantization error and BER in the RC approach could be due to the fact that $f_P,q_P$ are coupled via the backward pass framework (see Section \ref{train}).
+The improved performance for both quantization error and BER in the RC approach could be due to the fact that $f_P,q_P$ are coupled via the backward pass framework.
 Also, from from Fig.
@@
 \noindent For simulating the achievable rate, we quantize the sigma values ($\Sigma_{i,t}$ from SVD of $\bH_{i,t}$) using a 2 bit vector quantizer ($k$-means), and feed them back to the transmitter for subcarriers ($\{9k, k \in \{0,1,\ldots,7\}\}$).
-For the non-fed back subcarriers, they are interpolated using a convex combination interpolation as in \cite{Gupt1905:Predictive}.
+For the non-fed back subcarriers, they are interpolated using a convex combination interpolation as in \cite{}.
 Observe from Fig.
@@
 \vspace{-5pt}
-\caption{The red curve is the ideal case, with exact $\bU_{i,t}$ for all 64 subcarriers available at each time instant at the transmitter.
-The \{green/yellow/blue\} curves corresponds to the case in which \{$\bU_{9k,t}$/$\tilde{\bU}_{9k,t}$ from reservoir method/$\tilde{\bU}_{9k,t}$ from \cite{6891198}\} is available at each time instant, and non fed back precoders are interpolated via the Cayley method.
-The BER for the proposed framework BER provides significant improvement in $E_b/N_0$ levels over \cite{6891198} (normalized Doppler $f_DT_s=10^{-4}$).}
+\caption{For normalized Doppler $f_DT_s=10^{-4}$, the
+  \{green/yellow/blue\} curves correspond to the cases in which
+  \{$\bU_{9k,t}$/$\tilde{\bU}_{9k,t}$ from reservoir
+  method/$\tilde{\bU}_{9k,t}$ from \cite{6891198}\} is available at
+  each time instant, and non fed back precoders are interpolated via
+  the Cayley method. The proposed framework achieves an improved BER
+  other approaches.}
 \vspace{5pt}
@@
 These improvements are due to the training method for the reservoir framework, which refines the predicted coarse estimates as the reservoir evolves.
-Our results use only temporal correlations for predictive quantization, and could improve if frequency correlations are also xexploited simultaneously..
+Our results use only temporal correlations for predictive quantization, and could improve if frequency correlations are also exploited simultaneously..
 Future work would focus on better reservoir frameworks, and a detailed analysis of impact on performance caused by choice of different reservoir parameters like $\bA,\text{tanh}(\cdot),$ and $D_{\text{resv}}$.

### 2019-10-20 paper/main.tex
5 page version

--- 2019-09-30 paper/main.tex
@@
 
-  Precoding in MIMO wireless systems is essential for achieving
-  channel capacity. However, the receiver should quantize and feed
-  back the precoder using very few bits of overhead. The precoder's
-  underlying manifold structure aids this feedback and allows the use
-  of channel temporal/frequency correlation for predictive
-  quantization. We introduce a reservoir computing framework for
-  predictive quantization by exploiting temporal correlations. Past
-  methods primarily use the geometry of the underlying manifold for
-  precoder prediction.  We, instead, use a dynamical reservoir state
-  as part of the online training process of the reservoir.
-  Simulations reveal reduces quantization error, lower BER and
-  improved achievable rates.
+SVD based precoding matrices have been theoretically proven to perform optimum power allocation and lower BER transmissions in MIMO wireless systems. 
+% A key step enabling this improved performance is the feedback of these precoders to the transmitter from the receiver.
+% Gievn the limited bit budget for such Channel State Information (CSI) feedback, these precoders need to be quantized effectively using just a few bits.
+However, in a practical setting, for a $N_T \times N_R$ MIMO system ($N_{\{T/R\}}$: Number of Transmit/Receive Antennas), the receiver needs to quantize and feedback the $N_T \times N_R$ precoding matrix obtained from SVD of the channel matrix, with just a few bits to respect the limited bit budget constraint.
+This task is aided by the presence of an underlying manifold structure and temporal/frequency correlations in the precoders. 
+Predictive quantization methods exploit the correlations in the previously fed back precoders for prediction, followed by quantization of the incremental information required to obtain the actual precoder from the predicted value.
+In this work, we introduce a reservoir computing framework for predictive quantization by exploiting temporal correlations. 
+Past methods have primarily exploited the nonlinear geometry of the underlying manifold structure for precoder prediction.
+Here, this non-linear relationship is captured using the dynamical reservoir state as part of the online training process of the reservoir.
+Simulations reveal that this approach produces reduced quantization error, which results in lower BER as well as improved achievable rates when compared to earlier work.
 \end{abstract}
@@
 % Can remove MIMO wireless systems
-In MIMO wireless systems, precoding matrices are used to transform of an $N_S$-dimensional ($N_S \leq \text{min}(N_T,N_R))$ data stream onto an $N_T$-dimensional transmit signal.
+In MIMO wireless systems, precoding matrices are used for transformation of an $N_S$-dimensional ($N_S \leq \text{min}(N_T,N_R))$ data stream onto an $N_T$-dimensional transmit signal.
 The precoding matrix used to maximize the achievable rate using optimal power allocation is obtained via the SVD of the MIMO channel matrix \cite{love2008overview}.
@@
 % Elaborate on each point (what people have done before) lecunnas
-Past approaches have generally utilized the fact that the optimum precoders are not actually $2N_TN_R$ dimensional entities, but have an underlying manifold structure that allows to work with effective lower dimensions for transformations \cite{pitaval2013codebooks}.
+Past work has used two inherent properties of the optimal precoders to enable effective quantization with just a few bits.
+First, the optimum precoders are not actually $2N_TN_R$ dimensional entities, but have an underlying manifold structure that allows to work with effective lower dimensions, when performing operations over the manifold directly \cite{pitaval2013codebooks}.
 Second, these precoders are correlated in both time and frequency \cite{Gupt1905:Predictive}.
-Utilizing the available correlations permit the use of predictive quantization algorithms, which improve the quantization error with time.
-This improvement is obtained because of feeding back only incremental information needed over the past fed back precoders, as compared to the new precoder in its entirety.
-Combining these two inherent properties (viz.
-manifold structure and correlations) to perform manifold based predictive quantization requires a generalization of various linear algorithms for prediction, quantization and interpolation to the non-linear manifold structure.
+Utilizing the available correlations permit the use of predictive quantization algorithms, which enable improvement of the quantization error with time.
+This improvement is obtained because of feeding back just the small extra information needed on top of the past fed back precoders, as compared to the new precoder information in the entirety.
+% Exploiting frequency correlations permits the use of interpolation algorithms, which reduce the feedback overhead in a single OFDM frame, by feeding back CSI only for certain subcarriers, and interpolating over the others.
+
+Combining the two inherent properties (viz.
+manifold structure and correlations) to frame manifold based predictive quantization algorithms, require a generalization of various well known linear algorithms for prediction, quantization and interpolation, to the underlying non-linear manifold structure.
 This is typically done by exploiting the differential geometry of the manifold and relevant past work in this direction has been presented in \cite{Gupt1905:Predictive,6891198,6545375,5671092,Li2016,krishnamachari2013geometry,chang2011adaptive}.
-Such approaches for predictive quantization have provided significant performance benefits, since they operate using lower effective dimensions for prediction and quantization.
-However, these approaches require specific complicated operations over the non-linear manifold differential geometry.
-In this paper, we aim to capture the above non-linear relations using a reservoir computing based predictive quantizer to exploit channel temporal correlations.
-This framework offers a simple solution to the predictive quantization problem that is easy to implement while also improving performance, when compared to corresponding manifold based approach.
+Manifold based approaches for predictive quantization have provided significant performance benefits, given that they work with the effective lower dimensions while framing the manifold operations to predict and quantize.
+However, these approaches are non-trivial, since they require specific operations over the non-linear manifold differential geometry.
+In this paper, we aim to capture the above non-linear relations using a reservoir computing based predictive quantizer to exploit the temporal correlations effectively.
+The proposed framework offers a simple solution to the predictive quantization problem, which brings about ease of implementation, along with improved performance, when compared to \cite{6891198}, which proposed a corresponding manifold based method to the problem considered in this paper.
 
@@
 % Its design is inspired from several frameworks of Recurrent Neural Networks \cite{jaeger2004harnessing}, including Liquid State Machines \cite{jalalvand2015real} and Echo State Networks \cite{mosleh2017brain,pathak2017using}.
-The RC framework represents the non-linear relationships in data using the higher dimensional dynamical reservoir state vector, which is transformed (using matrices, referred to as `couplers') to the lower dimensional input/output vectors.
-The couplers are learnt over time to optimally map the transformations from the reservoir state to the output.
+The RC framework represents the non-linear relationships in the data via the higher dimensional dynamical reservoir state vector, which is transformed (using matrices, referred to as `couplers') to the lower dimensional input/output vectors.
+The couplers are learnt over time to map the transformations from reservoir state to the output, optimally.
 % A reservoir computing system maps the inputs to temporal patterns in a higher dimensional dynamical reservoir state.
@@
 % Key advantages of reservoir computing framework include ease of training in comparison to its counterparts like Deep Neural Networks \cite{mosleh2017brain}.
-RC has been successfully used to solve problems like handwritten digit image recognition \cite{jalalvand2015real}, climate prediction \cite{pathak2017using}, and problems in the domain of wireless communications \cite{jaeger2004harnessing,mosleh2017brain,shafin2018realizing}.
-\cite{jaeger2004harnessing} used the RC framework to harness channel non-linearities for improved channel equalization.
-\cite{mosleh2017brain,shafin2018realizing} demonstrates a framework for OFDM symbol detection that accounts for channel and power amplifier non-linearities.
-In our work, we utilize a RC framework to capture the underlying nonlinear relations between the previously fed back precoders and the precoder at next time instant for predictive quantization.
-This is analogous to time series prediction algorithms, for which the RC framework has been shown to work effectively \cite{mosleh2017brain}.
+RC has been successfully used to solve problems like handwritten digit image recognition \cite{jalalvand2015real}, climate prediction \cite{pathak2017using}, as well as problems in the domain of wireless communications \cite{jaeger2004harnessing,mosleh2017brain,shafin2018realizing}.
+\cite{jaeger2004harnessing} used RC framework to harness channel non-linearities for improved channel equalization.
+\cite{mosleh2017brain,shafin2018realizing} utilized the framework for OFDM symbol detection while accounting for channel and power amplifier non-linearities.
+In our work, we utilize a RC framework to capture the underlying nonlinear relations between the previously fed back precoders and the precoder at next time instant, for predictive quantization.
+This becomes analogous to time series prediction algorithms, for which the RC framework has been cited to work effectively \cite{mosleh2017brain}.
 
@@
 As the prediction becomes closer to the original value, the quantization error also decreases.
-The quantization algorithm is illustrated in Section 3.3
+The quantization algorithm is illustrated in Section III.3
 
@@
 The matrices $\bU_{i,t}$ reside on the Stiefel manifold $\text{St}(N_T,N_R)$, since the columns of $\bU_{i,t}$ form a set of $N_R$ orthogonal vectors in $N_T$ dimensions \cite{Gupt1905:Predictive,6891198}.
-Practically, only limited feedback is available from the receiver, and the objective is to estimate $\bU_{i,t}$, via $\tilde{\bU}_{i,t}$, using the available feedback bits.
+Given practical limitations, only limited feedback is available from the receiver, and the objective is to estimate $\bU_{i,t}$, via $\tilde{\bU}_{i,t}$, using the available feedback bits.
 Independent quantization algorithms analogous to the Lloyd codebook algorithm have been studied for quantizing the complete $\text{St}(N_T,N_R)$ \cite{6678348}.
-However, this treats precoders close to each other in time/frequency as independent, and does not exploit any temporal/frequency correlations.
+However, this approach treats precoders close to each other in time/frequency as independent, since it does not exploit any temporal/frequency correlations.
 
@@
 Suppose that we predict the current precoding matrix based on the past $p$ observed precoding matrices.
-For this, assume that $\tilde{\bU}_{i,t-p},\ldots,\tilde{\bU}_{i,t-1}$ have been fed back to the transmitter.
-By using a prediction algorithm to exploit the time correlations among precoders at time instances $t-p,\ldots,t-1$, the transmitter can obtain a prediction (viz.
-a coarse estimate) of $\bU_{i,t}$, given by $\bP_{i,t}=f_P(\tilde{\bU}_{i,t-p},\ldots,\tilde{\bU}_{i,t-1})$, where $f_P(\cdot)$ is a prediction function.
+For this, assume that $\tilde{\bU}_{i,t-p},\tilde{\bU}_{i,t-p+1},\ldots,\tilde{\bU}_{i,t-1}$ have been fed back to the transmitter.
+By using a prediction algorithm to exploit the time correlations among precoders at time instances $t-p,t-p+1,\ldots,t-1$, the transmitter can obtain a prediction (viz.
+a coarse estimate) of $\bU_{i,t}$, given by $\bP_{i,t}=f_P(\tilde{\bU}_{i,t-p},\tilde{\bU}_{i,t-p+1},\ldots,\tilde{\bU}_{i,t-1})$, where $f_P: \text{St}(N_T,N_R)^{p} \to \text{St}(N_T,N_R)$ is a prediction function.
 Now, since the transmitter already possesses a coarse estimate $\bP_{i,t}$ of $\bU_{i,t}$, the receiver just quantizes the local space of $\text{St}(N_T,N_R)$ nearby $\bP_{i,t}$.
 The receiver feeds back this quantized information, enabling a refined estimate of $\bU_{i,t}$, given by $\tilde{\bU}_{i,t}$.
-That is, the transmitter utilizes a quantization function $q_P(\cdot)$, to obtain $\tilde{\bU}_{i,t} \gets q_P(\bP_{i,t},\text{fb}_{i,t})$, where $\text{fb}_{i,t} \in \{1,2\ldots2^{\mathcal{B}}\}$ is feedback for the precoder at $i$-th subcarrier, $t$-th time instant, considering bit budget of $\mathcal{B}$ bits.
+That is, the transmitter utilizes a quantization function $q_P:\text{St}(N_T,N_R) \times \mathbb{N} \to \text{St}(N_T,N_R)$, to obtain $\tilde{\bU}_{i,t} \gets q_P(\bP_{i,t},\text{fb}_{i,t})$, where $\text{fb}_{i,t} \in \{1,2\ldots2^{\mathcal{B}}\}$ is feedback for the precoder at $i$-th subcarrier, $t$-th time instant, considering bit budget of $\mathcal{B}$ bits.
 In \cite{Gupt1905:Predictive,6891198,6545375}, $\text{fb}_{i,t}$ denotes the codeword index for the codebook obtained by quantizing the local tangent space at $\bP_{i,t}$.
@@
 % Analogous to this, for $\text{St}(N_T,N_R)$, quantization error is reduced by quantizing a subspace around the predicted value that is much smaller than the entire manifold.
+
 In our work, we propose a RC framework which implements the prediction function $f_p(\cdot)$.
@@
 %Explain prediction and quantization steps here itself ! (succintly)
-\section{RC for Predictive Quantization}
+\section{Reservoir Framework for Pred. Qtizn.}
 \label{section3}
-% \subsection{Vectorizing matrices in the Stiefel Manifold}
+\subsection{Reservoir Forward Pass}
 % \label{vectorize}
@@
 
-\begin{figure}[ht]
+\begin{figure*}[ht]
 \centering
-\includegraphics[width=0.5\textwidth]{images/system2.pdf}
+\includegraphics[width=0.8\textwidth]{images/system2.pdf}
 % \caption{System Overview: The RC framework takes the precoder estimate at $t-1$ (viz.
@@
 $\tilde{\bu}_{i,t}$, top right of fig.) using receiver feedback $\text{fb}_{i,t}$ via $q_P$ \eqref{eqn:cn2}.
-Feedback Estimation (Cyan): The Receiver estimates the ideal $\text{fb}_{i,t}$ using the exact precoders $\bU_{i,t}$ via \eqref{eqn:cn1}.
+\\Feedback Estimation (Cyan): The Receiver estimates the ideal $\text{fb}_{i,t}$ using the exact precoders $\bU_{i,t}$ via \eqref{eqn:cn1}.
 The transmitter observes only the feedback $\text{fb}_{i,t}$\\ Backward Pass (Blue): $\bW^{\text{out}}_{i,t}$ is updated via \eqref{wout_upd} for optimizing $\mathcal{O}_{i,t}$.
@@
 \label{res_overview}
-\end{figure}
+\vspace{-5pt}
+\end{figure*}
 % \begin{equation}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \subsection{Reservoir Training Procedure, the backward pass}
-% \label{train}
-\noindent Having described the technicalities of $f_P,q_P$, we now describe the training process for the reservoir, which couples $f_P$ with $q_P$.
+\subsection{Reservoir Training Procedure, the backward pass}
+\label{train}
+\noindent Having described technical details of $f_P,q_P$, we now describe the training process for the reservoir, which couples $f_P$ with $q_P$.
+Recall that, to obtain $\tilde{\bU}_{i,t}$ from $\tilde{\bU}_{i,t-1}$, we have,
+\begin{equation}
+\tilde{\bU}_{i,t}=q_P(\bP_{i,t},\text{fb}_{i,t})=q_P(f_P(\tilde{\bU}_{i,t-1}),\text{fb}_{i,t})
+\label{fpqp}
+\end{equation}
 The key idea for reservoir training is that, as the predicted matrix $\bP_{i,t}$ (the coarse estimate) gets closer to $\tilde{\bU}_{i,t}$ (the refined estimate), the receiver has to quantize even smaller subspaces, and can thus provide a more refined estimate from the feedback $\text{fb}_{i,t}$.
@@
 
-\noindent The simulations have been performed for the IEEE Pedestrian-A channel, with $N_T=4$, $N_R=2$.  The channel matrices $\bH_{i,t}$ are generated using Jake's model.
+\subsection{Simulation setting considered}
+\label{setting}
+
+\noindent The simulations have been performed for the IEEE Pedestrian-A channel, with $N_T=4$, $N_R=2$.
+The channel matrices $\bH_{i,t}$ are generated using Jake's model via IT++ library through the python wrapper py-itpp \cite{ViditPy}.
 We compare the results obtained by our framework with \cite{6891198}, which presented a manifold geometry method to exploit temporal correlations for predictive quantization.
@@
 $\bP_{i,t}=\tilde{\bU}_{i,t-1}$) is used for 10 time instances to provide the initial training data for the reservoir and to overcome the initial transient response of the reservoir (also discussed in \cite{mosleh2017brain}).
-A 5 bit base codebook is used for the quantization function $q_P$ and is generated according to the method presented in Section \ref{qp}, similar to \cite{Gupt1905:Predictive}.
+A 5 bit base codebook is used for the quantization function $q_P$ and is generated according to the method presented in \cite{Gupt1905:Predictive}.
 Hence, both initialization and subsequent feedback, $\text{fb}_{i,t}$ can be encoded using 6 bits (i.e. $\mathcal{B}=6$ Section \ref{section2}).
@@
 Unlike \cite{Gupt1905:Predictive}, we do not exploit frequency correlations for predictive quantization, and the $8$ reservoirs for prediction of $8$ fed-back subcarriers are kept independent of each other.
-All these 8 reservoirs are initialized with $\bA_{i\in\{9k\}}$ being an Erdos-Reny\"i graph, with probability of edge connections being $0.2$, $\lambda=2$, $\bW^{\text{out/in}}_{i\in\{9k\},0}$ initialized randomly, $D_{\text{in}}=D_{\text{out}}=14$ (vectorized representation of $4\times2$ semi-unitary matrix, Section \ref{vectorize}) and $D_{\text{resv}}=60$.
+All these 8 reservoirs are initialized with $\bA_{i\in\{9k\}}$ being an Erdos-Reny\"i graph, with probability of edge connections being $0.2$, $\lambda=2$, $\bW^{\text{out/in}}_{i\in\{9k\},0}$ initialized randomly, $D_{\text{in}}=D_{\text{out}}=14$ (vectorized representation of $4\times2$ semi-unitary matrix, Section III) and $D_{\text{resv}}=60$.
 % All these 8 reservoirs are initialized with $\bA_{i\in\{9k\}}$ being an Erdos-Reny\"i graph, with 
@@
 \centering
-\includegraphics[width=0.4\textwidth]{images/table.pdf}
+\includegraphics[width=0.5\textwidth]{images/table.pdf}
 \caption{The transmitter obtains feedback for $\{9k, k \in \{0,1,\ldots,7\}$ subcarriers, and uses $\tilde{\bU}_{i,t-1}$, along with $f_P,q_P$ \eqref{fpqp} to obtain $\tilde{\bU}_{i,t}$, illustrated in the figure via cyan arrows.
-For each time instant, the transmitter uses the Cayley method  \eqref{eqn:cayley_i1_i2} to interpolate $\tilde{\bU}_{i,t}$ at $i\neq\{9k\}$ non fed back subcarriers (green arrows}
+For each time instant, the transmitter uses the Cayley method  \eqref{eqn:cayley_i1_i2} to interpolate $\tilde{\bU}_{i,t}$ at $i\neq\{9k\}$ non fed back subcarriers (green arrows)}
 \label{table}
@@
 
+\subsection{Quantization error, BER and Achievable Rate Results}
+\label{res}{}
 % To mitigate errors in prediction upon the presence of randomly appearing drastic events in wireless channels, such as sudden interferences and dynamic environments, only 100 channel evolutions are considered for the simulations, and the algorithm is re-starte.
@@
 \centering
-\includegraphics[width=0.3\textwidth]{images/qtizErr.pdf}
-\caption{Quantization error in terms of chordal distance to the actual precoder $\bU_{\{9k\},t}$ observed at the receiver, from the quantized estimate $\tilde{\bU}_{\{9k\},t}$ averaged over $\{9k\}$ fed back subcarriers, viz.
-$\frac{1}{8}\Sigma_{i \in 9k}d_S(\tilde{\bU}_{i,t}, \bU_{i,t})$ and 10 independent channel realizations (normalized Doppler $f_DT_s=10^{-4}$).}
+\includegraphics[width=0.4\textwidth]{images/qtizErr.pdf}
+\caption{Quantization error in terms of chordal distance to the actual precoder $\bU_{\{9k\},t}$ observed at the receiver, from the quantized estimate $\tilde{\bU}_{\{9k\},t}$ averaged over $\{9k\}$ fed back subcarriers $\Big($ viz.
+$\frac{\Sigma_{i \in 9k}d_S(\tilde{\bU}_{i,t}, \bU_{i,t})}{8}$ $\Big)$ and 10 independent channel realizations (normalized Doppler $f_DT_s=10^{-4}$).}
 \label{qtiz_err}
+\vspace{-10pt}
 \end{figure}
@@
 \ref{BER} that RC framework is able to achieve substantial improvements in $\text{E}_\text{b}\text{N}_0$ levels at $\text{BER}\leq 10^{-4}$.
-Particularly, for $\text{BER}=10^{-5}$ we observe around $5$ dB improvement.
+Particularly, for $\text{BER}=10^{-5}$ we observe around $4$ dB improvement.
+We hypothesize that the key reason for the improved performance for both quantization error and BER in the RC approach, is the fact that $f_P,q_P$ are coupled via the backward pass framework (explained towards the end of Section III).
+% Also, observe from Fig.
+\ref{BER} that the proposed framework BER curve (green) comes very close to the ideal $8$ feedback curve (red).
+This can be explained due to the fact that the semi-unitary precoder basically rotates the data vector via its matrix transformation.
+For QPSK, we get some reasonable error margin for this rotation, which becomes more stringent as the simulated BER is reduced.
+Hence, we match the ideal curve for high BER region, and for low BER region, as the margin of error reduces, the curves diverge.
 
-The improved performance for both quantization error and BER in the RC approach could be due to the fact that $f_P,q_P$ are coupled via the backward pass framework (see Section \ref{train}).
-Also, from from Fig.
-\ref{BER}, the proposed framework BER curve (yellow) performs close to the ideal $8$ feedback curve (green), since the semi-unitary precoder rotates the data vector using its matrix transformation.
-For QPSK, we observe a reasonable error margin for this rotation, which becomes more stringent as the simulated BER is reduced.
-Thus, we match the ideal curve for high BER region, and for the low BER region, as the margin of error reduces, the curves diverge.
-
-\noindent For simulating the achievable rate, we quantize the sigma values ($\Sigma_{i,t}$ from SVD of $\bH_{i,t}$) using a 2 bit vector quantizer ($k$-means), and feed them back to the transmitter for subcarriers ($\{9k, k \in \{0,1,\ldots,7\}\}$).
-For the non-fed back subcarriers, they are interpolated using a convex combination interpolation as in \cite{Gupt1905:Predictive}.
+\noindent For simulating the achievable rate, we quantize the sigma values ($\Sigma_{i,t}$ from SVD of $\bH_{i,t}$) using a 2 bit vector quantizer ($k$-means), and feed them back to the transmitter for fed back subcarriers ($\{9k, k \in \{0,1,\ldots,7\}\}$).
+For the non-fed back subcarriers, they are interpolated via a simple convex combination interpolation method as in \cite{Gupt1905:Predictive}.
 Observe from Fig.
 \ref{achievrate} that the RC framework offers improvement in achievable rate for $f_DT_s=10^{-4}$.
-Since the temporal variations for $f_DT_s=10^{-2}, 10^{-1}$ are higher, the RC framework has to learn faster varying functions thus degrading performance.
-However, it still matches the performance of the predictive quantizer in \cite{6891198} for $f_DT_s=10^{-2}$ and slightly outperforms it for $f_DT_s=10^{-1}$.
+Since the temporal variations for $f_DT_s=10^{-2}, 10^{-1}$ are higher, the RC framework has to learn a faster-varying function, and hence the degradation in performance.
+However, it still matches the performance of the predictive quantizer in \cite{6891198} for $f_DT_s=10^{-2}$ and performs slightly better for $f_DT_s=10^{-1}$.
 \vspace{-3pt}
@@
 \centering
-\includegraphics[width=0.3\textwidth]{images/BER_res.pdf}
+\includegraphics[width=0.43\textwidth]{images/BER_res.pdf}
 \vspace{-5pt}
-\caption{The red curve is the ideal case, with exact $\bU_{i,t}$ for all 64 subcarriers available at each time instant at the transmitter.
-The \{green/yellow/blue\} curves corresponds to the case in which \{$\bU_{9k,t}$/$\tilde{\bU}_{9k,t}$ from reservoir method/$\tilde{\bU}_{9k,t}$ from \cite{6891198}\} is available at each time instant, and non fed back precoders are interpolated via the Cayley method.
-The BER for the proposed framework BER provides significant improvement in $E_b/N_0$ levels over \cite{6891198} (normalized Doppler $f_DT_s=10^{-4}$).}
+\caption{BER results: Here, green curve is the most ideal case considering exact $\bU_{i,t}$ for all 64 subcarriers, at each time instant are available at the transmitter.
+The \{yellow/blue\} curves corresponds to the case in which \{$\tilde{\bU}_{9k,t}$ from reservoir method/$\tilde{\bU}_{9k,t}$ from \cite{6891198}\} are available for each time instant, and non fed back precoders are interpolated via Cayley method.
+Observe that the proposed framework BER curve provides significant improvement in $\text{E}_\text{b}\text{N}_0$ levels over \cite{6891198} (normalized Doppler $f_DT_s=10^{-4}$).}
 \vspace{5pt}
@@
 \centering
-\includegraphics[width=0.32\textwidth]{images/hopRate2.pdf}
+\includegraphics[width=0.43\textwidth]{images/hopRate2.pdf}
 \vspace{-5pt}
-\caption{The percentage of the ideal achievable rate obtained when the transmitter has the accurate (unquantized) and non-interpolated estimates of $\bU_{i,t}$ for each subcarrier and each time instant.}
+\caption{The results are presented as a percentage of the ideal achievable rate obtained when the transmitter has the accurate (unquantized) and non-interpolated estimates of $\bU_{i,t}$ for each subcarrier and each time instant.}
 \label{achievrate}
@@
 
-We have presented a reservoir computing framework for predictive quantization of MIMO precoders that exploits temporal correlations.
-Simulations reveal significant improvement in quantization error, BER, and achievable rate.
-These improvements are due to the training method for the reservoir framework, which refines the predicted coarse estimates as the reservoir evolves.
-Our results use only temporal correlations for predictive quantization, and could improve if frequency correlations are also xexploited simultaneously..
-Future work would focus on better reservoir frameworks, and a detailed analysis of impact on performance caused by choice of different reservoir parameters like $\bA,\text{tanh}(\cdot),$ and $D_{\text{resv}}$.
+In this paper, we have presented a reservoir computing framework for predictive quantization of SVD precoders by exploiting temporal correlations.
+The simulations reveal significant improvement in quantization error, BER, and achievable rate.
+The novelty that enables these improvements lies in the training method for the reservoir framework, which refines the predicted coarse estimates as the reservoir evolves.
+Note that these results have been obtained by exploiting just the temporal correlations for predictive quantization, and can potentially improve if temporal-frequency correlations are exploited jointly.
+This motivates further study into the reservoir framework, and a detailed analysis of impact on performance caused by choice of different reservoir parameters like $\bA,\text{tanh}(\cdot),$ and $D_{\text{resv}}$.
 \vspace{-4pt}

### 2019-10-31 paper/main.tex
More changes by Kumar

@@
 
-\title{\vspace{-10pt}Predictive Quantization for MIMO-OFDM SVD Precoders using Reservoir Computing Framework \vspace{-10pt}}
+\title{Predictive Quantization for MIMO-OFDM SVD Precoders using Reservoir Computing Framework}
 
@@
  \authorblockA{Department of Electrical Engineering, Indian Institute of Technology Bombay\\
- \{agrim,pranavs,akumar,manojg\}@ee.iitb.ac.in \vspace{-18pt}}
+ \{agrim,pranavs,akumar,manojg\}@ee.iitb.ac.in}
 % \thanks{Parts of this work was supported by the Bharti Centre for Communication in
@@
 
-\vspace{-5pt}
 \section{Introduction}
-\vspace{-5pt}
 \label{intro}
@@
 However, since the MIMO channel matrix is estimated at the receiver, the transmitter requires receiver feedback for optimal precoding.
-Therefore, the receiver needs to quantize and feed back the precoders while respecting the bit budget imposed by limited feedback schemes.
+Therefore, the receiver needs to quantize and feed back the precoders within the bit budget imposed by limited feedback schemes.
 Given the high dimensionality of precoders (which form a $N_T \times N_R$ complex-valued matrix, viz.
@@
 % Elaborate on each point (what people have done before) lecunnas
-Past work has used two inherent properties of the optimal precoders to enable effective quantization with just a few bits.
-First, the optimum precoders are not actually $2N_TN_R$ dimensional entities, but have an underlying manifold structure that allows to work with effective lower dimensions, when performing operations over the manifold directly \cite{pitaval2013codebooks}.
-Second, these precoders are correlated in both time and frequency \cite{Gupt1905:Predictive}.
-Utilizing the available correlations permit the use of predictive quantization algorithms, which enable improvement of the quantization error with time.
-This improvement is obtained because of feeding back just the small extra information needed on top of the past fed back precoders, as compared to the new precoder information in the entirety.
-% Exploiting frequency correlations permits the use of interpolation algorithms, which reduce the feedback overhead in a single OFDM frame, by feeding back CSI only for certain subcarriers, and interpolating over the others.
-
-Combining the two inherent properties (viz.
-manifold structure and correlations) to frame manifold based predictive quantization algorithms, require a generalization of various well known linear algorithms for prediction, quantization and interpolation, to the underlying non-linear manifold structure.
-This is typically done by exploiting the differential geometry of the manifold and relevant past work in this direction has been presented in \cite{Gupt1905:Predictive,6891198,6545375,5671092,Li2016,krishnamachari2013geometry,chang2011adaptive}.
-Manifold based approaches for predictive quantization have provided significant performance benefits, given that they work with the effective lower dimensions while framing the manifold operations to predict and quantize.
-However, these approaches are non-trivial, since they require specific operations over the non-linear manifold differential geometry.
-In this paper, we aim to capture the above non-linear relations using a reservoir computing based predictive quantizer to exploit the temporal correlations effectively.
-The proposed framework offers a simple solution to the predictive quantization problem, which brings about ease of implementation, along with improved performance, when compared to \cite{6891198}, which proposed a corresponding manifold based method to the problem considered in this paper.
+Past approaches have generally utilized the fact that the optimum precoders are not $2N_TN_R$ dimensional entities, but have an underlying manifold structure that allows to work with effective lower dimensions for transformations \cite{pitaval2013codebooks}.
+These precoders are also correlated in both time and frequency \cite{5946308,khaled2005quantized}.
+Predictive quantization can utilize these correlations by needing to feed back only incremental information needed over the past fed back precoders, as compared to the complete new precoder.
+Such a an approach to predictive quantization requires generalization of various linear prediction, quantization and interpolation to the non-linear manifold structure.
+This is typically done by exploiting the differential geometry of the manifold and relevant past work in this direction has been presented in \cite{6891198,6545375,5671092,Li2016,krishnamachari2013geometry,chang2011adaptive}.
+Such approaches for predictive quantization have provided significant performance benefits, since they operate using lower effective dimensions for prediction and quantization.
+However, these approaches require specific complicated operations over the non-linear manifold differential geometry.
+In this paper, we aim to capture the above non-linear relations using a reservoir computing based predictive quantizer to exploit channel temporal correlations.
+This framework offers a simple solution to the predictive quantization problem that is easy to implement while also improving performance, when compared to corresponding manifold based approach.
 
@@
 
-\vspace{-1pt}
 \section{System Model}
 \label{section2}
-\vspace{-1pt}
 We consider a $N_T\times N_R$ MIMO-OFDM wireless system with $N$ subcarriers, and assume $N_T > N_R$ and $N_s = N_R$.
-Consistent with notation in \cite{6891198,Gupt1905:Predictive}, the data stream received on the $i$-th subcarrier, $t$-th time instant (or the $t$-th OFDM frame) is,
-\vspace{-1pt}
+Consistent with notation in \cite{6891198}, the data stream received on the $i$-th subcarrier, $t$-th time instant (or the $t$-th OFDM frame) is
 \begin{equation}
@@
 \end{equation}
-\vspace{-1pt}
 Here, $\tilde{\bU}_{i,t} \in \mathbb{C}^{N_T \times N_R}$ is the quantized estimate of precoding matrix, $\by_{i,t} \in \mathbb{C}^{N_R \times 1}$ is the received data stream, $\bx_{i,t} \in \mathbb{C}^{N_T \times 1}$ denotes the transmitted signal, $\bH_{i,t} \in \mathbb{C}^{N_T \times N_R}$ denotes the point-to-point MIMO channel matrix and $\bw_{i,t}$ denotes the i.i.d.
@@
 % Analogous to this, for $\text{St}(N_T,N_R)$, quantization error is reduced by quantizing a subspace around the predicted value that is much smaller than the entire manifold.
-
 In our work, we propose a RC framework which implements the prediction function $f_p(\cdot)$.
-We reuse the $q_P$ algorithm from \cite{Gupt1905:Predictive,6891198}.
-However, by incorporating the $q_P$ in the reservoir framework, $f_P$ and $q_P$ get coupled in the sense that $f_P$ is optimized via online training of the reservoir by minimizing the norm difference between $\bP_{i,t}=f_P(\cdot)$, and $\tilde{\bU}_{i,t}=q_P(f_P(\cdot),\text{fb}_{i,t})$.
-Previous work \cite{Gupt1905:Predictive,6891198} has considered $f_P$ and $q_P$ to be uncoupled with each other.
+We reuse the $q_P$ algorithm from \cite{6891198}.
+Previous work \cite{6891198} has considered $f_P$ and $q_P$ to be uncoupled with each other.
+However, by incorporating the $q_P$ in the reservoir framework, $f_P$ and $q_P$ get coupled, in the sense that $f_P$ is optimized via online training of the reservoir by minimizing the norm difference between $\bP_{i,t}=f_P(\cdot)$, and $\tilde{\bU}_{i,t}=q_P(f_P(\cdot),\text{fb}_{i,t})$.
 % A detailed discussion on the RC based model for $f_P$ and $q_P$ is presented in Section \ref{section3}.
@@
 \label{res_overview}
-\vspace{-5pt}
 \end{figure*}
@@
 
-We now describe the quantization function $q_P(\cdot)$ which is essentially the same as considered in \cite{Gupt1905:Predictive,6891198}, that exploits the fact that tangent spaces local to a point in manifold are vector spaces.
+We now describe the quantization function $q_P(\cdot)$ which is
+essentially the same as that considered in \cite{6891198}, where the
+the fact that tangent spaces local to a point in manifold are vector
+spaces is exploited.
 To do so, the quantization algorithm quantizes the local tangent space at the predicted precoder $\bP_{i,t}$ to get a codebook, $T^\mathcal{C}$ having $2^{\mathcal{B}}$ codeword tangents in the tangent space.
 The quantized precoders are obtained by traversing along the `codeword tangents' from the predicted precoder $\bP_{i,t}$, using a retraction map (denoted by $\text{retract}(\cdot)$).
-The receiver conveys the feedback $\text{fb}_{i,t}$ to the transmitter, which minimizes the chordal distance metric ($d_s(\bX,\bY)$ for $\bX,\bY \in \text{St}(N_T,N_R)$ detailed in \cite{Gupt1905:Predictive,6891198}) between the quantized precoders and the ideal precoder $\bU_{i,t}$ estimated from SVD of $\bH_{i,t}$ \eqref{eqn:cn1}
+The receiver conveys the feedback $\text{fb}_{i,t}$ to the transmitter, which minimizes the chordal distance metric ($d_s(\bX,\bY)$ for $\bX,\bY \in \text{St}(N_T,N_R)$ detailed in \cite{6891198}) between the quantized precoders and the ideal precoder $\bU_{i,t}$ estimated from SVD of $\bH_{i,t}$ \eqref{eqn:cn1}
  \begin{equation}
@@
 Here $\lambda>1$ is the history parameter, and $||\cdot||$ is $\mathcal{L}^2$ norm.
-We wish to perform the following optimization in order to find the optimum $\bW_{i,t}^{\text{out}}$ from the available estimates till time $t$:
+We wish to perform the following optimization to find the optimum $\bW_{i,t}^{\text{out}}$ from the available estimates till time $t$:
 \begin{equation}
@@
 
-To conclude this section, we summarize and highlight the novel aspects of the proposed framework.
-The first key advantage of the proposed approach over the past work \cite{Gupt1905:Predictive,6891198,6545375} is that here the prediction function, $f_P$ is coupled with the quantization function, $q_P$.
-Past work for predictive quantization has largely kept $f_P$ and $q_P$ uncoupled in the sense that, the obtained precoder is just composite function of $f_P$ and $q_P$, applied to the previous $p$ precoder estimates i.e.
-$q_P(f_P(\cdot))$ (Section \ref{section2}).
-In the proposed framework, $f_P$ changes with time due to the update equation of $\bW_{i,t}^{\text{out}}$ \eqref{wout_upd}.
-Recall that $\bW_{i,t}^{\text{out}}$ update equation is obtained from optimizing \eqref{oit}, which minimizes the norm error between the prediction $\bp_{i,t}$ (the coarse estimate) and the quantized value $\tilde{\bu}_{i,t}$ (the refined estimate).
-Hence, backward pass ensures that the coarse estimate provided by $f_P$ gets more refined with time, since optimizing $\bW_{i,t}^{\text{out}}$ to minimize $\mathcal{O}_{i,t}$ brings the predicted estimates $\bp_{i,s\leq t}$ closer to the quantized estimates $\tilde{\bu}_{i,s\leq t}$.
-The updated $\bW_{i,t}^{\text{out}}$ is then used to obtain $\bP_{i,t+1}$, which is likely to be closer to $\tilde{\bU}_{i,t+1}$, than $\bP_{i,t}$ was to $\tilde{\bU}_{i,t}$, due to optimization of $\mathcal{O}_{i,t}$.
-This enables $q_P$ to quantize even smaller subspaces, since the coarse estimate itself has improved, which in turn brings about lower quantization error, and thus improved performance.
+To conclude this section, we summarize and highlight the novel aspects
+of the proposed framework.  The first key advantage of the proposed
+approach over the past work \cite{6891198,6545375} is that here the
+prediction function, $f_P$ is coupled with the quantization function,
+$q_P$.  Past work for predictive quantization has largely kept $f_P$
+and $q_P$ uncoupled in the sense that, the obtained precoder is just
+composite function of $f_P$ and $q_P$, applied to the previous $p$
+precoder estimates i.e. $q_P(f_P(\cdot))$ (Section \ref{section2}). In
+the proposed framework, $f_P$ changes with time due to the update
+equation of $\bW_{i,t}^{\text{out}}$ \eqref{wout_upd}. Recall that the
+$\bW_{i,t}^{\text{out}}$ update equation is obtained from optimizing
+\eqref{oit}, which minimizes the norm error between the prediction
+$\bp_{i,t}$ (the coarse estimate) and the quantized value
+$\tilde{\bu}_{i,t}$ (the refined estimate). Hence, the backward pass
+ensures that the coarse estimate provided by $f_P$ gets refined with
+time, since optimizing $\bW_{i,t}^{\text{out}}$ to minimize
+$\mathcal{O}_{i,t}$ brings the predicted estimates $\bp_{i,s\leq t}$
+closer to the quantized estimates $\tilde{\bu}_{i,s\leq t}$.  The
+updated $\bW_{i,t}^{\text{out}}$ is then used to obtain $\bP_{i,t+1}$,
+which is likely to be closer to $\tilde{\bU}_{i,t+1}$, than
+$\bP_{i,t}$ was to $\tilde{\bU}_{i,t}$, due to optimization of
+$\mathcal{O}_{i,t}$.  This enables $q_P$ to quantize even smaller
+subspaces, since the coarse estimate itself has improved, which in
+turn brings about lower quantization error, and thus improved
+performance.
 
@@
 \label{section4}
-
-\subsection{Simulation setting considered}
-\label{setting}
-
-\noindent The simulations have been performed for the IEEE Pedestrian-A channel, with $N_T=4$, $N_R=2$.
-The channel matrices $\bH_{i,t}$ are generated using Jake's model via IT++ library through the python wrapper py-itpp \cite{ViditPy}.
+Simulations have been performed for the Pedestrian-A channel model~\cite{3rd2009lte}, with $N_T=4$, $N_R=2$.  The channel matrices $\bH_{i,t}$ are generated using Jake's model.
 We compare the results obtained by our framework with \cite{6891198}, which presented a manifold geometry method to exploit temporal correlations for predictive quantization.
-% The forward prediction function $f_P$ of the proposed framework, has $p$ (Section \ref{section2}) to be $1$ \eqref{fpqp}, whereas the backward pass $p$ for time instant $t$ is $t$ (Observe the framing of $\mathcal{O}_{i,t}$).
-We keep $p=4$ for the $f_P$ presented in \cite{6891198}.
-The quantization function $q_P$ is kept to be same, as described in \cite{6545375,6891198,Gupt1905:Predictive} for both the approaches.
+% The forward prediction function $f_P$ of the proposed framework, has $p$ (Section \ref{section2}) to be $1$, whereas the backward pass $p$ for time instant $t$ is $t$ (Observe the framing of $\mathcal{O}_{i,t}$).
+We choose $p=4$ for the $f_P$ presented in \cite{6891198}.
+The quantization function $q_P$ is kept to be same, as described in \cite{6545375,6891198} for both the approaches.
 Although in both our work and \cite{6891198}, only temporal correlations are exploited, we compare the simulation results for the complete MIMO-OFDM setting (visually illustrated in Fig.
@@
 \label{table}
-\vspace{5pt}
 \end{figure}
@@
 \includegraphics[width=0.4\textwidth]{images/qtizErr.pdf}
-\caption{Quantization error in terms of chordal distance to the actual precoder $\bU_{\{9k\},t}$ observed at the receiver, from the quantized estimate $\tilde{\bU}_{\{9k\},t}$ averaged over $\{9k\}$ fed back subcarriers $\Big($ viz.
-$\frac{\Sigma_{i \in 9k}d_S(\tilde{\bU}_{i,t}, \bU_{i,t})}{8}$ $\Big)$ and 10 independent channel realizations (normalized Doppler $f_DT_s=10^{-4}$).}
+\caption{Quantization error in terms of chordal distance to the actual precoder $\bU_{\{9k\},t}$ observed at the receiver, from the quantized estimate $\tilde{\bU}_{\{9k\},t}$ averaged over $\{9k\}$ fed back subcarriers, viz.
+$\frac{1}{8}\Sigma_{i \in 9k}d_S(\tilde{\bU}_{i,t}, \bU_{i,t})$ and 10 independent channel realizations (normalized Doppler $f_DT_s=10^{-4}$).}
 \label{qtiz_err}
-\vspace{-10pt}
 \end{figure}
 
-From Fig.
-\ref{qtiz_err} it is evident that the proposed framework is able to reduce the quantization error below what was obtained from the existing temporal correlations based predictive quantizer in \cite{6891198}.
-In addition, the quantization error plot is much smoother as well, which can be explained from the fact that the RC approach optimizes $\mathcal{O}_{i,t}$, that captures the long term dynamics of the channel and hence, does not face jittery variations.
-We simulate (uncoded QPSK) BER performance for all the 64 subcarriers' precoders obtained after interpolation ($\tilde{\bU}_{i\neq\{9k\},t}$) and quantization ($\tilde{\bU}_{\{9k\},t}$).
-Observe from Fig.
-\ref{BER} that RC framework is able to achieve substantial improvements in $\text{E}_\text{b}\text{N}_0$ levels at $\text{BER}\leq 10^{-4}$.
-Particularly, for $\text{BER}=10^{-5}$ we observe around $4$ dB improvement.
-We hypothesize that the key reason for the improved performance for both quantization error and BER in the RC approach, is the fact that $f_P,q_P$ are coupled via the backward pass framework (explained towards the end of Section III).
+From Fig. \ref{qtiz_err} it is evident that the proposed framework is
+able to reduce the quantization error to a value smaller than that
+obtained from the temporal correlations based predictive quantizer in
+\cite{6891198}. Moreover, the quantization error varies more
+gradually, since the RC approach optimizes $\mathcal{O}_{i,t}$, which
+captures the long term dynamics of the channel and hence, does not
+face jittery variations. We simulate (uncoded QPSK) BER performance
+for all the 64 subcarriers' precoders obtained after interpolation
+($\tilde{\bU}_{i\neq\{9k\},t}$) and quantization
+($\tilde{\bU}_{\{9k\},t}$). Fig. \ref{BER} shows that the RC framework
+is able to achieve substantial improvements in
+$\text{E}_\text{b}\text{N}_0$ levels at $\text{BER}\leq
+10^{-4}$. Particularly, for $\text{BER}=10^{-5}$ we observe around $4$
+dB improvement. The improved performance for both
+quantization error and BER in the RC approach can be attributed to the
+fact that $f_P$ and $q_P$ are coupled via the backward pass framework,
+as discussed in Section III.
 % Also, observe from Fig.
@@
 However, it still matches the performance of the predictive quantizer in \cite{6891198} for $f_DT_s=10^{-2}$ and performs slightly better for $f_DT_s=10^{-1}$.
-\vspace{-3pt}
 
@@
 \includegraphics[width=0.43\textwidth]{images/BER_res.pdf}
-\vspace{-5pt}
 \caption{BER results: Here, green curve is the most ideal case considering exact $\bU_{i,t}$ for all 64 subcarriers, at each time instant are available at the transmitter.
@@
 Observe that the proposed framework BER curve provides significant improvement in $\text{E}_\text{b}\text{N}_0$ levels over \cite{6891198} (normalized Doppler $f_DT_s=10^{-4}$).}
-\vspace{5pt}
 \label{BER}
@@
 \includegraphics[width=0.43\textwidth]{images/hopRate2.pdf}
-\vspace{-5pt}
 \caption{The results are presented as a percentage of the ideal achievable rate obtained when the transmitter has the accurate (unquantized) and non-interpolated estimates of $\bU_{i,t}$ for each subcarrier and each time instant.}
 \label{achievrate}
-\vspace{-10pt}
 \end{figure}
@@
 
-In this paper, we have presented a reservoir computing framework for predictive quantization of SVD precoders by exploiting temporal correlations.
-The simulations reveal significant improvement in quantization error, BER, and achievable rate.
-The novelty that enables these improvements lies in the training method for the reservoir framework, which refines the predicted coarse estimates as the reservoir evolves.
-Note that these results have been obtained by exploiting just the temporal correlations for predictive quantization, and can potentially improve if temporal-frequency correlations are exploited jointly.
-This motivates further study into the reservoir framework, and a detailed analysis of impact on performance caused by choice of different reservoir parameters like $\bA,\text{tanh}(\cdot),$ and $D_{\text{resv}}$.
-\vspace{-4pt}
+We have presented a reservoir computing framework for predictive quantization of MIMO precoders that exploits temporal correlations.
+Simulations reveal significant improvement in quantization error, BER, and achievable rate.
+These improvements are due to the training method for the reservoir framework, which refines the predicted coarse estimates as the reservoir evolves.
+Our results use only temporal correlations for predictive quantization, and could improve if frequency correlations are also exploited simultaneously..
+Future work would focus on better reservoir frameworks, and a detailed analysis of impact on performance caused by choice of different reservoir parameters like $\bA,\text{tanh}(\cdot),$ and $D_{\text{resv}}$.
 

### 2019-12-27 paper/main.tex
Minor change
Generate one column version
Adding new BER/Rate Results

--- 2019-10-20 paper/main.tex
@@
 \section{Introduction}
-\vspace{-5pt}
 \label{intro}
@@
 \label{section2}
-\vspace{-1pt}
+
 We consider a $N_T\times N_R$ MIMO-OFDM wireless system with $N$ subcarriers, and assume $N_T > N_R$ and $N_s = N_R$.
@@
 As the prediction becomes closer to the original value, the quantization error also decreases.
-The quantization algorithm is illustrated in Section III.3
+The quantization algorithm is illustrated in Section 3.3
 
@@
 Suppose that we predict the current precoding matrix based on the past $p$ observed precoding matrices.
-For this, assume that $\tilde{\bU}_{i,t-p},\tilde{\bU}_{i,t-p+1},\ldots,\tilde{\bU}_{i,t-1}$ have been fed back to the transmitter.
-By using a prediction algorithm to exploit the time correlations among precoders at time instances $t-p,t-p+1,\ldots,t-1$, the transmitter can obtain a prediction (viz.
-a coarse estimate) of $\bU_{i,t}$, given by $\bP_{i,t}=f_P(\tilde{\bU}_{i,t-p},\tilde{\bU}_{i,t-p+1},\ldots,\tilde{\bU}_{i,t-1})$, where $f_P: \text{St}(N_T,N_R)^{p} \to \text{St}(N_T,N_R)$ is a prediction function.
+For this, assume that $\tilde{\bU}_{i,t-p},\ldots,\tilde{\bU}_{i,t-1}$ have been fed back to the transmitter.
+By using a prediction algorithm to exploit the time correlations among precoders at time instances $t-p,\ldots,t-1$, the transmitter can obtain a prediction (viz.
+a coarse estimate) of $\bU_{i,t}$, given by $\bP_{i,t}=f_P(\tilde{\bU}_{i,t-p},\ldots,\tilde{\bU}_{i,t-1})$, where $f_P(\cdot)$ is a prediction function.
 Now, since the transmitter already possesses a coarse estimate $\bP_{i,t}$ of $\bU_{i,t}$, the receiver just quantizes the local space of $\text{St}(N_T,N_R)$ nearby $\bP_{i,t}$.
 The receiver feeds back this quantized information, enabling a refined estimate of $\bU_{i,t}$, given by $\tilde{\bU}_{i,t}$.
-That is, the transmitter utilizes a quantization function $q_P:\text{St}(N_T,N_R) \times \mathbb{N} \to \text{St}(N_T,N_R)$, to obtain $\tilde{\bU}_{i,t} \gets q_P(\bP_{i,t},\text{fb}_{i,t})$, where $\text{fb}_{i,t} \in \{1,2\ldots2^{\mathcal{B}}\}$ is feedback for the precoder at $i$-th subcarrier, $t$-th time instant, considering bit budget of $\mathcal{B}$ bits.
+That is, the transmitter utilizes a quantization function $q_P(\cdot)$, to obtain $\tilde{\bU}_{i,t} \gets q_P(\bP_{i,t},\text{fb}_{i,t})$, where $\text{fb}_{i,t} \in \{1,2\ldots2^{\mathcal{B}}\}$ is feedback for the precoder at $i$-th subcarrier, $t$-th time instant, considering bit budget of $\mathcal{B}$ bits.
 In \cite{Gupt1905:Predictive,6891198,6545375}, $\text{fb}_{i,t}$ denotes the codeword index for the codebook obtained by quantizing the local tangent space at $\bP_{i,t}$.
@@
 \label{section3}
-\subsection{Reservoir Forward Pass}
+% \subsection{Vectorizing matrices in the Stiefel Manifold}
 % \label{vectorize}
@@
 Then, both the receiver and transmitter execute the backward pass (shaded in blue) to optimize $\mathcal{O}_{i,t}$ \eqref{oit}, to ensure identical evolution of both the reservoirs}
-\caption{RC Framework Overview: Forward Prediction (Green): Both TX and RX utilize identical RCs and quantized precoder estimate at $t-1$ (i.e.
-$\tilde{\bu}_{i,t-1}$, top left of fig.) to obtain $\bP_{i,t}$ via \eqref{pred_op}.
-The transmitter estimates the quantized precoder at $t$ (i.e.
-$\tilde{\bu}_{i,t}$, top right of fig.) using receiver feedback $\text{fb}_{i,t}$ via $q_P$ \eqref{eqn:cn2}.
-\\Feedback Estimation (Cyan): The Receiver estimates the ideal $\text{fb}_{i,t}$ using the exact precoders $\bU_{i,t}$ via \eqref{eqn:cn1}.
-The transmitter observes only the feedback $\text{fb}_{i,t}$\\ Backward Pass (Blue): $\bW^{\text{out}}_{i,t}$ is updated via \eqref{wout_upd} for optimizing $\mathcal{O}_{i,t}$.
+\caption{Framework Overview: \textbf{Forward Prediction (Green)}: Both TX and RX utilize identical reservoirs and quantized precoder at $t-1$ (i.e.
+$\tilde{\bu}_{i,t-1}$, top left of Fig.) to obtain $\bP_{i,t}$ via \eqref{pred_op}.
+The transmitter estimates the precoder at $t$ (i.e.
+$\tilde{\bu}_{i,t}$, top right of Fig.) using receiver feedback $\text{fb}_{i,t}$ via $q_P$ \eqref{eqn:cn2}
+\textbf{Feedback Estimation (Cyan)}: RX estimates $\text{fb}_{i,t}$ using exact precoder $\bU_{i,t}$, and communicates this to the TX using $\mathcal{B}$ bit feedback, by utilizing \eqref{eqn:cn1}\\ 
+\textbf{Backward Pass (Blue)}: $\bW^{\text{out}}_{i,t}$ is updated via \eqref{wout_upd} for optimizing $\mathcal{O}_{i,t}$.
 This is done at both TX and RX to ensure identical evolution of the reservoirs}
 \label{res_overview}
-\vspace{-5pt}
-\end{figure*}
+\end{figure}
 % \begin{equation}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Reservoir Training Procedure, the backward pass}
-\label{train}
-\noindent Having described technical details of $f_P,q_P$, we now describe the training process for the reservoir, which couples $f_P$ with $q_P$.
-Recall that, to obtain $\tilde{\bU}_{i,t}$ from $\tilde{\bU}_{i,t-1}$, we have,
-\begin{equation}
-\tilde{\bU}_{i,t}=q_P(\bP_{i,t},\text{fb}_{i,t})=q_P(f_P(\tilde{\bU}_{i,t-1}),\text{fb}_{i,t})
-\label{fpqp}
-\end{equation}
+% \subsection{Reservoir Training Procedure, the backward pass}
+% \label{train}
+\noindent Having described the technicalities of $f_P,q_P$, we now describe the training process for the reservoir, which couples $f_P$ with $q_P$.
 The key idea for reservoir training is that, as the predicted matrix $\bP_{i,t}$ (the coarse estimate) gets closer to $\tilde{\bU}_{i,t}$ (the refined estimate), the receiver has to quantize even smaller subspaces, and can thus provide a more refined estimate from the feedback $\text{fb}_{i,t}$.
@@
 To conclude this section, we summarize and highlight the novel aspects of the proposed framework.
-The first key advantage of the proposed approach over the past work \cite{Gupt1905:Predictive,6891198,6545375} is that here the prediction function, $f_P$ is coupled with the quantization function, $q_P$.
+The key advantage of the proposed approach over the past work \cite{Gupt1905:Predictive,6891198,6545375} is that here the prediction function, $f_P$ is coupled with the quantization function, $q_P$.
 Past work for predictive quantization has largely kept $f_P$ and $q_P$ uncoupled in the sense that, the obtained precoder is just composite function of $f_P$ and $q_P$, applied to the previous $p$ precoder estimates i.e.
@@
 
-\subsection{Simulation setting considered}
+\subsection{Simulation setting}
 \label{setting}
@@
 % The forward prediction function $f_P$ of the proposed framework, has $p$ (Section \ref{section2}) to be $1$ \eqref{fpqp}, whereas the backward pass $p$ for time instant $t$ is $t$ (Observe the framing of $\mathcal{O}_{i,t}$).
-We keep $p=4$ for the $f_P$ presented in \cite{6891198}.
 The quantization function $q_P$ is kept to be same, as described in \cite{6545375,6891198,Gupt1905:Predictive} for both the approaches.
-Although in both our work and \cite{6891198}, only temporal correlations are exploited, we compare the simulation results for the complete MIMO-OFDM setting (visually illustrated in Fig.
-2) with $N=64$ subcarriers.
-Channels are fed back for $8$ evenly spaced subcarriers indexed from 0, viz.
+
+To evaluate the complete MIMO-OFDM setting, predictive quantization algorithms should be considered in conjunction with interpolation algorithms to estimate the precoders at non fed-back points.
+We perform simulation for the complete MIMO-OFDM setting (visually illustrated in Fig.
+2) with $N=64$ subcarriers, and receiver feeding back quantized precoder information for $8$ subcarriers, and transmitter utilizing Caley interpolation to estimate the precoder at other subcarriers.
+The transmitter obtains feed back for $8$ evenly spaced subcarriers indexed from 0, viz.
 $\{0,9,\ldots,63\}$ ($\{9k, k \in \{0,1,\ldots,7\}\}$).
-Hence, the transmitter obtains only $\text{fb}_{\{9k\},t}$.
-For non fed back subcarriers $i\neq 9k$, $9n < i < 9(n+1)$, the Cayley method \cite{Gupt1905:Predictive} is used to interpolate $\tilde{\bU}_{i,t}$, from available estimates, $\tilde{\bU}_{9n,t}$ and $\tilde{\bU}_{9(n+1), t}$
+For non fed back subcarriers $i\neq 9k$, the Cayley method \cite{Gupt1905:Predictive} is used to interpolate $\tilde{\bU}_{i,t}$, from available estimates, $\tilde{\bU}_{9n,t}$, $\tilde{\bU}_{9(n+1), t}$
+
 \begin{equation}
@@
 \end{equation}
-For a detailed treatment on $\text{Exp}, \text{Exp}^{-1}$, refer \cite{DBLP:journals/corr/abs-1708-00045}.
+For a detailed treatment on $\text{Exp}, \text{Exp}^{-1}$, refer \cite{Gupt1905:Predictive,DBLP:journals/corr/abs-1708-00045}.
 
-A 6 bit codebook generated using the Lloyd codebook algorithm for the Stiefel Manifold presented in \cite{6678348} is used for initial feedback ($\tilde{\bU}_{\{9k\},0}$) and differential quantization (i.e.
+A $6$ bit codebook generated using the Lloyd codebook algorithm for the Stiefel Manifold presented in \cite{6678348} is used for initial feedback ($\tilde{\bU}_{\{9k\},0}$) and differential quantization (i.e.
 $\bP_{i,t}=\tilde{\bU}_{i,t-1}$) is used for 10 time instances to provide the initial training data for the reservoir and to overcome the initial transient response of the reservoir (also discussed in \cite{mosleh2017brain}).
-A 5 bit base codebook is used for the quantization function $q_P$ and is generated according to the method presented in \cite{Gupt1905:Predictive}.
+A $6$ bit tangent codebook is used for the quantization function $q_P$ and is generated according to the method similar to the one presented in \cite{Gupt1905:Predictive}.
 Hence, both initialization and subsequent feedback, $\text{fb}_{i,t}$ can be encoded using 6 bits (i.e. $\mathcal{B}=6$ Section \ref{section2}).
@@
 
-For predicting channels at each of the $8$ fed-back subcarriers, we consider $8$ separate reservoirs, each of them evolved separately, with $i\in\{9k, k \in \{0,1,\ldots,7\}\}$ in both the forward pass prediction and quantization ($f_P,q_P$) \eqref{fpqp} and backward pass to update $\bW_{i,t}^{\text{out}}$ \eqref{backpass}.
+For predicting precoders at each of the $8$ fed-back subcarriers, we consider $8$ separate reservoirs, each of them evolved separately, with $i\in\{9k, k \in \{0,1,\ldots,7\}\}$.
 Unlike \cite{Gupt1905:Predictive}, we do not exploit frequency correlations for predictive quantization, and the $8$ reservoirs for prediction of $8$ fed-back subcarriers are kept independent of each other.
-All these 8 reservoirs are initialized with $\bA_{i\in\{9k\}}$ being an Erdos-Reny\"i graph, with probability of edge connections being $0.2$, $\lambda=2$, $\bW^{\text{out/in}}_{i\in\{9k\},0}$ initialized randomly, $D_{\text{in}}=D_{\text{out}}=14$ (vectorized representation of $4\times2$ semi-unitary matrix, Section III) and $D_{\text{resv}}=60$.
+These 8 reservoirs are initialized with $\bA_{i\in\{9k\}}$ being Erdos-Reny\"i graph, with probability of edge connections being $0.2$, $\lambda=2$, $\bW^{\text{out/in}}_{i\in\{9k\},0}$ is initialized randomly, $D_{\text{in}}=D_{\text{out}}=14$ (vectorized rep.
+of $4\times2$ semi-unitary matrix) and $D_{\text{resv}}=60$.
 % All these 8 reservoirs are initialized with $\bA_{i\in\{9k\}}$ being an Erdos-Reny\"i graph, with
+
 \begin{figure}
@@
 \includegraphics[width=0.5\textwidth]{images/table.pdf}
-\caption{The transmitter obtains feedback for $\{9k, k \in \{0,1,\ldots,7\}$ subcarriers, and uses $\tilde{\bU}_{i,t-1}$, along with $f_P,q_P$ \eqref{fpqp} to obtain $\tilde{\bU}_{i,t}$, illustrated in the figure via cyan arrows.
-For each time instant, the transmitter uses the Cayley method  \eqref{eqn:cayley_i1_i2} to interpolate $\tilde{\bU}_{i,t}$ at $i\neq\{9k\}$ non fed back subcarriers (green arrows)}
+\caption{TX obtains feedback for $\{9k, k \in \{0,1,\ldots,7\}$ subcarriers, and uses $\tilde{\bU}_{i,t-1}$ to obtain $\tilde{\bU}_{i,t}$ using \eqref{pred_op} (cyan).
+For each time instant, TX uses Cayley method  \eqref{eqn:cayley_i1_i2} to interpolate $\tilde{\bU}_{i,t}$ at $i\neq\{9k\}$ non fed back subcarriers (green)}
 \label{table}
@@
 % To mitigate errors in prediction upon the presence of randomly appearing drastic events in wireless channels, such as sudden interferences and dynamic environments, only 100 channel evolutions are considered for the simulations, and the algorithm is re-starte.
-\noindent To ensure that the simulation results hold in general for the chosen IEEE Pedestrian A channel profile, we perform averaging over 10 independent channel realizations.
-Therefore, the quantization error, BER and achievable rate results are averaged over 1000 channel instances, with 100 channel evolutions of 10 independent channel realizations.
+\noindent To ensure that the simulation results hold in general for the chosen IEEE Pedestrian A channel profile, we perform averaging over 100 independent channel realizations, each realization further evolved over 100 time instances as per the chosen doppler.
+Therefore, the quantization error, BER and achievable rate results are averaged over 10000 channel instances.
+From Fig.
+\ref{qtiz_err} it is evident that the RC framework is able to reduce the quantization error below what was obtained from the existing temporal correlations based predictive quantizer in \cite{6891198}.
 \begin{figure}
 \centering
-\includegraphics[width=0.4\textwidth]{images/qtizErr.pdf}
-\caption{Quantization error in terms of chordal distance to the actual precoder $\bU_{\{9k\},t}$ observed at the receiver, from the quantized estimate $\tilde{\bU}_{\{9k\},t}$ averaged over $\{9k\}$ fed back subcarriers $\Big($ viz.
-$\frac{\Sigma_{i \in 9k}d_S(\tilde{\bU}_{i,t}, \bU_{i,t})}{8}$ $\Big)$ and 10 independent channel realizations (normalized Doppler $f_DT_s=10^{-4}$).}
+\includegraphics[width=0.35\textwidth]{images/qtizErr.pdf}
+\caption{Quantization error in terms of chordal distance to the actual precoder $\bU_{\{9k\},t}$ observed at the receiver, from the quantized estimate $\tilde{\bU}_{\{9k\},t}$}
 \label{qtiz_err}
-\vspace{-10pt}
 \end{figure}
 
-From Fig.
-\ref{qtiz_err} it is evident that the proposed framework is able to reduce the quantization error below what was obtained from the existing temporal correlations based predictive quantizer in \cite{6891198}.
-In addition, the quantization error plot is much smoother as well, which can be explained from the fact that the RC approach optimizes $\mathcal{O}_{i,t}$, that captures the long term dynamics of the channel and hence, does not face jittery variations.
-We simulate (uncoded QPSK) BER performance for all the 64 subcarriers' precoders obtained after interpolation ($\tilde{\bU}_{i\neq\{9k\},t}$) and quantization ($\tilde{\bU}_{\{9k\},t}$).
+Observe from Fig.
+\ref{BER} that RC framework improves the BER performance substantially in the high SNR region.
+In the low SNR region, past work \cite{6891198} comes close to the lower bound curve (perfect estimates of 8 $\bU_{\{9k\},t}$ available at the transmitter), and hence, RC framework is not able to further improve the performance.
+However, for the high SNR region, there is considerable gap between the lower bound curve and BER curve by past work, and the RC framework BER curve lies in between the two, with improvements in $\frac{\text{E}_\text{b}}{\text{N}_0}$ greater than 5 dB at BERs lower than $\sim 10^{-6}$.
+% We simulate (uncoded QPSK) BER performance for all the 64 subcarriers' precoders obtained after interpolation ($\tilde{\bU}_{i\neq\{9k\},t}$) and quantization ($\tilde{\bU}_{\{9k\},t}$).
 Observe from Fig.
 \ref{BER} that RC framework is able to achieve substantial improvements in $\text{E}_\text{b}\text{N}_0$ levels at $\text{BER}\leq 10^{-4}$.
-Particularly, for $\text{BER}=10^{-5}$ we observe around $4$ dB improvement.
-We hypothesize that the key reason for the improved performance for both quantization error and BER in the RC approach, is the fact that $f_P,q_P$ are coupled via the backward pass framework (explained towards the end of Section III).
+Particularly, for $\text{BER}=10^{-5}$ we observe around $5$ dB improvement.
+We hypothesize that the key reason for the improved performance for both quantization error and BER in the RC approach, is the fact that $f_P,q_P$ are coupled via the backward pass framework (explained towards the end of Section 2).
 % Also, observe from Fig.
-\ref{BER} that the proposed framework BER curve (green) comes very close to the ideal $8$ feedback curve (red).
+\ref{BER} that the proposed framework BER curve (yellow) comes very close to the ideal $8$ feedback curve (green).
 This can be explained due to the fact that the semi-unitary precoder basically rotates the data vector via its matrix transformation.
@@
 Hence, we match the ideal curve for high BER region, and for low BER region, as the margin of error reduces, the curves diverge.
-
-\noindent For simulating the achievable rate, we quantize the sigma values ($\Sigma_{i,t}$ from SVD of $\bH_{i,t}$) using a 2 bit vector quantizer ($k$-means), and feed them back to the transmitter for fed back subcarriers ($\{9k, k \in \{0,1,\ldots,7\}\}$).
-For the non-fed back subcarriers, they are interpolated via a simple convex combination interpolation method as in \cite{Gupt1905:Predictive}.
+For simulating the achievable rate, we quantize the sigma values ($\Sigma_{i,t}$ from SVD of $\bH_{i,t}$) using a 2 bit $k$-means vector quantizer, and feed them back to the transmitter for fed back subcarriers.
+For non-fed back subcarriers, they are interpolated via a simple convex combination interpolation method as in \cite{Gupt1905:Predictive}.
 Observe from Fig.
@@
 Since the temporal variations for $f_DT_s=10^{-2}, 10^{-1}$ are higher, the RC framework has to learn a faster-varying function, and hence the degradation in performance.
-However, it still matches the performance of the predictive quantizer in \cite{6891198} for $f_DT_s=10^{-2}$ and performs slightly better for $f_DT_s=10^{-1}$.
+% However, it still matches the performance of the predictive quantizer in \cite{6891198} for $f_DT_s=10^{-2}$ and performs slightly better for $f_DT_s=10^{-1}$.
 \vspace{-3pt}
@@
 \centering
-\includegraphics[width=0.43\textwidth]{images/BER_res.pdf}
+\includegraphics[width=0.35\textwidth]{images/BER_res.pdf}
 \vspace{-5pt}
-\caption{BER results: Here, green curve is the most ideal case considering exact $\bU_{i,t}$ for all 64 subcarriers, at each time instant are available at the transmitter.
-The \{yellow/blue\} curves corresponds to the case in which \{$\tilde{\bU}_{9k,t}$ from reservoir method/$\tilde{\bU}_{9k,t}$ from \cite{6891198}\} are available for each time instant, and non fed back precoders are interpolated via Cayley method.
-Observe that the proposed framework BER curve provides significant improvement in $\text{E}_\text{b}\text{N}_0$ levels over \cite{6891198} (normalized Doppler $f_DT_s=10^{-4}$).}
+\caption{BER results: Here, red curve is the most ideal case considering exact $\bU_{i,t}$ for all 64 subcarriers, at each time instant are available at the transmitter.
+The \{green/yellow/blue\} curves corresponds to the case in which \{$\bU_{9k,t}$/$\tilde{\bU}_{9k,t}$ from reservoir method/$\tilde{\bU}_{9k,t}$ from \cite{6891198}\} is available for each time instant, and non fed back precoders are interpolated via Cayley method.
+Observe that the proposed framework BER curve provides significant improvement in $\text{E}_\text{b}\text{N}_0$ levels over \cite{6891198}}
 \vspace{5pt}
@@
 \centering
-\includegraphics[width=0.43\textwidth]{images/hopRate2.pdf}
+\includegraphics[width=0.35\textwidth]{images/hopRate.pdf}
 \vspace{-5pt}
-\caption{The results are presented as a percentage of the ideal achievable rate obtained when the transmitter has the accurate (unquantized) and non-interpolated estimates of $\bU_{i,t}$ for each subcarrier and each time instant.}
+\caption{Achievable Rate results: Here, the results are presented as a percentage of the ideal rate obtained when the transmitter has full CSI, viz.
+the accurate(unquantized) $\bU_{i,t}$ for each subcarrier at each time instant.
+For both reservoir method, and Stiefel manifold method \cite{6891198}, 8 precoders are fed back similar to the setting for BER results (Fig.
+\ref{BER})}
 \label{achievrate}

### 2020-01-02 paper/main.tex
Minor fixes

@@
   channel capacity. However, the receiver should quantize and feed
-  back the precoder using very few bits of overhead. The precoder's
+  back the precoder using very few bits of overhead. The precoders'
   underlying manifold structure aids this feedback and allows the use
@@
 % Elaborate on each point (what people have done before) lecunnas
-Past work has used two inherent properties of the optimal precoders to enable effective quantization with just a few bits.
-First, the optimum precoders are not actually $2N_TN_R$ dimensional entities, but have an underlying manifold structure that allows to work with effective lower dimensions, when performing operations over the manifold directly \cite{pitaval2013codebooks}.
+Past work has used two inherent properties of optimal precoders to enable effective quantization with just a few bits.
+First, the optimum precoders are not actually $2N_TN_R$ dimensional entities, but have an underlying manifold structure that has lower effective number of dimensions when performing operations over the manifold directly \cite{pitaval2013codebooks}.
 Second, these precoders are correlated in both time and frequency \cite{Gupt1905:Predictive}.
-Utilizing the available correlations permit the use of predictive quantization algorithms, which enable improvement of the quantization error with time.
+Utilizing the available correlations permits the use of predictive quantization algorithms, which enable improvement of the quantization error with time.
 This improvement is obtained because of feeding back just the small extra information needed on top of the past fed back precoders, as compared to the new precoder information in the entirety.
@@
 
-Combining the two inherent properties (viz.
-manifold structure and correlations) to frame manifold based predictive quantization algorithms, require a generalization of various well known linear algorithms for prediction, quantization and interpolation, to the underlying non-linear manifold structure.
-This is typically done by exploiting the differential geometry of the manifold and relevant past work in this direction has been presented in \cite{Gupt1905:Predictive,6891198,6545375,5671092,Li2016,krishnamachari2013geometry,chang2011adaptive}.
-Manifold based approaches for predictive quantization have provided significant performance benefits, given that they work with the effective lower dimensions while framing the manifold operations to predict and quantize.
+Combining these two inherent properties (viz.
+manifold structure and correlations) to frame manifold based predictive quantization algorithms requires a generalization of various well known linear algorithms for prediction, quantization and interpolation, to the underlying non-linear manifold structure.
+This is typically done by exploiting the differential geometry of the manifold, and relevant past work in this direction has been presented in \cite{Gupt1905:Predictive,6891198,6545375,5671092,Li2016,krishnamachari2013geometry,chang2011adaptive}.
+Manifold based approaches for predictive quantization have provided significant performance benefits, given that they work with the lower number of effective dimensions while framing the manifold operations to predict and quantize.
 However, these approaches are non-trivial, since they require specific operations over the non-linear manifold differential geometry.
@@
 % To mitigate errors in prediction upon the presence of randomly appearing drastic events in wireless channels, such as sudden interferences and dynamic environments, only 100 channel evolutions are considered for the simulations, and the algorithm is re-starte.
-\noindent To ensure that the simulation results hold in general for the chosen IEEE Pedestrian A channel profile, we perform averaging over 100 independent channel realizations, each realization further evolved over 100 time instances as per the chosen doppler.
+\noindent To ensure that the simulation results hold in general for the chosen IEEE Pedestrian A channel profile, we perform averaging over 100 independent channel realizations, each realization further evolved over 100 time instances as per the chosen Doppler.
 Therefore, the quantization error, BER and achievable rate results are averaged over 10000 channel instances.
@@
 Simulations reveal significant improvement in quantization error, BER, and achievable rate.
-The novelty that enables these improvements is the training method for the reservoir framework, which refines the predicted coarse estimates as the reservoir evolves.
-Our results have been obtained by exploiting only temporal correlations for predictive quantization, and can potentially improve if frequency correlations are also exploited simultaneously..
+The innovation that enables these improvements is the novel training method for the reservoir framework, which refines the predicted coarse estimates as the reservoir evolves.
+Our results have been obtained by exploiting only temporal correlations for predictive quantization, and can potentially improve if frequency correlations are also exploited simultaneously.
 Future work would focus on better reservoir frameworks, and a detailed analysis of impact on performance caused by choice of different reservoir parameters like $\bA,\text{tanh}(\cdot),$ and $D_{\text{resv}}$.

### 2020-01-04 paper/main.tex
Spelling fix
Adding minor changes (removing not necesarry citations etc)

@@
 manifold structure and correlations) to frame manifold based predictive quantization algorithms requires a generalization of various well known linear algorithms for prediction, quantization and interpolation, to the underlying non-linear manifold structure.
-This is typically done by exploiting the differential geometry of the manifold, and relevant past work in this direction has been presented in \cite{Gupt1905:Predictive,6891198,6545375,5671092,Li2016,krishnamachari2013geometry,chang2011adaptive}.
+This is typically done by exploiting the differential geometry of the manifold, and relevant past work in this direction has been presented in \cite{Gupt1905:Predictive,6891198,6545375,Li2016,chang2011adaptive}.
 Manifold based approaches for predictive quantization have provided significant performance benefits, given that they work with the lower number of effective dimensions while framing the manifold operations to predict and quantize.
@@
 where $\bA_i$ is the adjacency matrix that captures the reservoir dynamics, and $\text{tanh}$ is applied element wise.
-Typical choices for $\bA_i$ have been Erdos-Renyi graphs with an upper bounded maximum eigenvalue \cite{mosleh2017brain,pathak2017using}.
+Typical choices for $\bA_i$ have been Erdos-Reny\"i graphs with an upper bounded maximum eigenvalue \cite{mosleh2017brain,pathak2017using}.
 The output of the reservoir is $\bp_{i,t}$ (vectorized representation of $\bP_{i,t}$), which denotes the predicted precoder at $i$-th subcarrier, $t$-th time instant.
@@
 The quantized precoders are obtained by traversing along the `codeword tangents' from the predicted precoder $\bP_{i,t}$, using a retraction map (denoted by $\text{retract}(\cdot)$).
-The receiver conveys the feedback $\text{fb}_{i,t}$ to the transmitter, which minimizes the chordal distance metric ($d_s(\bX,\bY)$ for $\bX,\bY \in \text{St}(N_T,N_R)$ detailed in \cite{Gupt1905:Predictive,6891198}) between the quantized precoders and the ideal precoder $\bU_{i,t}$ estimated from SVD of $\bH_{i,t}$ \eqref{eqn:cn1}
+The receiver conveys the feedback $\text{fb}_{i,t}$ to the transmitter, which minimizes the chordal distance metric ($d_s(\bX,\bY)$ for $\bX,\bY \in \text{St}(N_T,N_R)$ \cite{Gupt1905:Predictive,6891198}) between the quantized precoders and the ideal precoder $\bU_{i,t}$ estimated from SVD of $\bH_{i,t}$ \eqref{eqn:cn1}
  \begin{equation}
@@
 We perform simulation for the complete MIMO-OFDM setting (visually illustrated in Fig.
-2) with $N=64$ subcarriers, and receiver feeding back quantized precoder information for $8$ subcarriers, and transmitter utilizing Caley interpolation to estimate the precoder at other subcarriers.
+2) with $N=64$ subcarriers.
 The transmitter obtains feed back for $8$ evenly spaced subcarriers indexed from 0, viz.

### 2020-01-04 paper/cover_letter.tex
Adding cover letter

\documentclass{letter}
\usepackage[left=1in,top=0.15in,twoside=false]{geometry}
\usepackage{color,hyperref}
\definecolor{darkblue}{rgb}{0.0,0.0,0.7}
\hypersetup{colorlinks,breaklinks,
            linkcolor=darkblue,urlcolor=darkblue,
            anchorcolor=darkblue,citecolor=darkblue}

% \signature{Agrim Gupta}
\address{From \\
Agrim Gupta\\
Department of Electrical  Engineering\\
Indian Institute of Technology Bombay, Mumbai\\
India\\
E-mail: agrim9gupta@gmail.com
\date{\today}
}

\begin{document}
\begin{letter}{To\\
Prof. M. Di Renzo\\
Editor-in-Chief\\
IEEE Communication Letters}
\vspace{0.5in}

\opening{Dear Prof. M. Di Renzo,}

Subject: \textbf{Submission of manuscript title ``Reservoir Computing Framework for Predictive Quantization of MIMO-OFDM SVD Precoders'' for potential publication in
  IEEE Communication Letters.}

Please find enclosed our manuscript titled ``Reservoir Computing Framework for Predictive Quantization of MIMO-OFDM SVD Precoders'' for review and potential
  publication in IEEE Communication Letters. The co-authors of this manuscripts are
\begin{enumerate}
\item  Pranav Sankhe

Department of Electrical  Engineering

Indian Institute of Technology Bombay, Mumbai

India

E-mail: pranavsankhe40@gmail.com

\item Prof. Kumar Appaiah

Department of Electrical  Engineering

Indian Institute of Technology Bombay, Mumbai

India

E-mail: akumar@ee.iitb.ac.in

\item Prof. Manoj Gopalkrishnan

Department of Electrical  Engineering

Indian Institute of Technology Bombay, Mumbai

India

E-mail: manojg@ee.iitb.ac.in

\end{enumerate}

Should you require additional details, please do e-mail me.

Thank you.
\vspace{0.3in}

Sincerely,

Agrim Gupta

\end{letter}
\end{document}

### 2020-01-04 paper/main.tex
Adding cover letter

@@
 
-\title{\vspace{-10pt}Predictive Quantization for MIMO-OFDM SVD Precoders using Reservoir Computing Framework \vspace{-10pt}}
+\title{\vspace{-10pt}Reservoir Computing Framework for Predictive Quantization of MIMO-OFDM SVD Precoders  \vspace{-10pt}}
 
@@
 
- \author{\authorblockN{Agrim Gupta, Pranav Sankhe, Kumar Appaiah, Manoj Gopalkrishnan}
+ \author{\authorblockN{Author 1, Author 2, Author 3, Author 4}
  \
- \authorblockA{Department of Electrical Engineering, Indian Institute of Technology Bombay\\
- \{agrim,pranavs,akumar,manojg\}@ee.iitb.ac.in \vspace{-18pt}}
+ \authorblockA{Institute 1, Institute 2\vspace{-18pt}}
 % \thanks{Parts of this work was supported by the Bharti Centre for Communication in
